### 2015-02-28 model-notes.tex
add model-notes document with notes from Feb. 12

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}

\setcounter{secnumdepth}{-1}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\ga}{\gamma}

\begin{document}

\title{\vskip-0.6in \Large Political Uncertainty}
\author{Kristy Buzard}
\date{\vskip-.1in \today}
\maketitle

\un{Skype with Sebastian, Feb. 12, 2015} \\
We agreed to focus efforts for now on finding a base model to facilitate empirical identification. Our candidates:
		\begin{enumerate}
			\item Groseclose $\&$ Snyder (1996)
				\begin{itemize}
					\item Perhaps add, as in Sebastian's book, that legislators are constrained by voters?
				\end{itemize}
			\item Dal Bo, Bribing Voters
				\begin{itemize}
					\item Adds uncertainty to Groseclose/Snyder. What kind?
				\end{itemize}
			\item Justin Fox, Political Analysis (2011)
			\item A variant of Grossman and Helpman I've been working on
		\end{enumerate}

\vskip.3in
Questions
\begin{enumerate}
	\item What kinds of results do we want to produce?
\end{enumerate}

\end{document}

### 2015-02-28 model-notes.tex
add notes on Fox and Rothenberg to model-notes

@@
 				\end{itemize}
-			\item Justin Fox, Political Analysis (2011)
+			\item Justin Fox and Larry Rothenberg, ``Influence without Bribes: A Noncontracting Model of Campaign
+Giving and Policymaking,'' Political Analysis (2011)
+				\begin{itemize}
+					\item This is a model where no contracting is possible [someday I'd love to write a model that isn't perfect contracting or no contracting---but that shows how this quasi-enforcement that we end up with comes about, but I think we're better off with a contracting model for now]
+					\item Uncertainty is about the politician's policy preferences; there are two periods of policy choice with an election in between, and the interest group uses the first policy choice to learn about preferences before making campaign donation (PBE is soln.
+concept)
+					\item Politician's types are private info; drawn from independent density functions $f_i$ (incumbent) and $f_c$ (challenger)
+				  \item Election winner chooses preferred policy in second period
+					\item There is one interest group (they say results extend to more), and it never donates to more than one of the two politicians
+					\item There are only two politicians with unitary decision making depending on who's in office; this contrasts with our legislative data, so I think it would be hard to adapt to our context
+				\end{itemize}
 			\item A variant of Grossman and Helpman I've been working on

### 2015-03-08 model-notes.tex
add notes on Dal Bo (2007)

@@
 					\item Adds uncertainty to Groseclose/Snyder. What kind?
+					\item Pivotal bribes allow for costless influence
+						\begin{itemize}
+							\item Not clear how this could be reconciled to our data since there are almost always supermajorities; not clear how lobbies can implement pivotal bribecs
+						\end{itemize}
+					\item Assume commitment even though it's a one-shot game (footnote 11)
+					\item A more demanding majority rule raises the price of capture if offers are restricted, e.g. can't be fully contingent, such as on pivotality
+					\item Section on vote-related costs: leg. loses $\eta > 0$ if vote yet on bad project in addition to $\theta > 0$ if bad project passes
+					\item Extension: probability $p$ that each member is corruptible (I think this is the uncertainty that Sebastian was talking about).
+Then there is updating on moral type of all members if bad project passes and voting is secret
+						\begin{itemize}
+							\item For our purposes: I don't think we care that much ``how corruptible'' legislators are, not in a binary sense.
+Maybe, if we're getting really fancy, we care about how persuadable they are in a continuous sense, but I don't think we want to deal with the machinery of updating in a second stage of voting about whether to keep legislators in office or not
+						\end{itemize}
+					\item Dal Bo shows that political parties can facilitate cooperation among legislators to overcome prisoners dilemma/costless capture or at least set optimal price for capture
 				\end{itemize}

### 2015-03-08 model-notes.tex
summarize GS96 and add initial thoughts for extension with uncertainty

@@
 					\item Perhaps add, as in Sebastian's book, that legislators are constrained by voters?
+					\item I think this is the most promising of the three (GS1996, Dal Bo, Fox and Rothenberg), so have devoted a separate section to it below
 				\end{itemize}
@@
 			\item A variant of Grossman and Helpman I've been working on
+				\begin{itemize}
+					\item It's based on the CJR model, so aims to fit the specification underlying the data work
+				\end{itemize}
 		\end{enumerate}
@@
 
+\newpage
+Groseclose and Snyder (1996), ``Buying Supermajorities,'' APSR
+\begin{itemize}
+	\item For each legislator $i$, $v(i) = u_i(x) - u_i(s)$, measured in money; call this the reservation price of $i$
+		\begin{itemize}
+			\item WLOG, label legislators so that $v(i)$ is a non-increasing function 
+			\item Note legislators only have preferences over how they vote, not over which alternative wins
+		\end{itemize}
+	\item There are two vote buyers; each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP
+		\begin{itemize}
+			\item $A$ prefers $x$; $W_A$ is $A$'s willingness to pay (WTP) for $x$ measured in money
+			\item $B$ prefers $s$; $W_B$ is $B$'s WTP for $s$
+		\end{itemize}
+	\item Bribe offer functions: $a(i)$ and $b(i)$ are $A$ and $B$'s offers to $i$. Legislators take these bribe offers as given and then vote for the alternative that maximizes their payoff
+	\item A moves first; $a(i)$ perfectly observable to $B$ when he moves.
+	\item Goal: characterize SPNE in pure strategies
+		\begin{itemize}
+			\item Assume unbribed legislators who are indifferent vote for $s$; all bribed legislators who are indifferent vote for whoever bribed them last
+		\end{itemize}
+	\item Assume continuum of legislators on $\left[-\frac{1}{2},\frac{1}{2}\right]$
+	\item Assume $W_A$ large enough that $x$ wins in equilibrium (no uncertainty case)
+	\item $m + \frac{1}{2}$ is the fraction of legislators who vote for $x$, the new policy (as opposed to the status quo, $s$)
+	\item Prop 1: three types of equilibria in which $x$ wins; depend on size of $W_B$
+	\item Prop 2: $m^*$ (the optimal coalition size) is unique, and provides three cases parameterizing its size in terms of $W_B$, $v(-\frac{1}{2})$ and $v(m^*)$
+	\item Prop 3/4: special case where $v(z) = \alpha - \beta v$
+\end{itemize}
+
+\vskip.2in
+\begin{itemize}
+	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
+		\begin{itemize}
+			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty
+		\end{itemize}
+	\item I'm pretty sure all this predicts that $B$ should never pay anything.
+		\begin{itemize}
+			\item Uncertainty should reverse this, right?
+			\item What is uncertainty? I think just make $v(z)$ stochastic
+		\end{itemize}
+\end{itemize}
+
 \end{document}

### 2015-03-09 GS-extension.tex
move Groseclose Snyder model description into new file GS-extension.tex

--- 2015-03-08 model-notes.tex
@@
 
-\un{Skype with Sebastian, Feb. 12, 2015} \\
-We agreed to focus efforts for now on finding a base model to facilitate empirical identification. Our candidates:
-		\begin{enumerate}
-			\item Groseclose $\&$ Snyder (1996)
-				\begin{itemize}
-					\item Perhaps add, as in Sebastian's book, that legislators are constrained by voters?
-					\item I think this is the most promising of the three (GS1996, Dal Bo, Fox and Rothenberg), so have devoted a separate section to it below
-				\end{itemize}
-			\item Dal Bo, Bribing Voters
-				\begin{itemize}
-					\item Adds uncertainty to Groseclose/Snyder. What kind?
-					\item Pivotal bribes allow for costless influence
-						\begin{itemize}
-							\item Not clear how this could be reconciled to our data since there are almost always supermajorities; not clear how lobbies can implement pivotal bribecs
-						\end{itemize}
-					\item Assume commitment even though it's a one-shot game (footnote 11)
-					\item A more demanding majority rule raises the price of capture if offers are restricted, e.g. can't be fully contingent, such as on pivotality
-					\item Section on vote-related costs: leg. loses $\eta > 0$ if vote yet on bad project in addition to $\theta > 0$ if bad project passes
-					\item Extension: probability $p$ that each member is corruptible (I think this is the uncertainty that Sebastian was talking about).
-Then there is updating on moral type of all members if bad project passes and voting is secret
-						\begin{itemize}
-							\item For our purposes: I don't think we care that much ``how corruptible'' legislators are, not in a binary sense.
-Maybe, if we're getting really fancy, we care about how persuadable they are in a continuous sense, but I don't think we want to deal with the machinery of updating in a second stage of voting about whether to keep legislators in office or not
-						\end{itemize}
-					\item Dal Bo shows that political parties can facilitate cooperation among legislators to overcome prisoners dilemma/costless capture or at least set optimal price for capture
-				\end{itemize}
-			\item Justin Fox and Larry Rothenberg, ``Influence without Bribes: A Noncontracting Model of Campaign
-Giving and Policymaking,'' Political Analysis (2011)
-				\begin{itemize}
-					\item This is a model where no contracting is possible [someday I'd love to write a model that isn't perfect contracting or no contracting---but that shows how this quasi-enforcement that we end up with comes about, but I think we're better off with a contracting model for now]
-					\item Uncertainty is about the politician's policy preferences; there are two periods of policy choice with an election in between, and the interest group uses the first policy choice to learn about preferences before making campaign donation (PBE is soln.
-concept)
-					\item Politician's types are private info; drawn from independent density functions $f_i$ (incumbent) and $f_c$ (challenger)
-				  \item Election winner chooses preferred policy in second period
-					\item There is one interest group (they say results extend to more), and it never donates to more than one of the two politicians
-					\item There are only two politicians with unitary decision making depending on who's in office; this contrasts with our legislative data, so I think it would be hard to adapt to our context
-				\end{itemize}
-			\item A variant of Grossman and Helpman I've been working on
-				\begin{itemize}
-					\item It's based on the CJR model, so aims to fit the specification underlying the data work
-				\end{itemize}
-		\end{enumerate}
-
-\vskip.3in
-Questions
-\begin{enumerate}
-	\item What kinds of results do we want to produce?
-\end{enumerate}
-
-\newpage
-Groseclose and Snyder (1996), ``Buying Supermajorities,'' APSR
+On Feb. 12, Sebastian and I agreed to focus efforts on finding a base model to facilitate empirical identification. I am pursuing Groseclose $\&$ Snyder (1996), ``Buying Supermajorities,'' APSR
 \begin{itemize}

### 2015-03-09 GS-extension.tex
add first stab at model explication to GS-extension

@@
 \usepackage{cite}
-\usepackage{times, verbatim,bm,pifont}
+\usepackage{times, verbatim,bm,pifont,bbm}
 
@@
 \begin{itemize}
-	\item For each legislator $i$, $v(i) = u_i(x) - u_i(s)$, measured in money; call this the reservation price of $i$
+	\item For each legislator $i$, $v(i) = u_i(x) - u_i(s)$, measured in money; this is the reservation price of $i$
 		\begin{itemize}
+			\item $x$ is an alternative policy proposal; $s$ is the status quo
 			\item WLOG, label legislators so that $v(i)$ is a non-increasing function 
@@
 	\item Bribe offer functions: $a(i)$ and $b(i)$ are $A$ and $B$'s offers to $i$. Legislators take these bribe offers as given and then vote for the alternative that maximizes their payoff
-	\item A moves first; $a(i)$ perfectly observable to $B$ when he moves.
+	\item A moves first; $a(i)$ is perfectly observable to $B$ when he moves
 	\item Goal: characterize SPNE in pure strategies
@@
 	\item Assume $W_A$ large enough that $x$ wins in equilibrium (no uncertainty case)
-	\item $m + \frac{1}{2}$ is the fraction of legislators who vote for $x$, the new policy (as opposed to the status quo, $s$)
+	\item $m + \frac{1}{2}$ is fraction of legislators who vote for $x$ as opposed to the status quo, $s$
+	\item Results
+	\begin{itemize}
 		\item Prop 1: three types of equilibria in which $x$ wins; depend on size of $W_B$
@@
 	\end{itemize}
+\end{itemize}
 
-\vskip.2in
+\vskip.3in
+General thoughts on extension to uncertainty
 \begin{itemize}
@@
 		\begin{itemize}
-			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty
+			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
 		\end{itemize}
-	\item I'm pretty sure all this predicts that $B$ should never pay anything.
+	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
 		\begin{itemize}
 			\item Uncertainty should reverse this, right?
-			\item What is uncertainty? I think just make $v(z)$ stochastic
+			\item What is uncertainty? Make $v(z)$ stochastic is most natural
+				\begin{itemize}
+					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty:
+						\[
+						  v(z) = \alpha -\beta \cdot z + \ve_z
+						\]
+						we can decide later on the distributional assumptions for $\ve_z$, and whether / when we want to make the $\ve$ vary by legislator ($z$)
+				\end{itemize}
 		\end{itemize}
@@
 
+\vskip.3in
+Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
+\begin{enumerate}
+	\item Legislature
+		\begin{itemize}
+			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $\ve_z$, $a(z)$ and $b(z)$. Votes for $x$ if
+			  \[
+				  v(z) = \alpha -\beta \cdot z + \ve_z + a(z) + b(z) > 0
+				\]
+				(whether the inequality is weak or strict depends on tie-breaking rules set out in the paper)
+			\item Payoff for vote buyer A if $x$ wins is $U_A(x) - \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj$
+			\item Payoff for vote buyer A if $s$ wins is $U_A(s) - \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj$
+			\item I think the cleanest way to write the condition for whether $x$ wins is
+				\[
+				  \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[v(j) \geq 0 \right] dj \geq \frac{1}{2}
+				\]
+		\end{itemize}
+	\item Vote buyer B
+		\begin{itemize}
+			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
+			\item This has to be adapted to passing his preferred policy in expectation? Do we do something like they each have $\frac{1}{2}$ probability of winning? (as long as WTP constraint is satisfied)
+			\item Groseclose and Snyder formulation would suggest something like
+				\[
+				  \min_{b(z)} \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \hskip.2in \text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq U_B(s) - U_B(x)
+				\]
+				\[
+				\text{and however we write the ``while passing his preferred policy'' constraint}
+				\]
+
+			\begin{itemize}
+					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
+					\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
+					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
+					\item Maybe it's a much simpler maximize probability of winning net of bribes?
+				\end{itemize}
+		\end{itemize}	
+	\item Vote buyer A
+		\begin{itemize}
+			\item Whatever we decide for vote buyer B will be the same for vote buyer A
+		\end{itemize}
+\end{enumerate}
+
 \end{document}

### 2015-03-19 GS-extension.tex
add possible objective function for maximization of winning probability under uncertainty (line 137)
fixed typo in GS-extension
update GS-extension with FOC for vote buyer B under uncertainty

@@
 		\item Prop 2: $m^*$ (the optimal coalition size) is unique, and provides three cases parameterizing its size in terms of $W_B$, $v(-\frac{1}{2})$ and $v(m^*)$
-		\item Prop 3/4: special case where $v(z) = \alpha - \beta v$
+		\item Prop 3/4: special case where $v(z) = \alpha - \beta z$
 	\end{itemize}
@@
 		\begin{itemize}
-			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $\ve_z$, $a(z)$ and $b(z)$. Votes for $x$ if
+			\item Each legislator $z$ will decide whether to vote for $x$ or $s$ given $z$, $a(z)$ and $b(z)$. Votes for $x$ if
 			  \[
-				  v(z) = \alpha -\beta \cdot z + \ve_z + a(z) + b(z) > 0
+				  v(z) = \alpha -\beta \cdot z + a(z) + b(z) > 0
 				\]
 				(whether the inequality is weak or strict depends on tie-breaking rules set out in the paper)
+					\begin{itemize}
+						\item Let's start out by thinking of $z$ as being a random variable distributed $N(z,\sigma_z)$
+					\end{itemize}
 			\item Payoff for vote buyer A if $x$ wins is $U_A(x) - \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj$
@@
 			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
-			\item This has to be adapted to passing his preferred policy in expectation? Do we do something like they each have $\frac{1}{2}$ probability of winning? (as long as WTP constraint is satisfied)
+			\item This has to be adapted to our situation with uncertainty
+				\begin{itemize}
 					\item Groseclose and Snyder formulation would suggest something like
@@
 						\]
-
-			\begin{itemize}
 					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
@@
 					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
-					\item Maybe it's a much simpler maximize probability of winning net of bribes?
+				\end{itemize}
+			\item Let's start with the simple maximize expected value of winning (WTP times probability of winning) net of bribes:
+						\begin{multline}
+							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \geq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
+							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
+						\end{multline}
+				\begin{itemize}
+					\item Problem is that the indicator function will never equal 1 when $J \sim N(j,\sigma_j)$
+					\item So what's a reasonable objective function? 
+						\begin{itemize}
+							\item Maximizing the total probability mass where $v(j) \geq 0$?
+							  \begin{multline}
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \geq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
+									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
+								\end{multline}
+							\item Suppressing the constraint for now and using the fact that $J \sim N(j,\sigma_j)$, this can be re-written as
+								\begin{equation}
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \geq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
+								\end{equation}
+								or
+								\begin{equation}
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \geq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
+								\end{equation}
+								where $Z \sim N(0,1)$. \\
+							\item	So, this can be written as
+								\begin{equation}
+									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \cdot \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj
+								\end{equation}
+							\item If the realizations of $Z$ are i.i.d. and the bribes are independent across legislators, (I believe) this can be maximized pointwise.
+							\item The FOC for each $j$ is then
+								\begin{equation}
+								  W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
+								\end{equation}
+						\end{itemize}
 				\end{itemize}

### 2015-03-19 GS-extension.tex
fix inequalities for vote buyer B
add notes about constraint for vote buyer B; also notes from today's chat with Sebastian

@@
 						\begin{multline}
-							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \geq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
+							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
 							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
@@
 							  \begin{multline}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \geq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
 									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
@@
 								\begin{equation}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \geq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
 								\end{equation}
@@
 								\begin{equation}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \geq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
 								\end{equation}
@@
 							\item	So, this can be written as
-								\begin{equation}
-									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \cdot \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj
-								\end{equation}
-							\item If the realizations of $Z$ are i.i.d. and the bribes are independent across legislators, (I believe) this can be maximized pointwise.
+								\begin{multline}
+									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\
+									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
+								\end{multline}
+							\item If the realizations of $Z$ are i.i.d. and the bribes are independent across legislators, (I believe) this can be maximized pointwise--except for the constraint
 							\item The FOC for each $j$ is then
 								\begin{equation}
-								  W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
+								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
 								\end{equation}
+								as long as the constraint is satisfied.
+									\begin{itemize}
+										\item I don't know how decisions are made if the constraint binds---how the rationing happens
+										\item If the constraint is not binding, vote buyer B will pay every single legislator (we could put in some kind of fixed cost of dealing with each legislator to short circuit this outcome)
+										\item Perhaps there's something in equilibrium I'm not seeing yet that will reduce the number of legislators that are paid
+									\end{itemize}
 						\end{itemize}
@@
 
+\newpage
+Notes from 3/19 Skype chat (Kristy and Sebastian)
+\begin{itemize}
+	\item We can use the data we have to horse-race this model against other hypotheses about how lobbyists distribute bribes
+		\begin{itemize}
+			\item Allocate equally among legislators
+			\item Groseclose Snyder with full information: only one side pays
+			\item Our model with one dimension
+				\begin{itemize}
+					\item Could we use the econometric model to benchmark to one where uncertainty disappears? Or, as it does theoretically, does the model have to change completely?
+				\end{itemize}
+			\item Our model with multiple dimensions
+		\end{itemize}
+	\item We can think of this as looking for the effect of uncertainty on prices---we'd be pricing uncertainty relative to a model with uncertainty
+		\begin{itemize}
+			\item ``a metric in dollars of uncertainty''
+			\item this is a model of vote buying under uncertainty
+		\end{itemize}
+	\item Given how different the environment with uncertainty is, Kristy should explore both the sequential model that parrots GS96 and a simultaneous model that is more like GH94 (menu auction)
+	\item When mapping to the data, we're going to want to know from the model whether/when total contributions represent WTP.
+		\begin{itemize}
+			\item It clearly doesn't in the case of certainty. One side pays nothing; the other pays either as much as is necessary to shut down its opponent, or nothing at all the necessary amount exceeds WTP
+			\item May be able to show it doesn't matter, that the proportion of total expenditures is a sufficient statistic
+		\end{itemize}
+	\item Finish writing the model, and then see if we can use the estimates we already have to write a first, very rough draft
+\end{itemize}
+
 \end{document}

### 2015-03-21 GS-extension.tex
add notes on uncertainty from 3/16

@@
 				\begin{itemize}
-					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty:
+					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
 						\[
-						  v(z) = \alpha -\beta \cdot z + \ve_z
+						  v(z) = \alpha -\beta \cdot z
 						\]
-						we can decide later on the distributional assumptions for $\ve_z$, and whether / when we want to make the $\ve$ vary by legislator ($z$)
+						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$.
+This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z''
+							\begin{itemize}
+								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
+								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
+								\item Uncertainty comes from: log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for
+							\end{itemize}
 				\end{itemize}
@@
 \newpage
+Notes from 3/16 Skype chat (Kristy and Sebastian)
+\begin{itemize}
+	\item Seems like FOC for lobby will boil down to each one buying votes until marginal benefit = marginal cost
+	\item May want to use some simplified rule / heuristic for lobby's decision: perhaps they reorder the legislators by their $\pm 2$ std. dev. and make some decision based on that ordering who to lobby
+	\item Will some kind of rule that looks like RMSE come out of the math? Is it possible to get anything closed-form at all?
+\end{itemize}
+
+\vskip.3in
 Notes from 3/19 Skype chat (Kristy and Sebastian)

### 2015-03-23 GS-extension.tex
change to subtracting bribes from vote buyer B

@@
 								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
-								\item Uncertainty comes from: log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for
+								\item Uncertainty comes from: \textbf{log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for}
 							\end{itemize}
@@
 			  \[
-				  v(z) = \alpha -\beta \cdot z + a(z) + b(z) > 0
+				  v(z) = \alpha -\beta \cdot z + a(z) - b(z) > 0
 				\]
@@
 						\item Let's start out by thinking of $z$ as being a random variable distributed $N(z,\sigma_z)$
+						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
 					\end{itemize}
@@
 						\begin{multline}
-							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
+							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
 							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
@@
 							  \begin{multline}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) + b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
 									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
@@
 								\begin{equation}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) + b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) - b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
 								\end{equation}
@@
 								\begin{equation}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
+									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
 								\end{equation}
@@
 								\begin{multline}
-									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\
+									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\
 									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
@@
 								\begin{equation}
-								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) + b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
+								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
 								\end{equation}

### 2015-03-23 GS-extension.tex
add non-negativity constraint on b(j)

@@
 							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
-							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
+							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
 						\end{multline}
@@
 									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
-									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
+									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B  \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
 								\end{multline}
+									\begin{itemize}
+										\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
+										\item Some legislators who are past FOC point will not be lobbied
+									\end{itemize}
 							\item Suppressing the constraint for now and using the fact that $J \sim N(j,\sigma_j)$, this can be re-written as
@@
 									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\
-									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B
+									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B  \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
 								\end{multline}

### 2015-03-23 GS-extension.tex
prep to add FOC analysis

@@
 								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
+									\label{eq:foc}
 								\end{equation}
@@
 										\item I don't know how decisions are made if the constraint binds---how the rationing happens
-										\item If the constraint is not binding, vote buyer B will pay every single legislator (we could put in some kind of fixed cost of dealing with each legislator to short circuit this outcome)
-										\item Perhaps there's something in equilibrium I'm not seeing yet that will reduce the number of legislators that are paid
+										\item If the constraint is not binding, vote buyer B will pay all legislators (we could put in some kind of fixed cost of dealing with each legislator to short circuit this outcome) except those who are already so favorable to him that they are past the FOC point
+										\item Perhaps there's something in equilibrium I'm not seeing yet that will reduce further the number of legislators that are paid
 									\end{itemize}
 						\end{itemize}
+				\end{itemize}
+			\item Let's examine the FOC, assuming pointwise maximization is okay as in Equation~\ref{eq:foc}
+				\begin{itemize}
+					\item 
 				\end{itemize}

### 2015-03-23 GS-extension.tex
work out FOC for vote buyer B in terms of PDF

@@
 				\begin{itemize}
-					\item 
+					\item It's easier for me to think of the CDF in terms of the non-standardized Normal distribution before taking the derivative. Then, if my math is right, the FOC becomes
+						\begin{equation}
+							  \frac{1}{\beta}\frac{1}{\sigma_j \sqrt{2\pi}} \: e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{1}{W_B} 
+						\end{equation}
+							\begin{itemize}
+								\item This just says the pdf has to equal $\beta$ divided by the willingness to pay
+							\end{itemize}
+					\item How do we deal with this r.v. with continuous support when the range of ideal points is posited to be finite ($[-\frac{1}{2},\frac{1}{2}]$)?
+
 				\end{itemize}

### 2015-03-25 GS-extension.tex
solve for b(j) in vote buyer B's FOC
add plus/minus and intuition for two roots on B's FOC

@@
 								\item This just says the pdf has to equal $\beta$ divided by the willingness to pay
+								\item Rearranging to solve for $b(j)$:
+									\begin{equation}
+							  		e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{\beta\sigma_j \sqrt{2\pi}}{W_B} 
+									\end{equation}
+									\begin{equation}
+							  		- \left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2 =2\sigma_j^2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)
+									\end{equation}
+								Since the log statement on the RHS will almost certainly be negative, I can take the negative sign to the right and take the square root without worrying about imaginary numbers
+								  \begin{equation}
+							  		\frac{\alpha + a(j) - b(j)}{\beta} - j = \pm \sqrt{-2\sigma_j^2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)}
+									\end{equation}
+										\begin{itemize}
+											\item Notice there are two roots: could be to the left of the mode (less than 0.5 cumulative probability), or to the right (more than 0.5 cumulative probability)
+										\end{itemize}
+									\begin{equation}
+							  		\alpha + a(j) - b(j) = \pm \beta\sigma_j \sqrt{-2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)} + j \beta
+									\end{equation}
+									\begin{equation}
+							  		b(j) = \alpha + a(j)  - j \beta \pm \beta\sigma_j \sqrt{-2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)}
+									\end{equation}
+									\begin{equation}
+							  		b(j) = \alpha + a(j)  - \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
+									\end{equation}
+								\item So, the bribe for legislator $j$ takes legislator j's preferences back to zero in expectation (the first three terms) and then relative to that, either adds or subtracts a term that involves WTP, variance and $\beta$
+									\begin{itemize}
+										\item Do we have a way of distinguishing between the two? They have very different implications for the CDF, even though the same implications for the pdf
+										\item It makes more intuitive sense that the bribe would be increasing in $W_B$ (WTP)
+										\item Perhaps we derive the different implications and let the data speak
+										\item All the comparative statics will come out with same magnitude, both signs
+										\item SOC is obviously okay (essentially $-x e^{\frac{x^2}{2}}$)
+									\end{itemize}
 							\end{itemize}

### 2015-03-25 GS-extension.tex
add comparative statics for B and note on why sequential model is not interesting

@@
 									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B  \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
+									\label{ex:objB}
 								\end{multline}
@@
 							  		b(j) = \alpha + a(j)  - \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
+										\label{eq:focB}
 									\end{equation}
@@
 			\item Whatever we decide for vote buyer B will be the same for vote buyer A
+			\item Adapting Expression~\ref{ex:objB} for Vote Buyer A
+				\begin{multline}
+					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj \\
+						\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj \leq W_A  \hskip.2in \text{and} \hskip.2in a(j)\geq0 \ \forall j
+							\label{ex:objA}
+				\end{multline}
+					\begin{itemize}
+						\item Major problem if we solve this game sequentially: when substituting the FOC for Vote Buyer B (Equation~\ref{eq:focB}) into Vote Buyer A's objective function, the $a(j)$'s cancel out ($b(j)$ is linear in $a(j)$) so the benefit term is constant in $a(j)$
+					\end{itemize}
 		\end{itemize}
 \end{enumerate}
+
+\newpage
+Comparative statics
+\begin{itemize}
+	\item Vote buyer B (3/25/15)
+		\begin{itemize}
+			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
+				\[
+					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
+				\]
+			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
+				\[
+				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
+				\]
+				\[
+				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
+				\]
+		\end{itemize}
+\end{itemize}
 

### 2015-03-27 GS-extension.tex
solve for Vote Buyer A's simultaneous game FOC
add solution to static problem

@@
 							  \frac{1}{\beta}\frac{1}{\sigma_j \sqrt{2\pi}} \: e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{1}{W_B} 
+								\label{eq:focB2}
 						\end{equation}
@@
 				\begin{multline}
-					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj \\
+					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - a(j) \right] dj \\
 						\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj \leq W_A  \hskip.2in \text{and} \hskip.2in a(j)\geq0 \ \forall j
@@
 						\item Major problem if we solve this game sequentially: when substituting the FOC for Vote Buyer B (Equation~\ref{eq:focB}) into Vote Buyer A's objective function, the $a(j)$'s cancel out ($b(j)$ is linear in $a(j)$) so the benefit term is constant in $a(j)$
+						\item Static best response
+						  \begin{equation}
+								  W_A \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial a(j)} = 1
+									\label{eq:focA}
+							\end{equation}
+						\item Math looks exactly the same as Eqn. \ref{eq:focB2} to \ref{eq:focB} except with $W_A$ replacing $W_B$ and all the opposite signs, so
+							\begin{equation}
+								a(j) = -\alpha + b(j)  + \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_A - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
+									\label{eq:focA3}
+							\end{equation}		
+					\end{itemize}
+				\item Plugging either one of the vote buyers' FOCs into the other just implies that $W_A = W_B$, but doesn't say anything about the level of bribes. Use some kind of pareto ranking to choose one?
+					\begin{itemize}
+						\item Note that to get a solution, I've taken both FOCs to have the same root (either both positive or both negative; Otherwise, we need a very special combination of parameters to get an equilibrium)
+						\item Intuition for this equilibrium: each vote buyer exactly brings legislator $j$ back to neutral (compensating both for inherent preference $\alpha - \beta \cdot j$) and the other vote buyer's bribe; they also each tack on a term related to WTP, $\beta$, and $\sigma_j$, but these terms cancel out as well as long as $W_A = W_B$.
+If $W_A \neq W_B$, then there is not such an interior equilibrium as far as I can tell.
+							\begin{itemize}
+								\item Need to look for more equilibria, perhaps in mixed strategies.
+								\item Especially a way to get asymmetric pure strategies (I'm happy to have asymmetry between $W_A$ and $W_B$ if necessary)
+							\end{itemize}
 					\end{itemize}
@@
 \begin{itemize}
-	\item Vote buyer B (3/25/15)
+	\item Vote buyer B (3/25/15) --- note these are not super useful yet --- they're comparative statics of the best response function, but not of the equilibrium
 		\begin{itemize}

### 2015-03-27 GS-extension.tex
fix typo on line 153
add new section on 3-legislator (discrete) model

@@
 						\begin{itemize}
-							\item Maximizing the total probability mass where $v(j) \geq 0$?
+							\item Maximizing the total probability mass where $v(j) \leq 0$?
 							  \begin{multline}
@@
 \newpage
+Discrete version (Conversation between Kristy and Frank, 3/27/15)
+\begin{itemize}
+	\item Purpose: try to understand what the right objective function is. Does maximizing total probability also maximize the probability of winning?
+		\begin{itemize}
+			\item Note that this model \textit{may} introduce interdependence between the bid functions that does not exist in the continuous model
+			\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
+		\end{itemize}
+	\item Frank prefers to write
+	  \[
+		  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
+		\]
+			\begin{itemize}
+				\item Note that, in a probit we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
+				\item Also going to ignore Vote Buyer A's choice for now, so we have
+			\end{itemize}
+	  \[
+		  v(z) = \alpha -\beta z + \ve - b(z)
+		\]
+	\item Then the probability that legislator $z$ votes against the new proposal is
+	  \[
+		  \Pr\left[v(z)\leq 0 \right] = \Pr\left[\alpha -\beta z + \ve - b(z) \leq 0 \right] 
+			                            = \Pr\left[\ve \leq \beta z - \alpha + b(z) \right] 
+		\]
+		Assuming $\ve \sim N(0,1)$, the probability that legislator $z$ votes ``no'' is $\Phi\left(\beta z - \alpha + b(z) \right)$
+	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. Then the three probabilities are
+		\begin{itemize}
+			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(z) \right)$, $\Phi\left(- \alpha + b(z) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(z) \right)$
+			\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
+				\[
+				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \Phi\left(\beta z - \alpha + b(z) \right)
+				\]
+			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
+			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
+			  \[
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} \Pr(X\left(-\frac{1}{2}\right)=1)\Pr(X\left(0\right)=1)\Pr(X\left(\frac{1}{2}\right)=0)  + ...
+				\]
+		\end{itemize}
+\end{itemize}
+
+\newpage
 Comparative statics

### 2015-04-03 GS-extension.tex
finish 3-leg obj fcn
work out FOCs (cheating with symmetry for now)

@@
 			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
-			  \[
-			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} \Pr(X\left(-\frac{1}{2}\right)=1)\Pr(X\left(0\right)=1)\Pr(X\left(\frac{1}{2}\right)=0)  + ...
-				\]
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
+					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right)
+				\end{multline}
+			Substituting from the definition of $X$,
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
+					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
+					\left(1-\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
+					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)
+				\end{multline}
+			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is
+				\begin{multline}
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - \\
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+				\end{multline}
+			Simplifying:
+			  \begin{multline}
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)+ \\
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\
+					- 2\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+				\end{multline}
+			Further:
+			  \begin{multline}
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \\ \left[ \Phi\left(- \alpha + b(0) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)
+					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \right] = 0
+				\end{multline}
+			So I think we have three conditions:
+			\begin{equation}
+					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
+					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+			\end{equation}
+			\begin{equation}
+					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
+					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) = 0
+			\end{equation}
+			\begin{equation}
+					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
+					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+			\end{equation}
 		\end{itemize}

### 2015-04-07 GS-extension.tex
fixed typo on line 298; verified chain rule is correct (line 322)
correct obj fcn (add WTP and cost) and push through
add notes from chat with Frank 4/3 and calculate logistic version of FOC

@@
 		\begin{itemize}
-			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(z) \right)$, $\Phi\left(- \alpha + b(z) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(z) \right)$
+			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)$, $\Phi\left(- \alpha + b(0) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)$
 			\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
@@
 			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
-					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
+					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
 					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
 					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
-					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right)
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
 				\end{multline}
@@
 			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
-					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
+					W_B \biggl[ \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
 					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
 					\left(1-\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
-					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)
+					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
 				\end{multline}
@@
 				\begin{multline}
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
+					W_B \biggl[ \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
 					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - \\
 					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
 				\end{multline}
@@
 			\begin{multline}
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)+ \\
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\
-					- 2\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+					W_B \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \biggl[ \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
+					\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - 
+					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
+					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
 				\end{multline}
-			Further:
+			Simplifying further:
 			  \begin{multline}
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \\ \left[ \Phi\left(- \alpha + b(0) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)
-					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \right] = 0
+					\Phi\left(- \alpha + b(0) \right)+ \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
+					- 2\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\right)^2}{2}} }
+					\label{eq:firstfoc}
 				\end{multline}
-			So I think we have three conditions:
+
+			The two symmetric conditions would be:
+			\begin{multline}
+					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
+					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
+				\end{multline}
+			\begin{multline}
+					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
+					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
+				\end{multline}
+		\end{itemize}
+	\item Some notes
+		\begin{itemize}
+			\item If we divide through by 2, the left side is the average minus the product
+			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
+			\item Need to check SOC at some point
+			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
+			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
+		\end{itemize}
+	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
 		\begin{equation}
-					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
-					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
+					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
+					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)} }
 				\end{equation}
-			\begin{equation}
-					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
-					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) = 0
-			\end{equation}
-			\begin{equation}
-					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
-					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) = 0
-			\end{equation}
-		\end{itemize}
 \end{itemize}

### 2015-04-23 GS-extension.tex
add solution to base model; start separate page for calculations
add math that supports base model solution

@@
 					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
-					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)} }
+					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)} }
+					\label{eq:logistic}
 				\end{equation}
+		\begin{itemize}
+			\item A LOT of math (I will put it somewhere else) leads to three equations:
+				\[
+				  \left[ - \alpha + b(0) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] + \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
+				\]
+				\[
+				   \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] =\left[ - \alpha + b(0) \right]+ \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
+				\]
+				\[
+				   \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] +\left[ - \alpha + b(0) \right]
+				\]
+			\item A little more math implies that all three quantities in brackets must equal zero.
+		\end{itemize}
 \end{itemize}
@@
 		\end{itemize}
+\end{itemize}
+
+\newpage
+The math that follows from Equation \ref{eq:logistic}:
+\begin{itemize}
+	\item Let
+		\begin{enumerate}
+			\item $ X - \alpha + b(0)$ 
+			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
+		\end{enumerate}
+	\item Then Equation \ref{eq:logistic} is equivalent to:
+		\begin{equation}
+			\frac{e^{X}}{1+e^{X}} + \frac{e^{Y}}{1+e^{Y }} - 2\frac{e^{X}}{1+e^{X}}  \frac{e^{Y }}{1+e^{Y }} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
+					\label{eq:logistic2}
+		\end{equation}
+		\[
+			\frac{e^{X} + 2e^{X+Y} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} - 2\frac{e^{X+Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
+		\]
+		\[
+			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
+		\]
+		\begin{equation}
+			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{1}{W_B}
+		\end{equation}
+		Likewise, we have
+		\begin{equation}
+			\frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}= \frac{1}{W_B}
+		\end{equation}
+		Setting the left-hand size of these two equations equal to each other,
+		\[
+		  \frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}
+		\]
+		\[
+		  \frac{e^{X+Z} + e^{Y+Z}}{1+e^{Z}}= \frac{e^{X+Y} + e^{Y+Z}}{1+e^{Y}}
+		\]
+		\[
+		  e^{X+Z} + e^{Y+Z} + e^{X+Y+Z} +e^{2Y+Z}= e^{X+Y} + e^{Y+Z} + e^{X+Y+Z} +e^{Y+2Z}
+		\]
+		\[
+		  e^{X+Z} +e^{2Y+Z}= e^{X+Y} +e^{Y+2Z}
+		\]
+		\[
+		  e^{X}\left(e^{Z} - e^{Y} \right) = e^{Y+Z}\left(e^{Z} - e^{Y} \right)
+		\]
+		\[
+		  e^{X} = e^{Y+Z}
+		\]
+		\[
+		  X = Y+Z
+		\]
+		By symmetry, we also have
+		\[
+		  Y = X + Z
+		\]
+		\[
+		  Z = X + Y
+		\]
 \end{itemize}

### 2015-04-23 GS-extension.tex
finish math that supports base model solution
rearrange extra math so it directly follows section on discrete model
add notes on next steps, intuition and questions

@@
 				\]
-			\item A little more math implies that all three quantities in brackets must equal zero.
+			\item A little more math implies that all three quantities in brackets must equal zero
+				\begin{itemize}
+					\item That is, Vote Buyer B's bribe should make each legislator just indifferent between the new proposal and the status quo
+					\item First question: why doesn't this depend on willingness-to-pay?
+						\begin{itemize}
+							\item FOC says each bribe should be calibrated so that $W_B \cdot \text{marginal contribution to probability} = 1$, or $\frac{\partial \text{probability}}{\partial \text{bribe}} = \frac{1}{W_B}$
+							\item Something happens when all three conditions come together...what's the intuition?
+						\end{itemize}
+					\item To do next: see what non-negativity of bribes implies
+						\begin{itemize}
+							\item Also, insert Vote Buyer A's behavior
+							\item And give the various legislators different variances
 						\end{itemize}
 				\end{itemize}
-
-\newpage
-Comparative statics
-\begin{itemize}
-	\item Vote buyer B (3/25/15) --- note these are not super useful yet --- they're comparative statics of the best response function, but not of the equilibrium
-		\begin{itemize}
-			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
-				\[
-					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
-				\]
-			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
-				\[
-				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
-				\]
-				\[
-				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
-				\]
 		\end{itemize}
@@
 		\]
+		\begin{equation}
+		  X = Y+Z
+			\label{eq:X}
+		\end{equation}
+		By symmetry, we also have
+		\begin{equation}
+		  Y = X + Z
+			\label{eq:Y}
+		\end{equation}
+		\begin{equation}
+		  Z = X + Y
+			\label{eq:Z}
+		\end{equation}
+		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
 		\[
-		  X = Y+Z
+		  X = Y + X + Y = X = 2Y \Rightarrow Y = 0
 		\]
-		By symmetry, we also have
+		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
 		\[
-		  Y = X + Z
+		  X = Y = Z = 0
+		\]		
+\end{itemize}
+
+\newpage
+Comparative statics
+\begin{itemize}
+	\item Vote buyer B (3/25/15) --- note these are not super useful yet --- they're comparative statics of the best response function, but not of the equilibrium
+		\begin{itemize}
+			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
+				\[
+					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
+				\]
+			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
+				\[
+				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
 				\]
 				\[
-		  Z = X + Y
+				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
 				\]
+		\end{itemize}
 \end{itemize}

### 2015-04-24 GS-extension.tex
add SOC; shows solution is an inflection point

@@
 		\begin{equation}
-					\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}} + \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)}}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}
-					- 2\frac{e^{- \alpha + b(0)}}{1+e^{- \alpha + b(0)}}  \frac{e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }}{1+e^{\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)} }
+					\frac{1}{1+e^{\alpha - b(0)}} + \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }}
+					- 2\frac{1}{1+e^{\alpha - b(0)}}  \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)} }
 					\label{eq:logistic}
@@
 		\begin{enumerate}
-			\item $ X - \alpha + b(0)$ 
+			\item $X = -\alpha + b(0)$ 
 			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
@@
 		\begin{equation}
-			\frac{e^{X}}{1+e^{X}} + \frac{e^{Y}}{1+e^{Y }} - 2\frac{e^{X}}{1+e^{X}}  \frac{e^{Y }}{1+e^{Y }} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
+			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
 					\label{eq:logistic2}
@@
 		\[
-			\frac{e^{X} + 2e^{X+Y} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} - 2\frac{e^{X+Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
+			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
 		\]
 		\[
-			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} = \frac{\left(1+e^{Z}\right)^2}{W_B \: e^{Z} }
+			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
 		\]
 		\begin{equation}
-			\frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{1}{W_B}
+			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
 		\end{equation}
@@
 		\begin{equation}
-			\frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}= \frac{1}{W_B}
+			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
 		\end{equation}
@@
 		\[
-		  \frac{e^{X} + e^{Y}}{\left(1+e^{X}\right)\left(1+e^{Y }\right)} \frac{e^{Z}}{\left(1+e^{Z}\right)^2}= \frac{e^{X} + e^{Z}}{\left(1+e^{X}\right)\left(1+e^{Z}\right)} \frac{e^{Y}}{\left(1+e^{Y}\right)^2}
+		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
 		\]
 		\[
-		  \frac{e^{X+Z} + e^{Y+Z}}{1+e^{Z}}= \frac{e^{X+Y} + e^{Y+Z}}{1+e^{Y}}
+		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
 		\]
 		\[
-		  e^{X+Z} + e^{Y+Z} + e^{X+Y+Z} +e^{2Y+Z}= e^{X+Y} + e^{Y+Z} + e^{X+Y+Z} +e^{Y+2Z}
+		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
 		\]
 		\[
-		  e^{X+Z} +e^{2Y+Z}= e^{X+Y} +e^{Y+2Z}
+		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
 		\]
 		\[
-		  e^{X}\left(e^{Z} - e^{Y} \right) = e^{Y+Z}\left(e^{Z} - e^{Y} \right)
+		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
 		\]
 		\[
-		  e^{X} = e^{Y+Z}
+		  e^{-X} = e^{-Y-Z}
 		\]
 		\begin{equation}
-		  X = Y+Z
+		  -X = -Y-Z
 			\label{eq:X}
@@
 		\begin{equation}
-		  Y = X + Z
+		  -Y = -X - Z
 			\label{eq:Y}
@@
 		\begin{equation}
-		  Z = X + Y
+		  -Z = -X - Y
 			\label{eq:Z}
@@
 		\[
-		  X = Y + X + Y = X = 2Y \Rightarrow Y = 0
+		  - X = - Y - X - Y \Rightarrow 0 = 2Y \Rightarrow Y = 0
 		\]
@@
 \end{itemize}
+
+\vskip1in
+Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page).
+The first derivative of the objective function w.r.t.
+$b(-\frac{1}{2})$ is (in logistic form)
+\[
+  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
+\]
+\[
+  W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
+\]
+Now, the second derivative:
+\[
+  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2\left(1+e^{-Z}\right) e^{-Z}-\left(1+e^{-Z}\right)^2 e^{-Z}}{\left(1+e^{-Z}\right)^4} \right]
+\]
+\[
+  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} 2 e^{-Z}-\left(1+e^{-Z}\right) e^{-Z}}{\left(1+e^{-Z}\right)^3} \right]
+\]
+\[
+  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-\left(1+e^{-Z}\right) \right\}}{\left(1+e^{-Z}\right)^3} \right]
+\]
+\[
+  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{2 e^{-Z}-1-e^{-Z} \right\}}{\left(1+e^{-Z}\right)^3} \right]
+\]
+\[
+  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z} \left\{e^{-Z}-1 \right\}}{\left(1+e^{-Z}\right)^3} \right]
+\]
+\[
+  W_B\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-Z}}{\left(1+e^{-Z}\right)^3} \right] \left\{e^{-Z}-1 \right\}
+\]
+Everything except for the expression in the curly braces is positive.
+The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$.
+So this objective function appears to have an inflection point at $z=0$.
 

### 2015-04-25 machina_triangle_graph.m
add Matlab file for graphing objective function of discrete model

@@ -1,0 +1,50 @@
+b0 = [0:.01:1];
+bp5 = [0:.01:1];
+[b0,bp5]=meshgrid(b0,bp5);
+
+t = 1;
+bnp5 = t - b0 - bp5;
+
+al = .5;
+
+X = -.5 - al + bnp5;
+Y = - al + b0;
+Z = .5 - al + bp5;
+
+WB = 3;
+
+obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
+
+obj2=obj;
+
+bs = size(b0,2);
+
+for j=1:bs
+     for i=1:bs
+        if i + j < 102
+        obj2(i,j) = 0;
+        end
+end
+
+
+figure1 = figure('Color',[1 1 1],...
+  'FileName','C:\Users\Kristy\Documents\My Dropbox\Research\Separation of Powers\Write ups\lobby_br.jpg',...
+  'PaperPosition',[1 3.313 5.833 4.375]);
+ 
+%% Create axes
+axes1 = axes('Parent',figure1);
+axis([0 .12 0 .0035]);
+%title(axes1,'Lobby''s Optimal Expenditure');
+xlabel(axes1,'Trade Agreement Tariff');
+ylabel(axes1,'Lobbying Expenditure');
+hold(axes1,'all');
+ 
+
+
+
+%% Create plot
+plot2 = plot(TA,opt_C_13,'DisplayName','\theta \sim U[-.14,14]','Color',[0 0 1],'LineStyle','--','LineWidth',1,'Parent',axes1);
+legend1 = legend(axes1,{'\theta \sim U[-.01,01]','\theta \sim U[-.14,14]'},'Position',[0.1794 0.7725 0.1714 0.119]);
+
+
+saveas(gcf,'C:\Users\Kristy\Documents\Dropbox\Research\Separation_of_Powers\Work\lobby_br.jpg');

### 2015-04-26 machina_triangle_graph.m
modify code to attempt to set obj. fcn. values outside simplex to zero

@@ -15,15 +15,19 @@ WB = 3;
 
 obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
 
-obj2=obj;
+s0 = size(b0,2);
+s5 = size(bp5,2);
 
-bs = size(b0,2);
+obj2 = zeros(101);
 
-for j=1:bs
-     for i=1:bs
-        if i + j < 102
-        obj2(i,j) = 0;
+for j=1:101
+    j=50
+    i = 25
+     for i=1:101
+        if bnp5(i,j) ge 0
+            disp('test2')
         end
+     obj2(i,j) = obj(i,j)
 end
 
 

### 2015-04-27 machina_triangle_graph.m
abdul gave me soln to simplex problem

@@ -15,25 +15,8 @@ WB = 3;
 
 obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
 
-s0 = size(b0,2);
-s5 = size(bp5,2);
+obj2 = obj.*(bnp5>=0);
 
-obj2 = zeros(101);
-
-for j=1:101
-    j=50
-    i = 25
-     for i=1:101
-        if bnp5(i,j) ge 0
-            disp('test2')
-        end
-     obj2(i,j) = obj(i,j)
-end
-
-
-figure1 = figure('Color',[1 1 1],...
-  'FileName','C:\Users\Kristy\Documents\My Dropbox\Research\Separation of Powers\Write ups\lobby_br.jpg',...
-  'PaperPosition',[1 3.313 5.833 4.375]);
  
 %% Create axes
 axes1 = axes('Parent',figure1);

### 2015-04-28 machina_triangle_graph.m
generalize for different values of total contribution; direction of prob change doesn't makes sense

@@ -1,8 +1,8 @@
-b0 = [0:.01:1];
-bp5 = [0:.01:1];
+t = 2
+b0 = [0:.01*t:t];
+bp5 = [0:.01*t:t];
 [b0,bp5]=meshgrid(b0,bp5);
 
-t = 1;
 bnp5 = t - b0 - bp5;
 
 al = .5;
@@ -11,13 +11,20 @@ X = -.5 - al + bnp5;
 Y = - al + b0;
 Z = .5 - al + bp5;
 
-WB = 3;
+WB = 5;
 
 obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
 
 obj2 = obj.*(bnp5>=0);
 
- 
+[value, location] = max(obj2(:));
+prob = value/5
+[R,C] = ind2sub(size(obj2),location);
+
+%%Outer loop
+v = value - b0(R,C) - bp5(R,C) - bnp5(R,C)
+
+mesh(obj2);
 %% Create axes
 axes1 = axes('Parent',figure1);
 axis([0 .12 0 .0035]);

### 2015-04-28 machina_triangle_graph.m
finalize loop contents

@@ -1,28 +1,25 @@
-t = 2
+%%parameters (beta = 1)
+WB = 5;
+al = .5;
+
+t = 1;
 b0 = [0:.01*t:t];
 bp5 = [0:.01*t:t];
 [b0,bp5]=meshgrid(b0,bp5);
-
 bnp5 = t - b0 - bp5;
-
-al = .5;
 
 X = -.5 - al + bnp5;
 Y = - al + b0;
 Z = .5 - al + bp5;
 
-WB = 5;
-
 obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
-
 obj2 = obj.*(bnp5>=0);
 
 [value, location] = max(obj2(:));
-prob = value/5
 [R,C] = ind2sub(size(obj2),location);
+prob = (value+b0(R,C) + bp5(R,C) + bnp5(R,C))/WB;
+out = [t,prob,value]
 
-%%Outer loop
-v = value - b0(R,C) - bp5(R,C) - bnp5(R,C)
 
 mesh(obj2);
 %% Create axes

### 2015-04-28 machina_triangle_graph.m
maximization loop working. first parameter choice points to no lobbying as solution

@@ -2,23 +2,26 @@
 WB = 5;
 al = .5;
 
-t = 1;
-b0 = [0:.01*t:t];
-bp5 = [0:.01*t:t];
-[b0,bp5]=meshgrid(b0,bp5);
-bnp5 = t - b0 - bp5;
+out = zeros(100,3,'double');
+for t = 0.01:.01:1;
+    b0 = [0:.01*t:t];
+    bp5 = [0:.01*t:t];
+    [b0,bp5]=meshgrid(b0,bp5);
+    bnp5 = t - b0 - bp5;
 
-X = -.5 - al + bnp5;
-Y = - al + b0;
-Z = .5 - al + bp5;
+    X = -.5 - al + bnp5;
+    Y = - al + b0;
+    Z = .5 - al + bp5;
 
-obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
-obj2 = obj.*(bnp5>=0);
+    obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
+    obj2 = obj.*(bnp5>=0);
 
-[value, location] = max(obj2(:));
-[R,C] = ind2sub(size(obj2),location);
-prob = (value+b0(R,C) + bp5(R,C) + bnp5(R,C))/WB;
-out = [t,prob,value]
+    [value, location] = max(obj2(:));
+    [R,C] = ind2sub(size(obj2),location);
+    prob = (value+b0(R,C) + bp5(R,C) + bnp5(R,C))/WB;
+    t2 = round(t*100);
+    out(t2,:) = [t,prob,value];
+ end
 
 
 mesh(obj2);

### 2015-04-28 machina_triangle_graph.m
add row and column data to output

@@ -1,9 +1,9 @@
 %%parameters (beta = 1)
-WB = 5;
+WB = 15;
 al = .5;
 
-out = zeros(100,3,'double');
-for t = 0.01:.01:1;
+out = zeros(100,5,'double');
+for t = 0.01:.01:10;
     b0 = [0:.01*t:t];
     bp5 = [0:.01*t:t];
     [b0,bp5]=meshgrid(b0,bp5);
@@ -20,7 +20,7 @@ for t = 0.01:.01:1;
     [R,C] = ind2sub(size(obj2),location);
     prob = (value+b0(R,C) + bp5(R,C) + bnp5(R,C))/WB;
     t2 = round(t*100);
-    out(t2,:) = [t,prob,value];
+    out(t2,:) = [t,prob,value,R,C];
  end
 
 

### 2015-05-16 GS-extension.tex
add section headings / toc to GS-extension
add 2nd derivative w.r.t. Z for SOC
add cross-partial for SOC

@@
 
+\section{Groseclose and Snyder 1996}
 On Feb. 12, Sebastian and I agreed to focus efforts on finding a base model to facilitate empirical identification. I am pursuing Groseclose $\&$ Snyder (1996), ``Buying Supermajorities,'' APSR
@@
 
+\section{Our Extension to Uncertainty}
 \vskip.3in
@@
 
+\subsection{Solving the Model}
 \vskip.3in
@@
 
+\section{Discrete Model}
 \newpage
@@
 
+\subsection{Math for Discrete Model}
 \newpage
@@
 
-\vskip1in
+\subsection{Second Order Condition}
 Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page).
@@
 $b(-\frac{1}{2})$ is (in logistic form)
-\[
+\begin{equation}
   W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} \right] - 1
-\]
-\[
+\end{equation}
+\begin{equation}
   W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1
-\]
+	\label{eq:firstderiv}
+\end{equation}
 Now, the second derivative:
@@
 So this objective function appears to have an inflection point at $z=0$.
+\begin{itemize}
+	\item When $z < 0$ (as when this legislator is naturally against you and you don't bribe her), this expression is negative
+\end{itemize}
+
+\vskip1in
+We also need cross partials. Let's start with the first derivative for $b\left(\frac{1}{2}\right)$, analogous to Expression~\ref{eq:firstderiv} for $b\left(-\frac{1}{2}\right)$:
+\begin{equation}
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1
+\end{equation}
+
+Taking the derivative of this expression with respect to $b\left(0\right)$:
+\[
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)(-1)e^{-X} -\left(e^{-X}+ e^{-Z}\right)\left(-e^{-X}- e^{-X-Z}\right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+\]
+\[
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{\left(e^{-X}+ e^{-Z}\right)\left(e^{-X} + e^{-X-Z}\right) - \left(1+e^{-X}\right)\left(1+e^{-Z}\right)e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+\]
+\[
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{\left(e^{-2X} + e^{-2X-Z} + e^{-X-Z} + e^{-X-2Z}\right) - \left(1 +e^{-X} +e^{-Z}+ e^{-X-Z} \right)e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+\]
+\[
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-2X} + e^{-2X-Z} + e^{-X-Z} + e^{-X-2Z} - e^{-X} - e^{-2X} - e^{-X-Z} - e^{-2X-Z}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+\]
+\[
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X-2Z} - e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+\]
+\[
+  W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X}\left(e^{-2Z} - 1 \right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+\]
 
 \newpage
+\section{Some Comparative Statics}			
 Comparative statics
@@
 
+\section{Notes from March}
 \newpage

### 2015-05-16 GS-extension.tex
add section on non-negativity constraints

@@
 					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+					\label{eq:obj}
 				\end{multline}
@@
 
+\subsection{Adding Non-negativity Constraints for Bribes}
+The Lagrangian for the problem is the same as Expression~\ref{eq:obj}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$
+
+The full set of FOCs (in logistic form) is then:
+\[
+    W_B\frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_X = 0
+\]
+\[
+    W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1 + \lambda_Y = 0 
+\]
+\[
+    W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_Z = 0
+\]
+\[
+  b\left(0\right) \geq0 \hskip.2in b\left(\frac{1}{2}\right) \geq0 \hskip.2in b\left(-\frac{1}{2}\right) \geq0 
+\]
+\[
+  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
+\]
+\[
+  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(-\frac{1}{2}\right) = 0 
+\]
+There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = \left(b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\
+
+Note that the complementary slackness condition implies that either a bribe is zero, \un{or} its multiplier is zero (or both).
+
+\newpage
 \subsection{Math for Discrete Model}
-\newpage
 The math that follows from Equation \ref{eq:logistic}:

### 2015-06-02 GS-extension.tex
start conditions for two positive bribes

@@
 \]
-There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = \left(b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\
+There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = (b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\
 
 Note that the complementary slackness condition implies that either a bribe is zero, \un{or} its multiplier is zero (or both).
+
+\vskip.5in
+Simulations show that for many sets of parameters, $b\left(0\right)$ and $b\left(\frac{1}{2}\right)$ are positive while $b\left(-\frac{1}{2}\right) = 0$.
+\begin{itemize}
+	\item Then $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = -\frac{\beta}{2} - \alpha $
+	\item $\lambda_Z$ is likely positive
+	\item $\lambda_X = \lambda_Y = 0$
+\end{itemize}
+So we'll have $-Z = -X-Y$
+\begin{itemize}
+	\item Which is
+		\[
+		  \frac{\beta}{2} + \alpha = \alpha - b(0) - \frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right)
+		\]
+		\[
+		  \beta = \alpha - \left(b(0) + b\left(\frac{1}{2}\right) \right)
+		\]
+\end{itemize}
 

### 2015-06-05 machina_triangle_graph.R
begin converting machina_triangle_graph from matlab to R

@@ -1,0 +1,48 @@
+library("pracma", lib.loc="~/R/win-library/3.1")
+
+%%parameters (beta = 1)
+WB = 10
+al = .5
+
+v = seq(0.01,WB,0.01)
+out = matrix(0,100,5)
+
+
+for (t in v)
+  b0 = seq(0,t,.01*t)
+  bp5 = seq(0,t,.01*t)
+
+  tmp=meshgrid(b0,bp5)
+  b0=tmp$b0
+  bp5=tmp$bp5
+
+  
+
+  bnp5 = t - b0 - bp5;
+
+  Z = -.5 - al + bnp5;
+  X = - al + b0;
+  Y = .5 - al + bp5;
+
+  obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
+  obj2 = obj.*(bnp5>=0);
+
+  [value, location] = max(obj2(:));
+  [R,C] = ind2sub(size(obj2),location);
+  prob = (value+b0(R,C) + bp5(R,C) + bnp5(R,C))/WB;
+  t2 = round(t*100);
+  out(t2,:) = [t,prob,value,R,C];
+end
+
+[v, l] = max(out(:,3));
+bribe0 = (out(l,5)-1)*l/10000
+bribep5 = (out(l,4)-1)*l/10000
+bribenp5 = l/100 - bribe0 -bribep5
+
+z = -.5 - al + bribenp5
+x = - al + bribe0
+y = .5 - al + bribep5
+
+lhs_y = (exp(-x)+exp(-z))/((1+exp(-x))*(1+exp(-z)))*(exp(-y)/((1+exp(-y))^2))
+lhs_x = (exp(-y)+exp(-z))/((1+exp(-y))*(1+exp(-z)))*(exp(-x)/((1+exp(-x))^2))
+lhs_z = (exp(-y)+exp(-x))/((1+exp(-y))*(1+exp(-x)))*(exp(-z)/((1+exp(-z))^2))

### 2015-06-05 machina_triangle_graph.m

@@ -31,22 +31,11 @@ end
     z = -.5 - al + bribenp5
     x = - al + bribe0
     y = .5 - al + bribep5
+    
+    lhs_y = (exp(-x)+exp(-z))/((1+exp(-x))*(1+exp(-z)))*(exp(-y)/((1+exp(-y))^2))
+    lhs_x = (exp(-y)+exp(-z))/((1+exp(-y))*(1+exp(-z)))*(exp(-x)/((1+exp(-x))^2))
+    lhs_z = (exp(-y)+exp(-x))/((1+exp(-y))*(1+exp(-x)))*(exp(-z)/((1+exp(-z))^2))
+
+
      
 mesh(obj2);
-%% Create axes
-axes1 = axes('Parent',figure1);
-axis([0 .12 0 .0035]);
-%title(axes1,'Lobby''s Optimal Expenditure');
-xlabel(axes1,'Trade Agreement Tariff');
-ylabel(axes1,'Lobbying Expenditure');
-hold(axes1,'all');
- 
-
-
-
-%% Create plot
-plot2 = plot(TA,opt_C_13,'DisplayName','\theta \sim U[-.14,14]','Color',[0 0 1],'LineStyle','--','LineWidth',1,'Parent',axes1);
-legend1 = legend(axes1,{'\theta \sim U[-.01,01]','\theta \sim U[-.14,14]'},'Position',[0.1794 0.7725 0.1714 0.119]);
-
-
-saveas(gcf,'C:\Users\Kristy\Documents\Dropbox\Research\Separation_of_Powers\Work\lobby_br.jpg');

### 2015-06-05 machina_triangle_graph.R
more development of R version of machina_triangle_graph

@@ -16,6 +16,7 @@ for (t in v) {
   Bp5=meshgrid(b0,bp5)$Y
   Bnp5 = t - B0 - BP5
 
+<<<<<<< HEAD
   Z = -.5 - al + Bnp5
   X = - al + B0
   Y = .5 - al + Bp5
@@ -34,6 +35,23 @@ for (t in v) {
   out[t,5] = RC[t,2]
 }
 
+=======
+  bnp5 = t - b0 - bp5;
+
+  Z = -.5 - al + bnp5;
+  X = - al + b0;
+  Y = .5 - al + bp5;
+
+  obj = WB.*((1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-Z))) + (1./(1+exp(-X))).*(1./(1+exp(-Z))).*(1-1./(1+exp(-Y))) + (1./(1+exp(-Z))).*(1./(1+exp(-Y))).*(1-1./(1+exp(-X))) + (1./(1+exp(-X))).*(1./(1+exp(-Y))).*(1./(1+exp(-Z)))) - b0 - bp5 - bnp5;
+  obj2 = obj.*(bnp5>=0);
+
+  [value, location] = max(obj2(:));
+  [R,C] = ind2sub(size(obj2),location);
+  prob = (value+b0(R,C) + bp5(R,C) + bnp5(R,C))/WB;
+  t2 = round(t*100);
+  out(t2,:) = [t,prob,value,R,C];
+end
+>>>>>>> more development of R version of machina_triangle_graph
 
 [v, l] = max(out(:,3));
 bribe0 = (out(l,5)-1)*l/10000

### 2015-09-25 GS-extension.tex
took out wrong statements that resulted from dividing by zero

--- 2015-05-16 GS-extension.tex
@@
 
+\vskip.5in
+Simulations show that for many sets of parameters, $b\left(0\right)$ and $b\left(\frac{1}{2}\right)$ are positive while $b\left(-\frac{1}{2}\right) = 0$.
+\begin{itemize}
+	\item Then $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = -\frac{\beta}{2} - \alpha $
+	\item $\lambda_Z$ is likely positive
+	\item $\lambda_X = \lambda_Y = 0$
+\end{itemize}
+
 \newpage
@@
 		\]
-		\[
-		  e^{-X} = e^{-Y-Z}
-		\]
-		\begin{equation}
-		  -X = -Y-Z
-			\label{eq:X}
-		\end{equation}
-		By symmetry, we also have
-		\begin{equation}
-		  -Y = -X - Z
-			\label{eq:Y}
-		\end{equation}
-		\begin{equation}
-		  -Z = -X - Y
-			\label{eq:Z}
-		\end{equation}
-		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
-		\[
-		  - X = - Y - X - Y \Rightarrow 0 = 2Y \Rightarrow Y = 0
-		\]
-		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
-		\[
-		  X = Y = Z = 0
-		\]		
-\end{itemize}
 

### 2015-09-25 GS-extension.tex
substitute correct combining of FOCs in 'math for discrete model' section

@@
 		\end{equation}
-		Setting the left-hand size of these two equations equal to each other,
+		and
+		\begin{equation}
+			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+		\end{equation}
+		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
 		\[
-		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
+		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
 		\]
 		\[
-		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
+		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
 		\]
 		\[
-		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
+		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
 		\]
 		\[
-		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
+		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
 		\]
 		\[
-		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
+		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
 		\]
+		\begin{equation}
+		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
+			\label{eq:twoways}
+		\end{equation}
+   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
+		\[
+		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
+		\]
+		\[
+		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
+		\]
+  	Second, multiplying through by zero:
+	  \[
+		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
+		\]
+	\end{itemize}
 
-\subsection{Second Order Condition}
+\newpage		
+\subsection{Second Order Conditions}
 Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page).

### 2015-10-02 GS-extension.tex
complete conditions for 2 non-negative bribes

@@
 		\]
-		\[
+		\begin{equation}
 		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
-		\]
+			\label{eq:1}
+		\end{equation}
   	Second, multiplying through by zero:
-	  \[
+	  \begin{equation}
 		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
-		\]
+			\label{eq:2}
+		\end{equation}
+	\end{itemize}	
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$.
+Note that this is due to the construction of the problem.
+This means $e^Z < 1$.
+In this case,
+	\begin{itemize}
+		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
+		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
+	\end{itemize}
+The second order conditions will pin down the solution in this case of two non-negative bribes.
+
+\begin{itemize}
+	\item SOCs imply that both $X$ and $Y$ are positive.
 \end{itemize}

### 2015-10-08 GS-extension.tex
add bordered Hessian and conditions for two non-negative bribes case
add one principal minor condition to SOC section

@@
 
+\vskip.5in
+The SOCs when one non-negativity constraint binds; bordered Hessian is 4x4. \\
+		\begin{tabular}{cccc}
+			0 & $\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_1}{\partial b\left(-0\right)}$ & $\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ \\
+			$\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			$\frac{\partial g_1}{\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			$\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular} \\
+
+\vskip.2in		
+Evaluating the constraint terms:\\
+\begin{tabular}{cccc}
+			0 & -1 & 0 & 0 \\
+			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular}
+
+The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.
+\begin{itemize}
+	\item First we need the determinant of the next-to-last principal minor, the 3x3 matrix that is the upper-lefthand corner of this matrix.
+This determinant should be positive.
+We can use the trick by which one copies the first two rows to the right of the matrix and then multiplies down the columns to the right and up the columns to the right (these terms get a negative sign).
+Then the determinant is
+	  \[
+		  0 + 0 + 0 - \left[0 + 0 + (-1)(-1)\frac{\partial^2 L}{\partial b(0)^2} \right] = - \frac{\partial^2 L}{\partial b(0)^2}
+		\]
+		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is positive.
+\end{itemize}
+
 \newpage

### 2015-10-08 GS-extension.tex
add second principal minor condition to SOC section

@@
 		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is positive.
+	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
+		\[
+		  0 \cdot \left|\text{something} \right| - (-1)\cdot 
+			\left|\begin{array}{ccc}
+				- 1 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			0 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right| + 0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right|
+		\]
+		\[ 
+			=
+			\left|\begin{array}{ccc}
+				- 1 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			0 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right|
+		\]
+		\[
+		  = - 1 \cdot \left|\begin{array}{cc}
+			\frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right|
+		\]
+		\[
+		  = - 1 \cdot \left(
+			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
+		\]
+		\[
+		  = \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+		\]
+
+  We need this determinant to be negative, that is
+		\[
+		  = \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} > \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 
+		\]
+	  The right hand side is positive because it's a square.
+The left hand side must then be positive, and since we know that one term is positive from the previous principal minor result, the other must be positive as well.
+Thus both $b(0)$ and $b\left(\frac{1}{2}\right)$ must be positive.
 \end{itemize}
+Note that nothing useful seems to come out of trying to expand and then simplify this expression. I get:
+\[
+  2e^{-X}e^{-Y} + 2 > e^{-2Z} + e^{-X}e^{-2Z} + e^{-Y}e^{-2Z} + e^{-X}e^{-Y}e^{-2Z}
+\]
 

### 2015-10-09 constrained-optimization.r
update constrained-optimization program to integrate willingness-to-pay parameter

@@ -1,4 +1,4 @@
-WB = 10 #willingness to pay parameter
+WB = 7 #willingness to pay parameter
 al = .5 #alpha
 
 #the objective function with a negative sign since optim in a minimizer
@@ -6,16 +6,16 @@ obj <- function(B) {
   B0 <- B[1]
   Bp5 <- B[2]
   Bnp5 <- B[3]
-  -10*((1/(1+exp(.5 - B0)))*(1/(1+exp(.5 - .5 - Bp5)))*(1-1/(1+exp(.5 + .5 - Bnp5))) + (1/(1+exp(.5 - B0)))*(1/(1+exp(.5 + .5 - Bnp5)))*(1-1/(1+exp(.5 - .5 - Bp5))) + (1/(1+exp(.5 + .5 - Bnp5)))*(1/(1+exp(.5 - .5 - Bp5)))*(1-1/(1+exp(.5 - B0))) + (1/(1+exp(.5 - B0)))*(1/(1+exp(.5 - .5 - Bp5)))*(1/(1+exp(.5 + .5 - Bnp5)))) + B0 + Bp5 + Bnp5
+  -WB*((1/(1+exp(.5 - B0)))*(1/(1+exp(.5 - .5 - Bp5)))*(1-1/(1+exp(.5 + .5 - Bnp5))) + (1/(1+exp(.5 - B0)))*(1/(1+exp(.5 + .5 - Bnp5)))*(1-1/(1+exp(.5 - .5 - Bp5))) + (1/(1+exp(.5 + .5 - Bnp5)))*(1/(1+exp(.5 - .5 - Bp5)))*(1-1/(1+exp(.5 - B0))) + (1/(1+exp(.5 - B0)))*(1/(1+exp(.5 - .5 - Bp5)))*(1/(1+exp(.5 + .5 - Bnp5)))) + B0 + Bp5 + Bnp5
 }
 
 #optim function minimizes 'obj'; c vector are starting values; lower is the
 #constraint; I choose a null gradient because it was easiest to get up and running
 optim(c(0.01,0.01,0.01),obj,gr=NULL,method = "L-BFGS-B", lower = c(0,0,0))
 
-X = - al + 1.930073       #these are shorthand variables for the exponents
-Y = .5 - al + 1.430073   #in the logistic CDFs; I don't use them in the function
-Z = -.5 - al + 0.000000         #but I've pasted in values here to check
+X = - al + 1.905965        #these are shorthand variables for the exponents
[…]

### 2015-12-10 constrained-optimization.r
add note to constrainted-optimization that beta is fixed at 1

@@ -1,5 +1,6 @@
 #optim function minimizes 'f'; c vector are starting values; lower is the
 #constraint; I choose a null gradient because it was easiest to get up and running
+#note that here the beta parameter is hard coded in as equal to 1
 
 h <- function(WB,al) {
   

### 2015-12-11 GS-extension.tex
add intuition for pos/neg alpha

@@
 \newcommand{\ga}{\gamma}
+\newcommand{\al}{\alpha}
 
@@
 \newpage
+\subsection{Intuition}
+\begin{itemize}
+	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
+		\[
+		  v(z) = \al - \beta z + a(z) - b(z) > 0
+		\]
+	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
+		\[
+		  \al - \beta z - b(z) < 0
+		\]
+
+		\begin{center}
+		or 
+		\end{center}
+		\[
+		  \beta z - \al + b(z) > 0
+		\]
+		\item If $\al > 0$, legislators on average are biased against B.
+			\begin{itemize}
+				\item If $\al < 0$, legislators on average are biased in favor of B.
+				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
+			\end{itemize}
+\end{itemize}
+
+\newpage
 \section{Some Comparative Statics}			
@@
 
+\newpage		
 \section{Notes from March}
-\newpage
 Notes from 3/16 Skype chat (Kristy and Sebastian)

### 2015-12-14 GS-extension.tex
add eqn # and label for cross partial in SOCs
fix details on one non-neg constraint case about pos vs. non-neg SOC

@@
 \]
-\[
+\begin{equation}
   W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X}\left(e^{-2Z} - 1 \right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
-\]
+	\label{eq:xpartial}
+\end{equation}
 
@@
 		\]
-		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is positive.
+		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is non-negative
 	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
@@
 
-  We need this determinant to be negative, that is
+  We need this determinant to be non-positive, that is
 		\[
-		  = \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} > \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 
+		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 
 		\]
 	  The right hand side is positive because it's a square.
+Moreover, it is strictly positive because $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ is strictly positive: examine Equation~\ref{eq:xpartial}.
+Since $Z < 0$ in the case under examination, Equation~\ref{eq:xpartial} must be strictly positive.
+(This strengthens us from the negative semi-definite condition condition that supplies only a weak inequality).
+
 		The left hand side must then be positive, and since we know that one term is positive from the previous principal minor result, the other must be positive as well.
-Thus both $b(0)$ and $b\left(\frac{1}{2}\right)$ must be positive.
+Thus both $X$ and $Y$ must be positive.
 \end{itemize}

### 2015-12-16 GS-extension.tex
create section for numerical results in GS-extension
fill in misc notes on numerical results

@@
 
+\newpage
 \section{Discrete Model}
-\newpage
 Discrete version (Conversation between Kristy and Frank, 3/27/15)
@@
 \newpage
+\subsection{Numerical Results}	
+For all of these, $\beta = 1$ and there are three legislators with $b\in\left\{-\frac{1}{2},0,\frac{1}{2}\right\}$.
+
+\vskip.2in
+For $\al = -1.5$	
+	\begin{tabular}{crrrrr}
+			            & -2 & -1.5 						& -1\\
+			up to WB=19	&	0	&		0					 &	0 \\		
+			only WB = 20   	&	0	&0	& just a little
+	\end{tabular}
+
+\vskip.2in
+For $\al = -1.3$	
+	\begin{tabular}{crrrrr}
+			            & -1.8 & -1.3 						& -0.8\\
+			up to WB=15	&	0	&		0					 &	0 \\		
+			WB = 16 to 20   	&	0	&0	& just a little
+	\end{tabular}
+
+\vskip.2in
+For $\al = -1.1$	
+	\begin{tabular}{crrrrr}
+			            & -1.6 & -1.1 						& -0.6\\
+			up to WB=13	&	0	&		0					 &	0 \\		
+			WB = 14 to 15  & 	0& 0 &	just a little	\\
+			WB = 16 to 20   &	0& some, always increasing &	some + .5	\\
+	\end{tabular}
+
+\vskip.2in
+For $\al = -0.9$	
+	\begin{tabular}{crrrrr}
+			            & -1.4 & -0.9 						& -0.4\\
+			up to WB=11	&	0	&		0					 &	0 \\		
+			WB = 12 to 13  & 	0& 0 &	just a little	\\
+			WB = 14 to 19   &	0& some, always increasing &	some + .5	\\
+			WB = 20 & some & some + .5 & some + 1
+	\end{tabular}
+
+\vskip.2in
+For $\al = -0.6$	
+	\begin{tabular}{crrrrr}
+			            & -1.1 & -0.6 						& -0.1\\
+			up to WB=8	&	0	&		0					 &	0 \\		
+			WB = 9 to 10  & 	0& some &	0	\\
+			WB = 11 to 14   &	0& some, always increasing &	some + .5	\\
+			WB = 15 to 20 & some & some + .5 & some + 1
+	\end{tabular}
+
+	\vskip.2in	
+		$\al = -0.6$ pattern holds to $\al = -0.2$
+
+\vskip.2in
+For $\al = -0.1$	
+	\begin{tabular}{crrrrr}
+			            & -0.6 & -0.1 						& 0.4\\
+			up to WB=7	&	0	&		0					 &	0 \\		
+			WB = 8   & 	0& some &	0	\\
+			WB = 9   &	some& some + .5&	0	\\
+			WB = 15 to 20 & some & some + .5 & some + 1
+	\end{tabular}
+
+	\vskip.2in	
+		$\al = -0.1$ pattern holds to $\al = 0.5$ at least
+
+\vskip.2in
+For $\al = 0.5$	
+	\begin{tabular}{crrrrr}
+			            & 0.0 & 0.5 						& 1.0\\
+			up to WB=8	&	0	&		0					 &	0 \\		
+			WB = 9 to 11  & 	$>1$& $>1+.5$ &	0	\\
+			WB = 12 to 20 & significant & significant + .5 & significant + 1
+	\end{tabular}
+
+\vskip.2in
+For $\al = 1.1$	
+	\begin{tabular}{crrrrr}
+			            & 0.6 & 1.1 						& 1.6\\
+			up to WB=13	&	0	&		0					 &	0 \\		
+			WB = 9 to 20  & 	$>2$& $>2+.5$ &	0
+	\end{tabular}
+
+\newpage
 \section{Some Comparative Statics}			

### 2015-12-16 GS-extension.tex
add a bit of intuition about see-saw
fill in central numerical example of al = 0

@@
 
+\vskip.2in
+Pattern more or less is to get the guy who is WHAT?
+\begin{itemize}
+	\item Imagine a see-saw; these guys are weights on the see-saw.
+\end{itemize}
+
 \newpage
@@
 
+		\vskip.5in
+Going to explore in-depth case of $\al = 0.0$	\\
+	\begin{tabular}{crrrrr}
+			            & -0.5 & 0.0 						& 0.5\\
+			up to WB=7	&	0	&		0					 &	0 \\		
+			WB = 8    & 	0&  some &	0	\\
+			WB = 9   & 	some & some + .5 &	0	\\
+			WB = 10 to 20 & some & some + .5 & some + 1
+	\end{tabular}
+
 \newpage

### 2015-12-17 GS-extension.tex
add focs and start of socs for one non-neg bribe case

@@
 \newpage
+\subsection{One Non-negative Bribe}
+When $\al = 0$ and $WB=8$, we find that $b\left(-\frac{1}{2}\right)$ and $b\left(\frac{1}{2}\right)$ are zero. Only $b(0)$ is positive.
+\begin{itemize}
+	\item Only the FOC for $X$ holds with equality (i.e. $\lambda_X = 0$)
+		\[
+			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+		\]
+	\item We know exactly what $Y$ and $Z$ will be since $b\left(-\frac{1}{2}\right)$ and $b\left(\frac{1}{2}\right)$ are zero. Given $WB$, we can solve for $X$ and then $b(0)$.
+	\item Looking at the SOC, when there are three inequality constraints and 2 bind, we only need a condition on the last principal minor of a suitably constructed bordered Hessian.
+		\begin{itemize}
+			\item It should be negative because $n=3$
+			\item It's a 5x5 matrix because there are two binding inequality constraints.
+		\end{itemize}
+		The SOCs when one non-negativity constraint binds; bordered Hessian is 5x5. \\
+		\begin{tabular}{ccccc}
+			0 & 0 & $\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_1}{\partial b\left(-0\right)}$ & $\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ \\
+			0 & 0 & $\frac{\partial g_3}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_3}{\partial b\left(-0\right)}$ & $\frac{\partial g_3}{\partial b\left(\frac{1}{2}\right)}$ \\
+			$\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_3}{\partial b\left(-\frac{1}{2}\right)}$& $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			$\frac{\partial g_1}{\partial b\left(0\right)}$ & $\frac{\partial g_3}{\partial b\left(-0\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			$\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial g_3}{\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular} \\
+
+\vskip.2in		
+Evaluating the constraint terms:\\
+\begin{tabular}{ccccc}
+			0 & 0 & -1 & 0 & 0 \\
+			0 & 0 & 0 & 0 & -1 \\
+			-1 & 0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			0 & 0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			0 & -1 &$\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular}
+
+		Solving for the determinant of this matrix:
+		\[
+		  (-1)\cdot 
+			\left|\begin{array}{cccc}
+				0 & 0 & 0 & -1\\
+				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right|
+		\]
+	\end{itemize}
+
+\newpage
 \subsection{Numerical Results}	

### 2015-12-31 GS-extension.tex
add notes on SOC for one non-neg bribe case and general conditions for SOCs

@@
 
+\vskip1in
+In general
+\begin{itemize}
+	\item $n$ is the number of choice variables ($n=3$ in my case for the three bribes)
+	\item If there are $k$ inequality constraints ($k=3$ in my case, for 3 non-negativity constraints)
+	\item And $g_1$ through $g_b$ are binding (i.e. $b$ is the number of bribes that are zero)
+	\item $m$ is the number of equality constraints (0 in my case)
+	\item Then there are restrictions on the last ($n-b+m$) minors
+		\begin{itemize}
+			\item If one bribe is zero, then need the last two $3-1 =2$ minors to alternate in sign with the last being $(-1)^n = (-1)^3 = -1 <0$, i.e. negative
+			\item If no bribes are zero, there are restrictions on the last three minors, but the matrix is 3x3 (no constraint rows)
+			\item If two bribes are binding, there is only a restriction on the last minor, but it's a 5x5 matrix.
+				\begin{itemize}
+					\item But can't wipe out $\frac{1}{W_B}$ using two FOCs because only one holds with equality
+				\end{itemize}
+		\end{itemize}
+	\item If all three non-negativity constraints bind, we know all bribes are zero. No restriction on SOC?
+\end{itemize}
+
 \newpage
@@
 			\end{array} \right|
+		=
+						  (-1)\cdot (-1) \cdot (-1)
+			\left|\begin{array}{ccc}
+				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2}\\
+			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
+			\end{array} \right| =
 		\]
+		\[
+		  (-1) \cdot (-1)
+			\left|\begin{array}{cc}	
+			0 & \frac{\partial^2 L}{\partial b(0)^2}\\
+			-1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
+			\end{array} \right| = 0 - (-1) \cdot \frac{\partial^2 L}{\partial b(0)^2} = \frac{\partial^2 L}{\partial b(0)^2}
+		\]
+		\item Thus we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$
+			\begin{itemize}
+				\item This boils down to $\left(e^{-X} - 1\right) < 0$
+				\item Implies $X > 0$
+				\item i.e. $-\al + b(0) > 0$ or $b(0) > \al$
+			\end{itemize}
+		\item \textbf{Why does $b(0)$ have to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$?}
+		\item Can write out SOC (just after equation 33) and FOC, sub together to get
+			\[
+			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
+			\]
+			Not sure what this means
 	\end{itemize}

### 2016-01-25 constrained-optimization.r
change rounding to 2 significant digits

@@ -11,12 +11,12 @@ f <- function(B,WB,al) {
   -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5)))*(1-1/(1+exp(al + .5 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bnp5)))*(1-1/(1+exp(al - .5 - Bp5))) + (1/(1+exp(al + .5 - Bnp5)))*(1/(1+exp(al - .5 - Bp5)))*(1-1/(1+exp(al - B0))) + (1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5)))*(1/(1+exp(al + .5 - Bnp5)))) + B0 + Bp5 + Bnp5
 }   
 
-#o <- optim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0))
-o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
+o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
+#o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
 
-X = round(- al + o$par[2], digits = 1)       #B0   these are shorthand variables for the exponents
-Y = round(.5 - al + o$par[3], digits = 1)    #Bp5  in the logistic CDFs; I don't use them in the function
-Z = round(-.5 - al + o$par[1], digits=1)   #Bnp5 but I've pasted in values here to check
+X = round(- al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
+Y = round(.5 - al + o$par[3], digits = 2)    #Bp5  in the logistic CDFs; I don't use them in the function
+Z = round(-.5 - al + o$par[1], digits=2)   #Bnp5 but I've pasted in values here to check
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
[…]

### 2016-01-25 GS-extension.tex
add guidance at top of numerical results
correct wrong assumption about one non-neg bribe case

@@
 			\end{itemize}
-		\item \textbf{Why does $b(0)$ have to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$?}
+		\item It is NOT the case that $b(0)$ has to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$. In fact, it seems in numerical examples that this does \textit{not} happen.
+			\begin{itemize}
+				\item However, I do see that this existence of the one non-negative bribe is not common. It exists for $\al = 0$ and WB = 8, but goes away as soon as $\al = 0.1$ or WB = 9.
+			\end{itemize}
 		\item Can write out SOC (just after equation 33) and FOC, sub together to get
@@
 For all of these, $\beta = 1$ and there are three legislators with $b\in\left\{-\frac{1}{2},0,\frac{1}{2}\right\}$.
+\begin{itemize}
+	\item Below, the column headings are $v(z)$ before the bribe.
+	\item That is, from left to right, $-Z,-Y,-X$.
+\end{itemize}
 

### 2016-01-26 GS-extension.tex
explain how to solve for values of bribes in 2 nnb case
add intuition for knife-edge in 1 NNB case

@@
 			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+			\label{eq:base}
 		\end{equation}
@@
 \end{itemize}
+
+Once we know that both $X=Y>0$ (or $X=Z>0$), go back to one of the equations like \ref{eq:base} and substitute for one of the variables.
+Given that the third equals zero, for a particular value of $\left(\alpha,W_B\right)$, we can solve for the two relevant bribes.
 
@@
 			\begin{itemize}
-				\item However, I do see that this existence of the one non-negative bribe is not common. It exists for $\al = 0$ and WB = 8, but goes away as soon as $\al = 0.1$ or WB = 9.
+				\item However, I do see that this existence of the one non-negative bribe (NNB) is not common. It exists for $\al = 0$ and WB = 8, but goes away as soon as $\al = 0.1$ or $W_B$ = 9.
+				\item In both cases, I can see that changing the parameter would push the value of $b(0)$ over $0.5$, making $X > Y$. This is when the solution switches to 2 NNB's.
 			\end{itemize}

### 2016-01-27 GS-extension.tex
add conjecture for what drives case of 1 NNB

@@
 				\item In both cases, I can see that changing the parameter would push the value of $b(0)$ over $0.5$, making $X > Y$. This is when the solution switches to 2 NNB's.
+				\item {\color{blue} CONJECTURE}: Group B chooses 1 NNB until it would be large enough to make $X > Y$ (when $\al \approx 0$) or $Z > Y$ (when $\al$ large and negative), then switch to 2 NBB
+					\begin{itemize}
+						\item {\color{blue} This is not strictly true around $-0.7$}
+						\item When $\al$ is large and positive, go straight from 0 NNB to 2 NNB
+					\end{itemize}
 			\end{itemize}

### 2016-01-28 GS-extension.tex
add intuiton for what positive X,Y,Z means
add subsection on 3 NNBs

@@
 			\end{itemize}
+		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,\frac{1}{2},$ or $-\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
 \end{itemize}
@@
 			Not sure what this means
+	\end{itemize}
+
+\newpage
+\subsection{All Three Bribes are Non-negative}
+In many cases all three bribes are non-negative. Here are very loose results
+\begin{itemize}
+	\item I always observe that $X=Y=Z$. I think it's easy to show this analytically.
+	\item From the FOCs, when $X$ and $Y$ are non-negative, it can be shown that a set of inequalities just below Equations~\ref{eq:1} and \ref{eq:2} must hold.
+	\item The SOCs when 0 non-negativity constraints bind are on the 3x3 matrix of second derivatives. There are three conditions:
+		\[
+		  \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \left\{\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right\} \leq 0
+		\]
+		\[
+		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \geq 0
+		\]
+		\[
+		  \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} \leq 0
+		\]
+		The last one says that $Y$ must be non-negative. The first and second together say that $Z$ must be non-negative.
+	\item $Y$ non-negative combined with the inequalities below Equations ~\ref{eq:1} and \ref{eq:2} tells us that $X=Y > 0$.
+	\item Similar logic that leads to those inequalities can be used to derive analagous inequalities for $X$ and $Z$ (or $Y$ and $Z$). Then $Z$ non-negative tells us $Z=Y>0$ so that $X=Y=Z >0$.
+\end{itemize}
+
+\vskip.3in
+Now as to when this case occurs
+\begin{itemize}
+	\item When $X=Z$ (the two left-most legislators), bribe to $\frac{1}{2}$ is added in before $X$ would move to the right of $Y$, i.e. when $X \rightarrow 0.5$.
+	\item This is NOT the case when $X$ and $Y$ are the two non-negative bribes. They can get very large before the left-most legislator is bribed.
 \end{itemize}

### 2016-02-03 constrained-optimization.r
modify code to output value and winning probability

@@ -20,13 +20,14 @@ Z = round(-.5 - al + o$par[1], digits=2)   #Bnp5 but I've pasted in values here 
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
-out <- list("solns" = o$par[1:3], "pos" = pos, "objMax" = -o$value, "a" = al, "wb" = WB)
+win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
+out <- list("solns" = o$par[1:3], "pos" = pos, "objMax" = -o$value, "a" = al, "wb" = WB, "winProb" = win)
 return(out)
 }
 
 # Create a dataframe of parameter values
-wb_vector <- 7:15 
-a_vector <- seq(-0.2, 0.2, 0.1)
+wb_vector <- 0:20 
+a_vector <- seq(0.0, 0.0, 0.1)
 params <- expand.grid("wb" = wb_vector, "a" = a_vector)
 
 # Use "Map" to evaluate the "h" function at each pair of parameter values
@@ -36,8 +37,14 @@ results <- Map(h, al = params$a, WB = params$wb)
 # WOULD LIKE TO HAVE BOTH SOLUTIONS AND POSITIONS IN OUTPUT VECTOR BUT DON'T KNOW HOW
 solns <- lapply(seq_along(results), function(x) results[[x]]$solns)
 netpos <- lapply(seq_along(results), function(x) results[[x]]$pos)
+val <- lapply(seq_along(results), function(x) results[[x]]$objMax)
+winProb <- lapply(seq_along(results), function(x) results[[x]]$winProb)
 solns <- do.call("rbind", solns)
 netpos <- do.call("rbind", netpos)
+val <- do.call("rbind", val)
+winProb <- do.call("rbind", winProb)
 colnames(solns) <- c("person1", "person2", "person3")
 colnames(netpos) <- c("Z", "X", "Y")
-solns <- cbind(params, solns,netpos)
+colnames(val) <- c("value")
+colnames(winProb) <- c("winProb")
+solns <- cbind(params, solns,netpos,val,winProb)

### 2016-02-03 constrained-optimization.r
rename legislator columns

@@ -43,7 +43,7 @@ solns <- do.call("rbind", solns)
 netpos <- do.call("rbind", netpos)
 val <- do.call("rbind", val)
 winProb <- do.call("rbind", winProb)
-colnames(solns) <- c("person1", "person2", "person3")
+colnames(solns) <- c("left", "middle", "right")
 colnames(netpos) <- c("Z", "X", "Y")
 colnames(val) <- c("value")
 colnames(winProb) <- c("winProb")

### 2016-02-03 constrained-optimization.r
rename legislator columns again

@@ -43,7 +43,7 @@ solns <- do.call("rbind", solns)
 netpos <- do.call("rbind", netpos)
 val <- do.call("rbind", val)
 winProb <- do.call("rbind", winProb)
-colnames(solns) <- c("left", "middle", "right")
+colnames(solns) <- c("friend", "middle", "foe")
 colnames(netpos) <- c("Z", "X", "Y")
 colnames(val) <- c("value")
 colnames(winProb) <- c("winProb")

### 2016-02-03 GS-extension.tex
add obj fcn in terms of logit
add intuition on 0 to 1 to 2 to 3, further questions

@@
 					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+				\end{multline}
+			Substituting from the definition of $X$ but substituting Logit for Probit and using the shorthand notation on the top of page~\pageref{page:sh},
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
+					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
+					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
+					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
 					\label{eq:obj}
 				\end{multline}
-			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is
+
+			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is (in terms of probit)
 				\begin{multline}
@@
 			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
-			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
 		\end{enumerate}
@@
 
+\vskip1in
+The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
+\begin{itemize}
+	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
+	\item \textbf{Next question: How general is this result?
+That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
+My conjecture is that it leans on having an interior single mode}
+\end{itemize}
+
 \newpage

### 2016-02-04 pdf-graph.R
add R program to graph pdfs

@@ -1,0 +1,15 @@
+#this code plots the three PDFs around the zero line, 
+#to the right of which the legislator votes for the status quo (B's favorite option)
+
+s = -.0                          #scale parameter to shift each pdf; add negative to alpha value
+lpdf0 <- dlogis(v0, location = 0+s, scale = 1, log = FALSE)      #middle / X
+lpdfnp5 <- dlogis(v0, location = -0.5+s, scale = 1, log = FALSE) #friend / left / Z
+lpdfp5 <- dlogis(v0, location = 0.5+s, scale = 1, log = FALSE)   #foe / right / Y
+
+plot(v0,lpdf0,col=2, type="l")   #col=2 is red
+par(new=T)                       #holds plot for next series
+plot(v0,lpdfnp5,col=3, type="l") #col=3 is green
+par(new=T)
+plot(v0,lpdfp5,col=4, type="l")  #col=4 is blue
+par(new=T)
+abline(v=0)                      #draws vertical black line

### 2016-02-04 pdf-graph.R
re-add and smooth x-axis vector

@@ -1,7 +1,8 @@
 #this code plots the three PDFs around the zero line, 
 #to the right of which the legislator votes for the status quo (B's favorite option)
+v0 <- seq(-1.5, 1.5, 0.1)
 
-s = -.0                          #scale parameter to shift each pdf; add negative to alpha value
+s = -.1                          #scale parameter to shift each pdf; add negative to alpha value
 lpdf0 <- dlogis(v0, location = 0+s, scale = 1, log = FALSE)      #middle / X
 lpdfnp5 <- dlogis(v0, location = -0.5+s, scale = 1, log = FALSE) #friend / left / Z
 lpdfp5 <- dlogis(v0, location = 0.5+s, scale = 1, log = FALSE)   #foe / right / Y

### 2016-02-04 GS-extension.tex
add intuition for which legislator is first lobbied

@@
 \begin{itemize}
-	\item Imagine a see-saw; these guys are weights on the see-saw.
+	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
+	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
 \end{itemize}

### 2016-02-05 GS-extension.tex
add X,Y,Z defns to intuition page

@@
 
-\vskip.2in
+\vskip.1in
+Recall:
+		\begin{enumerate}
+			\item $X = -\alpha + b(0)$ 
+			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
+		\end{enumerate}
+
+\vskip.1in
 Pattern more or less is to get the guy who is WHAT?
@@
 
-\vskip1in
+\vskip.1in
 The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point

### 2016-02-05 pdf-graph.R
add calculations for one NNB; improve comments

@@ -1,16 +1,39 @@
-#this code plots the three PDFs around the zero line, 
+#this code plots the PDF for the preferences of each of the three legislators around the zero line, 
 #to the right of which the legislator votes for the status quo (B's favorite option)
-v0 <- seq(-1.5, 1.5, 0.1)
+v0 <- seq(-1.5, 1.5, 0.1) #x-axis, preference-space
 
-s = -.1                          #scale parameter to shift each pdf; add negative to alpha value
+s = .3                          #scale parameter to shift each pdf; this is negative of alpha value
 lpdf0 <- dlogis(v0, location = 0+s, scale = 1, log = FALSE)      #middle / X
-lpdfnp5 <- dlogis(v0, location = -0.5+s, scale = 1, log = FALSE) #friend / left / Z
-lpdfp5 <- dlogis(v0, location = 0.5+s, scale = 1, log = FALSE)   #foe / right / Y
+lpdfnp5 <- dlogis(v0, location = -0.5+s, scale = 1, log = FALSE) #foe / left / Z
+lpdfp5 <- dlogis(v0, location = 0.5+s, scale = 1, log = FALSE)   #friend / right / Y
 
-plot(v0,lpdf0,col=2, type="l")   #col=2 is red
+plot(v0,lpdf0,col=2, type="l",ylab="")   #col=2 is red for middle legislator
 par(new=T)                       #holds plot for next series
-plot(v0,lpdfnp5,col=3, type="l") #col=3 is green
+plot(v0,lpdfnp5,col=3, type="l",yaxt="n",ylab="") #col=3 is green for most friendly legislator
 par(new=T)
-plot(v0,lpdfp5,col=4, type="l")  #col=4 is blue
+plot(v0,lpdfp5,col=4, type="l",yaxt="n",ylab="")  #col=4 is blue for most opposed legislator
 par(new=T)
 abline(v=0)                      #draws vertical black line
+
+
+#Calculate potential bribe values for WB=8, al=-.3
+WB=8
+X=s
+Y=0.5 +s
+Z=-0.5+s
+
[…]

### 2016-02-05 constrained-optimization.r
rename columns yet again; pretty sure they're right this time!

@@ -43,7 +43,7 @@ solns <- do.call("rbind", solns)
 netpos <- do.call("rbind", netpos)
 val <- do.call("rbind", val)
 winProb <- do.call("rbind", winProb)
-colnames(solns) <- c("friend", "middle", "foe")
+colnames(solns) <- c("foe", "middle", "friend")
 colnames(netpos) <- c("Z", "X", "Y")
 colnames(val) <- c("value")
 colnames(winProb) <- c("winProb")

### 2016-02-06 pdf-graph.R
fix comments for friendly/opposed legislator

@@ -7,13 +7,13 @@ lpdf0 <- dlogis(v0, location = 0+s, scale = 1, log = FALSE)      #middle / X
 lpdfnp5 <- dlogis(v0, location = -0.5+s, scale = 1, log = FALSE) #foe / left / Z
 lpdfp5 <- dlogis(v0, location = 0.5+s, scale = 1, log = FALSE)   #friend / right / Y
 
-plot(v0,lpdf0,col=2, type="l",ylab="")   #col=2 is red for middle legislator
-par(new=T)                       #holds plot for next series
-plot(v0,lpdfnp5,col=3, type="l",yaxt="n",ylab="") #col=3 is green for most friendly legislator
+plot(v0,lpdf0,col=2, type="l",ylab="")            #col=2 is red for middle legislator
+par(new=T)                                        #holds plot for next series
+plot(v0,lpdfnp5,col=3, type="l",yaxt="n",ylab="") #col=3 is green for most opposed legislator
 par(new=T)
-plot(v0,lpdfp5,col=4, type="l",yaxt="n",ylab="")  #col=4 is blue for most opposed legislator
+plot(v0,lpdfp5,col=4, type="l",yaxt="n",ylab="")  #col=4 is blue for most friendly legislator
 par(new=T)
-abline(v=0)                      #draws vertical black line
+abline(v=0)                                       #draws vertical black line
 
 
 #Calculate potential bribe values for WB=8, al=-.3

### 2016-02-06 constrained-optimization.r
simplified objective function

@@ -8,7 +8,7 @@ f <- function(B,WB,al) {
   Bnp5 <- B[1]
   B0 <- B[2]
   Bp5 <- B[3]
-  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5)))*(1-1/(1+exp(al + .5 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bnp5)))*(1-1/(1+exp(al - .5 - Bp5))) + (1/(1+exp(al + .5 - Bnp5)))*(1/(1+exp(al - .5 - Bp5)))*(1-1/(1+exp(al - B0))) + (1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5)))*(1/(1+exp(al + .5 - Bnp5)))) + B0 + Bp5 + Bnp5
+  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bnp5))) + (1/(1+exp(al + .5 - Bnp5)))*(1/(1+exp(al - .5 - Bp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5)))*(1/(1+exp(al + .5 - Bnp5)))) + B0 + Bp5 + Bnp5
 }   
 
 o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))

### 2016-02-06 pdf-graph.R
add code to pdf-graph to explore shape of foc and obj fcn

@@ -2,7 +2,7 @@
 #to the right of which the legislator votes for the status quo (B's favorite option)
 v0 <- seq(-1.5, 1.5, 0.1) #x-axis, preference-space
 
-s = .3                          #scale parameter to shift each pdf; this is negative of alpha value
+s = 1                          #scale parameter to shift each pdf; this is negative of alpha value
 lpdf0 <- dlogis(v0, location = 0+s, scale = 1, log = FALSE)      #middle / X
 lpdfnp5 <- dlogis(v0, location = -0.5+s, scale = 1, log = FALSE) #foe / left / Z
 lpdfp5 <- dlogis(v0, location = 0.5+s, scale = 1, log = FALSE)   #friend / right / Y
@@ -17,7 +17,7 @@ abline(v=0)                                       #draws vertical black line
 
 
 #Calculate potential bribe values for WB=8, al=-.3
-WB=8
+WB=13
 X=s
 Y=0.5 +s
 Z=-0.5+s
@@ -26,7 +26,7 @@ Z=-0.5+s
 fx <- function(x) ((exp(-Z)+exp(-Y))*exp(-x))/((1+exp(-Z))*(1+exp(-Y))*(1+exp(-x))^2)-1/8
 x <-uniroot(fx, c(0,5))
 fz <- function(z) ((exp(-X)+exp(-Y))*exp(-z))/((1+exp(-X))*(1+exp(-Y))*(1+exp(-z))^2)-1/8
-z <-uniroot(fz, c(-0.1,.2))
+z <-uniroot(fz, c(-0,1))
 fy <- function(y) ((exp(-X)+exp(-Z))*exp(-y))/((1+exp(-X))*(1+exp(-Z))*(1+exp(-y))^2)-1/8
 y <-uniroot(fy, c(0,5))
 
@@ -37,3 +37,26 @@ valx <- WB*((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*
 Y=y$root #redefine Y to be inclusive of optimal bribe
 #compute value when y is only NNB
[…]

### 2016-02-08 pdf-graph.R
fix input to final plot command in pdf-graph

@@ -59,4 +59,4 @@ plot(Z,valz)
 z = seq(0.2,.3,.05)
 #test = ((exp(-Z)+exp(-Y))*exp(-x))/((1+exp(-Z))*(1+exp(-Y))*(1+exp(-x))^2)-1/8
 z_foc = ((exp(-X)+exp(-Y))*exp(-z-.5))/((1+exp(-X))*(1+exp(-Y))*(1+exp(-z-.5))^2) -1/13
-plot(z,test2)
+plot(z,z_foc)

### 2016-02-08 pdf-graph.R
replace hard-coding of WB in pdf-graph, add code for graphing foc, obj fcn of X

@@ -23,12 +23,12 @@ Y=0.5 +s
 Z=-0.5+s
 
 #solve for net position if each legislator was the only one with a NNB
-fx <- function(x) ((exp(-Z)+exp(-Y))*exp(-x))/((1+exp(-Z))*(1+exp(-Y))*(1+exp(-x))^2)-1/8
-x <-uniroot(fx, c(0,5))
-fz <- function(z) ((exp(-X)+exp(-Y))*exp(-z))/((1+exp(-X))*(1+exp(-Y))*(1+exp(-z))^2)-1/8
-z <-uniroot(fz, c(-0,1))
-fy <- function(y) ((exp(-X)+exp(-Z))*exp(-y))/((1+exp(-X))*(1+exp(-Z))*(1+exp(-y))^2)-1/8
-y <-uniroot(fy, c(0,5))
+fx <- function(x) ((exp(-Z)+exp(-Y))*exp(-x))/((1+exp(-Z))*(1+exp(-Y))*(1+exp(-x))^2)-1/WB
+x <-uniroot(fx, c(0,1.5))
+fz <- function(z) ((exp(-X)+exp(-Y))*exp(-z))/((1+exp(-X))*(1+exp(-Y))*(1+exp(-z))^2)-1/WB
+z <-uniroot(fz, c(0,2))
+fy <- function(y) ((exp(-X)+exp(-Z))*exp(-y))/((1+exp(-X))*(1+exp(-Z))*(1+exp(-y))^2)-1/WB
+y <-uniroot(fy, c(0,2))
 
 X=x$root #redefine X to be inclusive of optimal bribe
 #compute value when x is only NNB
@@ -49,14 +49,20 @@ Y=0.5 +s
 Z=-0.5+s
 
 #examine shape of optimal value function; remember to shift value of Z
-Z = seq(0,.5,.05)
-#valx <- WB*((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z))))- (X -s)
[…]

### 2016-02-08 GS-extension.tex
finally solved weird case at alpha = -.75

@@
 			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
-			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$ 
 		\end{enumerate}
@@
 					\begin{itemize}
-						\item {\color{blue} This is not strictly true around $-0.7$}
+						\item This is not strictly true around $-0.7$: but I can see for $\al = .75,$ when $W_B=10$ it's only $X$, then for $W_B=11$ it's only $Z$.
+This is because the non-negativity constraint for $Z$ binds at $W_B =10$, as it does for $Y$.
+$X$ is the only variable there for which it does not bind, and it is worthwhile shifting the middle legislator just a bit.
 						\item When $\al$ is large and positive, go straight from 0 NNB to 2 NNB

### 2016-02-08 old-draft.tex
add copy of draft03272014 from Phase_I as old-draft

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\linespread{1.5}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}
\usepackage[pdftex]{graphicx}
%\usepackage{pdfpages}

%\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont,pdfsync}
%\usepackage[hang,flushmargin]{footmisc}%unindents footnotes

% disables chapter, section and subsection numbering
%\setcounter{secnumdepth}{-1}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}
\usepackage[hang,flushmargin]{footmisc}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

\begin{document}
\title{\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY}
\author{Kristy Buzard\thanks{Syracuse University, Economics Department, 110 Eggers Hall, Syracuse, NY 13244. Ph: 315-443-4079. Fax: 315-443-3717. Email: kbuzard@syr.edu. http://faculty.maxwell.syr.edu/kbuzard.} \and Sebastian Saiegh\thanks{University of California, San Diego, Department of Political Science, Social Sciences Building 365, 9500 Gilman Drive, La Jolla, CA 92093. Ph: 858-534-7237. Fax: 858-534-7130. Email: ssaiegh@ucsd.edu. http://pages.ucsd.edu/~ssaiegh/.}} 
\date{\vskip-.1in \today}
\maketitle

%\begin{center} {\bf Abstract} \end{center}

%\begin{quote}
%{\small This paper

%\textit{JEL classification:} D72, D80 \\
%\textit{Keywords:} lobbying, political economy, legislatures, uncertainty}
%\end{quote}

\bigskip
\section{Introduction}
In democratic countries, legislatures are the authoritative source of statutory law. Saiegh (2011) identifies two major factors that shape lawmaking: the unpredictability of legislators' voting behavior, and whether buying legislative votes is a feasible option. The source of the uncertainty is the existence of cross-pressured legislators: in deciding how to vote, lawmakers consider a variety of influences, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership. Therefore, legislators' voting behavior can seldom be perfectly anticipated.

Campaign contribution and lobbying data show that lobbies do not expend equal efforts to influence all legislators; instead, they strategically choose to engage with only some members of the legislature. The uncertainty surrounding legislator's decision-making is likely to be a key decision variable in this calculus. In order to study how uncertainty affects the incentives for lobbying and the associated prospects for the passage of legislative actions, we must first quantify this uncertainty. We turn to this task first, adapting a standard technique from the political science literature.

This project will contribute to our understanding of a particular type of political uncertainty---that surrounding statutory lawmaking. We will introduce an innovative methodology for quantifying cross-industry political uncertainty, use these measures to deepen our understanding of lobbying behavior, and make the data available for future use in a wide range of applications.

\subsection{Related Literature}
%The foundations of this work rest

This work relates to the canonical studies on endogenous regulation (cf. Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)), as well as the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et. al. (2005), Dal Bo (2007)).

Also related is Le Breton and Salanie (2003), which studies lobbying when the lobby is uncertain about the preferences of a unitary decision maker. Le Breton and Zaporozhets (2007) go a step further and replace the unitary decision maker with a legislature with multiple actors.

%I will begin by ... Section~\ref{sec:main} then ... In Section~ \ref{sec:example}, ... Section~\ref{sec:dis} explores .... Several extensions of the model are explored in Section~\ref{sec:ext} and Section~\ref{sec:concl} concludes.

\section{The Model}
\label{sec:model}

Formal model coming soon.

%If we're going to do an empirical implementation of $\ga$ below, model needs to start with a basic understanding of uncertainty, run through lobbying response to it, up through aggregation into $\ga$ and how lobbying behavior turns into a ``yea'' vote total.

\section{Estimating Legislative Uncertainty}
\label{sec:main}

To understand how the presence and magnitude of uncertainty faced by a special interest group affects its lobbying behavior and the policy outcomes it is able to achieve, we must first quantify the uncertainty inherent in statutory lawmaking as, to the best of our knowledge, no such measures exist at the interest-group level. In order to do so, we will construct measures adapted from a well-accepted methodology in political science.

Recorded votes in legislatures (roll call data) are the most commonly used data source to measure politicians' spatial preferences. A well-established strategy is to use statistical techniques to represent patterns of legislative voting. The intuition behind these statistical models is that each roll call presents each legislator with a choice between a ``yea'' and a ``nay'' position. Legislators are presumed to vote for the position most similar to their own ideal policy position. As Clinton et al. (2004) note, it is possible to use Bayesian Markov chain simulation statistical methods to generate these preference estimates. This approach treats the unknown ideal points, bill parameters and legislators' utilities as random variables and condition upon the observed roll call data. The strategy is to impute values to these variables and estimate by regression the ideal points and bill parameters. The MCMC algorithm repeatedly performs these imputations and regressions and generates a large number of samples from the posterior density of the model parameters. Using this estimation procedure, we obtain summary statistics used for inference: legislators' mean and median ideal points as well as their 95$\%$ posterior confidence intervals. The latter are of particular interest to us, as we can use them to gauge the unpredictability of each legislator's voting behavior.

Legislators' ideal points do not necessarily have to be estimated using all the recorded votes cast by a legislature. Instead, one can use subsets of roll calls to establish a legislator's stance vis-a-vis a particular policy issue (Poole 2005). We will thus use subsets of roll call votes to estimate how friendly or unfriendly each legislator is with respect to a certain industry, as well as the unpredictability of his/her voting behavior when matters affecting that industry are considered.

These ``report cards'' will be built in the spirit of ADA scores. Americans for Democratic Action (ADA) identifies key policy issues, and tracks how members of Congress vote on these issues. Their annual report card gives each legislator a rating from 0, meaning complete disagreement with ADA policies (conservative), to 100, meaning complete agreement with ADA policies (liberal). To be consistent with the standard Bayesian methodology, our measures will label a legislator who is indifferent to a particular interest group as having an ideal point of 0, who opposes the interest group as having a negative ideal point, and who supports the group as having a positive ideal point.

To identify the relevant subset of roll calls for each industry, we rely on bill position determinations from \url{http://maplight.org}. This is a list, for each interest group, of the bills and amendments it supported or opposed beginning with the 110th Congress and continuously updated to the present. The determinations are made from public records such as Congressional hearing testimony, news databases, and member organizations' websites.\footnote{See \url{http://maplight.org/us-congress/guide/data/support-opposition} for details.} Groups are classified according to the Center for Responsive Politics's ``Category Code'' (\textit{catcode} for short) \footnote{See \url{https://www.opensecrets.org/resources/ftm/ch12p1.php} and \url{https://www.opensecrets.org/downloads/crp/CRP_Categories.txt}.}.

Voting data are for the U.S. House of Representatives for the 110th through 113th Congress and come from Vote View, a website maintained by Professor Keith Poole (\url{http://voteview.com}). Details on each legislative proposal are available electronically through Thomas (\url{http://thomas.loc.gov}) and the sites of the House and Senate registrars.

We analyze these votes using the Bayesian technique of Clinton et al. (2004) to capture each legislator's proximity to each group's interests, and to recover measures of uncertainty (the standard deviation of the posterior distribution) for each of those given groups.

We begin by estimating ideal points for all bills. Here we use uninformative priors and the standard identifying assumptions that ideal points have mean zero and unit variance.

We then estimate ideal points for subsets of bills: one subset for each interest group that includes all those actions in the U.S. House of Representatives on which that interest group took a public position. Here, we maintain the identifying assumption that ideal points have mean zero and unit variance and the uninformative variance for the prior distribution. We specify the vector of means for each prior distribution to be the ideal points estimated for the entire sample of bills.\footnote{This approach dramatically improves efficiency of the estimating algorithm and is justified by the observation that, with uninformative priors, the correlations between full-sample means and interest-group means are in the neighborhood of 85-90$\%$.}

This procedure produces an ideal point and standard deviation for each member of the House of Representatives for each special interest group. The ideal point can be interpreted as a measure of how supportive a particular politician is of the interest group's agenda \textit{on average}, while the standard deviation is an indication of how predictable his/her support or opposition is.

Aggregating these individual measures across the 112th Congress will give us our central measure of political uncertainty by industry. We expect this data to have a wide array of applications beyond our own.

\subsection{Alternative Measure of Uncertainty}
[This is an aside, but I would very much like your thoughts on it.]

This is a related, but alternative, measure of uncertainty that my co-author has proposed. We have not implemented it broadly yet, but it's from here that he got the idea to use the ideal points from the full sample as the priors for the interest-group samples. So in a sense, what we're doing now is a way to marry this alternative approach with the traditional Bayesian approach with completely uninformative priors.

Here is the idea: one way of framing the uncertainty we want to measure is to ask how well a lobbyist would do when he/she tries to predict how someone would vote. So, instead of using the standard deviation of the estimated ideal points, we could do the following:

\begin{enumerate}
	\item Calculate each legislator's ideal point using the full sample of roll call votes.
	\item Calculate each legislator's ideal point using the roll call votes on which an interest group took a position.
	\item Regress the ``interest group'' ideal point on the ``general'' ideal point.
\end{enumerate}

If a legislator is predictable in a specific policy area, then the residual should be close to 0; otherwise, he/she is more unpredictable. Figure~\ref{fig:br} plots the residuals (in absolute value) in the y-axis, as a function of their "general" ideology for commercial banks. For commercial banks, the $R^2$ in this regression was $0.92$.

\begin{figure}
\begin{center}
\includegraphics[height=4in, width=5in]{residuals.png}
\end{center}
\caption{``Residuals'' Approach\label{fig:br}}
\end{figure}

One advantage of this measure of uncertainty is that it is orthogonal to ideology. Note that the measure based on the standard errors of the estimates is not: it is clear that ideologically more extreme legislators have higher uncertainty (see Figure\ref{fig:six} below). These residuals seem to be uncorrelated with ideology.

%\subsection{Break Decision}
%\begin{figure}
%\begin{center}
%\includegraphics[height=4in, width=5in]{brprob2.jpg}
%\end{center}
%\caption{Probability Trade Agreement will be Broken\label{fig:br}}
%\end{figure}

\subsection{Uncertainty for Select Interest Groups}
\label{sec:select}
Do distinct interest groups face varying levels of uncertainty? Preliminary evidence shows that they do. Summary statistics for our measures of ideal points and the uncertainty surrounding them for six interest groups---manufacturing unions, commercial banks, the dairy industry, software firms, computer software firms, and the oil and gas industry---as well as the total docket of bills for the 112th Congress are given in the Appendix.

The first pattern that emerges is the the mean level of uncertainty is strongly correlated with the number of bills on which a group took a position. For the full universe of bills in the 112th Congress---over 1600 bills---the mean uncertainty is 0.04. For the Oil and Gas industry, which took a position on 96 bills, mean uncertainty is 0.19. Manufucturing Unions took a position on 90 bills and had a mean uncertainty of 0.161, and from here the relationship becomes monotonic: Commercial Banks with 65 positions has mean uncertainty of 0.206; Computer Software with 44 positions has mean uncertainty of 0.22; Real Estate with 27 positions has mean uncertainty of 0.286; and the Dairy industry with 23 positions has mean uncertainty of 0.29.

\begin{figure}
\begin{center}
\includegraphics[height=5.5in, width=6.5in]{densities.png}
\end{center}
\caption{Distribution of Uncertainty by Industry\label{fig:den}}
\end{figure}

Figure~\ref{fig:den} helps to visualize the data underlying this pattern. We will generate estimates for several hundred more interest groups to see if this pattern holds up---or, rather, how strongly it holds as it seems unlikely to disappear altogether. The fundamental question is whether we should view the increase in aggregate uncertainty that comes with a reduction in the number of votes that are observed as purely a statistical phenomenon, purely a real phenomenon confronted by special interests in their decision making, or some mixture of the two.

One interesting piece of initial evidence we have is that when we added the votes from the 110th and 111th Congress to the banking data, the range of standard deviations and the average did not change much. This is an exercise we will repeat, as we can take advantage of data from the 110th through the first half of the 113th Congresses to enlarge our sample size and in some cases in the later analysis break up the timing (perhaps, for instance, generating uncertainty measures from the first two Congresses and using them to predict contributions in the second two).

What is clear from Figure~\ref{fig:six} is that the mean level of uncertainty hides differing underlying distributions: the majority of banking interests' uncertainty appears to come from its supporters, whereas for manufacturing unions, the opposition in more fickle.\footnote{Note that all ideal points are scaled so that legislators who generally support the interest group have positive ideal points, while those who generally oppose the group have negative ideal points. For the full set of bills, negative ideal points are associated with left/liberal/Democratic positions and positive ideal points are associated with right/conservative/Republican stances on bills.} Much more than just the first moment of the distribution is of interest.

\begin{figure}
\begin{center}
\includegraphics[height=6.5in, width=6.5in]{six.pdf}
\end{center}
\caption{Distribution of Uncertainty by Industry\label{fig:six}}
\end{figure}

\section{(Plans for) Statistical Analysis}
\label{sec:dis}

Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we next turn to efforts to understand how the uncertainty surrounding statutory lawmaking is related to political contributions and voting behavior of legislators. Our units of analysis are the same interest groups defined by the Center for Responsive Politics with those interest groups' positions on bills identified by \url{http://maplight.org} (as explained above).

We will use political contributions data from the Center for Responsive Politics, as it uses the employment data that must be provided with all contributions over $\$$200 to classify contributions according to the donor's likely special interest affiliation. As these are the same codes used by Maplight to identify special interest groups' positions on bills, the contribution data cleanly matches the uncertainty measures derived from the positions these groups take on various pieces of legislation.

We will use both standard parametric and non-parametric techniques such as density estimation to explore the relationships between lobbying behavior, contributions and uncertainty. We have shown above that interest groups face differing amounts of uncertainty; here, we ask how those patterns relate to the lobbying strategies they employ.

Preliminary data analysis shows a very interesting relationship between uncertainty and lobbying expenditure across legislators at the aggregate level. That is, before the data is disaggregated by special interest group, we see an inverted U relationship between uncertainty and campaign contributions: legislators who are either very predictable or very unpredictable receive less, while those with an intermediate level of uncertainty are the target of the largest amounts of campaign contributions. We expect that additional important patterns will emerge when the data is disaggregated by industry.

For the purposes of using this work to inform further studies of the policy-making process, we are interested in not only how interest groups target individuals, but also how a lobby's overall strategy interacts with the uncertainty it faces to translate into political support differentially across interest groups. Thus we want to predict the ``yea'' vote totals on each bill as a function of lobbying effort, uncertainty, and political and economic controls tailored to the industry.

We will do this with a range of flexible parametric techniques in order to be reasonably confident that we have uncovered the true shape of this empirical implementation of the political support function. To address the potential simultaneity bias between vote totals and lobbying effort, we will instrument for lobbying effort using the total number of bills voted upon in the thirty days leading up to a bill's consideration. While a legislator's propensity to vote in favor of a particular bill should not be directly impacted by the number of bills considered in close succession, the level of legislative activity is likely to impact not only the cost of lobbying by changing the demand for lobbying services and therefore the rates that lobbying firms can charge, but also the benefits of lobbying through the amount of time and attention per bill legislators can pay to lobbying. \\

\section{Conclusion}
\label{sec:concl}

\section{Appendix}
\begin{figure}
%\begin{center}
\includegraphics[height=9in, width=6.5in]{summary_stats.pdf}
%\includegraphics{summary_stats.pdf}
%\end{center}
%\caption{Probability Trade Agreement will be Broken\label{fig:br}}
\end{figure}

\newpage
\section{References}

\begin{list}{}{\setlength{\leftmargin}{0.3in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{-0.3in}\setlength{\itemsep}{0.0in}}

\item Ansolabehere, S., J. de Figueiredo, and J. Snyder Jr. (2003), ``Why Is There so Little Money in U.S. Politics?,'' {\em Journal of Economic Perspectives}, 17, 105-130.

\item Becker, G., (1983) ``A Theory of Competition among Interest Groups for Political Influence.'' {\em Quarterly Journal of Economics} 98, 371-400.

\item Bombardini, M. (2008), ``Firm Heterogeneity and Lobby Participation,'' {\em Journal of International Economics}, 75, 329-348.

\item Bombardini, M., and F. Trebbi (2012): ``Competition and Political Organization: Together or Alone in Lobbying for Trade Policy?'' {\em Journal of International Economics}, 87, 18-26.

\item Clinton, J., Jackman, S., and D. Rivers, (2004): ``The Statistical Analysis of Roll Call Data.'' {\em American Political Science Review}, 98, 355-370.

\item Dal Bo, E. (2007): ``Bribing Voters.'' {\em American Journal of Political Science} 51, 789-803.

\item Dekel, E., Jackson, M., Wolinsky, A. (2005): {\em Vote Buying.} Unpublished manuscript, Caltech.

\item Gawande, K., P. Krishna and M. Robbins (2006): ``Foreign Lobbies and U.S. Trade Policy,'' {\em Review of Economics and Statistics}, 88, 563-571.

\item Goldberg, P. and G. Maggi (1999): ``Protection for Sale: An Empirical Investigation,'' {\em American Economic Review}, 89, 1135-1155.

\item Groseclose, T., Snyder, J. M. (1996): ``Buying Supermajorities.'' {\em American Political Science Review} 90, 303-315.

\item Grossman, G. and E. Helpman (1994): ``Protection for Sale,'' {\em The American Economic Review}, 84, 833-850.

\item Grossman, G. and E. Helpman (2005): ``A Protectionist Bias in Majoritarian Politics,'' {\em The Quarterly Journal of Economics}, 120, 1239-1282.

\item Henisz, W. and E. Mansfield (2006), ``Votes and Vetoes: The Political Determinants of Commercial Openness,'' {\em International Studies Quarterly}, 50, 189-211.

\item Kibris, A. (2012), ``Uncertainty and Ratification Failure,'' {\em Public Choice}, 150, 439-467.

\item Laffont, J., Tirole, J. (1994): ``A Theory of Incentives in Procurement and Regulation.'' Cambridge: MIT Press.

\item Laver, M. and K. Shepsle (1991), ``Divided Government: America is Not `Exceptional','' {\em Governance: An International Journal of Policy and Administration}, 4, 250-269.

\item Le Breton, M. and F. Salanie (2003), ``Lobbying under political uncertainty,'' {\em Journal of Public Economics}, 87, 2589-2610.

\item Le Breton, M. and V. Zaporozhets (2007), ``Legislative Lobbying under Political Uncertainty,'' Available at SSRN: \url{http://ssrn.com/abstract=1024686}.

\item Peltzman, S. (1976), ``Toward a More General Theory of Regulation.'' {\em Journal of Law and Economics} 19, 211-248.

\item Poole, K. T. (2005), ``Spatial Models of Parliamentary Voting.'' New York: Cambridge University Press.

\item Saiegh, S. (2009), ``Political  Prowess or Lady Luck? Evaluating Chief Executives' Legislative Success Rates,'' {\em The Journal of Politics}, 71, 1342-1356.

\item Saiegh, S. (2011) ``Ruling by Statute: How Uncertainty and Vote-Buying Shape Lawmaking.'' New York: Cambridge University Press.

\item Stigler, G. (1975) ``The Citizen and the State: Essays on Regulation.'' Chicago: Chicago University Press.

\end{list}

\end{document}

### 2016-02-08 draft.tex
save old-draft as draft and remove all but references

--- 2016-02-08 old-draft.tex
@@
 \section{Introduction}
-In democratic countries, legislatures are the authoritative source of statutory law.
-Saiegh (2011) identifies two major factors that shape lawmaking: the unpredictability of legislators' voting behavior, and whether buying legislative votes is a feasible option.
-The source of the uncertainty is the existence of cross-pressured legislators: in deciding how to vote, lawmakers consider a variety of influences, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership.
-Therefore, legislators' voting behavior can seldom be perfectly anticipated.
-
-Campaign contribution and lobbying data show that lobbies do not expend equal efforts to influence all legislators; instead, they strategically choose to engage with only some members of the legislature.
-The uncertainty surrounding legislator's decision-making is likely to be a key decision variable in this calculus.
-In order to study how uncertainty affects the incentives for lobbying and the associated prospects for the passage of legislative actions, we must first quantify this uncertainty.
-We turn to this task first, adapting a standard technique from the political science literature.
-
-This project will contribute to our understanding of a particular type of political uncertainty---that surrounding statutory lawmaking.
-We will introduce an innovative methodology for quantifying cross-industry political uncertainty, use these measures to deepen our understanding of lobbying behavior, and make the data available for future use in a wide range of applications.
 
 \subsection{Related Literature}
-%The foundations of this work rest
-
-This work relates to the canonical studies on endogenous regulation (cf.
-Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)), as well as the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et.
-al.
-(2005), Dal Bo (2007)).
-
-Also related is Le Breton and Salanie (2003), which studies lobbying when the lobby is uncertain about the preferences of a unitary decision maker.
-Le Breton and Zaporozhets (2007) go a step further and replace the unitary decision maker with a legislature with multiple actors.
 
@@
 
-Formal model coming soon.
-
 %If we're going to do an empirical implementation of $\ga$ below, model needs to start with a basic understanding of uncertainty, run through lobbying response to it, up through aggregation into $\ga$ and how lobbying behavior turns into a ``yea'' vote total.
@@
 
-To understand how the presence and magnitude of uncertainty faced by a special interest group affects its lobbying behavior and the policy outcomes it is able to achieve, we must first quantify the uncertainty inherent in statutory lawmaking as, to the best of our knowledge, no such measures exist at the interest-group level.
-In order to do so, we will construct measures adapted from a well-accepted methodology in political science.
-
-Recorded votes in legislatures (roll call data) are the most commonly used data source to measure politicians' spatial preferences.
-A well-established strategy is to use statistical techniques to represent patterns of legislative voting.
-The intuition behind these statistical models is that each roll call presents each legislator with a choice between a ``yea'' and a ``nay'' position.
-Legislators are presumed to vote for the position most similar to their own ideal policy position.
-As Clinton et al.
-(2004) note, it is possible to use Bayesian Markov chain simulation statistical methods to generate these preference estimates.
-This approach treats the unknown ideal points, bill parameters and legislators' utilities as random variables and condition upon the observed roll call data.
-The strategy is to impute values to these variables and estimate by regression the ideal points and bill parameters.
-The MCMC algorithm repeatedly performs these imputations and regressions and generates a large number of samples from the posterior density of the model parameters.
-Using this estimation procedure, we obtain summary statistics used for inference: legislators' mean and median ideal points as well as their 95$\%$ posterior confidence intervals.
-The latter are of particular interest to us, as we can use them to gauge the unpredictability of each legislator's voting behavior.
-
-Legislators' ideal points do not necessarily have to be estimated using all the recorded votes cast by a legislature.
-Instead, one can use subsets of roll calls to establish a legislator's stance vis-a-vis a particular policy issue (Poole 2005).
-We will thus use subsets of roll call votes to estimate how friendly or unfriendly each legislator is with respect to a certain industry, as well as the unpredictability of his/her voting behavior when matters affecting that industry are considered.
-
-These ``report cards'' will be built in the spirit of ADA scores.
-Americans for Democratic Action (ADA) identifies key policy issues, and tracks how members of Congress vote on these issues.
-Their annual report card gives each legislator a rating from 0, meaning complete disagreement with ADA policies (conservative), to 100, meaning complete agreement with ADA policies (liberal).
-To be consistent with the standard Bayesian methodology, our measures will label a legislator who is indifferent to a particular interest group as having an ideal point of 0, who opposes the interest group as having a negative ideal point, and who supports the group as having a positive ideal point.
-
-To identify the relevant subset of roll calls for each industry, we rely on bill position determinations from \url{http://maplight.org}.
-This is a list, for each interest group, of the bills and amendments it supported or opposed beginning with the 110th Congress and continuously updated to the present.
-The determinations are made from public records such as Congressional hearing testimony, news databases, and member organizations' websites.\footnote{See \url{http://maplight.org/us-congress/guide/data/support-opposition} for details.} Groups are classified according to the Center for Responsive Politics's ``Category Code'' (\textit{catcode} for short) \footnote{See \url{https://www.opensecrets.org/resources/ftm/ch12p1.php} and \url{https://www.opensecrets.org/downloads/crp/CRP_Categories.txt}.}.
-
-Voting data are for the U.S.
-House of Representatives for the 110th through 113th Congress and come from Vote View, a website maintained by Professor Keith Poole (\url{http://voteview.com}).
-Details on each legislative proposal are available electronically through Thomas (\url{http://thomas.loc.gov}) and the sites of the House and Senate registrars.
-
-We analyze these votes using the Bayesian technique of Clinton et al.
-(2004) to capture each legislator's proximity to each group's interests, and to recover measures of uncertainty (the standard deviation of the posterior distribution) for each of those given groups.
-
-We begin by estimating ideal points for all bills. Here we use uninformative priors and the standard identifying assumptions that ideal points have mean zero and unit variance.
-
-We then estimate ideal points for subsets of bills: one subset for each interest group that includes all those actions in the U.S.
-House of Representatives on which that interest group took a public position.
-Here, we maintain the identifying assumption that ideal points have mean zero and unit variance and the uninformative variance for the prior distribution.
-We specify the vector of means for each prior distribution to be the ideal points estimated for the entire sample of bills.\footnote{This approach dramatically improves efficiency of the estimating algorithm and is justified by the observation that, with uninformative priors, the correlations between full-sample means and interest-group means are in the neighborhood of 85-90$\%$.}
-
-This procedure produces an ideal point and standard deviation for each member of the House of Representatives for each special interest group.
-The ideal point can be interpreted as a measure of how supportive a particular politician is of the interest group's agenda \textit{on average}, while the standard deviation is an indication of how predictable his/her support or opposition is.
-
-Aggregating these individual measures across the 112th Congress will give us our central measure of political uncertainty by industry.
-We expect this data to have a wide array of applications beyond our own.
-
-\subsection{Alternative Measure of Uncertainty}
-[This is an aside, but I would very much like your thoughts on it.]
-
-This is a related, but alternative, measure of uncertainty that my co-author has proposed.
-We have not implemented it broadly yet, but it's from here that he got the idea to use the ideal points from the full sample as the priors for the interest-group samples.
-So in a sense, what we're doing now is a way to marry this alternative approach with the traditional Bayesian approach with completely uninformative priors.
-
-Here is the idea: one way of framing the uncertainty we want to measure is to ask how well a lobbyist would do when he/she tries to predict how someone would vote.
-So, instead of using the standard deviation of the estimated ideal points, we could do the following:
-
-\begin{enumerate}
-	\item Calculate each legislator's ideal point using the full sample of roll call votes.
-	\item Calculate each legislator's ideal point using the roll call votes on which an interest group took a position.
-	\item Regress the ``interest group'' ideal point on the ``general'' ideal point.
-\end{enumerate}
-
-If a legislator is predictable in a specific policy area, then the residual should be close to 0; otherwise, he/she is more unpredictable.
-Figure~\ref{fig:br} plots the residuals (in absolute value) in the y-axis, as a function of their "general" ideology for commercial banks.
-For commercial banks, the $R^2$ in this regression was $0.92$.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=4in, width=5in]{residuals.png}
-\end{center}
-\caption{``Residuals'' Approach\label{fig:br}}
-\end{figure}
-
-One advantage of this measure of uncertainty is that it is orthogonal to ideology.
-Note that the measure based on the standard errors of the estimates is not: it is clear that ideologically more extreme legislators have higher uncertainty (see Figure\ref{fig:six} below).
-These residuals seem to be uncorrelated with ideology.
-
 %\subsection{Break Decision}
-%\begin{figure}
-%\begin{center}
-%\includegraphics[height=4in, width=5in]{brprob2.jpg}
-%\end{center}
-%\caption{Probability Trade Agreement will be Broken\label{fig:br}}
-%\end{figure}
 
@@
 \label{sec:select}
-Do distinct interest groups face varying levels of uncertainty?
-Preliminary evidence shows that they do.
-Summary statistics for our measures of ideal points and the uncertainty surrounding them for six interest groups---manufacturing unions, commercial banks, the dairy industry, software firms, computer software firms, and the oil and gas industry---as well as the total docket of bills for the 112th Congress are given in the Appendix.
-
-The first pattern that emerges is the the mean level of uncertainty is strongly correlated with the number of bills on which a group took a position.
-For the full universe of bills in the 112th Congress---over 1600 bills---the mean uncertainty is 0.04.
-For the Oil and Gas industry, which took a position on 96 bills, mean uncertainty is 0.19.
-Manufucturing Unions took a position on 90 bills and had a mean uncertainty of 0.161, and from here the relationship becomes monotonic: Commercial Banks with 65 positions has mean uncertainty of 0.206; Computer Software with 44 positions has mean uncertainty of 0.22; Real Estate with 27 positions has mean uncertainty of 0.286; and the Dairy industry with 23 positions has mean uncertainty of 0.29.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=5.5in, width=6.5in]{densities.png}
-\end{center}
-\caption{Distribution of Uncertainty by Industry\label{fig:den}}
-\end{figure}
-
-Figure~\ref{fig:den} helps to visualize the data underlying this pattern.
-We will generate estimates for several hundred more interest groups to see if this pattern holds up---or, rather, how strongly it holds as it seems unlikely to disappear altogether.
-The fundamental question is whether we should view the increase in aggregate uncertainty that comes with a reduction in the number of votes that are observed as purely a statistical phenomenon, purely a real phenomenon confronted by special interests in their decision making, or some mixture of the two.
-
-One interesting piece of initial evidence we have is that when we added the votes from the 110th and 111th Congress to the banking data, the range of standard deviations and the average did not change much.
-This is an exercise we will repeat, as we can take advantage of data from the 110th through the first half of the 113th Congresses to enlarge our sample size and in some cases in the later analysis break up the timing (perhaps, for instance, generating uncertainty measures from the first two Congresses and using them to predict contributions in the second two).
-
-What is clear from Figure~\ref{fig:six} is that the mean level of uncertainty hides differing underlying distributions: the majority of banking interests' uncertainty appears to come from its supporters, whereas for manufacturing unions, the opposition in more fickle.\footnote{Note that all ideal points are scaled so that legislators who generally support the interest group have positive ideal points, while those who generally oppose the group have negative ideal points.
-For the full set of bills, negative ideal points are associated with left/liberal/Democratic positions and positive ideal points are associated with right/conservative/Republican stances on bills.} Much more than just the first moment of the distribution is of interest.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=6.5in, width=6.5in]{six.pdf}
-\end{center}
-\caption{Distribution of Uncertainty by Industry\label{fig:six}}
-\end{figure}
 
@@
 \label{sec:dis}
-
-Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we next turn to efforts to understand how the uncertainty surrounding statutory lawmaking is related to political contributions and voting behavior of legislators.
-Our units of analysis are the same interest groups defined by the Center for Responsive Politics with those interest groups' positions on bills identified by \url{http://maplight.org} (as explained above).
-
-We will use political contributions data from the Center for Responsive Politics, as it uses the employment data that must be provided with all contributions over $\$$200 to classify contributions according to the donor's likely special interest affiliation.
-As these are the same codes used by Maplight to identify special interest groups' positions on bills, the contribution data cleanly matches the uncertainty measures derived from the positions these groups take on various pieces of legislation.
-
-We will use both standard parametric and non-parametric techniques such as density estimation to explore the relationships between lobbying behavior, contributions and uncertainty.
-We have shown above that interest groups face differing amounts of uncertainty; here, we ask how those patterns relate to the lobbying strategies they employ.
-
-Preliminary data analysis shows a very interesting relationship between uncertainty and lobbying expenditure across legislators at the aggregate level.
-That is, before the data is disaggregated by special interest group, we see an inverted U relationship between uncertainty and campaign contributions: legislators who are either very predictable or very unpredictable receive less, while those with an intermediate level of uncertainty are the target of the largest amounts of campaign contributions.
-We expect that additional important patterns will emerge when the data is disaggregated by industry.
-
-For the purposes of using this work to inform further studies of the policy-making process, we are interested in not only how interest groups target individuals, but also how a lobby's overall strategy interacts with the uncertainty it faces to translate into political support differentially across interest groups.
-Thus we want to predict the ``yea'' vote totals on each bill as a function of lobbying effort, uncertainty, and political and economic controls tailored to the industry.
-
-We will do this with a range of flexible parametric techniques in order to be reasonably confident that we have uncovered the true shape of this empirical implementation of the political support function.
-To address the potential simultaneity bias between vote totals and lobbying effort, we will instrument for lobbying effort using the total number of bills voted upon in the thirty days leading up to a bill's consideration.
-While a legislator's propensity to vote in favor of a particular bill should not be directly impacted by the number of bills considered in close succession, the level of legislative activity is likely to impact not only the cost of lobbying by changing the demand for lobbying services and therefore the rates that lobbying firms can charge, but also the benefits of lobbying through the amount of time and attention per bill legislators can pay to lobbying.
-\\
 
@@
 \section{Appendix}
-\begin{figure}
-%\begin{center}
-\includegraphics[height=9in, width=6.5in]{summary_stats.pdf}
-%\includegraphics{summary_stats.pdf}
-%\end{center}
-%\caption{Probability Trade Agreement will be Broken\label{fig:br}}
-\end{figure}
 

### 2016-02-09 two-groups.tex
save GS-extension as two-groups for model with two interest groups

--- 2016-02-08 GS-extension.tex
@@
 
+\vskip.3in
 \section{Our Extension to Uncertainty}
-\vskip.3in
 General thoughts on extension to uncertainty
@@
 
+\vskip.3in
 \subsection{Solving the Model}
-\vskip.3in
 Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
@@
 \section{Discrete Model}
-Discrete version (Conversation between Kristy and Frank, 3/27/15)
-\begin{itemize}
-	\item Purpose: try to understand what the right objective function is. Does maximizing total probability also maximize the probability of winning?
 \begin{itemize}
@@
 	\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
-		\end{itemize}
-	\item Frank prefers to write
+	\item We write
 	  \[
@@
 			\begin{itemize}
-				\item Note that, in a probit we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
+				\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
 				\item Also going to ignore Vote Buyer A's choice for now, so we have
@@
 		\]
-		Assuming $\ve \sim N(0,1)$, the probability that legislator $z$ votes ``no'' is $\Phi\left(\beta z - \alpha + b(z) \right)$
-	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. Then the three probabilities are
+		Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}$. 
+	\item Take a model with three legislators with ideal points at $z=-\frac{1}{2}$, $z=0$ and $z=\frac{1}{2}$. For ease of notation, let
+		\begin{enumerate}
+			\item $X = -\alpha + b(0)$ 
+			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
+		\end{enumerate}
+	\item Then the three probabilities are
 		\begin{itemize}
-			\item $\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)$, $\Phi\left(- \alpha + b(0) \right)$, and $\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)$
+			\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$
 			\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
 				\[
-				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \Phi\left(\beta z - \alpha + b(z) \right)
+				  X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
 				\]
@@
 			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
-					W_B \biggl[ \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
-					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
-					\left(1-\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
-					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
-				\end{multline}
-			Substituting from the definition of $X$ but substituting Logit for Probit and using the shorthand notation on the top of page~\pageref{page:sh},
-			  \begin{multline}
-			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
 					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
@@
 					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+				\end{multline}
+			This can be simplified as 
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
+					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
+					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
 					\label{eq:obj}
@@
 
-			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is (in terms of probit)
-				\begin{multline}
-					W_B \biggl[ \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - \\
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
-					\frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
-				\end{multline}
+			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is 
+				\begin{equation}
+					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
+				\end{equation}
 			Simplifying:
-			\begin{multline}
-					W_B \frac{1}{\sqrt{2\pi}} \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}\right)^2}{2}} \biggl[ \Phi\left(- \alpha + b(0) \right)\left(1-\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\right)  + \\
-					\left(1-\Phi\left(- \alpha + b(0) \right)\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) - 
-					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) + \\
-					\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \biggr]  = 1
-				\end{multline}
-			Simplifying further:
-			  \begin{multline}
-					\Phi\left(- \alpha + b(0) \right)+ \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
-					- 2\Phi\left(- \alpha + b(0) \right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(-\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\right)^2}{2}} }
-					\label{eq:firstfoc}
-				\end{multline}
+			\begin{equation}
+					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
+					\label{eq:logistic}
+				\end{equation}
+			Further math related to this equation is on Page~\pageref{eq:logistic2}.
 
-			The two symmetric conditions would be:
-			\begin{multline}
-					\Phi\left(- \alpha + b(0) \right)+  \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) 
-					- 2 \Phi\left(- \alpha + b(0) \right)\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right) \\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left(\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\right)^2}{2}} }
-				\end{multline}
-			\begin{multline}
-					\Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2}) \right)+  \Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right) 
-					- 2 \Phi\left(-\frac{\beta}{2} - \alpha + b(-\frac{1}{2})\right)\Phi\left(\frac{\beta}{2} - \alpha + b(\frac{1}{2}) \right)\\ = \frac{\sqrt{2\pi}}{W_B \: e^{- \frac{\left( - \alpha + b\left(0\right)\right)^2}{2}} }
-				\end{multline}
 		\end{itemize}
@@
 			\item If we divide through by 2, the left side is the average minus the product
-			\item If that is set equal to zero, the only solutions (for just one equation) are at (0,0) and (1,1). The right hand side modifies that.
-			\item Need to check SOC at some point
 			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
-			\item First I'm going to try to get closed form answer / intuition by substituting logistic for normal CDF/PDF
-		\end{itemize}
-	\item Substituting logistic for normal in Equation~\ref{eq:firstfoc}
-		\begin{equation}
-					\frac{1}{1+e^{\alpha - b(0)}} + \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }}
-					- 2\frac{1}{1+e^{\alpha - b(0)}}  \frac{1}{1+e^{-\frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right) }} = \frac{\left(1+e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)}\right)^2}{W_B \: e^{\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2}\right)} }
-					\label{eq:logistic}
-				\end{equation}
-		\begin{itemize}
-			\item A LOT of math (I will put it somewhere else) leads to three equations:
-				\[
-				  \left[ - \alpha + b(0) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] + \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
-				\]
-				\[
-				   \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] =\left[ - \alpha + b(0) \right]+ \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right]
-				\]
-				\[
-				   \left[ -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) \right] = \left[ \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right) \right] +\left[ - \alpha + b(0) \right]
-				\]
-			\item A little more math implies that all three quantities in brackets must equal zero
-				\begin{itemize}
-					\item That is, Vote Buyer B's bribe should make each legislator just indifferent between the new proposal and the status quo
-					\item First question: why doesn't this depend on willingness-to-pay?
-						\begin{itemize}
-							\item FOC says each bribe should be calibrated so that $W_B \cdot \text{marginal contribution to probability} = 1$, or $\frac{\partial \text{probability}}{\partial \text{bribe}} = \frac{1}{W_B}$
-							\item Something happens when all three conditions come together...what's the intuition?
-						\end{itemize}
-					\item To do next: see what non-negativity of bribes implies
-						\begin{itemize}
-							\item Also, insert Vote Buyer A's behavior
-							\item And give the various legislators different variances
-						\end{itemize}
-				\end{itemize}
 		\end{itemize}
@@
 \begin{itemize}
-	\item Let
-		\begin{enumerate}
-			\item $X = -\alpha + b(0)$ 
-			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
-			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
-		\end{enumerate}
 	\item Then Equation \ref{eq:logistic} is equivalent to:

### 2016-02-09 two-groups.tex
remove more material on continuous model

@@
 					\begin{itemize}
-						\item Let's start out by thinking of $z$ as being a random variable distributed $N(z,\sigma_z)$
 						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
 					\end{itemize}
-			\item Payoff for vote buyer A if $x$ wins is $U_A(x) - \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj$
-			\item Payoff for vote buyer A if $s$ wins is $U_A(s) - \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj$
-			\item I think the cleanest way to write the condition for whether $x$ wins is
-				\[
-				  \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[v(j) \geq 0 \right] dj \geq \frac{1}{2}
-				\]
 		\end{itemize}
@@
 				\begin{itemize}
-					\item Groseclose and Snyder formulation would suggest something like
-						\[
-							\min_{b(z)} \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \hskip.2in \text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq U_B(s) - U_B(x)
-						\]
-						\[
-							\text{and however we write the ``while passing his preferred policy'' constraint}
-						\]
 					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
@@
 					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
-				\end{itemize}
-			\item Let's start with the simple maximize expected value of winning (WTP times probability of winning) net of bribes:
-						\begin{multline}
-							\max_{b(j)} \ W_B\left\{ \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \mathbbm{1}\left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right]\geq \frac{1}{2} \right\} - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
-							\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
-						\end{multline}
-				\begin{itemize}
-					\item Problem is that the indicator function will never equal 1 when $J \sim N(j,\sigma_j)$
-					\item So what's a reasonable objective function? 
-						\begin{itemize}
-							\item Maximizing the total probability mass where $v(j) \leq 0$?
-							  \begin{multline}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\alpha -\beta \cdot j + a(j) - b(j) \leq 0 \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \\
-									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B  \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
-								\end{multline}
-									\begin{itemize}
 					\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
 					\item Some legislators who are past FOC point will not be lobbied
-									\end{itemize}
-							\item Suppressing the constraint for now and using the fact that $J \sim N(j,\sigma_j)$, this can be re-written as
-								\begin{equation}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\alpha + a(j) - b(j)}{\beta} \leq j \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
-								\end{equation}
-								or
-								\begin{equation}
-									\max_{b(j)} \ W_B \left[ \int_{-\frac{1}{2}}^\frac{1}{2} \Pr \left[\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \leq z \right] dj \right] - \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj
-								\end{equation}
-								where $Z \sim N(0,1)$. \\
-							\item	So, this can be written as
-								\begin{multline}
-									\max_{b(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_B \left(1- \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)\right) - b(j) \right] dj \\
-									\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} b(j) dj \leq W_B  \hskip.2in \text{and} \hskip.2in b(j)\geq0 \ \forall j
-									\label{ex:objB}
-								\end{multline}
-							\item If the realizations of $Z$ are i.i.d. and the bribes are independent across legislators, (I believe) this can be maximized pointwise--except for the constraint
-							\item The FOC for each $j$ is then
-								\begin{equation}
-								  - W_B \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial b(j)} = 1
-									\label{eq:foc}
-								\end{equation}
-								as long as the constraint is satisfied.
-									\begin{itemize}
-										\item I don't know how decisions are made if the constraint binds---how the rationing happens
-										\item If the constraint is not binding, vote buyer B will pay all legislators (we could put in some kind of fixed cost of dealing with each legislator to short circuit this outcome) except those who are already so favorable to him that they are past the FOC point
-										\item Perhaps there's something in equilibrium I'm not seeing yet that will reduce further the number of legislators that are paid
-									\end{itemize}
-						\end{itemize}
-				\end{itemize}
-			\item Let's examine the FOC, assuming pointwise maximization is okay as in Equation~\ref{eq:foc}
-				\begin{itemize}
-					\item It's easier for me to think of the CDF in terms of the non-standardized Normal distribution before taking the derivative. Then, if my math is right, the FOC becomes
-						\begin{equation}
-							  \frac{1}{\beta}\frac{1}{\sigma_j \sqrt{2\pi}} \: e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{1}{W_B} 
-								\label{eq:focB2}
-						\end{equation}
-							\begin{itemize}
-								\item This just says the pdf has to equal $\beta$ divided by the willingness to pay
-								\item Rearranging to solve for $b(j)$:
-									\begin{equation}
-							  		e^{- \frac{\left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2}{2\sigma_j^2} }= \frac{\beta\sigma_j \sqrt{2\pi}}{W_B} 
-									\end{equation}
-									\begin{equation}
-							  		- \left(\frac{\alpha + a(j) - b(j)}{\beta} - j\right)^2 =2\sigma_j^2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)
-									\end{equation}
-								Since the log statement on the RHS will almost certainly be negative, I can take the negative sign to the right and take the square root without worrying about imaginary numbers
-								  \begin{equation}
-							  		\frac{\alpha + a(j) - b(j)}{\beta} - j = \pm \sqrt{-2\sigma_j^2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)}
-									\end{equation}
-										\begin{itemize}
-											\item Notice there are two roots: could be to the left of the mode (less than 0.5 cumulative probability), or to the right (more than 0.5 cumulative probability)
-										\end{itemize}
-									\begin{equation}
-							  		\alpha + a(j) - b(j) = \pm \beta\sigma_j \sqrt{-2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)} + j \beta
-									\end{equation}
-									\begin{equation}
-							  		b(j) = \alpha + a(j)  - j \beta \pm \beta\sigma_j \sqrt{-2 \ln\left(\frac{\beta\sigma_j \sqrt{2\pi}}{W_B} \right)}
-									\end{equation}
-									\begin{equation}
-							  		b(j) = \alpha + a(j)  - \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
-										\label{eq:focB}
-									\end{equation}
-								\item So, the bribe for legislator $j$ takes legislator j's preferences back to zero in expectation (the first three terms) and then relative to that, either adds or subtracts a term that involves WTP, variance and $\beta$
-									\begin{itemize}
-										\item Do we have a way of distinguishing between the two? They have very different implications for the CDF, even though the same implications for the pdf
-										\item It makes more intuitive sense that the bribe would be increasing in $W_B$ (WTP)
-										\item Perhaps we derive the different implications and let the data speak
-										\item All the comparative statics will come out with same magnitude, both signs
-										\item SOC is obviously okay (essentially $-x e^{\frac{x^2}{2}}$)
-									\end{itemize}
-							\end{itemize}
-					\item How do we deal with this r.v. with continuous support when the range of ideal points is posited to be finite ($[-\frac{1}{2},\frac{1}{2}]$)?
-
-				\end{itemize}
-		\end{itemize}	
-	\item Vote buyer A
-		\begin{itemize}
-			\item Whatever we decide for vote buyer B will be the same for vote buyer A
-			\item Adapting Expression~\ref{ex:objB} for Vote Buyer A
-				\begin{multline}
-					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - a(j) \right] dj \\
-						\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj \leq W_A  \hskip.2in \text{and} \hskip.2in a(j)\geq0 \ \forall j
-							\label{ex:objA}
-				\end{multline}
-					\begin{itemize}
-						\item Major problem if we solve this game sequentially: when substituting the FOC for Vote Buyer B (Equation~\ref{eq:focB}) into Vote Buyer A's objective function, the $a(j)$'s cancel out ($b(j)$ is linear in $a(j)$) so the benefit term is constant in $a(j)$
-						\item Static best response
-						  \begin{equation}
-								  W_A \cdot \frac{ \partial \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right)}{\partial a(j)} = 1
-									\label{eq:focA}
-							\end{equation}
-						\item Math looks exactly the same as Eqn. \ref{eq:focB2} to \ref{eq:focB} except with $W_A$ replacing $W_B$ and all the opposite signs, so
-							\begin{equation}
-								a(j) = -\alpha + b(j)  + \beta j \pm \beta\sigma_j \sqrt{2 \left(\ln W_A - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}
-									\label{eq:focA3}
-							\end{equation}		
-					\end{itemize}
-				\item Plugging either one of the vote buyers' FOCs into the other just implies that $W_A = W_B$, but doesn't say anything about the level of bribes. Use some kind of pareto ranking to choose one?
-					\begin{itemize}
-						\item Note that to get a solution, I've taken both FOCs to have the same root (either both positive or both negative; Otherwise, we need a very special combination of parameters to get an equilibrium)
-						\item Intuition for this equilibrium: each vote buyer exactly brings legislator $j$ back to neutral (compensating both for inherent preference $\alpha - \beta \cdot j$) and the other vote buyer's bribe; they also each tack on a term related to WTP, $\beta$, and $\sigma_j$, but these terms cancel out as well as long as $W_A = W_B$.
-If $W_A \neq W_B$, then there is not such an interior equilibrium as far as I can tell.
-							\begin{itemize}
-								\item Need to look for more equilibria, perhaps in mixed strategies.
-								\item Especially a way to get asymmetric pure strategies (I'm happy to have asymmetry between $W_A$ and $W_B$ if necessary)
-							\end{itemize}
 				\end{itemize}
@@
 	\end{itemize}
+
+\subsection{Adding Vote Buyer A}
 

### 2016-02-09 two-groups.tex
revised legislature portion of sec:solve

@@
 		\end{itemize}
+	\item Note that this model \textit{may} introduce interdependence between the bid functions that does not exist in the continuous model
+	\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
 \end{itemize}
 
-\vskip.3in
-\subsection{Solving the Model}
+\newpage
+\section{Solving the Model}
+\label{sec:solve}
 Backward induction (legislature moves last; B makes last bribe; A makes first bribe)
@@
 			  \[
-				  v(z) = \alpha -\beta \cdot z + a(z) - b(z) > 0
+				  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
 				\]
@@
 						\item Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive
+						\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
 					\end{itemize}
-		\end{itemize}
-	\item Vote buyer B
-		\begin{itemize}
-			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
-			\item This has to be adapted to our situation with uncertainty
-				\begin{itemize}
-					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
-					\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
-					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
-					\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
-					\item Some legislators who are past FOC point will not be lobbied
-				\end{itemize}
-		\end{itemize}	
-\end{enumerate}
-
-\newpage
-\section{Discrete Model}
-\begin{itemize}
-	\item Note that this model \textit{may} introduce interdependence between the bid functions that does not exist in the continuous model
-	\item What is not clear is whether this happens when the WTP constraint is not binding, which I'm going to assume from the start, and maybe impose later
-	\item We write
-	  \[
-		  v(z) = \alpha -\beta z + \ve_z + a(z) - b(z)
-		\]
-			\begin{itemize}
-				\item Note that we will have to worry about separately identifying the parameters. So for now, will assume $\ve$ does not vary in $z$
 			\item Also going to ignore Vote Buyer A's choice for now, so we have
-			\end{itemize}
 				\[
@@
 						\]
+				\end{itemize}
+		\end{itemize}
+
+\item Vote buyer B
+		\begin{itemize}
+			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
+			\item This has to be adapted to our situation with uncertainty
+				\begin{itemize}
+					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
+					\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
+					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
+					\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
+					\item Some legislators who are past FOC point will not be lobbied
+				\end{itemize}
+		\end{itemize}
+
 			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
@@
 
-		\end{itemize}
 	\item Some notes
@@
 		\end{itemize}
-	\end{itemize}
 
-\subsection{Adding Vote Buyer A}
+\end{enumerate}
 
-\subsection{Adding Non-negativity Constraints for Bribes}
+\section{Adding Vote Buyer A}
+
+\section{Adding Non-negativity Constraints for Bribes}
 The Lagrangian for the problem is the same as Expression~\ref{eq:obj}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$

### 2016-02-09 two-groups.tex
revisse vote buyer B portion of sec: solve

@@
 		\begin{itemize}
-			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
-			\item This has to be adapted to our situation with uncertainty
-				\begin{itemize}
+			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''; this has to be adapted to our situation with uncertainty
 			\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
@@
 			\item Some legislators who are past FOC point will not be lobbied		
-				\end{itemize}
-		\end{itemize}
-
 			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
@@
 			Further math related to this equation is on Page~\pageref{eq:logistic2}.
-
-	\item Some notes
-		\begin{itemize}
 			\item If we divide through by 2, the left side is the average minus the product
@@
 		\end{itemize}
-
+	\item Vote Buyer A
 \end{enumerate}
-
-\section{Adding Vote Buyer A}
 
@@
 \newpage
-\subsection{Math for Discrete Model}
+\section{Math for Discrete Model}
 The math that follows from Equation \ref{eq:logistic}:

### 2016-02-09 two-groups.tex
move intuition section and change subsecs to full sections

@@
 \newpage
+\section{Intuition}
+\begin{itemize}
+	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
+		\[
+		  v(z) = \al - \beta z + a(z) - b(z) > 0
+		\]
+	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
+		\[
+		  \al - \beta z - b(z) < 0
+		\]
+
+		\begin{center}
+		or 
+		\end{center}
+		\[
+		  \beta z - \al + b(z) > 0
+		\]
+		\item If $\al > 0$, legislators on average are biased against B.
+			\begin{itemize}
+				\item If $\al < 0$, legislators on average are biased in favor of B.
+				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
+			\end{itemize}
+		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,\frac{1}{2},$ or $-\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
+\end{itemize}
+
+\vskip.1in
+Recall:
+		\begin{enumerate}
+			\item $X = -\alpha + b(0)$ 
+			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$ 
+		\end{enumerate}
+
+\vskip.1in
+Pattern more or less is to get the guy who is WHAT?
+\begin{itemize}
+	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
+	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
+\end{itemize}
+
+\vskip.1in
+The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
+\begin{itemize}
+	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
+	\item \textbf{Next question: How general is this result?
+That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
+My conjecture is that it leans on having an interior single mode}
+\end{itemize}
+
+\newpage
 \section{Math for Discrete Model}
@@
 \newpage		
-\subsection{Second Order Conditions}
+\section{Second Order Conditions}
 Perhaps more importantly, let's look at the second order condition (using the same substitutions at the top of the previous page).
@@
 \newpage
-\subsection{Intuition}
-\begin{itemize}
-	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
-		\[
-		  v(z) = \al - \beta z + a(z) - b(z) > 0
-		\]
-	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
-		\[
-		  \al - \beta z - b(z) < 0
-		\]
-
-		\begin{center}
-		or 
-		\end{center}
-		\[
-		  \beta z - \al + b(z) > 0
-		\]
-		\item If $\al > 0$, legislators on average are biased against B.
-			\begin{itemize}
-				\item If $\al < 0$, legislators on average are biased in favor of B.
-				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
-			\end{itemize}
-		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,\frac{1}{2},$ or $-\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
-\end{itemize}
-
-\vskip.1in
-Recall:
-		\begin{enumerate}
-			\item $X = -\alpha + b(0)$ 
-			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
-			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$ 
-		\end{enumerate}
-
-\vskip.1in
-Pattern more or less is to get the guy who is WHAT?
-\begin{itemize}
-	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
-	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
-\end{itemize}
-
-\vskip.1in
-The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
-\begin{itemize}
-	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
-	\item \textbf{Next question: How general is this result?
-That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
-My conjecture is that it leans on having an interior single mode}
-\end{itemize}
-
-\newpage
-\subsection{One Non-negative Bribe}
+\section{One Non-negative Bribe}
 When $\al = 0$ and $WB=8$, we find that $b\left(-\frac{1}{2}\right)$ and $b\left(\frac{1}{2}\right)$ are zero. Only $b(0)$ is positive.
@@
 \newpage
-\subsection{All Three Bribes are Non-negative}
+\section{All Three Bribes are Non-negative}
 In many cases all three bribes are non-negative. Here are very loose results
@@
 \newpage
-\subsection{Numerical Results}	
+\section{Numerical Results}	
 For all of these, $\beta = 1$ and there are three legislators with $b\in\left\{-\frac{1}{2},0,\frac{1}{2}\right\}$.

### 2016-02-09 two-groups.tex
add obj fcn for vote buyer A; fix Z,Y mixup up to sec:nonneg

@@
 					\item $X = -\alpha + b(0)$ 
-					\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
-					\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)\label{page:sh}$ 
+					\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
+					\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\label{page:sh}$ 
 				\end{enumerate}
@@
 				\begin{itemize}
-					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$
+					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$
 					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
@@
 					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
-					\label{eq:obj}
+					\label{eq:objb}
 				\end{multline}
 
-			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is 
+			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
 				\begin{equation}
@@
 	\item Vote Buyer A
+		\begin{itemize}
+			\item Vote buyer A's objective function is identical in form to that of Vote Buyer B (Expression~\ref{eq:objb} 
+			  \begin{multline}
+			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
+					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y}} +
+					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
+					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
+					\label{eq:obja}
+				\end{multline}
+				where 
+				\begin{enumerate}
+					\item $X_A = \alpha - b(0,a(0)) + a(0)$ 
+					\item $Y_A = -\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2},a\left(-\frac{1}{2}\right)\right)+ a\left(-\frac{1}{2}\right)$
+					\item $Z_A = \frac{\beta}{2} + \alpha - b\left(\frac{1}{2},a\left(\frac{1}{2}\right)\right)+ a\left(\frac{1}{2}\right)$
+				\end{enumerate}
+		\end{itemize}
 \end{enumerate}
 
+\newpage
 \section{Adding Non-negativity Constraints for Bribes}
-The Lagrangian for the problem is the same as Expression~\ref{eq:obj}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$
+\label{sec:nonneg}
+The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$
 

### 2016-02-09 constrained-optimization.r
fix constrained-optimization for Z,Y switch

@@ -5,18 +5,18 @@
 h <- function(WB,al) {
   
 f <- function(B,WB,al) {
-  Bnp5 <- B[1]
+  Bp5 <- B[1]
   B0 <- B[2]
-  Bp5 <- B[3]
-  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bnp5))) + (1/(1+exp(al + .5 - Bnp5)))*(1/(1+exp(al - .5 - Bp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bp5)))*(1/(1+exp(al + .5 - Bnp5)))) + B0 + Bp5 + Bnp5
+  Bnp5 <- B[3]
+  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bp5))) + (1/(1+exp(al + .5 - Bp5)))*(1/(1+exp(al - .5 - Bnp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bnp5)))*(1/(1+exp(al + .5 - Bp5)))) + B0 + Bp5 + Bnp5
 }   
 
 o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
 #o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
 
 X = round(- al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
-Y = round(.5 - al + o$par[3], digits = 2)    #Bp5  in the logistic CDFs; I don't use them in the function
-Z = round(-.5 - al + o$par[1], digits=2)   #Bnp5 but I've pasted in values here to check
+Y = round(.5 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
+Z = round(-.5 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here to check
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)

### 2016-02-09 two-groups.tex
fix constrained-optimization for Z,Y switch
fix Z,Y mixup through intuition sec; add more intuition

@@
 		\begin{itemize}
-			\item Vote buyer A's objective function is identical in form to that of Vote Buyer B (Expression~\ref{eq:objb} 
+			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
 			  \begin{multline}
 			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
-					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y}} +
-					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
-					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
+					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
+					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
+					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
 					\label{eq:obja}
@@
 \label{sec:nonneg}
-The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(\frac{1}{2}\right) + \lambda_Z b\left(-\frac{1}{2}\right)$
+The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(-\frac{1}{2}\right) + \lambda_Z b\left(\frac{1}{2}\right)$
 
@@
 \[
-  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(-\frac{1}{2}\right) = 0 
+  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(\frac{1}{2}\right) = 0 
 \]
@@
 \begin{itemize}
-	\item Then $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = -\frac{\beta}{2} - \alpha $
-	\item $\lambda_Z$ is likely positive
-	\item $\lambda_X = \lambda_Y = 0$
+	\item Then $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = \frac{\beta}{2} - \alpha $
+	\item $\lambda_Y$ is likely positive
+	\item $\lambda_X = \lambda_Z = 0$
 \end{itemize}
@@
 			\end{itemize}
-		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,\frac{1}{2},$ or $-\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
+		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
 \end{itemize}
@@
 			\item $X = -\alpha + b(0)$ 
-			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
-			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$ 
+			\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$ 
 		\end{enumerate}
@@
 	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
-	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote)
+	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
+		\begin{itemize}
+			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
+		\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{What's the intuition for why they should be equal? Draw graph of the three PDFs in ideal point / net ideal point space}
+	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
+	\item What's the intuition for why they should be equal?
+As far as I can tell, it's that the PDF is unimodal.
+If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
 	\item \textbf{Next question: How general is this result?

### 2016-02-10 draft.tex
update sections and labels
change section headers to roman, remove from appendix & concl
add text from NSF to intro of draft

@@
 \renewcommand{\baselinestretch}{1.0}
+\renewcommand{\thesection}{\Roman{section}} 
+\renewcommand{\thesubsection}{\thesection.\Roman{subsection}}
 \linespread{1.5}
@@
 
-%\usepackage[usenames,dvipsnames]{color}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
 \usepackage{cite}
@@
 \section{Introduction}
+\label{sec:intro}
+
+\textcolor{blue}{In democratic countries, legislatures are the authoritative source of statutory law.
+The PFS model doesn't capture several general features of policymaking in this environment: (2) how uncertainty affects the incentives for lobbying and the associated prospects for ratification of trade agreements; and (3) how the voting intentions of multiple legislators, rather than a single agent, change in response to incentives.}
+
+\textcolor{blue}{In this vein, Saiegh (2011) identifies two major factors that shape lawmaking: the unpredictability of legislators' voting behavior, and whether buying legislative votes is a feasible option.
+The source of the uncertainty is the existence of cross-pressured legislators: in deciding how to vote, lawmakers consider a variety of influences, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership.
+Therefore, legislators' voting behavior can seldom be perfectly anticipated.}
+
+\textcolor{blue}{From an empirical standpoint, the project will contribute to our understanding of the political uncertainty that surrounds statutory lawmaking.
+We will introduce an innovative methodology for quantifying cross-industry political uncertainty, establish the relevance of the resulting measures for policy-making and make the data available for future use in a wide range of applications.
+For example, our measure could be used to study he impact of policy uncertainty on firm-level investment and employment.}
 
 \subsection{Related Literature}
+\label{sec:lit}
+
+\textcolor{blue}{Related is Le Breton and Salanie (2003), which studies lobbying when the lobby is uncertain about the preferences of a unitary decision maker.
+Le Breton and Zaporozhets (2007) go a step further and replace the unitary decision maker with a legislature with multiple actors.
+Song (2008) is a model of endogenous lobbying with a ratification constraint in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership in a model with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.}
+
+\textcolor{blue}{As noted above, Saiegh (2009) argues that the uncertainty surrounding statutory lawmaking is in part related to governmental and political structure.
+Although they do not discuss uncertainty specifically, the cross-country empirical work of Gawande, Krishna and Olarreaga (2009) is the first to our knowledge that suggests that this kind of uncertainty plays a role in trade policy.
+They show that variables such as the number of checks and balances on the power of the legislature and the gap between the policy positions of the main political parties have predictive power for the PFS ``welfare-mindedness'' parameter.
+One of the objectives of this proposed project is to directly test the premise that legislative uncertainty indeed has an important impact on trade policy.}
+
+\textcolor{blue}{This work also relates to the canonical studies on endogenous regulation (cf.
+Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)), as well as the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et.
+al.
+(2005), Dal Bo (2007)).}
 
@@
 
+\section{Some Theoretical Results}
+\label{sec:res}
+
 \section{Estimating Legislative Uncertainty}
-\label{sec:main}
+\label{sec:est}
+
+\section{An Application to the U.S. House of Representatives}
+\label{sec:house}
 
@@
 
-\subsection{Uncertainty for Select Interest Groups}
-\label{sec:select}
-
-\section{(Plans for) Statistical Analysis}
-\label{sec:dis}
+%\subsection{Uncertainty for Select Interest Groups}
+%\label{sec:select}
 
@@
 
-\section{Appendix}
+\section*{Appendix}
 
 \newpage
-\section{References}
+\section*{References}
 

### 2016-02-10 draft.tex
add NSF figures and text for prelim evidence

@@
 
+\begin{figure}
+\centering
+\begin{minipage}{.5\textwidth}
+  \centering
+  \includegraphics[width=2.9in]{graph2.jpg}
+  \caption{Lobbying Effort and Support for KORUS
+	\label{fig:br}}
+\end{minipage}%
+\begin{minipage}{.5\textwidth}
+  \centering
+  \includegraphics[width=2.9in]{graph1.jpg}
+  \caption{Net Campaign Contributions, KORUS
+	\label{fig:g1}}
+\end{minipage}
+\end{figure}
+
+\textcolor{blue}{Figure 1 displays the relationship between lobbying effort and legislators' support for KORUS.
+The vertical axis represents the predicted probability that a legislator would vote ``yes'' on the agreement, and the horizontal axis shows the monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.
+The solid vertical red line indicates the average net contribution in the sample, and the dashed lines a one-standard deviation increase/decrease from that sample mean.
+The data indicate that exporting industries are more likely to exert lobbying effort to enlist the support of additional legislators (extensive margin) rather than secure stronger support from a given set of legislators (intensive margin), as well as that there are decreasing returns to lobbying effort.
+To generate these results,  we regressed a legislator's vote on his/her estimated ideal point as well as partisanship using a probit specification.
+Then we fitted a second-order polynomial to the predicted probabilities generated by the probit regression.
+The contribution data for both this and the follow figure was obtained from Maplight.}
+
+\textcolor{blue}{Figure 2 displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort.
+The vertical axis represents the predicted net contributions to members of the U.S.
+House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislator's voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress (more details on the methodology below).
+The solid vertical red line indicates the average uncertainty in the sample, and the vertical dashed red lines indicate increases/decreases of one-standard deviation from the average.
+The horizontal dashed green line indicates the predicted net payment in the sample.
+The data show a very strong relationship between uncertainty at the level of the individual legislator and campaign contributions.
+To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.
+While these data do not map perfectly onto our theoretical constructs, they indicate that there is strong preliminary support for our hypotheses making it highly likely that investment in data acquisition and analysis is worthwhile.}
+
 %\subsection{Break Decision}

### 2016-02-10 draft.tex
add NSF graph and integrate rest of project description

@@
 
+\textcolor{blue}{Recorded votes in legislatures (roll call data) are the most commonly used data source to measure politicians' spatial preferences.
+A well-established strategy is to use statistical techniques to represent patterns of legislative voting.
+The intuition behind these statistical models is that each roll call presents each legislator with a choice between a ``yea'' and a ``nay'' position.
+Legislators are presumed to vote for the position most similar to their own ideal policy position.
+As Clinton et al.
+(2004) note, it is possible to use Bayesian Markov chain simulation statistical methods to generate these preference estimates.
+This approach treats the unknown ideal points, bill parameters and legislators' utilities as random variables and condition upon the observed roll call data.
+The strategy is to impute values to these variables and estimate by regression the ideal points and bill parameters.
+The MCMC algorithm repeatedly performs these imputations and regressions and generates a large number of samples from the posterior density of the model parameters.
+Using this estimation procedure, we obtain summary statistics used for inference: legislators' mean and median ideal points as well as their 95$\%$ posterior confidence intervals.
+The latter are of particular interest to us, as we can use them to gauge the unpredictability of  legislators' voting behavior.}
+
+\textcolor{blue}{We are interested in unpredictability vis-a-vis particular policy issues.
+Poole (2005) suggests using subsets of roll calls to establish legislators' ideal points separately on each issue.
+Preliminary work with our data indicates that a more statistically-robust method is to use all roll call votes in a legislative session or group of sessions to estimate an ideal point that is multidimension---that is, with one dimension for each interest group---allowing the partial pooling of information across roll calls.
+Multilevel modeling techniques, of which the standard ideal point estimation is a basic case, are perfectly suited to this task.}
+
+\textcolor{blue}{We therefore estimate the model
+\begin{equation}
+  \Pr(y_{kj} = 1) = \text{logit}^{-1}\left( \sum_{g=1}^G \ga_k^{(g)}\left( \alpha_j^{(g)} - \beta_k^{(g)}\right) \right)
+	\label{eq:v2}
+\end{equation}
+with roll call votes numbered $k=1,\ldots,K$, legislators numbered $j=1,\dots,J$, and interest groups numbered $g=1,\dots,G$.
+$y_{jk}=1$ if legislator $j$ votes ``Yea'' on bill $k$; $y_{kj}=0$ if she votes ``Nay'' on bill $k$.
+Note that interest groups take positions on multiple roll call votes and different interest groups can take positions, often on opposing sides, on each vote.}
+
+\textcolor{blue}{This is a logistic item response (Rasch) model as adapted by Bafumi, et.
+al.
+(2005) to the legislative context.
+$\alpha_j^{(g)}$ is the ideal point of legislator $j$ on issue $g$ and $\beta_k^{(g)}$ is the ideal point of a legislator who is indifferent on vote $k$ for issue $g$.
+$\gamma_k^{(g)}$, the discrimination parameter, is a measure of the informativeness of issue $g$ for the vote on bill $k$: a large $\ga$ indicates that legislators are very likely to vote according to their preferences, whereas a small $\ga$ means that even significant margins of preference do not contribute much to the probability that legislators will vote in favor of the bill.}
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=3in, width=6.5in]{NSF_combined_graph.pdf}
+\end{center}
+\caption{Uncertainty by Industry\label{fig:combined}}
+\end{figure}
+
+\textcolor{blue}{We `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position.
+This produces estimates for how ``friendly'' or ``unfriendly'' each legislator is with respect to each interest group, as well as the unpredictability of his/her voting behavior when matters affecting that group are considered.
+In a preliminary run of this model with just ten interest groups (out of over 450) in the 112th Congress displayed in Figure~\ref{fig:combined}, we find that the chemical industry has the lowest average uncertainty (sd = 0.229); this is lower than the total uncertainty measure that can be interpreted as the standard left-right measure in ideal point models (sd = 0.233).
+The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).}
+
+\textcolor{blue}{We are experimenting with some of the more sophisticated measures of uncertainty that are possible with a rich model such as this one; for instance the group mean for $\ga$ and constructs that combine model parameters.}
+
+\textcolor{blue}{Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
+First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight (as explained above).}
+
+\textcolor{blue}{We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
+We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.
+From the data analysis that is represented above, we see a very interesting relationship between uncertainty and lobbying expenditure across legislators at the aggregate level in Figure~\ref{fig:br}, and we expect that additional important patterns will emerge when the data is disaggregated by industry.}
+
 \section{An Application to the U.S. House of Representatives}
 \label{sec:house}
+
+\subsection{Data}
+\textcolor{blue}{Voting data will be obtained from Vote View, a website maintained by Professor Keith Poole (\url{http://voteview.com}).
+Details on each legislative proposal are available electronically through Thomas (\url{http://thomas.loc.gov}) and the sites of the House and Senate registrars.}
+
+\textcolor{blue}{We will use Maplight's contributions data, which provides evidence on public declarations by special interest groups to determine the relevant PAC contributions for the bills under consideration.
+In a related effort to better connect special interest activity to the intent of that activity, we will use data made available pursuant to the U.S.
+Lobbying Disclosure Act of 1995 and the Honest Leadership and Open Government Act of 2007 via the U.S.
+Senate Office of Public Records and the Office of the Clerk of the U.S.
+House of Representatives.
+This data is particularly useful because lobbyists must declare the issue area on which they lobbied.}
+
+\textcolor{blue}{We will also explore whether there is a way to leverage the data and methodology of Lake and Millimet (2014b) that combine the contributions and lobbying data to improve precision, although there is a concern about the coarseness of the data that must be overcome.}
+
+\subsection{Evidence}
 
@@
 
-\textcolor{blue}{Figure 1 displays the relationship between lobbying effort and legislators' support for KORUS.
+\textcolor{blue}{Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for KORUS.
 The vertical axis represents the predicted probability that a legislator would vote ``yes'' on the agreement, and the horizontal axis shows the monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.
@@
 
-\textcolor{blue}{Figure 2 displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort.
+\textcolor{blue}{Figure~\ref{fig:g1} displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort.
 The vertical axis represents the predicted net contributions to members of the U.S.
@@
 \label{sec:concl}
+
+\textcolor{blue}{an alternative characterization of the legislative process would be one in which (i) bills have a quality dimension (such as their technical merit, or their appropriateness for a given situation); and (ii) legislators have access to different pieces of information about the quality of these proposals.
+Given our own long-term research agenda, adding common values and decentralized information to the analysis of the ratification of trade agreements will be one of the next steps in this project.
+Given the important set of governance characteristics identified in Mansfield and Milner (2012), we also look forward to taking advantage of what seems a rich opportunity to integrate important institutional variations into this modeling framework of endogenous lobbying with uncertainty.}
+
+\vskip.3in
+\textcolor{blue}{We expect this data will have a wide array of applications, such as exploring the links between policy uncertainty, the business cycle, and stock market volatility.}
 

### 2016-02-11 constrained-optimization-yzinit.R
copy constrained-optimization to modify code to move initial ideal points

@@ -1,0 +1,51 @@
+#optim function minimizes 'f'; c vector are starting values; lower is the
+#constraint; I choose a null gradient because it was easiest to get up and running
+#note that here the beta parameter is hard coded in as equal to 1
+
+h <- function(WB,al,y0) {
+  
+f <- function(B,WB,al,y0) {
+  Bp5 <- B[1]
+  B0 <- B[2]
+  Bnp5 <- B[3]
+  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bp5))) + (1/(1+exp(al + .5 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + .5 - Bp5)))) + B0 + Bp5 + Bnp5
+}   
+
+al = 0
+o <- optim(c(1,1,1,WB,al,y0),function(B) f(B,WB,al,y0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
+#o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
+
+X = round(- al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
+Y = round(-y0 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
+Z = round(-.5 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here to check
+
+pos <- c(Z,X,Y)
+bribes <- c(o$par,-o$value)
+win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
[…]

### 2016-02-11 constrained-optimization-yzinit.R
add code for moving Z

@@ -2,37 +2,41 @@
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
 
-h <- function(WB,al,y0) {
+h <- function(WB,al,y0,z0) {
   
-f <- function(B,WB,al,y0) {
+f <- function(B,WB,al,y0,z0) {
   Bp5 <- B[1]
   B0 <- B[2]
   Bnp5 <- B[3]
-  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bp5))) + (1/(1+exp(al + .5 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + .5 - Bp5)))) + B0 + Bp5 + Bnp5
+  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
 }   
 
 al = 0
-o <- optim(c(1,1,1,WB,al,y0),function(B) f(B,WB,al,y0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
+y0=-.5
+o <- optim(c(1,1,1,WB,al,y0,z0),function(B) f(B,WB,al,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
 #o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
 
 X = round(- al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
 Y = round(-y0 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
[…]

### 2016-02-11 A-optimization.R
create A-optimization from yzinit version

@@ -1,0 +1,56 @@
+#optim function minimizes 'f'; c vector are starting values; lower is the
+#constraint; I choose a null gradient because it was easiest to get up and running
+#note that here the beta parameter is hard coded in as equal to 1
+
+h <- function(WB,al,y0,z0,x0) {
+  
+f <- function(B,WB,al,y0,z0,x0) {
+  Bp5 <- B[1]
+  B0 <- B[2]
+  Bnp5 <- B[3]
+  -WB*((1/(1+exp(al +x0- B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al +x0- B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al +x0 - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
+}   
+
+WB=8
+al = 0
+y0=-.5
+o <- optim(c(1,1,1,WB,al,x0,y0,z0),function(B) f(B,WB,al,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
+#o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
+
+X = round(-x0 - al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
+Y = round(-y0 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
+Z = round(-z0 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here to check
+
+pos <- c(Z,X,Y)
+bribes <- c(o$par,-o$value)
+win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
[…]

### 2016-02-11 A-optimization.R
modify A-optimization for calculations across all three legislators

@@ -13,7 +13,6 @@ f <- function(B,WB,al,y0,z0,x0) {
 
 WB=8
 al = 0
-y0=-.5
 o <- optim(c(1,1,1,WB,al,x0,y0,z0),function(B) f(B,WB,al,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
 #o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
 
@@ -30,10 +29,10 @@ return(out)
 
 # Create a dataframe of parameter values
 x_vector <- seq(0, 1.0, 0.1) 
-#y_vector <- seq(-1.0, 0.0, 0.1)
+y_vector <- seq(-1.0, 0.0, 0.1)
 z_vector <- seq(.5, 1.0, 0.1)
 #params <- expand.grid("wb" = wb_vector, "y" = y_vector)
-params <- expand.grid("x" = x_vector, "z" = z_vector)
+params <- expand.grid("x" = x_vector, "y" = y_vector, "z" = z_vector)
 
 # Use "Map" to evaluate the "h" function at each pair of parameter values
 #results <- Map(h, y = params$y, WB = params$wb)

### 2016-02-12 A-optimization.R
add A's optimization problem

@@ -20,31 +20,37 @@ X = round(-x0 - al + o$par[2], digits = 2)       #B0   these are shorthand varia
 Y = round(-y0 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
 Z = round(-z0 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here to check
 
+A0 = x0 
+Ap5 = z0 - .5
+Anp5 = y0 + .5
+
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
+bribesA <- c(A0,Anp5,Ap5)
 win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
-out <- list("solns" = o$par[1:3], "pos" = pos, "objMax" = -o$value, "a" = al, "wb" = WB, "yInit" = y0, "zInit" = z0, "xInit" = x0, "winProb" = win)
+ValA = 10*(1-win) - A0 - Ap5 - Anp5
+out <- list("solns" = round(o$par[1:3],digits=3), "pos" = pos, "objMax" = -o$value, "a" = al, "wb" = WB, "yInit" = y0, "zInit" = z0, "xInit" = x0, "winProb" = win,"bribesA"=c(A0,Anp5,Ap5,ValA))
 return(out)
 }
 
 # Create a dataframe of parameter values
-x_vector <- seq(0, 1.0, 0.1) 
-y_vector <- seq(-1.0, 0.0, 0.1)
-z_vector <- seq(.5, 1.0, 0.1)
-#params <- expand.grid("wb" = wb_vector, "y" = y_vector)
+x_vector <- seq(0, 1, 0.1) 
+y_vector <- seq(-.5, 1.5, 0.1)
+z_vector <- seq(.5, 1.5, 0.1)
 params <- expand.grid("x" = x_vector, "y" = y_vector, "z" = z_vector)
 
 # Use "Map" to evaluate the "h" function at each pair of parameter values
-#results <- Map(h, y = params$y, WB = params$wb)
[…]

### 2016-02-12 A-optimization.R
take out hardcoding for WA

@@ -1,6 +1,7 @@
 #optim function minimizes 'f'; c vector are starting values; lower is the
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
+WA=8
 
 h <- function(WB,al,y0,z0,x0) {
   
@@ -11,7 +12,7 @@ f <- function(B,WB,al,y0,z0,x0) {
   -WB*((1/(1+exp(al +x0- B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al +x0- B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al +x0 - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
 }   
 
-WB=8
+WB=10
 al = 0
 o <- optim(c(1,1,1,WB,al,x0,y0,z0),function(B) f(B,WB,al,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
 #o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
@@ -28,15 +29,15 @@ pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
 bribesA <- c(A0,Anp5,Ap5)
 win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
-ValA = 10*(1-win) - A0 - Ap5 - Anp5
+ValA = WA*(1-win) - A0 - Ap5 - Anp5
[…]

### 2016-02-12 constrained-optimization.r
substitute shorter expression for winProb

@@ -20,7 +20,7 @@ Z = round(-.5 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here t
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
-win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
+win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y))) + (1/(1+exp(-X)))*(1/(1+exp(-Z))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y))) - 2*(1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
 out <- list("solns" = o$par[1:3], "pos" = pos, "objMax" = -o$value, "a" = al, "wb" = WB, "winProb" = win)
 return(out)
 }

### 2016-02-12 A-optimization.R
fix order of function inputs in A-optimization

@@ -3,9 +3,9 @@
 #note that here the beta parameter is hard coded in as equal to 1
 WA=8
 
-h <- function(WB,al,y0,z0,x0) {
+h <- function(WB,al,x0,y0,z0) {
   
-f <- function(B,WB,al,y0,z0,x0) {
+f <- function(B,WB,al,x0,y0,z0) {
   Bp5 <- B[1]
   B0 <- B[2]
   Bnp5 <- B[3]
@@ -15,11 +15,10 @@ f <- function(B,WB,al,y0,z0,x0) {
 WB=10
 al = 0
 o <- optim(c(1,1,1,WB,al,x0,y0,z0),function(B) f(B,WB,al,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
-#o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
 
-X = round(-x0 - al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
-Y = round(-y0 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
-Z = round(-z0 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here to check
+X = round(-x0 - al + o$par[2], digits = 3)       #B0   these are shorthand variables for the exponents
+Y = round(-y0 - al + o$par[3], digits = 3)    #Bnp5  in the logistic CDFs; I don't use them in the function
+Z = round(-z0 - al + o$par[1], digits=3)   #Bp5 but I've pasted in values here to check
 
 A0 = x0 
 Ap5 = z0 - .5
@@ -28,7 +27,7 @@ Anp5 = y0 + .5
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
 bribesA <- c(A0,Anp5,Ap5)
[…]

### 2016-02-12 constrained-optimization-yzinit.R
remove constrained-optimization-yzinit; superceded by A-optimization

@@ -1,55 +1,0 @@
-#optim function minimizes 'f'; c vector are starting values; lower is the
-#constraint; I choose a null gradient because it was easiest to get up and running
-#note that here the beta parameter is hard coded in as equal to 1
-
-h <- function(WB,al,y0,z0) {
-  
-f <- function(B,WB,al,y0,z0) {
-  Bp5 <- B[1]
-  B0 <- B[2]
-  Bnp5 <- B[3]
-  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
-}   
-
-al = 0
-y0=-.5
-o <- optim(c(1,1,1,WB,al,y0,z0),function(B) f(B,WB,al,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
-#o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
-
-X = round(- al + o$par[2], digits = 2)       #B0   these are shorthand variables for the exponents
-Y = round(-y0 - al + o$par[3], digits = 2)    #Bnp5  in the logistic CDFs; I don't use them in the function
-Z = round(-z0 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here to check
-
-pos <- c(Z,X,Y)
-bribes <- c(o$par,-o$value)
-win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-Z))) + (1/(1+exp(-X)))*(1/(1+exp(-Z)))*(1-1/(1+exp(-Y))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y)))*(1-1/(1+exp(-X))) + (1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
[…]

### 2016-02-12 A-optimization2.R
remake A-optim. as A-optimization2 to prepare for looping over WA and wB

@@ -1,0 +1,65 @@
+#optim function minimizes 'f'; c vector are starting values; lower is the
+#constraint; I choose a null gradient because it was easiest to get up and running
+#note that here the beta parameter is hard coded in as equal to 1
+WA=8
+WB=10
+al = 0
+
+h <- function(x0,y0,z0) {
+  
+  f <- function(B,x0,y0,z0) {
+    Bp5 <- B[1]
+    B0 <- B[2]
+    Bnp5 <- B[3]
+    -WB*((1/(1+exp(al +x0- B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al +x0- B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al +x0 - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
+  }   
+  
+  o <- optim(c(1,1,1,x0,y0,z0),function(B) f(B,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
+  
+  X = round(-x0 - al + o$par[2], digits = 3)       #B0   these are shorthand variables for the exponents
+  Y = round(-y0 - al + o$par[3], digits = 3)    #Bnp5  in the logistic CDFs; I don't use them in the function
+  Z = round(-z0 - al + o$par[1], digits=3)   #Bp5 but I've pasted in values here to check
+  
+  A0 = x0 
+  Ap5 = z0 - .5
+  Anp5 = y0 + .5
+  
+  pos <- c(Z,X,Y)
+  bribes <- c(o$par,-o$value)
+  bribesA <- c(A0,Anp5,Ap5)
+  win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y))) + (1/(1+exp(-X)))*(1/(1+exp(-Z))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y))) - 2*(1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
+  ValA = WA*(1-win) - A0 - Ap5 - Anp5
[…]

### 2016-02-12 A-optimization2.R
complete loop over WA in A-optim2

@@ -1,10 +1,17 @@
 #optim function minimizes 'f'; c vector are starting values; lower is the
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
-WA=8
-WB=10
 al = 0
+WB=8
 
+v = seq(4,12)
+o <- matrix(0,length(v),18)
+colnames(o) <- c("al","WA","WB","x", "y", "z","foe", "middle", "friend","Z", "X", "Y","value","wProbB","X_a", "Y_a", "Z_a","ValA")
+
+for (j in v[1]:v[length(v)]) {
+
+  WA = j
+  
 h <- function(x0,y0,z0) {
   
   f <- function(B,x0,y0,z0) {
@@ -60,6 +67,5 @@ val <- rbind(val)
 winProb <- rbind(winProb)
 params <- do.call("cbind",params)
 
-o <- matrix(0,length(1),18)
-colnames(o) <- c("al","WA","WB","x", "y", "z","foe", "middle", "friend","Z", "X", "Y","value","wProbB","X_a", "Y_a", "Z_a","ValA")
-o[1,] <- cbind(al,WA,WB,params,solns,netpos,val,winProb,bA)
+o[j-v[1]+1,] <- cbind(al,WA,WB,params,solns,netpos,val,winProb,bA)
+}

### 2016-02-12 two-groups.tex
add foc for vote buyer A
fix A's foc
add FOCs for parameterized uncertainty to two-groups

@@
 				\begin{enumerate}
-					\item $X_A = \alpha - b(0,a(0)) + a(0)$ 
-					\item $Y_A = -\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2},a\left(-\frac{1}{2}\right)\right)+ a\left(-\frac{1}{2}\right)$
-					\item $Z_A = \frac{\beta}{2} + \alpha - b\left(\frac{1}{2},a\left(\frac{1}{2}\right)\right)+ a\left(\frac{1}{2}\right)$
+					\item $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$ 
+					\item $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$
+					\item $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$
 				\end{enumerate}
+				with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$
+			\item Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
+			 \begin{multline}
+					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
+					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
+					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
+					\label{eq:focA}
+				\end{multline}
 		\end{itemize}
@@
 \end{itemize}
+
+\newpage
+\section{Parameterizing uncertainty that varies by legislator}
+\label{sec:uncert}
+I'm going to start by changing the uncertainty for just one legislator when there is just one vote buyer (B).
+I will do this for the legislator at position $-0.5$, which corresponds to $Y$.
+The FOCs become, for $Z$ (similarly for $X$, and from Equation~\ref{eq:logistic})
+	\begin{equation}
+		W_B \biggl[ \frac{e^{-X} + e^{-\frac{Y}{s_{-.5}}}}{\left(1+e^{-X}\right)\left(1+e^{-\frac{Y}{s_{-.5}}}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
+	\end{equation}
+	And for $Y$
+  \begin{equation}
+		W_B \biggl[ \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-\frac{Y}{s_{-.5}}}}{s_{-.5}\left[1+e^{-\frac{Y}{s_{-.5}}}\right]^2} \biggr]  = 1
+	\end{equation}
 

### 2016-02-13 constrained-optimization.r
modify constrainted-optim to handle non-standardized scale

@@ -1,14 +1,16 @@
 #optim function minimizes 'f'; c vector are starting values; lower is the
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
-
+rm(list = ls())
 h <- function(WB,al) {
+
+sy=1.2
   
 f <- function(B,WB,al) {
   Bp5 <- B[1]
   B0 <- B[2]
   Bnp5 <- B[3]
-  -WB*((1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bnp5))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bp5))) + (1/(1+exp(al + .5 - Bp5)))*(1/(1+exp(al - .5 - Bnp5))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp(al - .5 - Bnp5)))*(1/(1+exp(al + .5 - Bp5)))) + B0 + Bp5 + Bnp5
+  -WB*((1/(1+exp(al - B0)))*(1/(1+exp((al - .5 - Bnp5)/sy))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bp5))) + (1/(1+exp(al + .5 - Bp5)))*(1/(1+exp((al - .5 - Bnp5)/sy))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp((al - .5 - Bnp5)/sy)))*(1/(1+exp(al + .5 - Bp5)))) + B0 + Bp5 + Bnp5
 }   
 
 o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
@@ -20,7 +22,7 @@ Z = round(-.5 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here t
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
-win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y))) + (1/(1+exp(-X)))*(1/(1+exp(-Z))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y))) - 2*(1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
[…]

### 2016-02-13 constrained-optimization.r
modify constrainted-optim to handle non-standardized scale for Z

@@ -4,13 +4,14 @@
 rm(list = ls())
 h <- function(WB,al) {
 
-sy=1.2
+sy=1
+sz=1
   
 f <- function(B,WB,al) {
   Bp5 <- B[1]
   B0 <- B[2]
   Bnp5 <- B[3]
-  -WB*((1/(1+exp(al - B0)))*(1/(1+exp((al - .5 - Bnp5)/sy))) + (1/(1+exp(al - B0)))*(1/(1+exp(al + .5 - Bp5))) + (1/(1+exp(al + .5 - Bp5)))*(1/(1+exp((al - .5 - Bnp5)/sy))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp((al - .5 - Bnp5)/sy)))*(1/(1+exp(al + .5 - Bp5)))) + B0 + Bp5 + Bnp5
+  -WB*((1/(1+exp(al - B0)))*(1/(1+exp((al - .5 - Bnp5)/sy))) + (1/(1+exp(al - B0)))*(1/(1+exp((al + .5 - Bp5)/sz))) + (1/(1+exp((al + .5 - Bp5)/sz)))*(1/(1+exp((al - .5 - Bnp5)/sy))) - 2*(1/(1+exp(al - B0)))*(1/(1+exp((al - .5 - Bnp5)/sy)))*(1/(1+exp((al + .5 - Bp5)/sz)))) + B0 + Bp5 + Bnp5
 }   
 
 o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
@@ -22,7 +23,7 @@ Z = round(-.5 - al + o$par[1], digits=2)   #Bp5 but I've pasted in values here t
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
-win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y/sy))) + (1/(1+exp(-X)))*(1/(1+exp(-Z))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y/sy))) - 2*(1/(1+exp(-X)))*(1/(1+exp(-Y/sy)))*(1/(1+exp(-Z)))))
[…]

### 2016-02-14 two-groups.tex
add obj fcn with varying uncertainty to two-groups.tex
add notes on asymmetric uncertainty simulations

@@
 \newpage
-\section{Parameterizing uncertainty that varies by legislator}
+\section{Parameterizing Uncertainty to Vary by Legislator}
 \label{sec:uncert}
@@
 	\end{equation}
+
+\vskip.2in
+The same thing can be done for the legislator at position $0.5$. The objective function when both vary is
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} +
+					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} + \\
+					\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} - 2	\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+				\end{multline}
+
+\vskip.2in
+Now what impact does this have on Vote Buyer B's decisions (in the absence of bribes by Vote Buyer A)?
+\begin{itemize}
+	\item First, how does the probability that the legislator at $0.5$ (most unfriendly to $B$) votes with $B$ change when $s_{.5}$ goes from 1 to 2 (and there are no bribes)?
+		\begin{itemize}
+			\item When $s_{.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{1}}} = \frac{1}{1+e^{.5}} = 0.3775$
+			\item When $s_{.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{2}}} = \frac{1}{1+e^{.25}} = 0.4378$
+			\item That is, the probability that the least friendly legislator votes with $B$ \textit{rises}
+		\end{itemize}
+	\item Now, how does the probability that the legislator at $-0.5$ (most friendly to $B$) votes with $B$ change when $s_{-.5}$ goes from 1 to 2 (and there are no bribes)?
+		\begin{itemize}
+			\item When $s_{-.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{1}}} = \frac{1}{1+e^{-.5}} = 0.6225$
+			\item When $s_{-.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{2}}} = \frac{1}{1+e^{-.25}} = 0.5622$
+			\item That is, the probability that the least most legislator votes with $B$ \textit{falls}
+		\end{itemize}
+	\item Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
+		\begin{itemize}
+			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
+			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
+			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
+		\end{itemize}
+	\item Numerical example.
+Take $\al=0$ and ignore A.
+Take $s_{.5}$ from 1 to 1.5.
+$B$ stops bribing legislator $0.5$ (least friendly) altogether.
+Does better in welfare terms because the probability this guy votes in his favor shifts up
+		\begin{itemize}
+			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
+			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone).
+Then $Z$ and $Y$ together but $Z$ further on net than $Y$.
+Eventually all three, with $X=Y$, $Z$ further
+		\end{itemize}
+\end{itemize}
 

### 2016-02-14 A-optimization2.R
modify A-optim2 for asymmetric uncertainty

@@ -14,11 +14,14 @@ for (j in v[1]:v[length(v)]) {
   
 h <- function(x0,y0,z0) {
   
+  sy=1
+  sz=1
+  
   f <- function(B,x0,y0,z0) {
     Bp5 <- B[1]
     B0 <- B[2]
     Bnp5 <- B[3]
-    -WB*((1/(1+exp(al +x0- B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al +x0- B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al +x0 - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
+    -WB*((1/(1+exp(al + x0- B0)))*(1/(1+exp((al + y0 - Bnp5)/sy))) + (1/(1+exp(al +x0- B0)))*(1/(1+exp((al + z0 - Bp5)/sz))) + (1/(1+exp((al + z0 - Bp5)/sz)))*(1/(1+exp((al + y0 - Bnp5)/sy))) - 2*(1/(1+exp(al +x0 - B0)))*(1/(1+exp((al + y0 - Bnp5)/sy)))*(1/(1+exp((al + z0 - Bp5)/sz)))) + B0 + Bp5 + Bnp5
   }   
   
   o <- optim(c(1,1,1,x0,y0,z0),function(B) f(B,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
@@ -34,7 +37,7 @@ h <- function(x0,y0,z0) {
   pos <- c(Z,X,Y)
   bribes <- c(o$par,-o$value)
   bribesA <- c(A0,Anp5,Ap5)
-  win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y))) + (1/(1+exp(-X)))*(1/(1+exp(-Z))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y))) - 2*(1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
[…]

### 2016-02-14 A-optimization2.R
adjust A-optim2 to handle non-integer values

@@ -1,20 +1,21 @@
 #optim function minimizes 'f'; c vector are starting values; lower is the
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
+rm(list = ls())
 al = 0
 WB=8
 
-v = seq(4,12)
+v = seq(5,7,.2)
 o <- matrix(0,length(v),18)
 colnames(o) <- c("al","WA","WB","x", "y", "z","foe", "middle", "friend","Z", "X", "Y","value","wProbB","X_a", "Y_a", "Z_a","ValA")
 
-for (j in v[1]:v[length(v)]) {
+for (j in 1:length(v)) {
 
-  WA = j
+  WA = v[j]
   
 h <- function(x0,y0,z0) {
   
-  sy=1
+  sy=1.1
   sz=1
   
   f <- function(B,x0,y0,z0) {
@@ -70,5 +71,6 @@ val <- rbind(val)
 winProb <- rbind(winProb)
 params <- do.call("cbind",params)
 
-o[j-v[1]+1,] <- cbind(al,WA,WB,params,solns,netpos,val,winProb,bA)
+o[j,] <- cbind(al,WA,WB,params,solns,netpos,val,winProb,bA)
 }
+View(o)

### 2016-02-14 A-optimization2.R
add scale parameters to A-optim2 output

@@ -5,18 +5,17 @@ rm(list = ls())
 al = 0
 WB=8
 
-v = seq(5,7,.2)
-o <- matrix(0,length(v),18)
-colnames(o) <- c("al","WA","WB","x", "y", "z","foe", "middle", "friend","Z", "X", "Y","value","wProbB","X_a", "Y_a", "Z_a","ValA")
+v = seq(5,9,.4)
+o <- matrix(0,length(v),20)
+colnames(o) <- c("al","sy","sz","WA","WB","x", "y", "z","foe", "middle", "friend","Z", "X", "Y","value","wProbB","X_a", "Y_a", "Z_a","ValA")
 
 for (j in 1:length(v)) {
 
   WA = v[j]
+  sy=.9
+  sz=1.2
   
 h <- function(x0,y0,z0) {
-  
-  sy=1.1
-  sz=1
   
   f <- function(B,x0,y0,z0) {
     Bp5 <- B[1]
@@ -71,6 +70,6 @@ val <- rbind(val)
 winProb <- rbind(winProb)
 params <- do.call("cbind",params)
 
-o[j,] <- cbind(al,WA,WB,params,solns,netpos,val,winProb,bA)
+o[j,] <- cbind(al,sy,sz,WA,WB,params,solns,netpos,val,winProb,bA)
 }
 View(o)

### 2016-02-14 A-optimization.R
delete A-optimization.R b/c it was just a halfway point to new A-optim.R

@@ -1,62 +1,0 @@
-#optim function minimizes 'f'; c vector are starting values; lower is the
-#constraint; I choose a null gradient because it was easiest to get up and running
-#note that here the beta parameter is hard coded in as equal to 1
-WA=8
-
-h <- function(WB,al,x0,y0,z0) {
-  
-f <- function(B,WB,al,x0,y0,z0) {
-  Bp5 <- B[1]
-  B0 <- B[2]
-  Bnp5 <- B[3]
-  -WB*((1/(1+exp(al +x0- B0)))*(1/(1+exp(al + y0 - Bnp5))) + (1/(1+exp(al +x0- B0)))*(1/(1+exp(al + z0 - Bp5))) + (1/(1+exp(al + z0 - Bp5)))*(1/(1+exp(al + y0 - Bnp5))) - 2*(1/(1+exp(al +x0 - B0)))*(1/(1+exp(al + y0 - Bnp5)))*(1/(1+exp(al + z0 - Bp5)))) + B0 + Bp5 + Bnp5
-}   
-
-WB=10
-al = 0
-o <- optim(c(1,1,1,WB,al,x0,y0,z0),function(B) f(B,WB,al,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
-
-X = round(-x0 - al + o$par[2], digits = 3)       #B0   these are shorthand variables for the exponents
-Y = round(-y0 - al + o$par[3], digits = 3)    #Bnp5  in the logistic CDFs; I don't use them in the function
-Z = round(-z0 - al + o$par[1], digits=3)   #Bp5 but I've pasted in values here to check
-
-A0 = x0 
-Ap5 = z0 - .5
-Anp5 = y0 + .5
-
-pos <- c(Z,X,Y)
-bribes <- c(o$par,-o$value)
-bribesA <- c(A0,Anp5,Ap5)
-win <- c(((1/(1+exp(-X)))*(1/(1+exp(-Y))) + (1/(1+exp(-X)))*(1/(1+exp(-Z))) + (1/(1+exp(-Z)))*(1/(1+exp(-Y))) - 2*(1/(1+exp(-X)))*(1/(1+exp(-Y)))*(1/(1+exp(-Z)))))
-ValA = WA*(1-win) - A0 - Ap5 - Anp5
[…]

### 2016-02-14 draft.tex
move NSF text between sec:house and sec:est
add NSF references to draft

@@
 
+The model is based on that of Banks (2000)
+
 %If we're going to do an empirical implementation of $\ga$ below, model needs to start with a basic understanding of uncertainty, run through lobbying response to it, up through aggregation into $\ga$ and how lobbying behavior turns into a ``yea'' vote total.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[height=3in, width=6.5in]{NSF_combined_graph.pdf}
-\end{center}
-\caption{Uncertainty by Industry\label{fig:combined}}
-\end{figure}
-
-\textcolor{blue}{We `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position.
-This produces estimates for how ``friendly'' or ``unfriendly'' each legislator is with respect to each interest group, as well as the unpredictability of his/her voting behavior when matters affecting that group are considered.
-In a preliminary run of this model with just ten interest groups (out of over 450) in the 112th Congress displayed in Figure~\ref{fig:combined}, we find that the chemical industry has the lowest average uncertainty (sd = 0.229); this is lower than the total uncertainty measure that can be interpreted as the standard left-right measure in ideal point models (sd = 0.233).
-The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).}
-
 \textcolor{blue}{We are experimenting with some of the more sophisticated measures of uncertainty that are possible with a rich model such as this one; for instance the group mean for $\ga$ and constructs that combine model parameters.}
-
-\textcolor{blue}{Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
-First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight (as explained above).}
-
-\textcolor{blue}{We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
-We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.
-From the data analysis that is represented above, we see a very interesting relationship between uncertainty and lobbying expenditure across legislators at the aggregate level in Figure~\ref{fig:br}, and we expect that additional important patterns will emerge when the data is disaggregated by industry.}
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[height=3in, width=6.5in]{NSF_combined_graph.pdf}
+\end{center}
+\caption{Uncertainty by Industry\label{fig:combined}}
+\end{figure}
+
+\textcolor{blue}{We `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position.
+This produces estimates for how ``friendly'' or ``unfriendly'' each legislator is with respect to each interest group, as well as the unpredictability of his/her voting behavior when matters affecting that group are considered.
+In a preliminary run of this model with just ten interest groups (out of over 450) in the 112th Congress displayed in Figure~\ref{fig:combined}, we find that the chemical industry has the lowest average uncertainty (sd = 0.229); this is lower than the total uncertainty measure that can be interpreted as the standard left-right measure in ideal point models (sd = 0.233).
+The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).}
+
+\textcolor{blue}{Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
+First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight (as explained above).}
+
+\textcolor{blue}{We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
+We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.
+From the data analysis that is represented above, we see a very interesting relationship between uncertainty and lobbying expenditure across legislators at the aggregate level in Figure~\ref{fig:br}, and we expect that additional important patterns will emerge when the data is disaggregated by industry.}
+
 %\subsection{Break Decision}
@@
 
-\item Becker, G., (1983) ``A Theory of Competition among Interest Groups for Political Influence.'' {\em Quarterly Journal of Economics} 98, 371-400.
+\item Banks, J. S., (2000), ``Buying Supermajorities in Finite Legislatures.'' {\em The American Political Science Review} 94, 677-681.
+
+\item Becker, G., (1983), ``A Theory of Competition among Interest Groups for Political Influence.'' {\em Quarterly Journal of Economics} 98, 371-400.
 
@@
 
+\item Bafumi, J., Gelman, A., Park., D, Kaplan, N., 2005. Practical Issues in Implementing and Understanding Bayesian Ideal Point Estimation. Political Analysis 13, 171-187.
+
+	\item Buzard, K., 2014a. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.
+
+	\item Buzard, K., 2014b.
+Self-enforcing Trade Agreements, Dispute Settlement and Separation of Powers.
+Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/2014/04/Self-enforcing-Trade_Agreements.pdf}.
+
+\begin{sloppypar}	
+	\item Buzard, K., 2014c. Trade Agreements in the Shadow of Lobbying. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/TradeAgreements_Shadow_Lobbying.pdf}.
+		\end{sloppypar}
+
+	\item Coates, D., Ludema, R., 2001. A Theory of Trade Policy Leadership. Journal of Development Economics 65, 1-29.
+
+	\item Conconi, P., Facchini, G., Steinhardt, M.
+F., Zanardi, M., 2012.
+The political economy of trade and migration: Evidence from the US Congress.
+HWWI Research Paper 136.
+Available at: \url{http://hdl.handle.net/10419/67944}.
+
+	\item Dixit, A., Grossman, G., Helpman, E., 1997. Common Agency and Coordination: General Theory and Application to Government Policy Making. Journal of Political Economy 105, 752-769.
+
+	\item Feenstra, R., 1992. How Costly is Protectionism? Journal of Economic Perspectives 6, 159-178.
+
+	\item Gawande, K., Bandyopadhyay, U., 2000. Is Protection for Sale? Evidence on the Grossman-Helpman Theory of Endogenous Protection. The Review of Economics and Statistics 82, 139-152.
+
+	\item Gawande, K., Krishna, P., Olarreaga, M., 2009. What Governments Maximize and Why: The View from Trade. International Organization 63, 491-532.
+
+	\item Gawande, K., Krishna, P., Olarreaga, M., 2012. Lobbying Competition over Trade Policy. International Economic Review 53, 115-132.
+
+	\item Grossman, G., Helpman, E., 1995a. The Politics of Free-Trade Agreements. The American Economic Review 85, 667-690.
+
+	\item Grossman, G., Helpman, E., 1995b. Trade Wars and Trade Talks. The Journal of Political Economy 103, 675-708.
+
+	\item Iaryczower, M., Katz, G., Saiegh, S., 2013. Voting in the Bicameral Congress: Large Majorities as a Signal of Quality. Forthcoming in Journal of Law, Economics, and Organization.
+
+  \item Iida, K., 1996. Involuntary Defection in Two-Level Games. Public Choice 89, 283-303.
+
+	\item Lake, J., Millimet, D., 2014a.
+An Empirical Analysis of Trade-Related Redistribution and the Political Viability of Free Trade.
+Available at: \url{http://people.smu.edu/jlake/pdfs/VotingFTAs.pdf}
+
+	\item Lake, J., Millimet, D., 2014b. Revisiting the link between PAC Contributions and Lobbying Expenditures. Available at: \url{http://people.smu.edu/jlake/pdfs/PACcontributionsLobbying.pdf}
+
+	\item Mansfield, E., Milner, H., 2012. Votes, Vetoes, and the Political Economy of International Trade Agreements. Princeton and Oxford: Princeton  University Press.
+
+	\item Milner, H., Rosendorff, B.P., 1997.
+Democratic Politics and International trade Negotiations: Elections and Divided Government as Constraints on Trade Liberalization.
+Journal of Conflict Resolution 41, 117-147.
+
+	\item Ornelas, E., 2005. Rent Destruction and the Political Viability of Free Trade Agreements. Quarterly Journal of Economics 120, 1475-1506.
+
 \end{list}

### 2016-02-14 draft.tex
write model basics: payoff functions

@@
 
-The model is based on that of Banks (2000)
+The model is based on Banks' (2000) model of vote buying in a legislature, which is in turn a discrete version of Groseclose and Snyder's (1996) model with a continuum of legislators.
+The major difference here is the addition of uncertainty about the legislator's ideal points.
+
+Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$.
+The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units.
+Note that legislators only have preferences about how they vote, not over which alternative wins.
+
+There are two vote buyers labeled $A$ and $B$ who each prefers to maximize the expected value of his preferred policy net of the bribes he has to pay.
+$A$ prefers policy $x$ and has willingness to pay (WTP) $W_A$ for $x$ measured in money and values $s$ at zero.
+$B$ prefers $s$and has WTP $W_B$ for $s$.
+Each vote buyer would prefer to concede the issue rather than pay more than his WTP.
+
+Vote Buyer $A$ moves first, providing a bribe offer function $a(i)$.
+$a(i)$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b(i)$.
+Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff.
+I assume unbribed legislators who are indifferent vote for $s$ and that all bribed legislators who are indifferent vote for whoever bribed them last.
+
+(Remember that I've assumed a very specific functional form)
 
@@
 \label{sec:res}
+
+Goal: characterize SPNE in pure strategies
 

### 2016-02-15 draft.tex
write prop:2NNB

@@
 \newtheorem{result}{Result}
+\newtheorem{proposition}{Proposition}
 
@@
 Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff.
-I assume unbribed legislators who are indifferent vote for $s$ and that all bribed legislators who are indifferent vote for whoever bribed them last.
+I assume unbribed legislators who are indifferent vote for $s$.
 
@@
 
+Goal: characterize SPNE in pure strategies
+
 \section{Some Theoretical Results}
@@
 
-Goal: characterize SPNE in pure strategies
+I begin by examining the subgame that begins when Vote Buyer $B$ makes his offer.
+This not only serves to elucidate the basic logic of the model; it will also serve as a baseline from which to examine the incentives of Vote Buyer $A$.
+For now, assume that the uncertainty about each legislator's ideal point is the same.
+
+In a legislature with three voters, Vote Buyer $B$ can choose to bribe all three legislators, two, one or none of the legislators.
+It is most instructive to begin with the case where he bribes two of the legislators.
+
+\begin{proposition}
+  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that their ideal points net of the bribes are equalized.
+Which two voters are bribed depends on the bias parameter $\al$.
+	\label{prop:2NNB}
+\end{proposition}
 

### 2016-02-15 draft.tex
add proof of prop:2NNB

@@
 (Remember that I've assumed a very specific functional form)	
+\begin{itemize}
+	\item use $\al$ in prop:2NNB
+\end{itemize}
 
@@
 This not only serves to elucidate the basic logic of the model; it will also serve as a baseline from which to examine the incentives of Vote Buyer $A$.
-For now, assume that the uncertainty about each legislator's ideal point is the same.
+For now, assume that the uncertainty about ideal points is the same across legislators.
 
@@
 \begin{proposition}
-  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that their ideal points net of the bribes are equalized.
+  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points net of the bribes are equalized.
 Which two voters are bribed depends on the bias parameter $\al$.
@@
 \end{proposition}
+
+All proofs are in the Appendix.
 
@@
 \section*{Appendix}
+\label{sec:app}
+\noindent \textbf{\hypertarget{Pr_2NNB}{Proof of Proposition~\ref{prop:2NNB}}}: \\
+Without loss of generality, assume that it is the legislators at $-\frac{1}{2}$ and $0$ that are bribed. The first order conditions with respect to the bribes for these two legislators are
+	\begin{equation}
+		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
+	\end{equation}
+	and
+	\begin{equation}
+		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+		\label{eq:base}
+	\end{equation}
+
+		Setting the left-hand size of these two equations equal to each other and simplifying,
+		\[
+		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
+		\]
+		\[
+		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
+		\]
+		\[
+		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
+		\]
+		\[
+		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
+		\]
+		\[
+		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
+		\]
+		\begin{equation}
+		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
+			\label{eq:twoways}
+		\end{equation}
+   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
+		\[
+		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
+		\]
+		\begin{equation}
+		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
+			\label{eq:1}
+		\end{equation}
+  	Second, multiplying through by zero:
+	  \begin{equation}
+		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
+			\label{eq:2}
+		\end{equation}
+
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$.
+Note that this is due to the construction of the problem.
+This means $e^Z < 1$.
+In this case,
+	\begin{itemize}
+		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
+		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
+	\end{itemize}
+The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$.
+Note that once this is known, one can go back to, for instance, Equations~\ref{eq:base} and substitute for one of the variables.
+Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.
 

### 2016-02-15 draft.tex
paste model section from two-groups into draft and convert most of leg to text

@@
 I assume unbribed legislators who are indifferent vote for $s$.
+
+\subsection{Legislature}
+Let us look first at the legislature.
+Each legislator $i$ decides whether to vote for $x$ or $s$ given her preference $i$, $a(i)$ and $b(i)$.
+Although legislators are ordered on the interval according to their ideal points $i$, there is acknowledged uncertainty surrounding their preferences.
+We take this uncertainty to vary by legislator and also potentially by issue area when we extend the model to account for multi-dimensional voting and vote-buying.
+
+In order to keep the model tractable when introduing this uncertainty, we take the ideal point function to be linear in $i$.
+That is, legislator $i$'s ideal point is taken to be $\alpha -\beta i$.
+We model uncertainty by taking legislator $i$ to vote for $x$ if
+			  \[
+				  v(i) = \alpha -\beta i + \ve_i + a(i) - b(i) > 0
+				\]
+
+Notice that a bribe from $B$ is subtracted because it makes the alternative \textit{less} attractive.	We will begin by taking $\ve$ to not vary in $i$ and will shortly generalize.
+
+Given these assumptions, the probability that legislator $i$ votes against the new proposal is
+	\[
+					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a(i) - b(i) \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a(i) + b(i) \right] 
+	\]
+Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a(i) + b(i) \right)}}$.
+
+For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$. For ease of notation, let
+				\begin{enumerate}
+					\item $X = -\alpha + b(0)$ 
+					\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
+					\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\label{page:sh}$ 
+				\end{enumerate}
+
+\begin{itemize}	
+			\item Then the three probabilities are
+				\begin{itemize}
+					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$
+					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
+						\[
+							X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
+						\]
+				\end{itemize}
+		\end{itemize}
+
+\begin{enumerate}
+\item Vote buyer B
+		\begin{itemize}
+			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''; this has to be adapted to our situation with uncertainty
+			\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
+			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
+			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
+			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
+			\item Some legislators who are past FOC point will not be lobbied		
+			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
+			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
+					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+				\end{multline}
+			Substituting from the definition of $X$,
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
+					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
+					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
+					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+				\end{multline}
+			This can be simplified as 
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
+					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
+					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+					\label{eq:objb}
+				\end{multline}
+
+			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
+				\begin{equation}
+					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
+				\end{equation}
+			Simplifying:
+				\begin{equation}
+					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
+					\label{eq:logistic}
+				\end{equation}
+			Further math related to this equation is on Page~\pageref{eq:logistic2}.
+			\item If we divide through by 2, the left side is the average minus the product
+			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
+		\end{itemize}
+	\item Vote Buyer A
+		\begin{itemize}
+			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
+			  \begin{multline}
+			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
+					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
+					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
+					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
+					\label{eq:obja}
+				\end{multline}
+				where 
+				\begin{enumerate}
+					\item $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$ 
+					\item $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$
+					\item $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$
+				\end{enumerate}
+				with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$
+			\item Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
+			 \begin{multline}
+					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
+					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
+					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
+					\label{eq:focA}
+				\end{multline}
+		\end{itemize}
+\end{enumerate}
+
+\subsection{Adding Non-negativity Constraints for Bribes}
+\label{sec:nonneg}
+The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(-\frac{1}{2}\right) + \lambda_Z b\left(\frac{1}{2}\right)$
+
+The full set of FOCs (in logistic form) is then:
+\[
+    W_B\frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_X = 0
+\]
+\[
+    W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1 + \lambda_Y = 0 
+\]
+\[
+    W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_Z = 0
+\]
+\[
+  b\left(0\right) \geq0 \hskip.2in b\left(\frac{1}{2}\right) \geq0 \hskip.2in b\left(-\frac{1}{2}\right) \geq0 
+\]
+\[
+  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
+\]
+\[
+  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(\frac{1}{2}\right) = 0 
+\]
+There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = \left(b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\
+
+Note that the complementary slackness condition implies that either a bribe is zero, \un{or} its multiplier is zero (or both).
+
+\vskip.5in
+Simulations show that for many sets of parameters, $b\left(0\right)$ and $b\left(\frac{1}{2}\right)$ are positive while $b\left(-\frac{1}{2}\right) = 0$.
+\begin{itemize}
+	\item Then $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = \frac{\beta}{2} - \alpha $
+	\item $\lambda_Y$ is likely positive
+	\item $\lambda_X = \lambda_Z = 0$
+\end{itemize}
+
+\subsection{Parameterizing Uncertainty to Vary by Legislator}
+\label{sec:uncert}
+I'm going to start by changing the uncertainty for just one legislator when there is just one vote buyer (B).
+I will do this for the legislator at position $-0.5$, which corresponds to $Y$.
+The FOCs become, for $Z$ (similarly for $X$, and from Equation~\ref{eq:logistic})
+	\begin{equation}
+		W_B \biggl[ \frac{e^{-X} + e^{-\frac{Y}{s_{-.5}}}}{\left(1+e^{-X}\right)\left(1+e^{-\frac{Y}{s_{-.5}}}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
+	\end{equation}
+	And for $Y$
+  \begin{equation}
+		W_B \biggl[ \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-\frac{Y}{s_{-.5}}}}{s_{-.5}\left[1+e^{-\frac{Y}{s_{-.5}}}\right]^2} \biggr]  = 1
+	\end{equation}
+
+\vskip.2in
+The same thing can be done for the legislator at position $0.5$. The objective function when both vary is
+			  \begin{multline}
+			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} +
+					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} + \\
+					\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} - 2	\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+				\end{multline}
+
+\vskip.2in
+Now what impact does this have on Vote Buyer B's decisions (in the absence of bribes by Vote Buyer A)?
+\begin{itemize}
+	\item First, how does the probability that the legislator at $0.5$ (most unfriendly to $B$) votes with $B$ change when $s_{.5}$ goes from 1 to 2 (and there are no bribes)?
+		\begin{itemize}
+			\item When $s_{.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{1}}} = \frac{1}{1+e^{.5}} = 0.3775$
+			\item When $s_{.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{2}}} = \frac{1}{1+e^{.25}} = 0.4378$
+			\item That is, the probability that the least friendly legislator votes with $B$ \textit{rises}
+		\end{itemize}
+	\item Now, how does the probability that the legislator at $-0.5$ (most friendly to $B$) votes with $B$ change when $s_{-.5}$ goes from 1 to 2 (and there are no bribes)?
+		\begin{itemize}
+			\item When $s_{-.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{1}}} = \frac{1}{1+e^{-.5}} = 0.6225$
+			\item When $s_{-.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{2}}} = \frac{1}{1+e^{-.25}} = 0.5622$
+			\item That is, the probability that the least most legislator votes with $B$ \textit{falls}
+		\end{itemize}
+	\item Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
+		\begin{itemize}
+			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
+			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
+			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
+		\end{itemize}
+	\item Numerical example.
+Take $\al=0$ and ignore A.
+Take $s_{.5}$ from 1 to 1.5.
+$B$ stops bribing legislator $0.5$ (least friendly) altogether.
+Does better in welfare terms because the probability this guy votes in his favor shifts up
+		\begin{itemize}
+			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
+			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone).
+Then $Z$ and $Y$ together but $Z$ further on net than $Y$.
+Eventually all three, with $X=Y$, $Z$ further
+		\end{itemize}
+\end{itemize}
+
+\newpage
+\subsection{Intuition}
+\begin{itemize}
+	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
+		\[
+		  v(z) = \al - \beta z + a(z) - b(z) > 0
+		\]
+	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
+		\[
+		  \al - \beta z - b(z) < 0
+		\]
+
+		\begin{center}
+		or 
+		\end{center}
+		\[
+		  \beta z - \al + b(z) > 0
+		\]
+		\item If $\al > 0$, legislators on average are biased against B.
+			\begin{itemize}
+				\item If $\al < 0$, legislators on average are biased in favor of B.
+				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
+			\end{itemize}
+		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
+\end{itemize}
+
+\vskip.1in
+Recall:
+		\begin{enumerate}
+			\item $X = -\alpha + b(0)$ 
+			\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
+			\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$ 
+		\end{enumerate}
+
+\vskip.1in
+Pattern more or less is to get the guy who is WHAT?
+\begin{itemize}
+	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
+	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
+		\begin{itemize}
+			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
+		\end{itemize}
+\end{itemize}
+
+\vskip.1in
+The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
+\begin{itemize}
+	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
+	\item What's the intuition for why they should be equal?
+As far as I can tell, it's that the PDF is unimodal.
+If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
+	\item \textbf{Next question: How general is this result?
+That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
+My conjecture is that it leans on having an interior single mode}
+\end{itemize}
 

### 2016-02-15 draft.tex
finish legislator section of sec:model

@@
 
-Vote Buyer $A$ moves first, providing a bribe offer function $a(i)$.
-$a(i)$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b(i)$.
+Vote Buyer $A$ moves first, providing a bribe offer function $a_i$.
+$a_i$ is perfectly observable to Vote Buyer $B$ when he moves second and offers bribe offer function $b_i$.
 Each legislator takes these bribe offers as given and then votes for the alternative that maximizes her payoff.
@@
 Let us look first at the legislature.
-Each legislator $i$ decides whether to vote for $x$ or $s$ given her preference $i$, $a(i)$ and $b(i)$.
+Each legislator $i$ decides whether to vote for $x$ or $s$ given her preference $i$, $a_i$ and $b_i$.
 Although legislators are ordered on the interval according to their ideal points $i$, there is acknowledged uncertainty surrounding their preferences.
@@
 			  \[
-				  v(i) = \alpha -\beta i + \ve_i + a(i) - b(i) > 0
+				  v(i) = \alpha -\beta i + \ve_i + a_i - b_i > 0
 				\]
@@
 	\[
-					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a(i) - b(i) \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a(i) + b(i) \right] 
+					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a_i - b_i \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a_i + b_i \right] 
 	\]
-Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a(i) + b(i) \right)}}$.
+Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$.	Whether a legislator $i$ votes ``no'' is a random variable, denote it $Q(i)$, distributed Bernoulli with this probability:
+	\[
+		Q(i) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha -a_i+ b_i \right)}}
+	\]
 
-For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$. For ease of notation, let
-				\begin{enumerate}
-					\item $X = -\alpha + b(0)$ 
-					\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
-					\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)\label{page:sh}$ 
-				\end{enumerate}
+For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$.
+Then $Y_B = \frac{\beta}{2} - \alpha - a_{-\frac{1}{2}} + b_{-\frac{1}{2}}$, $X_B = -\alpha - a_0+ b_0$ and $Z_B = -\frac{\beta}{2} - \alpha - a_{\frac{1}{2}} + b_{\frac{1}{2}}\label{page:sh}$ represent the net ideal points in terms of $B$'s probability of winning the issue.
+We can then write the probability that each of the legislators, respectively, votes against the new proposal as $\frac{1}{1+e^{-Y_B}}$, $\frac{1}{1+e^{-X_B}}$ and $\frac{1}{1+e^{-Z_B}}$.
 
-\begin{itemize}	
-			\item Then the three probabilities are
-				\begin{itemize}
-					\item $\frac{1}{1+e^{-\left(- \alpha + b(0) \right)}} = \frac{1}{1+e^{-X}}$, $\frac{1}{1+e^{-\left(\frac{\beta}{2}- \alpha + b(\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Z}}$, $\frac{1}{1+e^{-\left(-\frac{\beta}{2}- \alpha + b(-\frac{1}{2}) \right)}} = \frac{1}{1+e^{-Y}}$
-					\item Whether a legislator $z$ votes ``no'' is a random variable, denote it $X(z)$, distributed Bernoulli with this probability:
-						\[
-							X(z) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha + b(z) \right)}}
-						\]
-				\end{itemize}
-		\end{itemize}
+Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes.
+So the net ideal points from her point of view---that is, in terms of her winning the issue---are $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$, $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$, and $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$.
+We can then write the probability that each of the legislators votes for the new proposal as $\frac{1}{1+e^{-Y_A}}$, $\frac{1}{1+e^{-X_A}}$ and $\frac{1}{1+e^{-Z_A}}$.
 
@@
 				\end{equation}
-			Further math related to this equation is on Page~\pageref{eq:logistic2}.
 			\item If we divide through by 2, the left side is the average minus the product

### 2016-02-15 draft.tex
finish vote buyer subsections of sec:model

@@
 Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes.
-So the net ideal points from her point of view---that is, in terms of her winning the issue---are $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$, $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$, and $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$.
+So the net ideal points from her point of view---that is, in terms of her winning the issue---are $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$, $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$, and $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$ with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$.
 We can then write the probability that each of the legislators votes for the new proposal as $\frac{1}{1+e^{-Y_A}}$, $\frac{1}{1+e^{-X_A}}$ and $\frac{1}{1+e^{-Z_A}}$.
 
-\begin{enumerate}
-\item Vote buyer B
-		\begin{itemize}
-			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''; this has to be adapted to our situation with uncertainty
-			\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
-			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
-			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
-			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
-			\item Some legislators who are past FOC point will not be lobbied		
-			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
-			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
+\subsection{Vote Buyer B}
+Groseclose and Snyder (1996) assume that the objective of each vote buyer is to ``minimize total bribes paid while passing his preferred policy.'' This has to be adapted out our environment with uncertainty about legislators' ideal points.
+The appropriate analog is that vote buyers maximize the expected value of winning the vote net of bribes that he/she must pay.
+Note that in order to maximize the probability of winning a majority in a three-seat legislature, one must maximize the probability of at least two legislators voting with you.
+The case of Vote Buyer $B$, this is the probability that at least two legislators vote in favor of the status quo: $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$.
+
+This means that the maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
 			  \begin{multline}
-			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+			    \max_{b_{-\frac{1}{2}}, b_0, b_{\frac{1}{2}}} 
 					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
@@
 					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
-					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b_j
 				\end{multline}
@@
 			  \begin{multline}
-			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+			    \max_{b_{-\frac{1}{2}}, b_0, b_{\frac{1}{2}}} 
 					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
@@
 					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
-					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b_j
 				\end{multline}
@@
 			  \begin{multline}
-			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
+			    \max_{b_{-\frac{1}{2}}, b_0, b_{\frac{1}{2}}} 
 					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
 					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
-					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b_j
 					\label{eq:objb}
@@
 
-			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
-				\begin{equation}
-					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
-				\end{equation}
-			Simplifying:
-				\begin{equation}
-					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
-					\label{eq:logistic}
-				\end{equation}
-			\item If we divide through by 2, the left side is the average minus the product
-			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
-		\end{itemize}
-	\item Vote Buyer A
-		\begin{itemize}
-			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
+\subsection{Vote Buyer A}
+Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
 			  \begin{multline}
-			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
+			    \max_{a_{-\frac{1}{2}}, a_0, a_{\frac{1}{2}}} 
 					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
 					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
-					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
+					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a_j .
 					\label{eq:obja}
 				\end{multline}
-				where 
-				\begin{enumerate}
-					\item $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$ 
-					\item $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$
-					\item $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$
-				\end{enumerate}
-				with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$
-			\item Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
-			 \begin{multline}
-					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
-					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
-					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
-					\label{eq:focA}
-				\end{multline}
-		\end{itemize}
-\end{enumerate}
+
+However, strategically Vote Buyer A is more complex because of the dependence of Vote Buyer $B$'s bids on her own.
 
@@
 All proofs are in the Appendix.
+
+\begin{itemize}
+				\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
+			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
+			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
+			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
+			\item Some legislators who are past FOC point will not be lobbied
+
+\end{itemize}
+
+\vskip.5in
+Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
+			 \begin{multline}
+					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
+					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
+					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
+					\label{eq:focA}
+				\end{multline}
 

### 2016-02-15 draft.tex
turn sec:nonneg into text

@@
 
-\subsection{Adding Non-negativity Constraints for Bribes}
+\subsection{Non-negativity Constraints for Bribes}
 \label{sec:nonneg}
-The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, adding on $\lambda_X b\left(0\right) + \lambda_Y b\left(-\frac{1}{2}\right) + \lambda_Z b\left(\frac{1}{2}\right)$
+It is not possible for a Vote Buyer to extract money from a legislator who is more favorably-inclined toward him than is optimal. This means that there are non-negativity constraints on all bribes.
 
-The full set of FOCs (in logistic form) is then:
+The Lagrangian for the problem is the same as Expression~\ref{eq:objb}, with the addition of three terms for the non-negativity constraints: $\lambda_X b_0 + \lambda_Y b_{-\frac{1}{2}} + \lambda_Z b_{\frac{1}{2}}$.
+Thus the full set of first order conditions are
 \[
@@
 \]
-There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = \left(b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\
-
-Note that the complementary slackness condition implies that either a bribe is zero, \un{or} its multiplier is zero (or both).
-
-\vskip.5in
-Simulations show that for many sets of parameters, $b\left(0\right)$ and $b\left(\frac{1}{2}\right)$ are positive while $b\left(-\frac{1}{2}\right) = 0$.
-\begin{itemize}
-	\item Then $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = \frac{\beta}{2} - \alpha $
-	\item $\lambda_Y$ is likely positive
-	\item $\lambda_X = \lambda_Z = 0$
-\end{itemize}
 

### 2016-02-15 draft.tex
finish model section by turning sec:uncert into text

@@
 
-\subsection{Parameterizing Uncertainty to Vary by Legislator}
+\subsection{Varying Uncertainty across Legislators}
 \label{sec:uncert}
-I'm going to start by changing the uncertainty for just one legislator when there is just one vote buyer (B).
-I will do this for the legislator at position $-0.5$, which corresponds to $Y$.
-The FOCs become, for $Z$ (similarly for $X$, and from Equation~\ref{eq:logistic})
-	\begin{equation}
-		W_B \biggl[ \frac{e^{-X} + e^{-\frac{Y}{s_{-.5}}}}{\left(1+e^{-X}\right)\left(1+e^{-\frac{Y}{s_{-.5}}}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
-	\end{equation}
-	And for $Y$
-  \begin{equation}
-		W_B \biggl[ \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-\frac{Y}{s_{-.5}}}}{s_{-.5}\left[1+e^{-\frac{Y}{s_{-.5}}}\right]^2} \biggr]  = 1
-	\end{equation}
-
-\vskip.2in
-The same thing can be done for the legislator at position $0.5$. The objective function when both vary is
+We allow the amount of uncertainty regarding each legislator's ideal point to vary across legislators by letting the scale parameter of the logistic distribution be different for each legislator.
+A larger scale parameter is associated with greater variance and thus more uncertainty as to the legislator's ideal point.
+The objective function for Vote Buyer $B$ becomes
  \begin{multline}
-			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
-					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} +
-					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} + \\
-					\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} - 2	\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
+    \max_{b_{-\frac{1}{2}}, b_0, b_{\frac{1}{2}}} 
+					W_B \biggl[ \frac{1}{1+e^{-\frac{X}{s_0}}} \frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} +
+					\frac{1}{1+e^{-\frac{X}{s_0}}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} + \\
+					\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} - 2	\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} \frac{1}{1+e^{-\frac{X}{s_0}}} \frac{1}{1+e^{-\frac{Z}{s_{.5}}}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b_j
 	\end{multline}
 
-\vskip.2in
-Now what impact does this have on Vote Buyer B's decisions (in the absence of bribes by Vote Buyer A)?
-\begin{itemize}
-	\item First, how does the probability that the legislator at $0.5$ (most unfriendly to $B$) votes with $B$ change when $s_{.5}$ goes from 1 to 2 (and there are no bribes)?
-		\begin{itemize}
-			\item When $s_{.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{1}}} = \frac{1}{1+e^{.5}} = 0.3775$
-			\item When $s_{.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{2}}} = \frac{1}{1+e^{.25}} = 0.4378$
-			\item That is, the probability that the least friendly legislator votes with $B$ \textit{rises}
-		\end{itemize}
-	\item Now, how does the probability that the legislator at $-0.5$ (most friendly to $B$) votes with $B$ change when $s_{-.5}$ goes from 1 to 2 (and there are no bribes)?
-		\begin{itemize}
-			\item When $s_{-.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{1}}} = \frac{1}{1+e^{-.5}} = 0.6225$
-			\item When $s_{-.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{2}}} = \frac{1}{1+e^{-.25}} = 0.5622$
-			\item That is, the probability that the least most legislator votes with $B$ \textit{falls}
-		\end{itemize}
-	\item Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
-		\begin{itemize}
-			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
-			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
-			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
-		\end{itemize}
-	\item Numerical example.
-Take $\al=0$ and ignore A.
-Take $s_{.5}$ from 1 to 1.5.
-$B$ stops bribing legislator $0.5$ (least friendly) altogether.
-Does better in welfare terms because the probability this guy votes in his favor shifts up
-		\begin{itemize}
-			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
-			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone).
-Then $Z$ and $Y$ together but $Z$ further on net than $Y$.
-Eventually all three, with $X=Y$, $Z$ further
-		\end{itemize}
-\end{itemize}
+We will see that allowing for this asymmetric uncertainty changes the predictions of the model in important ways.
+To lay the groundwork for the results to coming in Section~\ref{sec:resunc}, let's look at how the cumulative probabilities change for the most extreme legislators when the mean of their ideal point distribution is fixed but the scale parameter increases.
 
-\newpage
-\subsection{Intuition}
-\begin{itemize}
-	\item A legislator votes for $x$ (A's preferred policy, against the status quo) if 
-		\[
-		  v(z) = \al - \beta z + a(z) - b(z) > 0
-		\]
-	\item B needs 2 ``no'' votes, or two legislators with $v(z) < 0$. When $a(z) = 0$, this is
-		\[
-		  \al - \beta z - b(z) < 0
-		\]
+First, how does the probability that the legislator at $0.5$ (the one who is most unfriendly to $B$) votes with $B$ change when $s_{.5}$ goes from 1 to 2 in the absence of bribes?
+When $s_{.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{1}}} = \frac{1}{1+e^{.5}} = 0.3775$.
+When $s_{.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Z}{s_{.5}}}} = \frac{1}{1+e^{-\frac{-.5}{2}}} = \frac{1}{1+e^{.25}} = 0.4378$.
+That is, the probability that the least friendly legislator votes with $B$ \textit{rises} when the uncertainty surrounding her ideal point increases.
 
-		\begin{center}
-		or 
-		\end{center}
-		\[
-		  \beta z - \al + b(z) > 0
-		\]
-		\item If $\al > 0$, legislators on average are biased against B.
-			\begin{itemize}
-				\item If $\al < 0$, legislators on average are biased in favor of B.
-				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
-			\end{itemize}
-		\item If $X,Y,$ or $Z$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
-\end{itemize}
-
-\vskip.1in
-Recall:
-		\begin{enumerate}
-			\item $X = -\alpha + b(0)$ 
-			\item $Y = \frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
-			\item $Z = -\frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$ 
-		\end{enumerate}
-
-\vskip.1in
-Pattern more or less is to get the guy who is WHAT?
-\begin{itemize}
-	\item Frank: Imagine a see-saw; these guys are weights on the see-saw.
-	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
-		\begin{itemize}
-			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
-		\end{itemize}
-\end{itemize}
-
-\vskip.1in
-The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
-\begin{itemize}
-	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
-	\item What's the intuition for why they should be equal?
-As far as I can tell, it's that the PDF is unimodal.
-If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
-	\item \textbf{Next question: How general is this result?
-That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
-My conjecture is that it leans on having an interior single mode}
-\end{itemize}
-
-(Remember that I've assumed a very specific functional form)	
-\begin{itemize}
-	\item use $\al$ in prop:2NNB
-\end{itemize}
-
-%If we're going to do an empirical implementation of $\ga$ below, model needs to start with a basic understanding of uncertainty, run through lobbying response to it, up through aggregation into $\ga$ and how lobbying behavior turns into a ``yea'' vote total.
-
-Goal: characterize SPNE in pure strategies
+Now, how does the probability that the legislator at $-0.5$ (the one who is most friendly to $B$) votes with $B$ change when $s_{-.5}$ goes from 1 to 2?
+When $s_{-.5}$ is 1, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{1}}} = \frac{1}{1+e^{-.5}} = 0.6225$.
+When $s_{-.5}$ is 2, the probability is $\frac{1}{1+e^{-\frac{Y}{s_{-.5}}}} = \frac{1}{1+e^{-\frac{.5}{2}}} = \frac{1}{1+e^{-.25}} = 0.5622$.
+Here, the probability that the most friendly legislator votes with $B$ \textit{falls} when the uncertainty surrounding her ideal point increases.
 
@@
 \label{sec:res}
+
+Although uncertainty is present in the environment under consideration here, information about that uncertainty is symmetric.
+Therefore the appropriate equilibrium notion is subgame perfect Nash equilibrium.
 
@@
 				\end{multline}
+
+\subsection{Intuition}
+\begin{itemize}
+
+		\item If $\al > 0$, legislators on average are biased against B.
+			\begin{itemize}
+				\item If $\al < 0$, legislators on average are biased in favor of B.
+				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
+			\end{itemize}
+		\item If $X_B,Y_B,$ or $Z_B$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
+\end{itemize}
+
+\vskip.1in
+Pattern more or less is to get the guy who is WHAT?
+\begin{itemize}
+	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
+		\begin{itemize}
+			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
+		\end{itemize}
+\end{itemize}
+
+\vskip.1in
+The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
+\begin{itemize}
+	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
+	\item What's the intuition for why they should be equal?
+As far as I can tell, it's that the PDF is unimodal.
+If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
+	\item \textbf{Next question: How general is this result?
+That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
+My conjecture is that it leans on having an interior single mode}
+\end{itemize}
+
+\subsection{Varying Uncertainty across Legislators}
+\label{sec:resunc}
+Numerical example.
+Take $\al=0$ and ignore A.
+Take $s_{.5}$ from 1 to 1.5.
+$B$ stops bribing legislator $0.5$ (least friendly) altogether.
+Does better in welfare terms because the probability this guy votes in his favor shifts up
+		\begin{itemize}
+			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
+			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone).
+Then $Z$ and $Y$ together but $Z$ further on net than $Y$.
+Eventually all three, with $X=Y$, $Z$ further
+		\end{itemize}
+Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
+		\begin{itemize}
+			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
+			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
+			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
+		\end{itemize}
 

### 2016-02-15 draft.tex
shorten references list

@@
 
-\textcolor{blue}{Recorded votes in legislatures (roll call data) are the most commonly used data source to measure politicians' spatial preferences.
+Recorded votes in legislatures (roll call data) are the most commonly used data source to measure politicians' spatial preferences.
 A well-established strategy is to use statistical techniques to represent patterns of legislative voting.
@@
 Using this estimation procedure, we obtain summary statistics used for inference: legislators' mean and median ideal points as well as their 95$\%$ posterior confidence intervals.
-The latter are of particular interest to us, as we can use them to gauge the unpredictability of  legislators' voting behavior.}
+The latter are of particular interest to us, as we can use them to gauge the unpredictability of  legislators' voting behavior.
 
-\textcolor{blue}{We are interested in unpredictability vis-a-vis particular policy issues.
+We are interested in unpredictability vis-a-vis particular policy issues.
 Poole (2005) suggests using subsets of roll calls to establish legislators' ideal points separately on each issue.
-Preliminary work with our data indicates that a more statistically-robust method is to use all roll call votes in a legislative session or group of sessions to estimate an ideal point that is multidimension---that is, with one dimension for each interest group---allowing the partial pooling of information across roll calls.
-Multilevel modeling techniques, of which the standard ideal point estimation is a basic case, are perfectly suited to this task.}
+Preliminary work with our data indicates that a more statistically-robust method is to use all roll call votes in a legislative session or group of sessions to estimate an ideal point that is multidimensional---that is, with one dimension for each interest group---allowing the partial pooling of information across roll calls.
+Multilevel modeling techniques, of which the standard ideal point estimation is a basic case, are perfectly suited to this task.
 
-\textcolor{blue}{We therefore estimate the model
+We therefore estimate the model
 \begin{equation}
@@
 $y_{jk}=1$ if legislator $j$ votes ``Yea'' on bill $k$; $y_{kj}=0$ if she votes ``Nay'' on bill $k$.
-Note that interest groups take positions on multiple roll call votes and different interest groups can take positions, often on opposing sides, on each vote.}
+Note that interest groups take positions on multiple roll call votes and different interest groups can take positions, often on opposing sides, on each vote.
 
-\textcolor{blue}{This is a logistic item response (Rasch) model as adapted by Bafumi, et.
+This is a logistic item response (Rasch) model as adapted by Bafumi, et.
 al.
@@
 $\alpha_j^{(g)}$ is the ideal point of legislator $j$ on issue $g$ and $\beta_k^{(g)}$ is the ideal point of a legislator who is indifferent on vote $k$ for issue $g$.
-$\gamma_k^{(g)}$, the discrimination parameter, is a measure of the informativeness of issue $g$ for the vote on bill $k$: a large $\ga$ indicates that legislators are very likely to vote according to their preferences, whereas a small $\ga$ means that even significant margins of preference do not contribute much to the probability that legislators will vote in favor of the bill.}
+$\gamma_k^{(g)}$, the discrimination parameter, is a measure of the informativeness of issue $g$ for the vote on bill $k$: a large $\ga$ indicates that legislators are very likely to vote according to their preferences, whereas a small $\ga$ means that even significant margins of preference do not contribute much to the probability that legislators will vote in favor of the bill.
 
-\textcolor{blue}{We are experimenting with some of the more sophisticated measures of uncertainty that are possible with a rich model such as this one; for instance the group mean for $\ga$ and constructs that combine model parameters.}
+We are currently experimenting with some of the more sophisticated measures of uncertainty that are possible with a rich model such as this one; for instance the group mean for $\ga$ and constructs that combine model parameters.
 
@@
 
-\textcolor{blue}{We will also explore whether there is a way to leverage the data and methodology of Lake and Millimet (2014b) that combine the contributions and lobbying data to improve precision, although there is a concern about the coarseness of the data that must be overcome.}
+\textcolor{blue}{We will also explore whether there is a way to leverage the data and methodology of Lake (2015) that combine the contributions and lobbying data to improve precision, although there is a concern about the coarseness of the data that must be overcome.}
 
@@
 
+\item Bafumi, J., Gelman, A., Park., D, Kaplan, N., 2005. Practical Issues in Implementing and Understanding Bayesian Ideal Point Estimation. Political Analysis 13, 171-187.
+
 \item Banks, J. S., (2000), ``Buying Supermajorities in Finite Legislatures.'' {\em The American Political Science Review} 94, 677-681.
@@
 
+\begin{sloppypar}	
+	\item Buzard, K., 2014c. Trade Agreements in the Shadow of Lobbying. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/TradeAgreements_Shadow_Lobbying.pdf}.
+\end{sloppypar}
+
 \item Clinton, J., Jackman, S., and D. Rivers, (2004): ``The Statistical Analysis of Roll Call Data.'' {\em American Political Science Review}, 98, 355-370.
+
+\item Coates, D., Ludema, R., 2001. A Theory of Trade Policy Leadership. Journal of Development Economics 65, 1-29.
 
@@
 
-\item Gawande, K., P. Krishna and M. Robbins (2006): ``Foreign Lobbies and U.S. Trade Policy,'' {\em Review of Economics and Statistics}, 88, 563-571.
+\item Gawande, K., Krishna, P., Olarreaga, M., 2009. What Governments Maximize and Why: The View from Trade. International Organization 63, 491-532.
 
@@
 \item Grossman, G. and E. Helpman (1994): ``Protection for Sale,'' {\em The American Economic Review}, 84, 833-850.
+
+\item Grossman, G., Helpman, E., 1995a. The Politics of Free-Trade Agreements. The American Economic Review 85, 667-690.
+
+\item Grossman, G., Helpman, E., 1995b. Trade Wars and Trade Talks. The Journal of Political Economy 103, 675-708.
 
@@
 
+\item Lake, J., 2015. Revisiting the link between PAC Contributions and Lobbying Expenditures. European Journal of Political Economy 37, 86-101.
+
 \item Laver, M. and K. Shepsle (1991), ``Divided Government: America is Not `Exceptional','' {\em Governance: An International Journal of Policy and Administration}, 4, 250-269.
@@
 \item Le Breton, M. and V. Zaporozhets (2007), ``Legislative Lobbying under Political Uncertainty,'' Available at SSRN: \url{http://ssrn.com/abstract=1024686}.
+
+\item Mansfield, E., Milner, H., 2012. Votes, Vetoes, and the Political Economy of International Trade Agreements. Princeton and Oxford: Princeton  University Press.
 
@@
 
-\item Bafumi, J., Gelman, A., Park., D, Kaplan, N., 2005. Practical Issues in Implementing and Understanding Bayesian Ideal Point Estimation. Political Analysis 13, 171-187.
-
-	\item Buzard, K., 2014a. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.
-
-	\item Buzard, K., 2014b.
-Self-enforcing Trade Agreements, Dispute Settlement and Separation of Powers.
-Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/2014/04/Self-enforcing-Trade_Agreements.pdf}.
-
-\begin{sloppypar}	
-	\item Buzard, K., 2014c. Trade Agreements in the Shadow of Lobbying. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/TradeAgreements_Shadow_Lobbying.pdf}.
-		\end{sloppypar}
-
-	\item Coates, D., Ludema, R., 2001. A Theory of Trade Policy Leadership. Journal of Development Economics 65, 1-29.
-
-	\item Conconi, P., Facchini, G., Steinhardt, M.
-F., Zanardi, M., 2012.
-The political economy of trade and migration: Evidence from the US Congress.
-HWWI Research Paper 136.
-Available at: \url{http://hdl.handle.net/10419/67944}.
-
-	\item Dixit, A., Grossman, G., Helpman, E., 1997. Common Agency and Coordination: General Theory and Application to Government Policy Making. Journal of Political Economy 105, 752-769.
-
-	\item Feenstra, R., 1992. How Costly is Protectionism? Journal of Economic Perspectives 6, 159-178.
-
-	\item Gawande, K., Bandyopadhyay, U., 2000. Is Protection for Sale? Evidence on the Grossman-Helpman Theory of Endogenous Protection. The Review of Economics and Statistics 82, 139-152.
-
-	\item Gawande, K., Krishna, P., Olarreaga, M., 2009. What Governments Maximize and Why: The View from Trade. International Organization 63, 491-532.
-
-	\item Gawande, K., Krishna, P., Olarreaga, M., 2012. Lobbying Competition over Trade Policy. International Economic Review 53, 115-132.
-
-	\item Grossman, G., Helpman, E., 1995a. The Politics of Free-Trade Agreements. The American Economic Review 85, 667-690.
-
-	\item Grossman, G., Helpman, E., 1995b. Trade Wars and Trade Talks. The Journal of Political Economy 103, 675-708.
-
-	\item Iaryczower, M., Katz, G., Saiegh, S., 2013. Voting in the Bicameral Congress: Large Majorities as a Signal of Quality. Forthcoming in Journal of Law, Economics, and Organization.
-
-  \item Iida, K., 1996. Involuntary Defection in Two-Level Games. Public Choice 89, 283-303.
-
-	\item Lake, J., Millimet, D., 2014a.
-An Empirical Analysis of Trade-Related Redistribution and the Political Viability of Free Trade.
-Available at: \url{http://people.smu.edu/jlake/pdfs/VotingFTAs.pdf}
-
-	\item Lake, J., Millimet, D., 2014b. Revisiting the link between PAC Contributions and Lobbying Expenditures. Available at: \url{http://people.smu.edu/jlake/pdfs/PACcontributionsLobbying.pdf}
-
-	\item Mansfield, E., Milner, H., 2012. Votes, Vetoes, and the Political Economy of International Trade Agreements. Princeton and Oxford: Princeton  University Press.
-
-	\item Milner, H., Rosendorff, B.P., 1997.
-Democratic Politics and International trade Negotiations: Elections and Divided Government as Constraints on Trade Liberalization.
-Journal of Conflict Resolution 41, 117-147.
-
-	\item Ornelas, E., 2005. Rent Destruction and the Political Viability of Free Trade Agreements. Quarterly Journal of Economics 120, 1475-1506.
-
 \end{list}

### 2016-02-15 draft.tex
check data section; modify evidence section slightly

@@
 
+\subsection{Vote Buyer B}
+
 I begin by examining the subgame that begins when Vote Buyer $B$ makes his offer.
@@
 \begin{itemize}
-				\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
+
 			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
@@
 
+\subsection{Two Vote Buyers}
+
 \section{Estimating Legislative Uncertainty}
@@
 \label{sec:house}
+We look to voting patterns in the U.S.
+House of Representatives to see if the predictions of our model bear any resemblance to reality.
+We find suggestive preliminary evidence that adding uncertainty to a model of vote buying helps to understand observed patterns in the data and our next step is to pursue a better-identified model.
 
 \subsection{Data}
-\textcolor{blue}{Voting data will be obtained from Vote View, a website maintained by Professor Keith Poole (\url{http://voteview.com}).
-Details on each legislative proposal are available electronically through Thomas (\url{http://thomas.loc.gov}) and the sites of the House and Senate registrars.}
+Voting data will be obtained from Vote View, a website maintained by Professor Keith Poole (\url{http://voteview.com}).
+Details on each legislative proposal are available electronically through Thomas (\url{http://thomas.loc.gov}) and the sites of the House and Senate registrars.
 
-\textcolor{blue}{We will use Maplight's contributions data, which provides evidence on public declarations by special interest groups to determine the relevant PAC contributions for the bills under consideration.
+We will use Maplight's contributions data, which provides evidence on public declarations by special interest groups to determine the relevant PAC contributions for the bills under consideration.
 In a related effort to better connect special interest activity to the intent of that activity, we will use data made available pursuant to the U.S.
@@
 House of Representatives.
-This data is particularly useful because lobbyists must declare the issue area on which they lobbied.}
+This data is particularly useful because lobbyists must declare the issue area on which they lobbied.
 
-\textcolor{blue}{We will also explore whether there is a way to leverage the data and methodology of Lake (2015) that combine the contributions and lobbying data to improve precision, although there is a concern about the coarseness of the data that must be overcome.}
+We will also explore whether there is a way to leverage the data and methodology of Lake (2015) that combine the contributions and lobbying data to improve precision, although there is a concern about the coarseness of the data that must be overcome.
 
@@
   \includegraphics[width=2.9in]{graph2.jpg}
-  \caption{Lobbying Effort and Support for KORUS
+  \caption{\smallLobbying Effort and Support for KORUS
 	\label{fig:br}}
@@
   \includegraphics[width=2.9in]{graph1.jpg}
-  \caption{Net Campaign Contributions, KORUS
+  \caption{\smallNet Campaign Contributions, KORUS
 	\label{fig:g1}}
@@
 
-\textcolor{blue}{Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for KORUS.
+\textcolor{blue}{Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for one bill of interest, the Korea-U.S.
+Free Trade agreement, or KORUS.
 The vertical axis represents the predicted probability that a legislator would vote ``yes'' on the agreement, and the horizontal axis shows the monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.
@@
 Then we fitted a second-order polynomial to the predicted probabilities generated by the probit regression.
-The contribution data for both this and the follow figure was obtained from Maplight.}
+The contribution data for both this and the following figure was obtained from Maplight.}
 
@@
 The data show a very strong relationship between uncertainty at the level of the individual legislator and campaign contributions.
-To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.
-While these data do not map perfectly onto our theoretical constructs, they indicate that there is strong preliminary support for our hypotheses making it highly likely that investment in data acquisition and analysis is worthwhile.}
+To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.}
 
@@
 The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).}
-
-\textcolor{blue}{Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
-First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight (as explained above).}
-
-\textcolor{blue}{We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
-We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.
-From the data analysis that is represented above, we see a very interesting relationship between uncertainty and lobbying expenditure across legislators at the aggregate level in Figure~\ref{fig:br}, and we expect that additional important patterns will emerge when the data is disaggregated by industry.}
 
@@
 \textcolor{blue}{We expect this data will have a wide array of applications, such as exploring the links between policy uncertainty, the business cycle, and stock market volatility.}
+
+\textcolor{blue}{Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
+First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight (as explained above).}
+
+\textcolor{blue}{We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
+We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.}
 

### 2016-02-15 draft.tex
rough in results section

@@
 \subsection{Vote Buyer B}
-Groseclose and Snyder (1996) assume that the objective of each vote buyer is to ``minimize total bribes paid while passing his preferred policy.'' This has to be adapted out our environment with uncertainty about legislators' ideal points.
+Groseclose and Snyder (1996) assume that the objective of each vote buyer is to ``minimize total bribes paid while passing his preferred policy.'' This has to be adapted out our environment with uncertainty about legislators' ideal points, as with any probability distribution with infinite support both players will necessarily have a positive probability of winning in equilibrium regardless of their strategies.
 The appropriate analog is that vote buyers maximize the expected value of winning the vote net of bribes that he/she must pay.
@@
 \subsection{Vote Buyer B}
+\label{sec:resB}
 
@@
 \begin{proposition}
-  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points net of the bribes are equalized.
+  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points gross of bribes are equalized.
 Which two voters are bribed depends on the bias parameter $\al$.
@@
 
+\begin{proposition}
+  When Vote Buyer $B$ pays bribes to exactly one legislator, ... can be any one, not necessarily ideologically closest.
+	\label{prop:1NNB}
+\end{proposition}
+In contrast to models with no uncertainty about legislators' ideological positions, here we have an anti-result that the vote buyers do not necessarily bribe those who are ideologically most aligned with themselves.
+The non-negativity constraint often rules out bribing the most friendly legislator(s) because she/they don't contribute very much to the overall probability of winning the issue.
+
+Figure~\ref{fig:br} shows an example of a vote in which the most money went to the ideologically moderate--not the most extreme in a `leveling' strategy.
+
+\begin{proposition}
+  When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
+	\label{prop:3NNB}
+\end{proposition}
+
 \begin{itemize}
-
-			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
-			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
 			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
@@
 \end{itemize}
-
-\vskip.5in
-Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
-			 \begin{multline}
-					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
-					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
-					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
-					\label{eq:focA}
-				\end{multline}
 
@@
 If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
-	\item \textbf{Next question: How general is this result?
-That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold?
-My conjecture is that it leans on having an interior single mode}
 \end{itemize}
@@
 \label{sec:resunc}
+
+The results of Section~\ref{sec:resB} in which bribed legislators have their ideal points `leveled' so that their positions gross of bribes are equalized evidently hinge on the symmetry in uncertainty assumed there.
+
+\begin{proposition}
+  test
+\end{proposition}
+Very low, very high uncertainty gets lowest payments, middle uncertainty gets most (Figure \ref{fig:g1}.
+
+\vskip.2in
 Numerical example.
@@
 \subsection{Two Vote Buyers}		
+Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
+
+		\vskip.5in
+Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
+			 \begin{multline}
+					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
+					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
+					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
+					\label{eq:focA}
+				\end{multline}
+
+\begin{proposition}
+  It is possible for both vote buyers to bribe legislators on the same vote.
+\end{proposition}
+
+\begin{proposition}
+  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
+\end{proposition}
 
@@
   \includegraphics[width=2.9in]{graph2.jpg}
-  \caption{\smallLobbying Effort and Support for KORUS
+  \caption{\small Lobbying Effort and Support for KORUS
 	\label{fig:br}}
@@
   \includegraphics[width=2.9in]{graph1.jpg}
-  \caption{\smallNet Campaign Contributions, KORUS
+  \caption{\small Net Campaign Contributions, KORUS
 	\label{fig:g1}}

### 2016-02-15 draft.tex
write prop:asym and modify evidence section

@@
 \begin{proposition}
-  When Vote Buyer $B$ pays bribes to exactly one legislator, ... can be any one, not necessarily ideologically closest.
+  When Vote Buyer $B$ pays bribes to exactly one legislator, it may be any one of the three legislators depending on the bias parameter $\al$.
 	\label{prop:1NNB}
@@
 \begin{proposition}
-  test
+  When there is no bias in the positions of the legislators ($\al =0$), the bribes of legislators whose ideal points are at the median in terms of uncertainty receive the highest relative bribes.
+(conjecture)
+	\label{prop:asym}
 \end{proposition}
-Very low, very high uncertainty gets lowest payments, middle uncertainty gets most (Figure \ref{fig:g1}.
+In numerical examples, this pattern holds strongly.
+By `relative,' we mean that the bribes are scaled up relative to the equal gross position that occurs when uncertainty is symmetric.
+We also see that the bribes for legislators whose ideal points are more uncertain are scaled down while the bribes of legislators whose ideal points are less uncertain are scaled up, modulo relative position.
+That is, there is some effect of being more friendly versus less friendly, as the cumulative density that the legislator will vote in the vote buyer's favor changes in opposite directions when uncertainty rises depending on whether the legislator is friendly or unfriendly.
+This accords well with the finding in Figure \ref{fig:g1} that those legislators with very low and very high uncertainty gets the lowest payments, while those with more average levels of uncertainty receive the most.
 
@@
 
-\textcolor{blue}{Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for one bill of interest, the Korea-U.S.
+Figure~\ref{fig:br} displays the relationship between lobbying effort and legislators' support for one bill of interest, the Korea-U.S.
 Free Trade agreement, or KORUS.
@@
 The solid vertical red line indicates the average net contribution in the sample, and the dashed lines a one-standard deviation increase/decrease from that sample mean.
-The data indicate that exporting industries are more likely to exert lobbying effort to enlist the support of additional legislators (extensive margin) rather than secure stronger support from a given set of legislators (intensive margin), as well as that there are decreasing returns to lobbying effort.
 To generate these results,  we regressed a legislator's vote on his/her estimated ideal point as well as partisanship using a probit specification.
 Then we fitted a second-order polynomial to the predicted probabilities generated by the probit regression.
-The contribution data for both this and the following figure was obtained from Maplight.}
+The contribution data for both this and the following figure was obtained from Maplight.
+The data indicate that exporting industries were more likely to exert lobbying effort to enlist the support of additional, moderate legislators rather than secure stronger support from those most aligned with their interests.
+This accords well with Proposition~\ref{prop:1NNB}.
 
-\textcolor{blue}{Figure~\ref{fig:g1} displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort.
+Figure~\ref{fig:g1} displays the relationship between the unpredictability of legislators' voting behavior and lobbying effort.
 The vertical axis represents the predicted net contributions to members of the U.S.
-House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislator's voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress (more details on the methodology below).
+House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislator's voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress.
 The solid vertical red line indicates the average uncertainty in the sample, and the vertical dashed red lines indicate increases/decreases of one-standard deviation from the average.
 The horizontal dashed green line indicates the predicted net payment in the sample.
-The data show a very strong relationship between uncertainty at the level of the individual legislator and campaign contributions.
-To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.}
+To generate these results, we fitted a second-order polynomial to the data, and used monetary contributions to each legislator by lobbies who supported the passage of KORUS minus the contributions from lobbies opposing the agreement.
+The data show a very strong relationship between uncertainty at the level of the individual legislator and campaign contributions as predicted by Proposition~\ref{prop:asym}.
 
@@
 
+\vskip.3in
+\noindent \textbf{\hypertarget{Pr_1NNB}{Proof of Proposition~\ref{prop:1NNB}}}: \\
+When Vote Buyer B bribes just one legislator, two non-negativity constraints are binding and only one first order conditions holds with equality with the Lagrange multiplier equaling zero.
+We can easily solve this first order condition to find the value of the bribe.
+What determines which legislator is bribed is which legislator's ideal point distribution has the most mass near zero, as moving this individual has the greatest impact on total probability of winning the issue.
+
 \newpage

### 2016-02-15 draft.tex
finish empirical / evidence section

@@
 
-\textcolor{blue}{We `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position.
+Finally, we `turn on' the parameters for interest groups for each vote according to the data from Maplight, which includes a listing of the votes for which each interest group took a position.
 This produces estimates for how ``friendly'' or ``unfriendly'' each legislator is with respect to each interest group, as well as the unpredictability of his/her voting behavior when matters affecting that group are considered.
 In a preliminary run of this model with just ten interest groups (out of over 450) in the 112th Congress displayed in Figure~\ref{fig:combined}, we find that the chemical industry has the lowest average uncertainty (sd = 0.229); this is lower than the total uncertainty measure that can be interpreted as the standard left-right measure in ideal point models (sd = 0.233).
-The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).}
+The median group in terms of uncertainty is manufacturing unions (sd = 0.253), while construction equipment faced the highest uncertainty (sd = 0.285).
+This gives us a rich testing grounds for the model that is yet to be exploited.
 

### 2016-02-16 draft.tex
finish prop:3NNB and proof; conclusion

@@
 
+The first part of this result is similar in spirit to Groseclose and Snyder (1996) and Banks (2000) in that a `leveling' strategy is employed.
+But the non-negativity constraint here binds for the third, and which legislator is this third, un-bribed legislator depends on where the three ideal points are relative to the zero point at which a legislator has a 50$\%$ probability of voting for either the status quo or the new proposal.
+If $B$'s willingness to pay parameter increases, the non-negativity constraint becomes less binding until he finds himself in the following case.
+
+\begin{proposition}
+  When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
+	\label{prop:3NNB}
+\end{proposition}
+
+This has the feel of Groseclose and Snyder (1996) and Banks (2000) but the logic is different.
+There, gross ideal points are equalized so that there is no wasted effort, as the second mover would ignore whichever voter was most expensive to him.
+Remember that this result is in the context of only one vote buyer; he equalizes gross positions because the probability density functions are unimodal and the marginal value of a bribe should be the same across all bribed legislators.
+
 \begin{proposition}
@@
 Figure~\ref{fig:br} shows an example of a vote in which the most money went to the ideologically moderate--not the most extreme in a `leveling' strategy.
-
-\begin{proposition}
-  When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
-	\label{prop:3NNB}
-\end{proposition}
 
@@
 
-\textcolor{blue}{an alternative characterization of the legislative process would be one in which (i) bills have a quality dimension (such as their technical merit, or their appropriateness for a given situation); and (ii) legislators have access to different pieces of information about the quality of these proposals.
-Given our own long-term research agenda, adding common values and decentralized information to the analysis of the ratification of trade agreements will be one of the next steps in this project.
-Given the important set of governance characteristics identified in Mansfield and Milner (2012), we also look forward to taking advantage of what seems a rich opportunity to integrate important institutional variations into this modeling framework of endogenous lobbying with uncertainty.}
+We have characterized a model of vote buying in which there is uncertainty about the ideological positions of those whose votes are being bought, with information about this uncertainty symmetric among all players.
+This model describes some realistic aspects of lobbying and voting behavior: for instance, that lobbyists on both sides of an issue may be active at the same time, that moderate legislators and those about which there is average uncertainty receive more bribes than those that are ideologically extreme, and that ideal points gross of bribes need not be equalized.
 
-\vskip.3in
-\textcolor{blue}{We expect this data will have a wide array of applications, such as exploring the links between policy uncertainty, the business cycle, and stock market volatility.}
+An alternative characterization of the legislative process would be one in which (i) bills have a quality dimension (such as their technical merit, or their appropriateness for a given situation); and (ii) legislators have access to different pieces of information about the quality of these proposals.
+Adding common values and decentralized information to the analysis of the ratification of trade agreements will be one of the next steps in this project.
+Given the important set of governance characteristics identified in Mansfield and Milner (2012), we also look forward to taking advantage of what seems a rich opportunity to integrate important institutional variations into this modeling framework of endogenous lobbying with uncertainty.
 
-\textcolor{blue}{Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
-First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight (as explained above).}
+We are also in the process of using this model to develop well-identified measures of legislative uncertainty.
+We expect this data will have a wide array of applications, such as exploring the links between policy uncertainty, the business cycle, and stock market volatility.
 
-\textcolor{blue}{We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
-We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.}
+Having created these measures of political uncertainty---which are entirely new to the best of our knowledge---we will proceed to characterize this uncertainty across industries, as well as how it is related to lobbying, political contributions and voting behavior of legislators.
+First, we want to understand the patterns in these data in the context of the industry-relevant bills identified by Maplight as explained above.
+
+We will use descriptive analysis as well as both standard parametric and non-parametric techniques such as density estimation to explore the relationships between the above variables of interest.
+We will begin with very basic questions such as whether distinct industries face varying levels of political uncertainty (see preliminary evidence in Figure~\ref{fig:combined}) and how those patterns may relate to the lobbying strategies they employ.
+The research agenda that is opened up by this modeling framework and the data to which it leads is extensive and provides for many exciting opportunities to better understand political and policy-making processes.
 
@@
 Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.
+$\hfill\blacksquare$
+
+\vskip.3in
+\noindent \textbf{\hypertarget{Pr_1NNB}{Proof of Proposition~\ref{prop:3NNB}}}:
+
+From the first order conditions, when $X$ and $Y$ are non-negative, it can be shown that the same set of inequalities as in the proof of Proposition~\ref{prop:2NNB} hold.
+
+The second order conditions when there are no non-negativity constraints binding is simply that the 3x3 matrix of second derivatives be negative semi-definite. There are three conditions:
+		\[
+		  \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \left\{\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right\} \leq 0
+		\]
+		\[
+		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \geq 0
+		\]
+		\[
+		  \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} \leq 0
+		\]
+		The last one says that $Y$ must be non-negative. The first and second together say that $Z$ must be non-negative.
+
+	If we combine the requirement that $Y$ must be non-negative combined with the inequalities cited above, then we must have $X=Y > 0$.
+A similar logic can be used to show that we must have $X=Z > 0$.
+Combining these two expressions leads to the desired result: $X=Y=Z >0$.
+$\hfill\blacksquare$
 
@@
 What determines which legislator is bribed is which legislator's ideal point distribution has the most mass near zero, as moving this individual has the greatest impact on total probability of winning the issue.
+$\hfill\blacksquare$
 

### 2016-02-16 draft.tex
lit review; keywords

@@
 
-%\begin{center} {\bf Abstract} \end{center}
+\begin{center} {\bf Abstract} \end{center}
 
-%\begin{quote}
-%{\small This paper
+\begin{quote}
+{This paper
 
-%\textit{JEL classification:} D72, D80 \\
-%\textit{Keywords:} lobbying, political economy, legislatures, uncertainty}
-%\end{quote}
+\textit{JEL classification:} D72, D80, C72 \\
+\textit{Keywords:} lobbying, political economy, legislatures, uncertainty}
+\end{quote}
 
@@
 
-\textcolor{blue}{Related is Le Breton and Salanie (2003), which studies lobbying when the lobby is uncertain about the preferences of a unitary decision maker.
+This work relates to the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et.
+al.
+(2005), Dal Bo (2007)) as well as to the canonical studies on endogenous regulation (cf.
+Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)).
+
+Also related is Le Breton and Salanie (2003), which studies lobbying when the lobby is uncertain about the preferences of a unitary decision maker.
 Le Breton and Zaporozhets (2007) go a step further and replace the unitary decision maker with a legislature with multiple actors.
-Song (2008) is a model of endogenous lobbying with a ratification constraint in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership in a model with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.}
+Song (2008) is a model of endogenous lobbying with a ratification constraint in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership in a model with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.
 
-\textcolor{blue}{As noted above, Saiegh (2009) argues that the uncertainty surrounding statutory lawmaking is in part related to governmental and political structure.
+As noted above, Saiegh (2009) argues that the uncertainty surrounding statutory lawmaking is in part related to governmental and political structure.
 Although they do not discuss uncertainty specifically, the cross-country empirical work of Gawande, Krishna and Olarreaga (2009) is the first to our knowledge that suggests that this kind of uncertainty plays a role in trade policy.
 They show that variables such as the number of checks and balances on the power of the legislature and the gap between the policy positions of the main political parties have predictive power for the PFS ``welfare-mindedness'' parameter.
-One of the objectives of this proposed project is to directly test the premise that legislative uncertainty indeed has an important impact on trade policy.}
-
-\textcolor{blue}{This work also relates to the canonical studies on endogenous regulation (cf.
-Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)), as well as the literature on vote-buying and legislative behavior in political science (Groseclose and Snyder (1996), Dekel et.
-al.
-(2005), Dal Bo (2007)).}
+The model of Buzard (2016) indicates that the kind of political uncertainty modeled here can have an important impact on the formation and maintenance of trade agreements.
 
@@
 \vskip.3in
-\noindent \textbf{\hypertarget{Pr_1NNB}{Proof of Proposition~\ref{prop:3NNB}}}:
+\noindent \textbf{\hypertarget{Pr_3NNB}{Proof of Proposition~\ref{prop:3NNB}}}:
 
@@
 \begin{sloppypar}	
-	\item Buzard, K., 2014c. Trade Agreements in the Shadow of Lobbying. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/TradeAgreements_Shadow_Lobbying.pdf}.
+	\item Buzard, K., 2016. Trade Agreements in the Shadow of Lobbying. Available at: \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2168522}.
 \end{sloppypar}

### 2016-02-16 draft.tex
first shot at intro

@@
 
-\textcolor{blue}{In democratic countries, legislatures are the authoritative source of statutory law.
-The PFS model doesn't capture several general features of policymaking in this environment: (2) how uncertainty affects the incentives for lobbying and the associated prospects for ratification of trade agreements; and (3) how the voting intentions of multiple legislators, rather than a single agent, change in response to incentives.}
+In democratic countries, legislatures are the authoritative source of statutory law.
+This paper seeks to understand how uncertainty affects the incentives for lobbying and the associated prospects for the passage of legislation.
+Saiegh (2011) identifies two major factors that shape lawmaking: whether buying legislative votes is a feasible option and the unpredictability of legislators' voting behavior.
+The source of the uncertainty is the existence of cross-pressured legislators: in deciding how to vote, lawmakers consider a variety of influences, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership.
+Therefore, legislators' voting behavior can seldom be perfectly anticipated.
 
-\textcolor{blue}{In this vein, Saiegh (2011) identifies two major factors that shape lawmaking: the unpredictability of legislators' voting behavior, and whether buying legislative votes is a feasible option.
-The source of the uncertainty is the existence of cross-pressured legislators: in deciding how to vote, lawmakers consider a variety of influences, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership.
-Therefore, legislators' voting behavior can seldom be perfectly anticipated.}
+We solve a model of vote buying in which there is uncertainty about the ideological positions of legislators with information about this uncertainty symmetric among all players.
+This model is able to describe some realistic aspects of lobbying and voting behavior: for instance, it predicts that lobbyists on both sides of an issue may be active at the same time, that moderate legislators and those about which there is average uncertainty receive more bribes than those that are ideologically extreme, and that ideal points gross of bribes need not be equalized.
+We find support for these predictions in U.S.
+House of Representatives roll call data, from which we estimate ideal points using a logistic item response model.
 
-\textcolor{blue}{From an empirical standpoint, the project will contribute to our understanding of the political uncertainty that surrounds statutory lawmaking.
-We will introduce an innovative methodology for quantifying cross-industry political uncertainty, establish the relevance of the resulting measures for policy-making and make the data available for future use in a wide range of applications.
-For example, our measure could be used to study he impact of policy uncertainty on firm-level investment and employment.}
+In constructing the model, we follow Groseclose and Snyder (1996) and Banks (2000) in taking a policy proposal as given and studing the behavior of interest groups who may lobby legislators in an attempt to sway the outcome of the vote.
+In order to keep the model tractable, we study a three-person legislature in which two lobbyists---one for the new proposal and one against it---sequentially offer payments to the legislators.
+
+A payment to a legislator has the effect of shifting the legislator's ideal point, which we take to be known up to the mean and variance parameter of a given probability distribution.
+Thus bribing a legislator has the effect of changing the probability with which the legislator votes in the manner the vote buyer prefers.
+In this environment, the optimal vote-buying strategies are not immediately obvious.
+
+We find that the number of legislators a vote buyer chooses to lobby is increasing in the value he places on the policy.
+When a vote buyer's willingness-to-pay for his preferred policy is very low, he will bribe none of the legislators; if it is very high, he will bribe all of them.
+Buying one or two votes is also possible.
+
+Perhaps more interesting, and in contrast to results in a model without uncertainty, when only one or two legislators are bribed the legislator who remains unbribed is often he who is most ideologically-aligned with the vote buyer.
+When the legislators are roughly unbiased on average, it is the moderate legislator who is bribed first.
+This corresponds well with the data that shows that more moderate legislators receive more campaign contributions.
+
+If uncertainty is taken to be the same for the ideal points of all the legislators, we find that the vote buyers use `leveling strategies' as in Groseclose and Snyder (1996) and Banks (2000).
+Allowing for asymmetric levels of uncertainty, on the other hand, provides a more realistic picture that accords well with our empirical findings that legislators with moderate levels of uncertainty are the target of the highest levels of lobbying, while those about whom there are very high levels of uncertainty most often remain unbribed.
+
+A final result we find that is appealing from an empirical point of view: in this model, it is possible to have both vote buyers paying positive bribes on the same issue.
+Because the results of the model accord well with these important patterns in the data, we believe this model will contribute to the understanding of the political uncertainty that surrounds statutory lawmaking.
+
+Below we introduce an innovative methodology for quantifying cross-industry political uncertainty; the model under consideration here is being adapted as a means to properly identify political uncertainty in this context.
+We plan to establish the relevance of the resulting measures for policy-making and will make the data available for future use in a wide range of applications.
 

### 2016-02-16 draft.tex
add abstract

@@
 \begin{quote}
-{This paper
+{This paper seeks to understand how uncertainty affects the incentives for lobbying and the associated prospects for the passage of legislation.
+We introduce a model of vote buying in which there is uncertainty about the ideological positions of legislators with information about this uncertainty symmetric among all players.
+When legislators' voting behavior cannot be perfectly anticipated in this manner, the model is able to describe various realistic aspects of lobbying and voting behavior.
+For example, it predicts that lobbyists on both sides of an issue may be active at the same time, that moderate legislators and those about which there is average uncertainty receive more bribes than those that are ideologically extreme, and that ideal points gross of bribes need not be equalized.
+Estimating ideal points using a logistic item response model, we find support for these predictions in U.S.
+House of Representatives roll call data.
 

### 2016-02-16 draft.tex
proofread intro

@@
 
-In constructing the model, we follow Groseclose and Snyder (1996) and Banks (2000) in taking a policy proposal as given and studing the behavior of interest groups who may lobby legislators in an attempt to sway the outcome of the vote.
+In constructing the model, we follow Groseclose and Snyder (1996) and Banks (2000) in taking a policy proposal as given and studying the behavior of interest groups who may lobby legislators in an attempt to sway the outcome of the vote.
 In order to keep the model tractable, we study a three-person legislature in which two lobbyists---one for the new proposal and one against it---sequentially offer payments to the legislators.
 
-A payment to a legislator has the effect of shifting the legislator's ideal point, which we take to be known up to the mean and variance parameter of a given probability distribution.
+A payment to a legislator has the effect of shifting the legislator's ideal point, which we take to be known up to the mean and variance parameters of a given probability distribution.
 Thus bribing a legislator has the effect of changing the probability with which the legislator votes in the manner the vote buyer prefers.
@@
 
-Perhaps more interesting, and in contrast to results in a model without uncertainty, when only one or two legislators are bribed the legislator who remains unbribed is often he who is most ideologically-aligned with the vote buyer.
+Perhaps more interesting, and in contrast to results in a model without uncertainty, when only one or two legislators are bribed the legislator who remains unbribed is often the one who is most ideologically-aligned with the vote buyer.
 When the legislators are roughly unbiased on average, it is the moderate legislator who is bribed first.
@@
 
-A final result we find that is appealing from an empirical point of view: in this model, it is possible to have both vote buyers paying positive bribes on the same issue.
+We find one more result that is appealing from an empirical point of view.
+In this model, it is possible to have both vote buyers paying positive bribes on the same issue.
 Because the results of the model accord well with these important patterns in the data, we believe this model will contribute to the understanding of the political uncertainty that surrounds statutory lawmaking.

### 2016-02-16 draft.tex
finish vote buyer B results

@@
 
-\section{Some Theoretical Results}
+\section{Theoretical Results}
 \label{sec:res}
@@
 This has the feel of Groseclose and Snyder (1996) and Banks (2000) but the logic is different.
-There, gross ideal points are equalized so that there is no wasted effort, as the second mover would ignore whichever voter was most expensive to him.
-Remember that this result is in the context of only one vote buyer; he equalizes gross positions because the probability density functions are unimodal and the marginal value of a bribe should be the same across all bribed legislators.
+There, gross ideal points are equalized so that there is no wasted expenditure, as the second mover would ignore whichever voter was most expensive to him.
+Remember that these results are in the context of only one lobby buying votes: it equalizes the legislators' gross positions because the probability density functions are unimodal and the marginal value of a bribe should be the same across all bribed legislators.
 
@@
 The non-negativity constraint often rules out bribing the most friendly legislator(s) because she/they don't contribute very much to the overall probability of winning the issue.
+In fact, if it were possible, the vote buyer would often like to be paid by the most friendly legislator in exchange for her moving away from his position; that is, the most friendly legislator is often well past the point of optimality were the vote buyer to pay a bribe.
 
 Figure~\ref{fig:br} shows an example of a vote in which the most money went to the ideologically moderate--not the most extreme in a `leveling' strategy.
-
-\begin{itemize}
-			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
-			\item Some legislators who are past FOC point will not be lobbied
-
-\end{itemize}
 
@@
 \subsection{Two Vote Buyers}		
+Now we consider the entire game.
+
 Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes

### 2016-02-16 draft.tex
collapse intuition section into other results sections

@@
 But the non-negativity constraint here binds for the third, and which legislator is this third, un-bribed legislator depends on where the three ideal points are relative to the zero point at which a legislator has a 50$\%$ probability of voting for either the status quo or the new proposal.
-If $B$'s willingness to pay parameter increases, the non-negativity constraint becomes less binding until he finds himself in the following case.
+If $B$'s willingness to pay parameter increases, the non-negativity constraint becomes less binding.
+That is, when Vote Buyer $B$'s willingness to pay becomes high enough, the additional probability of winning gained by bribing the third legislator becomes worth the additional cost.
+When this happens, he finds himself in the following case.
 
@@
 Remember that these results are in the context of only one lobby buying votes: it equalizes the legislators' gross positions because the probability density functions are unimodal and the marginal value of a bribe should be the same across all bribed legislators.
+If the ideal points are very close, it would not be optimal to continue moving one legislator and leave the other behind because the marginal increase will be greater for whichever legislator's ideal point is to the left once both have achieved a gross position greater than zero.
 
@@
 Figure~\ref{fig:br} shows an example of a vote in which the most money went to the ideologically moderate--not the most extreme in a `leveling' strategy.
-
-\subsection{Intuition}
-\begin{itemize}
-
-		\item If $\al > 0$, legislators on average are biased against B.
-			\begin{itemize}
-				\item If $\al < 0$, legislators on average are biased in favor of B.
-				\item If $\al$ is negative enough, bribe only legislator furthest to the left (most against B)
-			\end{itemize}
-		\item If $X_B,Y_B,$ or $Z_B$ is positive, it means the probability of legislator $0,-\frac{1}{2},$ or $\frac{1}{2}$ voting for the status quo / against the new proposal / with interest group B is greater than $0.5$.
-\end{itemize}
-
-\vskip.1in
-Pattern more or less is to get the guy who is WHAT?
-\begin{itemize}
-	\item From looking at overlaided graphs of the pdfs (pdf-graph.R), it appears that the legislator who is chosen first is the one who has the most probability mass just to the left of 0 (it's probability mass to the right of zero that counts for winning the vote).
-		\begin{itemize}
-			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
-		\end{itemize}
-\end{itemize}
-
-\vskip.1in
-The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
-\begin{itemize}
-	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
-	\item What's the intuition for why they should be equal?
-As far as I can tell, it's that the PDF is unimodal.
-If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
-\end{itemize}
 

### 2016-02-16 draft.tex

@@
 
-In order to keep the model tractable when introduing this uncertainty, we take the ideal point function to be linear in $i$.
+In order to keep the model tractable when introducing this uncertainty, we take the ideal point function to be linear in $i$.
 That is, legislator $i$'s ideal point is taken to be $\alpha -\beta i$.
@@
 The results of Section~\ref{sec:resB} in which bribed legislators have their ideal points `leveled' so that their positions gross of bribes are equalized evidently hinge on the symmetry in uncertainty assumed there.
+The results become more interesting and more realistic if we allow for asymmetry in the uncertainty surrounding legislators' ideal points.
 
@@
   When there is no bias in the positions of the legislators ($\al =0$), the bribes of legislators whose ideal points are at the median in terms of uncertainty receive the highest relative bribes.
-(conjecture)
+[conjecture]
 	\label{prop:asym}
@@
 
-\vskip.2in
-Numerical example.
-Take $\al=0$ and ignore A.
-Take $s_{.5}$ from 1 to 1.5.
-$B$ stops bribing legislator $0.5$ (least friendly) altogether.
-Does better in welfare terms because the probability this guy votes in his favor shifts up
-		\begin{itemize}
-			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
-			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone).
-Then $Z$ and $Y$ together but $Z$ further on net than $Y$.
-Eventually all three, with $X=Y$, $Z$ further
-		\end{itemize}
-Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
-		\begin{itemize}
-			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
-			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
-			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
-		\end{itemize}
+We demonstrate via the following numerical example.
+Let the bias parameter $\al=0$ and ignore Vote Buyer A.
+When we increase the scale parameter $s_{.5}$ for the legislator at $0.5$---that is, the least friendly to Vote Buyer $B$---from 1 to 1.5, $B$ stops bribing the most friendly legislator altogether.
+Vote Buyer $B$ does better in welfare terms because the probability that this legislator votes in his favor shifts upward.
+In fact, For $s_{.5}$ must be much closer to $1$ in order for $B$ to bribe this legislator, and when he does, the gross ideal point is smaller in absolute value than that for the other two legislators.
+
+On the other hand, if $s_{.5}$ is reduced from 1 to $0.75$, for an intermediate range of $W_B$, the willingness to pay parameter, $B$ switches to \textit{only} bribing legislator $0.5$.
+As $W_B$ increases, eventually all three legislators are bribed again, but now this legislator receives a larger gross bribe.
+
+Recall that the effects are not necessarily entirely symmetric for the two extreme legislators because increasing uncertainty has an opposite effect on how much probability mass is above or below zero.
+However, there are strong similarities here.
+As $s_{-.5}$ is increased from 1 to 1.5 or larger, $B$ stops bribing this most friendly legislator and the asymmetry has to be reduced to below 1.2 in order for him to resume bribing legislator $-0.5$.
+When he does so, he will move this legislator less than the other two with lower uncertainty.
+If we instead reduce $-0.5$'s uncertainty, he moves him further
 
 \subsection{Two Vote Buyers}		
-Now we consider the entire game.
-
-Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
-
-		\vskip.5in
-Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
+Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes.
+Vote Buyer A's first order conditions are more complicated because of the dependencies on $\bm a$.
+Below is the first order condition with respect to $a_0$:
 			 \begin{multline}
@@
 
+Unlike in models with no uncertainty, we do not have knife edge results in which Vote Buyer $A$ uses Vote Buyer $B$'s indifference condition to ensure that he buys no votes--there is no such indifference condition in the presence of uncertainty.
+However, it's possible that one or both vote buyers will not bribe any legislator because the non-negativity constraints bind for all three bribes.
+This requires that the willingness-to-pay parameter is sufficiently small.
+
+\begin{proposition}
+  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
+\end{proposition}
+
+In many cases, Vote Buyer $A$ \textit{will} still find it optimal to bribe the legislators in such a manner than Vote Buyer $B$ does not counter any bribes.
+That is, its often optimal to choose $\bm a$ so that the partial derivatives of $B$'s bribes with respect to $a_0$ in Equation~\ref{eq:focA} are zero.
+This is not always the case with uncertainty, and especially in the case where uncertainty is asymmetric.
+
 \begin{proposition}
@@
 
-\begin{proposition}
-  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
-\end{proposition}
+This result in particular adds significant realism to the model predictions and will help to match the empirical patterns.
 

### 2016-02-18 draft.tex
add bookmarks for appendix and references
fix subsection labels
add sentence on multiple equilibria at top of sec:res

@@
 \renewcommand{\thesection}{\Roman{section}} 
-\renewcommand{\thesubsection}{\thesection.\Roman{subsection}}
+\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
 \linespread{1.5}
@@
 Although uncertainty is present in the environment under consideration here, information about that uncertainty is symmetric.
-Therefore the appropriate equilibrium notion is subgame perfect Nash equilibrium.
+Therefore the the solution concept employed here is subgame perfect Nash equilibrium.
+
+Whenever there is a possibility of multiple equilibria, I will focus on the one that maximizes the welfare of Vote Buyer A, the first mover.
 
@@
 \label{sec:app}
+\pdfbookmark{Appendix}{sec:appendix}
 \noindent \textbf{\hypertarget{Pr_2NNB}{Proof of Proposition~\ref{prop:2NNB}}}: \\
@@
 \section*{References}
+\pdfbookmark{References}{sec:refs}
 

### 2016-02-18 draft.tex
improve sec:resB, add prop:0NNB

@@
 This not only serves to elucidate the basic logic of the model; it will also serve as a baseline from which to examine the incentives of Vote Buyer $A$.
+These results also represent the outcomes when $A$'s willingness to pay is low, in which case it refrains from lobbying altogether and $B$'s incentives are the same as if Vote Buyer $A$ did not exist.
 For now, assume that the uncertainty about ideal points is the same across legislators.
@@
   When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points gross of bribes are equalized.
-Which two voters are bribed depends on the bias parameter $\al$.
+Which two legislators are bribed depends on the bias parameter $\al$.
 	\label{prop:2NNB}
@@
 But the non-negativity constraint here binds for the third, and which legislator is this third, un-bribed legislator depends on where the three ideal points are relative to the zero point at which a legislator has a 50$\%$ probability of voting for either the status quo or the new proposal.
-If $B$'s willingness to pay parameter increases, the non-negativity constraint becomes less binding.
+If $B$'s willingness-to-pay parameter increases, the non-negativity constraint becomes less binding.
 That is, when Vote Buyer $B$'s willingness to pay becomes high enough, the additional probability of winning gained by bribing the third legislator becomes worth the additional cost.
@@
 There, gross ideal points are equalized so that there is no wasted expenditure, as the second mover would ignore whichever voter was most expensive to him.
-Remember that these results are in the context of only one lobby buying votes: it equalizes the legislators' gross positions because the probability density functions are unimodal and the marginal value of a bribe should be the same across all bribed legislators.
-If the ideal points are very close, it would not be optimal to continue moving one legislator and leave the other behind because the marginal increase will be greater for whichever legislator's ideal point is to the left once both have achieved a gross position greater than zero.
+In contrast, these results are in the context of only one lobby buying votes: it equalizes the legislators' gross positions because the probability density functions are unimodal and the marginal value of a bribe should be the same across all bribed legislators.
+If the ideal points are very close, it would be sub-optimal to continue moving one legislator and leave the other behind: the marginal increase would be greater for whichever legislator's ideal point is to the left once both have achieved a gross position greater than zero.
 
@@
 Figure~\ref{fig:br} shows an example of a vote in which the most money went to the ideologically moderate--not the most extreme in a `leveling' strategy.
+
+Finally, for completeness we state a somewhat obvious result concerning the final possible case:
+
+\begin{proposition}
+  When Vote Buyer $B$ has a low willingness to pay, he does not bribe any legislator.
+	\label{prop:0NNB}
+\end{proposition}
+
+When $W_B$ is low enough, the non-negativity constraint binds for all three legislators and Vote Buyer $B$ finds it in his interest to take his chances with the ideal point distributions as they stand.
 

### 2016-02-18 draft.tex
proofread sec:resunc

@@
 
-The results of Section~\ref{sec:resB} in which bribed legislators have their ideal points `leveled' so that their positions gross of bribes are equalized evidently hinge on the symmetry in uncertainty assumed there.
+The results of Section~\ref{sec:resB} in which bribed legislators have their ideal points `leveled' so that their positions gross of bribes are equalized hinge on assumption that the uncertainty surrounding the ideal points of each legislator is the same.
 The results become more interesting and more realistic if we allow for asymmetry in the uncertainty surrounding legislators' ideal points.
@@
 In numerical examples, this pattern holds strongly.
-By `relative,' we mean that the bribes are scaled up relative to the equal gross position that occurs when uncertainty is symmetric.
+By `relative,' we mean that the bribes are scaled up relative to the bribe profile that creates equal gross position when uncertainty is symmetric.
 We also see that the bribes for legislators whose ideal points are more uncertain are scaled down while the bribes of legislators whose ideal points are less uncertain are scaled up, modulo relative position.
-That is, there is some effect of being more friendly versus less friendly, as the cumulative density that the legislator will vote in the vote buyer's favor changes in opposite directions when uncertainty rises depending on whether the legislator is friendly or unfriendly.
-This accords well with the finding in Figure \ref{fig:g1} that those legislators with very low and very high uncertainty gets the lowest payments, while those with more average levels of uncertainty receive the most.
+That is, there is some effect of being more friendly versus less friendly, as the cumulative density that the legislator will vote in the vote buyer's favor changes in opposite directions when uncertainty rises depending on whether the legislator is friendly or unfriendly (cfr Section~\ref{sec:uncert}).
+This accords well with the finding in Figure \ref{fig:g1} that those legislators with very low and very high uncertainty get the lowest payments, while those with more average levels of uncertainty receive the most.
 
 We demonstrate via the following numerical example.
-Let the bias parameter $\al=0$ and ignore Vote Buyer A.
+Let there be no bias on average in the un-bribed positions of the legislators (i.e.
+set the bias parameter at $\al=0$) and ignore Vote Buyer A.
 When we increase the scale parameter $s_{.5}$ for the legislator at $0.5$---that is, the least friendly to Vote Buyer $B$---from 1 to 1.5, $B$ stops bribing the most friendly legislator altogether.
 Vote Buyer $B$ does better in welfare terms because the probability that this legislator votes in his favor shifts upward.
-In fact, For $s_{.5}$ must be much closer to $1$ in order for $B$ to bribe this legislator, and when he does, the gross ideal point is smaller in absolute value than that for the other two legislators.
+In fact, $s_{.5}$ must be much closer to $1$ in order for $B$ to bribe this legislator, and when he does, the gross ideal point is smaller in absolute value than that for the other two legislators.
 
-On the other hand, if $s_{.5}$ is reduced from 1 to $0.75$, for an intermediate range of $W_B$, the willingness to pay parameter, $B$ switches to \textit{only} bribing legislator $0.5$.
+On the other hand, if $s_{.5}$ is reduced from 1 to $0.75$, for an intermediate range of the willingness to pay parameter $W_B$, Vote Buyer $B$ switches to \textit{only} bribing legislator $0.5$.
 As $W_B$ increases, eventually all three legislators are bribed again, but now this legislator receives a larger gross bribe.
@@
 As $s_{-.5}$ is increased from 1 to 1.5 or larger, $B$ stops bribing this most friendly legislator and the asymmetry has to be reduced to below 1.2 in order for him to resume bribing legislator $-0.5$.
-When he does so, he will move this legislator less than the other two with lower uncertainty.
-If we instead reduce $-0.5$'s uncertainty, he moves him further
+When he does so, he will move this legislator less than the other two legislators about whom there is less uncertainty.
+If we instead reduce $-0.5$'s uncertainty, Vote Buyer $B$ moves this legislator further than the other two.
 

### 2016-02-18 draft.tex
proofread sec:two

@@
 Thus the full set of first order conditions are
-\[
-    W_B\frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_X = 0
-\]
-\[
-    W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1 + \lambda_Y = 0 
-\]
-\[
-    W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_Z = 0
-\]
+\begin{equation}
+    \frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] = \frac{1 - \lambda_X}{W_B}
+		\label{eq:focB}
+\end{equation}
+\begin{equation}
+    \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] = \frac{1 - \lambda_Y}{W_B}
+\end{equation}
+\begin{equation}
+    \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] = \frac{1 - \lambda_Z}{W_B}
+\end{equation}
 \[
@@
 Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes.
-Vote Buyer A's first order conditions are more complicated because of the dependencies on $\bm a$.
-Below is the first order condition with respect to $a_0$:
+Vote Buyer A's first order conditions are more complicated than those of Vote Buyer $B$ because her choices $\bm a$ will impact those of Vote Buyer $B$.
+
+Below is the first order condition with respect to $a_0$, which can be compared to Equation~\ref{eq:focB} for Vote Buyer $B$:
 			 \begin{multline}
@@
 					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
-					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
+					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1 - \lambda_{XB}}{W_A}
 					\label{eq:focA}
@@
 
-Unlike in models with no uncertainty, we do not have knife edge results in which Vote Buyer $A$ uses Vote Buyer $B$'s indifference condition to ensure that he buys no votes--there is no such indifference condition in the presence of uncertainty.
+Unlike in models with no uncertainty, we do not have knife edge results in which Vote Buyer $A$ uses Vote Buyer $B$'s indifference condition to ensure that he buys no votes---there is no such indifference condition in the presence of uncertainty.
 However, it's possible that one or both vote buyers will not bribe any legislator because the non-negativity constraints bind for all three bribes.
-This requires that the willingness-to-pay parameter is sufficiently small.
+This requires that the willingness-to-pay parameters are sufficiently small for both vote buyers.
 
@@
   It is possible for both vote buyers to bribe legislators on the same vote.
+	\label{res:bothbribe}
 \end{proposition}

### 2016-02-18 draft.tex
rough in example for proof of prop:bothbribe

@@
 \subsection{Two Vote Buyers}
+\label{sec:two}
 Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes.
@@
   It is possible for both vote buyers to bribe legislators on the same vote.
-	\label{res:bothbribe}
+	\label{prop:bothbribe}
 \end{proposition}
@@
 
+\vskip.3in
+\noindent \textbf{\hypertarget{Pr_bothbribe}{Proof of Proposition~\ref{prop:bothbribe}}}: \\
+Take the following example.
+Let $\al=0$ so that the means of the ideal point distribution for the three legislators are $-\frac{1}{2}$, $0$ and $\frac{1}{2}$.
+Let the willingness-to-pay parameters be $W_A = 6$ and $W_B = 8$.
+And let the scale parameters for the legislators at $0$ and $\frac{1}{2}$ be 1 and $s_{-\frac{1}{2}} = 1.1$.
+
+In this example, the optimal bribe offer function for Vote Buyer $A$ is to offer nothing to the legislators at $0$ and $\frac{1}{2}$ and $a_{-\frac{1}{2}}=0.4$.
+Vote Buyer $B$ responds by offering nothing to the legislators at $-\frac{1}{2}$ and $\frac{1}{2}$ and $b_0 = 0.21$ to the legislator at zero.
+The final gross positions of the mean parameters for the three legislators are, from left to right, $\left\{ -0.1, -0.21, 0.5 \right\}$, with one legislator each being lobbied in each direction.
+
 \newpage

### 2016-02-18 draft.tex
start adding SOCs to proof of prop:2NNB

@@
 	\end{itemize}
-The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$.
+The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$ (see below).
 Note that once this is known, one can go back to, for instance, Equations~\ref{eq:base} and substitute for one of the variables.
 Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.
+
+\vskip.2in
+\noindent \un{Second Order Conditions} \\
+When one non-negativity constraint binds, the bordered Hessian is 4x4.\\
+		$\left|\begin{tabular}{cccc}
+			0 & $\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ \\
+			$\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
+			$\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
+			$\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
+		\end{tabular} \right|\\$
 $\hfill\blacksquare$

### 2016-02-19 draft.tex
add roadmap to end of sec:lit
rewrite first paragraph of intro

@@
 
-In democratic countries, legislatures are the authoritative source of statutory law.
-This paper seeks to understand how uncertainty affects the incentives for lobbying and the associated prospects for the passage of legislation.
+In the United States alone, nearly $4$ billion dollars is spent every year on lobbying and campaign contributions.
+Looking at the U.S.
+Congress, for instance, we see that special interest groups exert these economically significant amounts of effort and resources to influence a legislative process that is fraught with uncertainty.
+In particular, legislators' voting behavior can seldom be perfectly anticipated, as lawmakers consider a variety of influences when deciding how to vote, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership.
+
 Saiegh (2011) identifies two major factors that shape lawmaking: whether buying legislative votes is a feasible option and the unpredictability of legislators' voting behavior.
-The source of the uncertainty is the existence of cross-pressured legislators: in deciding how to vote, lawmakers consider a variety of influences, including their personal values, announced positions, the views of their constituents, and the preferences of their party leadership.
-Therefore, legislators' voting behavior can seldom be perfectly anticipated.
+When vote buying is possible and legislative uncertainty is present---as is often the case---the optimal lobbying strategies are far from obvious.
+This paper seeks to understand how uncertainty surrounding the preferences of legislators affects the incentives for lobbying and the associated prospects for the passage of legislation.
 
@@
 
-%I will begin by ...
-Section~\ref{sec:main} then ...
-In Section~ \ref{sec:example}, ...
-Section~\ref{sec:dis} explores ....
-Several extensions of the model are explored in Section~\ref{sec:ext} and Section~\ref{sec:concl} concludes.
+I will introduce the structural model in Section~\ref{sec:model} and discuss the theoretical results in Section~ \ref{sec:res}.
+Section~\ref{sec:est} discusses the estimation approach while Section~\ref{sec:house} applies this approach to the case of the U.S.
+House of Representatives.
+Section~\ref{sec:concl} concludes.
 

### 2016-02-19 draft.tex
finish rewriting intro

@@
 
-We solve a model of vote buying in which there is uncertainty about the ideological positions of legislators with information about this uncertainty symmetric among all players.
+We solve a model of vote buying in which there is uncertainty about the ideological positions of legislators.
 This model is able to describe some realistic aspects of lobbying and voting behavior: for instance, it predicts that lobbyists on both sides of an issue may be active at the same time, that moderate legislators and those about which there is average uncertainty receive more bribes than those that are ideologically extreme, and that ideal points gross of bribes need not be equalized.
@@
 A payment to a legislator has the effect of shifting the legislator's ideal point, which we take to be known up to the mean and variance parameters of a given probability distribution.
-Thus bribing a legislator has the effect of changing the probability with which the legislator votes in the manner the vote buyer prefers.
-In this environment, the optimal vote-buying strategies are not immediately obvious.
+We assume that information about the legislators' ideal points is symmetric among all players; the legislators are not strategic and there is no motive for signalling.
+Bribing a legislator only has the effect of changing the probability with which the legislator votes in the manner the vote buyer prefers.
 
-We find that the number of legislators a vote buyer chooses to lobby is increasing in the value he places on the policy.
+When the lobbyists are faced with this uncertainty about the preferences of the legislators, we find, quite intuitively, that the number of legislators a vote buyer chooses to lobby is increasing in the value he places on the policy.
 When a vote buyer's willingness-to-pay for his preferred policy is very low, he will bribe none of the legislators; if it is very high, he will bribe all of them.
-Buying one or two votes is also possible.
+Intermediate outcomes are also possible.
 
@@
 
-If uncertainty is taken to be the same for the ideal points of all the legislators, we find that the vote buyers use `leveling strategies' as in Groseclose and Snyder (1996) and Banks (2000).
+If we assume identical levels of uncertainty about the ideal points of all the legislators, we find that the vote buyers use `leveling strategies' as in Groseclose and Snyder (1996) and Banks (2000).
 Allowing for asymmetric levels of uncertainty, on the other hand, provides a more realistic picture that accords well with our empirical findings that legislators with moderate levels of uncertainty are the target of the highest levels of lobbying, while those about whom there are very high levels of uncertainty most often remain unbribed.
@@
 We find one more result that is appealing from an empirical point of view.
-In this model, it is possible to have both vote buyers paying positive bribes on the same issue.
-Because the results of the model accord well with these important patterns in the data, we believe this model will contribute to the understanding of the political uncertainty that surrounds statutory lawmaking.
+In models of vote buying that do not incorporate uncertainty, only one vote buyer will pay bribes on any given issue.
+In this model with uncertainty about legislators' ideal points, however, it is possible to have both vote buyers paying positive bribes on the same issue.
+The results of the model accord well with these important patterns in the data, and we believe this model makes an important contribution to the understanding of the political uncertainty that surrounds statutory lawmaking.
+It both brings more realism to the studying of legislative voting and vote buying \textit{and} gives us a window into an important, under-studied facet of the legislative environment.
 

### 2016-02-19 two-groups.tex
continue fixing Y,Z mixup in two-groups; stuck on math/SOCs

@@
 		\begin{itemize}
-			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$.
+			\item But this is not quite right: sometimes the non-negativity constraint binds on the PDF of that variables (as in the case of $\al=-0.3$ and $W_B = 8$).
 		\end{itemize}
@@
 	\end{itemize}	
-In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$.
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, we know that $Z < 0$ (not true because we can have $\alpha < -.5$).
 Note that this is due to the construction of the problem.
@@
 The first derivative of the objective function w.r.t.
-$b(-\frac{1}{2})$ is (in logistic form)
+$b(\frac{1}{2})$ is
 \begin{equation}
@@
 Everything except for the expression in the curly braces is positive.
-The expression in the curly braces is positive when $z\leq0$ and negative when $z\geq0$.
-So this objective function appears to have an inflection point at $z=0$.
+The expression in the curly braces is positive when $Z<0$ and negative when $Z>0$.
+So this objective function appears to have an inflection point at $Z=0$.
 \begin{itemize}
-	\item When $z < 0$ (as when this legislator is naturally against you and you don't bribe her), this expression is negative
+	\item When $Z > 0$ (as is the case as long as $\al > -0.5$), this expression is negative
 \end{itemize}
 
-\vskip1in
-We also need cross partials. Let's start with the first derivative for $b\left(\frac{1}{2}\right)$, analogous to Expression~\ref{eq:firstderiv} for $b\left(-\frac{1}{2}\right)$:
+\vskip.3in
+We also need cross partials. Let's start with the first derivative for $b\left(-\frac{1}{2}\right)$, analogous to Expression~\ref{eq:firstderiv} for $b\left(\frac{1}{2}\right)$:
 \begin{equation}
@@
 		\begin{tabular}{cccc}
-			0 & $\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_1}{\partial b\left(-0\right)}$ & $\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ \\
-			$\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
-			$\frac{\partial g_1}{\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
-			$\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+			0 & $\frac{\partial g_3}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_3}{\partial b\left(-0\right)}$ & $\frac{\partial g_3}{\partial b\left(\frac{1}{2}\right)}$ \\
+			$\frac{\partial g_3}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			$\frac{\partial g_3}{\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			$\frac{\partial g_3}{\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
 		\end{tabular} \\
 
+Evaluating the constraint terms:\\
+\begin{tabular}{cccc}
+			0 & 0 & 0 & -1 \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular}
+
+\vskip.3in
+The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.
+\begin{itemize}
+	\item First we need the determinant of the next-to-last principal minor, the 3x3 matrix that is the upper-lefthand corner of this matrix.
+This determinant should be non-negative.
+It's actually equal to zero because of the row / column of zeros, so gives no further conditions (note that this is NOT the case when either of the other two bribes are the single non-negative bribe).
+	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
+		\[
+		  0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right| + 0 \cdot \left|\text{something} \right| - (-1)\cdot 
+			\left|\begin{array}{ccc}
+				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
+			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
+			\end{array} \right| 
+		\]
+		\[ 
+			=
+			\left|\begin{array}{ccc}
+				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
+			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
+			\end{array} \right| 
+		\]
+		\[
+		  = - 1 \cdot \left|\begin{array}{cc}
+			\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} \\
+			\frac{\partial^2 L}{\partial b(0) \partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b(0)^2}
+			\end{array} \right|
+		\]
+		\[
+		  = - 1 \cdot \left(
+			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
+		\]
+		\[
+		  = \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}
+		\]
+
+  We need this determinant to be non-positive, that is
+		\[
+		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2
+		\]
+	  The right hand side is non-negative because it's a square.
+The left hand side must then be non-negative.
+, and since we know that one term is positive from the previous principal minor result, the other must be positive as well.
+Thus both $X$ and $Y$ must be positive.
+\end{itemize}
+Note that nothing useful seems to come out of trying to expand and then simplify this expression. I get:
+\[
+  2e^{-X}e^{-Y} + 2 > e^{-2Z} + e^{-X}e^{-2Z} + e^{-Y}e^{-2Z} + e^{-X}e^{-Y}e^{-2Z}
+\]		
+\begin{comment}
 \vskip.2in		
@@
 
+\vskip.3in
 The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.
@@
 \]		
+\end{comment}
 

### 2016-02-19 draft.tex
add SOCs to prop:2NNB proof, comment out for now

@@
 
+\begin{comment}
 \vskip.2in
@@
 		\end{tabular} \right|\\$
+
+		\vskip.2in		
+\noindent Evaluating the constraint terms, we have:\\
+\begin{tabular}{cccc}
+			0 & 0 & 0 & -1 \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular}
+
+\vskip.2in
+The second order condition is on the last two principal minors. The last must be negative. The next to last should then be positive.
+
+Let's begin with the next-to-last principle minor, which is the determinant of the 3x3 matrix that is the upper-lefthand corner of this matrix. This is
+	\[
+	  0 + 0 + 0 - \left[0 + 0 + (-1)(-1)\frac{\partial^2 L}{\partial b(0)^2} \right] = - \frac{\partial^2 L}{\partial b(0)^2}
+	\]
+\begin{itemize}
+	\item First we need the determinant of the next-to-last principal minor, the .
+This determinant should be positive.
+We can use the trick by which one copies the first two rows to the right of the matrix and then multiplies down the columns to the right and up the columns to the right (these terms get a negative sign).
+Then the determinant is
+	  \[
+		  0 + 0 + 0 - \left[0 + 0 + (-1)(-1)\frac{\partial^2 L}{\partial b(0)^2} \right] = - \frac{\partial^2 L}{\partial b(0)^2}
+		\]
+		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is non-negative
+	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
+		\[
+		  0 \cdot \left|\text{something} \right| - (-1)\cdot 
+			\left|\begin{array}{ccc}
+				- 1 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			0 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right| + 0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right|
+		\]
+		\[ 
+			=
+			\left|\begin{array}{ccc}
+				- 1 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			0 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right|
+		\]
+		\[
+		  = - 1 \cdot \left|\begin{array}{cc}
+			\frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
+			\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+			\end{array} \right|
+		\]
+		\[
+		  = - 1 \cdot \left(
+			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
+		\]
+		\[
+		  = \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
+		\]
+
+  We need this determinant to be non-positive, that is
+		\[
+		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 
+		\]
+	  The right hand side is positive because it's a square.
+Moreover, it is strictly positive because $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ is strictly positive: examine Equation~\ref{eq:xpartial}.
+Since $Z < 0$ in the case under examination, Equation~\ref{eq:xpartial} must be strictly positive.
+(This strengthens us from the negative semi-definite condition condition that supplies only a weak inequality).
+
+		The left hand side must then be positive, and since we know that one term is positive from the previous principal minor result, the other must be positive as well.
+Thus both $X$ and $Y$ must be positive.
+\end{itemize}
+\end{comment}
+
 $\hfill\blacksquare$

### 2016-02-20 two-groups.tex
fix mistake in FOCs for 2NNBs case

@@
 	\end{itemize}	
-In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, we know that $Z < 0$ (not true because we can have $\alpha < -.5$).
-Note that this is due to the construction of the problem.
-This means $e^Z < 1$.
-In this case,
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, there are two possibilities. If $Z < 0$, $e^Z < 1$. In this case,
 	\begin{itemize}
-		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
-		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
+		\item Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$, $X\geq 0 \geq Y$, or $0 \geq X \geq Y$.
+		\item Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$, $Y \geq 0 \geq X$, or $0 \geq Y \geq X$.
 	\end{itemize}
+
+If $Z > 0$, $e^Z < 1$. In this case, ...
+
 The second order conditions will pin down the solution in this case of two non-negative bribes.
@@
 \begin{itemize}
-	\item SOCs imply that both $X$ and $Y$ are positive.
+	\item SOCs imply that $X$ and $Y$ are either both positive, both negative, or one zero and the other unrestricted. But we can use these inequalities to get rid of the last case [finish this]
 \end{itemize}

### 2016-02-22 two-groups.tex
fix proof of prop:2NNB in two-groups

--- 2016-02-19 two-groups.tex
@@
 	\end{itemize}	
-In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, we know that $Z < 0$ (not true because we can have $\alpha < -.5$).
-Note that this is due to the construction of the problem.
-This means $e^Z < 1$.
-In this case,
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, there are three possibilities, $Z=0$, $Z>0$ and $Z<0$.
+I will take each in turn.
+\begin{enumerate}
+	\item When $Z = 0$, $e^Z = 1$. Then the only values of $X$ and $Y$ with which both Equation~\ref{eq:1} and \ref{eq:2} are consistent are $X=Y$.
 		\begin{itemize}
-		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
-		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
-	\end{itemize}
-The second order conditions will pin down the solution in this case of two non-negative bribes.
-
-\begin{itemize}
-	\item SOCs imply that both $X$ and $Y$ are positive.
+			\item Note that this is the only case in which $e^{-2Z} =1$, i.e.
+$\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} = 0$.
+In the other two cases, the right hand side of \ref{eq:soc} is positive so that the two second derivatives on the left hand side must be either both positive or both negative.
+This means that $X$ and $Y$ must be either both positive or both negative.
 		\end{itemize}
 
-Once we know that both $X=Y>0$ (or $X=Z>0$), go back to one of the equations like \ref{eq:base} and substitute for one of the variables.
+	\item When $Z > 0$, $e^Z > 1$. In this case, $X$ and $Y$ must be positive since they are greater than $Z$.
+		\begin{itemize}
+			\item Equation~\ref{eq:1} is consistent with $Y\geq X\geq 0$.
+			\item Equation~\ref{eq:2} is consistent with $X \geq Y \geq 0$.
+			\item Since both equations must hold, we have $X=Y \geq 0$
+		\end{itemize}
+
+	\item When $Z < 0$, $e^Z < 1$. In this case,
+			\begin{itemize}
+				\item Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$ or $0 \geq Y \geq X$.
+				\item Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$ or $0 \geq X \geq Y$.
+				\item Since both equations must hold, we have either $X=Y \geq 0$ or $X=Y \leq 0$
+		\end{itemize}
+
+\end{enumerate}
+
+Once we know that both $X=Y$ (or $X=Z$), go back to one of the equations like \ref{eq:base} and substitute for one of the variables.
 Given that the third equals zero, for a particular value of $\left(\alpha,W_B\right)$, we can solve for the two relevant bribes.
@@
   We need this determinant to be non-positive, that is
-		\[
+		\begin{equation}
 		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2
-		\]
+			\label{eq:soc}
+		\end{equation}
 	  The right hand side is non-negative because it's a square.

### 2016-02-22 two-groups.tex
clean up foc/socs for prop:2NNB proof in two-groups

@@
 So this objective function appears to have an inflection point at $Z=0$.
-\begin{itemize}
-	\item When $Z > 0$ (as is the case as long as $\al > -0.5$), this expression is negative
-\end{itemize}
 
@@
 \end{equation}
+The sign of this expression is the same as the sign of $e^{-2Z} - 1$. It's 0 when $Z=0$, positive when $Z < 0$ and negative when $Z > 0$.
 
@@
 		\end{equation}
-	  The right hand side is non-negative because it's a square.
-The left hand side must then be non-negative.
-, and since we know that one term is positive from the previous principal minor result, the other must be positive as well.
-Thus both $X$ and $Y$ must be positive.
+	  The right hand side is non-negative because it's a square. The left hand side must then be non-negative. 
 \end{itemize}

### 2016-02-22 draft.tex
rewrite first half of prop:2NNB proof in draft

--- 2016-02-19 draft.tex
@@
 
-\usepackage[pdftex,
-bookmarks=true,
-bookmarksnumbered=false,
-pdfview=fitH,
-bookmarksopen=true]{hyperref}
 \usepackage[pdftex]{graphicx}
@@
 \usepackage[hang,flushmargin]{footmisc}
+
+\usepackage[pdftex,
+bookmarks=true,
+bookmarksnumbered=false,
+pdfview=fitH,
+bookmarksopen=true]{hyperref}
 
@@
 		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
+		\label{eq:baseY}
 	\end{equation}
@@
 
+		\vskip.2in
+The second derivative, for instance with respect to $b_0$ is
+\begin{equation}
+  \frac{\partial^2 L}{\partial b(0)^2} = W_B\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-X}}{\left(1+e^{-X}\right)^3} \right] \left\{e^{-X}-1 \right\}
+	\label{eq:secderiv}
+\end{equation}
+Everything except for the expression in the curly braces is positive.
+The expression in the curly braces is positive when $X<0$ and negative when $X>0$.
+It is zero when $X=0$.
+Analogous expressions hold for the second derivatives with respect to $b_{-.5}$ and $b_{.5}$.
+
+\vskip.2in
+The cross partials are of the form 
+\begin{equation}
+  \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} = W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X}\left(e^{-2Z} - 1 \right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+	\label{eq:xpartial}
+\end{equation}
+The sign of this expression is the same as the sign of $e^{-2Z} - 1$. It's 0 when $Z=0$, positive when $Z < 0$ and negative when $Z > 0$.
+
+When one non-negativity constraint binds, the bordered Hessian is 4x4. \\
+		$\left|\begin{tabular}{cccc}
+			0 & $\frac{\partial g_3}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial g_3}{\partial b_{\frac{1}{2}}}$ \\
+			$\frac{\partial g_3}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
+			$\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
+			$\frac{\partial g_3}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
+		\end{tabular} \right|\\$
+
+Evaluating the constraint terms, we have\\
+\begin{tabular}{cccc}
+			0 & 0 & 0 & -1 \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
+			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
+			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
+		\end{tabular}
+
+\vskip.2in
+The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.
+
+The next-to-last principal minor is the 3x3 matrix that is the upper-lefthand corner of this matrix.
+This determinant should be non-negative but is identically equal to zero because of the first row of zeros.
+This therefore provides no restrictions on the problem.\footnote{In the case where it is the non-negativity constraint on either $b_0$ or $b_{-.5}$ that binds, this condition \textit{does} imply an extra constraint.
+When $b_0 = 0$, the extra constraint is that $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq0$, i.e.
+$Y\leq 0$.
+When $b_{-.5}=0$, the extra condition is that $X\leq 0$.}
+\begin{itemize}
+	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
+		\[
+		  0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right| + 0 \cdot \left|\text{something} \right| - (-1)\cdot 
+			\left|\begin{array}{ccc}
+				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
+			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
+			\end{array} \right| 
+		\]
+		\[ 
+			=
+			\left|\begin{array}{ccc}
+				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
+			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
+			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
+			\end{array} \right| 
+		\]
+		\[
+		  = - 1 \cdot \left|\begin{array}{cc}
+			\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} \\
+			\frac{\partial^2 L}{\partial b(0) \partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b(0)^2}
+			\end{array} \right|
+		\]
+		\[
+		  = - 1 \cdot \left(
+			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
+		\]
+		\[
+		  = \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}
+		\]
+
+  We need this determinant to be non-positive, that is
+		\begin{equation}
+		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2
+			\label{eq:soc}
+		\end{equation}
+	  The right hand side is non-negative because it's a square. The left hand side must then be non-negative. 
+\end{itemize}
+
+\vskip.5in
 		Setting the left-hand size of these two equations equal to each other and simplifying,
@@
    Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
-		\[
-		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
-		\]
 		\begin{equation}
@@
 
-\vskip.2in
-\noindent \un{Second Order Conditions} \\
-When one non-negativity constraint binds, the bordered Hessian is 4x4.\\
-		$\left|\begin{tabular}{cccc}
-			0 & $\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ \\
-			$\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
-			$\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
-			$\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
-		\end{tabular} \right|\\$
 $\hfill\blacksquare$

### 2016-02-23 draft.tex
clean up first half of prop:2NNB proof

@@
 But the non-negativity constraint here binds for the third, and which legislator is this third, un-bribed legislator depends on where the three ideal points are relative to the zero point at which a legislator has a 50$\%$ probability of voting for either the status quo or the new proposal.
+
 If $B$'s willingness-to-pay parameter increases, the non-negativity constraint becomes less binding.
@@
 \begin{equation}
-  \frac{\partial^2 L}{\partial b(0)^2} = W_B\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-X}}{\left(1+e^{-X}\right)^3} \right] \left\{e^{-X}-1 \right\}
+  \frac{\partial^2 L}{\partial b_0^2} = W_B\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-X}}{\left(1+e^{-X}\right)^3} \right] \left\{e^{-X}-1 \right\}
 	\label{eq:secderiv}
@@
 \begin{equation}
-  \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} = W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X}\left(e^{-2Z} - 1 \right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
+  \frac{\partial^2 L}{\partial b_{-.5} \partial b_0} = W_B\left[\frac{e^{-X}}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right] \left[ \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2} \right] \left\{e^{-2Z} - 1 \right\}
 	\label{eq:xpartial}
@@
 
-When one non-negativity constraint binds, the bordered Hessian is 4x4. \\
+When one non-negativity constraint binds, the bordered Hessian is 4x4: \\
 		$\left|\begin{tabular}{cccc}
-			0 & $\frac{\partial g_3}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial g_3}{\partial b_{\frac{1}{2}}}$ \\
-			$\frac{\partial g_3}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
-			$\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
-			$\frac{\partial g_3}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
+			0 & $\frac{\partial g_3}{\partial b_{-.5}}$ & $\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial g_3}{\partial b_{.5}}$ \\
+			$\frac{\partial g_3}{\partial b_{-.5}}$ & $\frac{\partial^2 L}{\partial b_{-.5}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-.5}}$ & $\frac{\partial^2 L}{\partial b_{.5} \partial b_{-.5}}$  \\
+			$\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-.5} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{.5}\partial b_0}$ \\
+			$\frac{\partial g_3}{\partial b_{.5}}$ & $\frac{\partial^2 L}{\partial b_{-.5}\partial b_{.5}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{.5}}$ & $\frac{\partial^2 L}{\partial b_{.5}^2}$
 		\end{tabular} \right|\\$
@@
 Evaluating the constraint terms, we have\\
-\begin{tabular}{cccc}
+$\left|\begin{tabular}{cccc}
 			0 & 0 & 0 & -1 \\
-			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
-			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
-			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
-		\end{tabular}
+			0 & $\frac{\partial^2 L}{\partial b_{-.5}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-.5}}$ & $\frac{\partial^2 L}{\partial b_{.5} \partial b_{-.5}}$  \\
+			0 & $\frac{\partial^2 L}{\partial b_{-.5} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{.5}\partial b_0}$ \\
+			-1 & $\frac{\partial^2 L}{\partial b_{-.5}\partial b_{.5}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{.5}}$ & $\frac{\partial^2 L}{\partial b_{.5}^2}$
+		\end{tabular} \right|$
 
@@
 This therefore provides no restrictions on the problem.\footnote{In the case where it is the non-negativity constraint on either $b_0$ or $b_{-.5}$ that binds, this condition \textit{does} imply an extra constraint.
-When $b_0 = 0$, the extra constraint is that $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq0$, i.e.
+When $b_0 = 0$, the extra constraint is that $\frac{\partial^2 L}{\partial b_{-.5}^2} \geq0$, i.e.
 $Y\leq 0$.

### 2016-02-23 draft.tex
clean up prop:2NNB proof up to final argument

@@
 		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
-		\label{eq:base}
+		\label{eq:baseX}
 	\end{equation}
@@
 \vskip.2in
-The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.
+The second order condition is on the last two principal minors. The largest must be non-positive. The next to last should then be non-negative.
 
@@
 When $b_{-.5}=0$, the extra condition is that $X\leq 0$.}
-\begin{itemize}
-	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
+
+The determinant of the last principal minor, which is the whole 4x4 matrix, must be non-positive. Because of the three zeros in the first row, this determinant can be simplified as follows:
 		\[
-		  0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right| + 0 \cdot \left|\text{something} \right| - (-1)\cdot 
+		  0 - 0 + 0 - (-1)\cdot 
 			\left|\begin{array}{ccc}
-				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
-			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
-			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
-			\end{array} \right| 
-		\]
-		\[ 
-			=
-			\left|\begin{array}{ccc}
-				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
-			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
-			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
-			\end{array} \right| 
-		\]
-		\[
-		  = - 1 \cdot \left|\begin{array}{cc}
-			\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} \\
-			\frac{\partial^2 L}{\partial b(0) \partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b(0)^2}
+				0 & \frac{\partial^2 L}{\partial b_{-.5}^2} & \frac{\partial^2 L}{\partial b_0\partial b_{-.5}}  \\
+			0 & \frac{\partial^2 L}{\partial b_{-.5} \partial b_0} & \frac{\partial^2 L}{\partial b_0^2} \\
+			-1 & \frac{\partial^2 L}{\partial b_{-.5}\partial b_{.5}} & \frac{\partial^2 L}{\partial b_0 \partial b_{.5}} 
+			\end{array} \right| =	
+			- 1 \cdot \left|\begin{array}{cc}
+			\frac{\partial^2 L}{\partial b_{-.5}^2} & \frac{\partial^2 L}{\partial b_0\partial b_{-.5}}  \\
+			\frac{\partial^2 L}{\partial b_{-.5} \partial b_0} & \frac{\partial^2 L}{\partial b_0^2}
 			\end{array} \right|
@@
 		  = - 1 \cdot \left(
-			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
+			\frac{\partial^2 L}{\partial b_{-.5}^2} \frac{\partial^2 L}{\partial b_0^2} - \left[\frac{\partial^2 L}{\partial b_0\partial b_{-.5}}\right]^2 \right) \leq 0
 		\]
-		\[
-		  = \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}
-		\]
-
-  We need this determinant to be non-positive, that is
+	Therefore we must have 
 		\begin{equation}
-		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2
+		  \frac{\partial^2 L}{\partial b_{-.5}^2} \frac{\partial^2 L}{\partial b_0^2} \geq \left[\frac{\partial^2 L}{\partial b_0\partial b_{-.5}}\right]^2 
 			\label{eq:soc}
 		\end{equation}
-	  The right hand side is non-negative because it's a square. The left hand side must then be non-negative. 
-\end{itemize}
-
-\vskip.5in
-		Setting the left-hand size of these two equations equal to each other and simplifying,
+	  The right hand side is non-negative because it's a square.
+The left hand side must then be non-negative.
+With this result in hand, we can proceed to an analysis of the first order conditions.
+Combining the left-hand side of Equations~\ref{eq:baseY} and \ref{eq:baseX} and simplifying, we have
 		\[
@@
 		\]
-		\[
-		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
-		\]
 		\begin{equation}
@@
 		\end{equation}
-  	Second, multiplying through by zero:
+  	Second:
 	  \begin{equation}
@@
 
-In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$.
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_{-\frac{1}{2}}$, we know that $Z < 0$.
 Note that this is due to the construction of the problem.
@@
 The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$ (see below).
-Note that once this is known, one can go back to, for instance, Equations~\ref{eq:base} and substitute for one of the variables.
+Note that once this is known, one can go back to, for instance, Equations~\ref{eq:baseX} and substitute for one of the variables.
 Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.

### 2016-02-23 draft.tex
paste in final argument for proof of prop:2NNB from two-groups

@@
 
-In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_{-\frac{1}{2}}$, we know that $Z < 0$.
-Note that this is due to the construction of the problem.
-This means $e^Z < 1$.
-In this case,
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, there are three possibilities, $Z=0$, $Z>0$ and $Z<0$.
+I will take each in turn.
+\begin{enumerate}
+	\item When $Z = 0$, $e^Z = 1$. Then the only values of $X$ and $Y$ with which both Equation~\ref{eq:1} and \ref{eq:2} are consistent are $X=Y$.
 		\begin{itemize}
-		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
-		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
+			\item Note that this is the only case in which $e^{-2Z} =1$, i.e.
+$\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} = 0$.
+In the other two cases, the right hand side of \ref{eq:soc} is positive so that the two second derivatives on the left hand side must be either both positive or both negative.
+This means that $X$ and $Y$ must be either both positive or both negative.
 		\end{itemize}
-The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$ (see below).
-Note that once this is known, one can go back to, for instance, Equations~\ref{eq:baseX} and substitute for one of the variables.
-Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.
+	\item When $Z > 0$, $e^Z > 1$. In this case, $X$ and $Y$ must be positive since they are greater than $Z$.
+		\begin{itemize}
+			\item Equation~\ref{eq:1} is consistent with $Y\geq X\geq 0$.
+			\item Equation~\ref{eq:2} is consistent with $X \geq Y \geq 0$.
+			\item Since both equations must hold, we have $X=Y \geq 0$
+		\end{itemize}
+	\item When $Z < 0$, $e^Z < 1$. In this case,
+			\begin{itemize}
+				\item Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$ or $0 \geq Y \geq X$.
+				\item Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$ or $0 \geq X \geq Y$.
+				\item Since both equations must hold, we have either $X=Y \geq 0$ or $X=Y \leq 0$
+		\end{itemize}
+\end{enumerate}
 

### 2016-02-23 draft.tex
complete proof of prop:2NNB

--- 2016-02-23 draft.tex
@@
 $Y\leq 0$.
-When $b_{-.5}=0$, the extra condition is that $X\leq 0$.}
+When $b_{-.5}=0$, the extra condition is that $X\leq 0$.\label{fn:extra}}
 
@@
 
-In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_{-\frac{1}{2}}$, we know that $Z < 0$.
-Note that this is due to the construction of the problem.
-This means $e^Z < 1$.
-In this case,
-	\begin{itemize}
-		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
-		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
-	\end{itemize}
-The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$ (see below).
-Note that once this is known, one can go back to, for instance, Equations~\ref{eq:baseX} and substitute for one of the variables.
-Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.
-
+In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_\frac{1}{2}$, there are three possibilities, $Z=0$, $Z>0$ and $Z<0$. I will take each in turn.
+\begin{enumerate}
+	\item $Z = 0$, $e^Z = 1$.
+Then the only values of $X$ and $Y$ with which both Equation~\ref{eq:1} and \ref{eq:2} are consistent are $X=Y$.\footnote{Note that this is the only case in which $e^{-2Z} =1$, i.e.
+$\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0} = 0$.
+In the other two cases, the right hand side of \ref{eq:soc} is strictly positive so that the two second derivatives on the left hand side must be either both positive or both negative.
+This means that $X$ and $Y$ must be either both positive or both negative.}
+	\item $Z > 0$, $e^Z > 1$.
+In this case, $X$ and $Y$ must be positive since they are greater than $Z$.
+Equation~\ref{eq:1} is consistent only with $Y\geq X\geq 0$, while Equation~\ref{eq:2} is consistent with $X \geq Y \geq 0$.
+Since both equations must hold, we have $X=Y \geq 0$.
+	\item $Z < 0$, $e^Z < 1$.
+In this case, Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$ or $0 \geq Y \geq X$.
+Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$ or $0 \geq X \geq Y$.
+Since both equations must hold, we have either $X=Y \geq 0$ or $X=Y \leq 0$.
+\end{enumerate}
+		In any case, it must be that $X = Y$.
+Similar, slightly simpler proofs go through when the zero bribe is for either of the other two legislators because of the extra condition described in Footnote~\ref{fn:extra}.
 $\hfill\blacksquare$

### 2016-02-24 draft.tex
clarify players, strategy spaces and timing in sec:model

@@
 
-The model is based on Banks' (2000) model of vote buying in a legislature, which is in turn a discrete version of Groseclose and Snyder's (1996) model with a continuum of legislators.
-The major difference here is the addition of uncertainty about the legislator's ideal points.
+The model borrows much from Banks' (2000) model of vote buying in a legislature, which is in turn a discrete version of Groseclose and Snyder's (1996) model with a continuum of legislators.
+The major difference here is the addition of uncertainty about the legislators' ideal points.
 
+There are five players in the model.
 Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$.
@@
 
-There are two vote buyers labeled $A$ and $B$ who each prefers to maximize the expected value of his preferred policy net of the bribes he has to pay.
+There are two vote buyers labeled $A$ and $B$ who each prefers to maximize the expected value of his preferred policy net of the bribes he has to pay; each chooses a vector of three non-negative bribes.
 $A$ prefers policy $x$ and has willingness to pay (WTP) $W_A$ for $x$ measured in money and values $s$ at zero.
-$B$ prefers $s$and has WTP $W_B$ for $s$.
-Each vote buyer would prefer to concede the issue rather than pay more than his WTP.
+$B$ prefers $s$ and has WTP $W_B$ for $s$ and values $x$ at zero.
 

### 2016-03-30 constrained-optimization.r
add ability to hard code bribes for A individually

@@ -2,10 +2,13 @@
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
 rm(list = ls())
-ap5 = 1.5
-a0 = ap5 + .5
-anp5 = ap5 + 1
+#ap5 = 1.5
+#a0 = ap5 + .5
+#anp5 = ap5 + 1
 
+ap5 = 2.19
+a0 = 0
+anp5 = 1.19
 
 h <- function(WB,al) {
 
@@ -35,7 +38,7 @@ return(out)
 }
 
 # Create a dataframe of parameter values
-wb_vector <- 9:10 
+wb_vector <- 9:20 
 a_vector <- seq(0.0, 0.0, 0.0)
 params <- expand.grid("wb" = wb_vector, "a" = a_vector)
 

### 2016-03-30 constrained-optimizationA.R
add program to calc bribes for A given B's bribes

@@ -1,0 +1,63 @@
+#optim function minimizes 'f'; c vector are starting values; lower is the
+#constraint; I choose a null gradient because it was easiest to get up and running
+#note that here the beta parameter is hard coded in as equal to 1
+rm(list = ls())
+#bp5 = 1.5
+#b0 = bp5 + .5
+#bnp5 = bp5 + 1
+
+bp5 = 0
+b0 = 0
+bnp5 = 0
+
+h <- function(WB,al) {
+
+sy=1
+sz=1
+  
+f <- function(B,WB,al) {
+  Ap5 <- B[1]
+  A0 <- B[2]
+  Anp5 <- B[3]
+  -WB*((1/(1+exp(-al - A0 + b0)))*(1/(1+exp((-al + .5 - Anp5 + bnp5)/sy))) + (1/(1+exp(-al - A0 + b0)))*(1/(1+exp((-al - .5 - Ap5 + bp5)/sz))) + (1/(1+exp((-al - .5 - Ap5 + bp5)/sz)))*(1/(1+exp((-al + .5 - Anp5 + bnp5)/sy))) - 2*(1/(1+exp(-al - A0 + b0)))*(1/(1+exp((-al + .5 - Anp5 + bnp5)/sy)))*(1/(1+exp((-al - .5 - Ap5 + bp5)/sz)))) + A0 + Ap5 + Anp5
+}   
+
+o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
+#o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
+
+X = round(al +b0 - o$par[2], digits = 2)       #A0   these are shorthand variables for the exponents
+Y = round(-.5 + al +bnp5 - o$par[3], digits = 2)    #Anp5  in the logistic CDFs; I don't use them in the function
+Z = round(.5 + al + bp5 - o$par[1], digits=2)   #Ap5 but I've pasted in values here to check
+
+pos <- c(Z,X,Y)
+bribes <- c(o$par,-o$value)
+#note I haven't fixed the win probability to include a's bribes
[…]

### 2016-03-30 constrained-optimizationA.R
fix signs on bribes in constrained-optimA

@@ -6,9 +6,9 @@ rm(list = ls())
 #b0 = bp5 + .5
 #bnp5 = bp5 + 1
 
-bp5 = 0
+bp5 = 2.36
 b0 = 0
-bnp5 = 0
+bnp5 = 1.36
 
 h <- function(WB,al) {
 
@@ -25,9 +25,9 @@ f <- function(B,WB,al) {
 o <- optim(c(1,1,1,WB,al),function(B) f(B,WB,al),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
 #o <- constrOptim(c(0.01,0.01,0.01,WB,al),function(B) f(B,WB,al),gr=NULL,method = "Nelder-Mead", ui = rbind(c(1,0,0),c(0,1,0),c(0,0,1)),ci=c(0,0,0))
 
-X = round(al +b0 - o$par[2], digits = 2)       #A0   these are shorthand variables for the exponents
-Y = round(-.5 + al +bnp5 - o$par[3], digits = 2)    #Anp5  in the logistic CDFs; I don't use them in the function
-Z = round(.5 + al + bp5 - o$par[1], digits=2)   #Ap5 but I've pasted in values here to check
+X = round(al -b0 + o$par[2], digits = 2)       #A0   these are shorthand variables for the exponents
+Y = round(-.5 + al -bnp5 + o$par[3], digits = 2)    #Anp5  in the logistic CDFs; I don't use them in the function
+Z = round(.5 + al - bp5 + o$par[1], digits=2)   #Ap5 but I've pasted in values here to check
 
 pos <- c(Z,X,Y)
 bribes <- c(o$par,-o$value)
@@ -38,7 +38,7 @@ return(out)
 }
 
 # Create a dataframe of parameter values
-wb_vector <- 9:20 
+wb_vector <- 9:10 
 a_vector <- seq(0.0, 0.0, 0.0)
 params <- expand.grid("wb" = wb_vector, "a" = a_vector)
 

### 2016-03-31 constrained-optimization.r
fix constrained-optimA for B's bribes

@@ -2,13 +2,13 @@
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
 rm(list = ls())
-#ap5 = 1.5
+#ap5 = .17
 #a0 = ap5 + .5
 #anp5 = ap5 + 1
 
-ap5 = 2.19
-a0 = 0
-anp5 = 1.19
+ap5 = 1.27
+a0 = 1.27
+anp5 = 1.27
 
 h <- function(WB,al) {
 
@@ -38,7 +38,7 @@ return(out)
 }
 
 # Create a dataframe of parameter values
-wb_vector <- 9:20 
+wb_vector <- 5:20 
 a_vector <- seq(0.0, 0.0, 0.0)
 params <- expand.grid("wb" = wb_vector, "a" = a_vector)
 

### 2016-03-31 constrained-optimizationA.R

@@ -2,13 +2,13 @@
 #constraint; I choose a null gradient because it was easiest to get up and running
 #note that here the beta parameter is hard coded in as equal to 1
 rm(list = ls())
-#bp5 = 1.5
-#b0 = bp5 + .5
-#bnp5 = bp5 + 1
+#bnp5 = .175
+#bp5 = bnp5 + 1
+#b0 = bnp5 + .5
 
-bp5 = 2.36
-b0 = 0
-bnp5 = 1.36
+bp5 = 1.1
+b0 = .6
+bnp5 = .1
 
 h <- function(WB,al) {
 
@@ -38,7 +38,7 @@ return(out)
 }
 
 # Create a dataframe of parameter values
-wb_vector <- 9:10 
+wb_vector <- 5:10 
 a_vector <- seq(0.0, 0.0, 0.0)
 params <- expand.grid("wb" = wb_vector, "a" = a_vector)
 

### 2016-04-11 presentation.tex
add PE shocks presentation from Rochester to start Midwest presentation

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

\usecolortheme{beaver}
\useinnertheme{default}
\setbeamertemplate{itemize item}[triangle]
\setbeamertemplate{itemize subitem}[triangle]
\setbeamertemplate{itemize subsubitem}[circle]
\setbeamertemplate{enumerate items}[default]
\setbeamertemplate{blocks}[upper=block head,rounded]
\setbeamercolor{item}{fg=black}
\usefonttheme{serif} %should allow ccfonts to take effect

\usepackage{cite}
\usepackage{times, verbatim,xcolor,bm}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{amsbsy,amssymb, amsmath, amsthm}
\usepackage{booktabs}
%David miller's fonts
	\usepackage[T1]{fontenc}
	\usepackage[boldsans]{ccfonts}
	%\usepackage[boldsans]{concmath}
	\usepackage[euler-hat-accent]{eulervm}

\newcommand{\al}{\alpha}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^{tw}}}
\newcommand{\ga}{\gamma}
\newcommand{\ve}{\varepsilon}
\newcommand{\ta}{\theta}
\newcommand{\de}{\delta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}

\newenvironment{changemargin}[2]{% 
  \begin{list}{}{% 
    \setlength{\topsep}{0pt}% 
    \setlength{\leftmargin}{#1}% 
    \setlength{\rightmargin}{#2}% 
    \setlength{\listparindent}{\parindent}% 
    \setlength{\itemindent}{\parindent}% 
    \setlength{\parsep}{\parskip}% 
  }% 
  \item[]}{\end{list}}

	\let\Tiny=\tiny

\title[Endogenous Politics and the Design of Trade Institutions\hspace{2.05in}\insertframenumber/\inserttotalframenumber]{Endogenous Politics and \\ the Design of Trade Institutions}
%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{April 6, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

\section{Overview}
\subsection{Preview}
\begin{frame}{The Questions}

\pause
\begin{enumerate}[<+->]
\item When is endogenizing political pressure important for answering optimal design questions?
	\begin{itemize}
		\item Exogenous vs. endogenous politics
	\end{itemize}
	\vskip.1in
\item Can trade agreements be used to manipulate domestic lobbying incentives?
	\begin{itemize}
		\item Government objective function
	\end{itemize}
\end{enumerate}

\end{frame}

\begin{frame}{Preview}
\frametitle{Political Economy of Trade Institutions}
\pause
With a few exceptions, TA literature has taken political economy forces to be exogenous. I:
\pause
\begin{itemize}[<+->]
	\item endogenize politics into a standard model for studying TA design questions
	\item carefully distinguish between dynamics induced by exogenous and endogenous politics for
		\begin{itemize}[<+->]
			\item base case with tariff caps
			\item tariff caps with escape clause
		\end{itemize}
	\item examine escape clause design when both exogenous and endogenous forces are present
\end{itemize}
\end{frame}

\begin{frame}{Preview}
\frametitle{Results}

\pause
\begin{itemize}[<+->]
	\item Show that TAs may be used to manipulate domestic political actors (no long-run distortions)
	\item For both tariff caps and escape clauses, outcomes are very different with endogenous politics
	\item Demonstrate that (standard, theoretical) escape clause can't work in the presence of endogenous political pressure
		\begin{itemize}
			\item Points to real-world design of WTO Agreement on Safeguards
			\item May explain why escape clause has fallen out of use
		\end{itemize}
\end{itemize}
\end{frame}

\begin{comment}
\begin{frame}{Outline of Talk}
\pause
\begin{enumerate}[<+->]
	\item Model
	\item Government Objective Function
	\item Base Model with Tariff Caps
	\item Escape Clause
	\item Conclusion
\end{enumerate}
\end{frame}
\end{comment}

\subsection{Role and Design of TAs}
\begin{frame}{Role of Trade Agreements: TOT Externality}
\pause
Bagwell and Staiger (2002)
\pause
\begin{itemize}[<+->]
	\item Joint social welfare maximized at free trade
	\item Trade war (i.e. no agreement)
		\begin{itemize}
			\item Maximize with respect to home country welfare only
			\item Terms of trade (TOT) externality $\Rightarrow$ positive tariffs  
		\end{itemize}
	\item Trade agreements
    \begin{itemize}
			\item Now take into account impact on foreign welfare
			\item Internalize TOT externality $\Rightarrow$ free trade
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Role of Trade Agreements: TOT Externality}
\pause
Grossman and Helpman (1995)
\pause
\begin{itemize}[<+->]
	\item Add endogenous politics
	\item Now in ``Trade War'': two reasons for positive tariff
		\begin{itemize}
			\item TOT externality + pressure from import competing lobby
		\end{itemize}

	\item Trade agreement: only internalizes TOT externality
\end{itemize}
\end{frame}

\begin{frame}{Role of Trade Agreements: New Trade Theory}
\pause
``New Trade Theory'' externalities
\pause
\begin{itemize}[<+->]
	\item Source: imperfect competition (firm level)
		\begin{itemize}
			\item Delocation: Ossa 2011, Bagwell and Staiger 2012
			\item Profit Shifting: Mrazova 2011, Ossa 2012  
		\end{itemize}
	\item Trade agreements
    \begin{itemize}
			\item Now take into account impact on foreign welfare
			\item Internalize these new externalities
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Role of Trade Agreements: Domestic Commitment}
\pause
\begin{itemize}[<+->]
	\item Maggi and Rodriguez-Clare (1998, 2007)
		\begin{itemize}
			\item Allow for (imperfect) capital mobility
			\item Domestic investment decisions depend on level of protection
			\item Inability to commit $\Rightarrow$ investment too high b/c importers know protection will respond
			\item Trade agreements provide commitment device
    \end{itemize}
	\item Mitra (2002)
		\begin{itemize}
			\item Here distortion is wasted resources in lobby formation
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Design of Trade Agreements}
\pause
\begin{itemize}[<+->]
	\item \textbf{Tariff caps}: Bagwell and Staiger 2005, Horn et al 2010, Amador and Bagwell 2012; Beshkar and Bond 2012
	\item \textbf{Escape clause}: Bagwell and Staiger 2005, Horn et al 2010, 
	\item \textbf{Shallow vs. deep integration}: Bagwell and Staiger 2001, DeRemer 2014
	\item \textbf{Dispute settlement}: Maggi 1999, Ludema 2001, Maggi and Staiger 2011/2013, Klimenko et al 2008
	%\item \textbf{Property vs. liability rules}: Pauwelyn 2008, Beshkar 2010, Maggi and Staiger 2014
	\item \textbf{Retaliation}: Bown 2002/2004, Beshkar 2010
\end{itemize}
\end{frame}

\section{Model}
\subsection{Economic and Political Structure}
\begin{frame}{Economy}
Two countries: home and foreign (${}^*$)
\pause
\begin{itemize}[<+->]
	\item Separable in two goods: $X$ and $Y$
			\begin{itemize}
				\item $P_i$: home price of good $i$
				\item $P_i^*$: foreign price of good $i$
			\end{itemize}
	\item Demand identical for both goods in both countries
		\begin{itemize}
			\item $D(P_i) = 1 - P_i$
		\end{itemize}
	\item Supply: $Q_X^*(P_X) > Q_X(P_X)$ $\forall P_X$; symmetric for $Y$ 
		\begin{itemize}
			\item $Q_X(P_X) = \frac{P_X}{2}$; $Q_Y(P_Y) = P_Y$
			\item Home net importer of $X$, net exporter of $Y$
		\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Policy and Politics}

\pause
Home levies $\tau$ on $X$, Foreign levies $\tau^*$ on $Y$
\pause
\begin{itemize}
	\item $P_X=P_X^W + \tau$ increasing in $\tau$
	\pause
	\item $\pi_X(P_X)$ increasing in $P_X$, therefore also $\tau$
\end{itemize}

\pause
\vskip.2in
Non-tradable specific factors motivate political activity
\end{frame}

\begin{frame}{Timeline}
\pause
%\vskip.1in
Each period:
\pause
\begin{enumerate}[<+->]
	\item {\bfseries Trade Agreement Formed}
		\begin{enumerate}[i.]
			%\pause
			\item Governments set trade policy in international agreement
		\end{enumerate}
	%\pause
	\item \textbf{Domestic Politics Played Out}
		\begin{enumerate}[i.]
			%\pause
			\item Exogenous shocks are realized AND/OR
			%\pause
			\item Import-competing industry lobbies government for protection 
		\end{enumerate}
	%\pause
	\item \textbf{Tariffs are Applied}
	%\pause
		\begin{enumerate}[i.]
			\item Given political pressure, governments choose applied tariff levels
		\end{enumerate}
\end{enumerate}
\end{frame}

\subsection{The Players}

\begin{frame}{Applied Tariff Decision}
\pause
  Baldwin-style government objective function:
\pause
\[
  W = \mathit{CS}_X(\tau) + \ga(s,e) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
\]
\vskip-.1in
\pause
\begin{itemize}[<+->]
	\item Standard \textit{except} weight on import-competing industry profits $\ga(s,e)$: 
		\begin{itemize}
			\item $s$: exogenous shock
			\item $e$: lobbying effort
		\end{itemize}
	\item Optimal applied tariff is a function of $\ga(s,e)$
		\begin{itemize}
			\item Ignores foreign welfare
			\item Takes into account trade agreement enforcement
		\end{itemize}
	\item Assume $\ga$, $\ga^*$ is private info of each government
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Domestic Political Pressure}
Two potential sources
\pause
\begin{enumerate}[<+->]
	\item Exogenous shocks
		\begin{itemize}[<+->]
			\item Shock directly to $\ga$ as in Bagwell $\&$ Staiger (2005): $\ga$, $\ga^*$ with CDF $H(\ga)$ on support $\left[\un{\ga},\ov{\ga}\right]$; or
			\item Can take $\ga$ as a function of $s$: $\ga(s)$
		\end{itemize}

	\item Endogenous effort choice of lobby, $e$
		\begin{itemize}[<+->]
			\item Lobby chooses effort to maximize profits, $\pi(\cdot)$, net of lobbying effort, $e$
			\item Call lobby's optimal effort choice $e^L$
						\[
						  e^L = \max_e \pi(\tau(\ga(e))) - e
						\]
		\end{itemize}
\end{enumerate}

\end{frame}

\begin{frame}{Trade Agreement Negotiation}
	\pause
Model as Nash bargain between the two countries' governments

	\pause
\begin{itemize}[<+->]
	\item Maximize joint political welfare
	\item Disagreement point: non-cooperative outcome
\end{itemize}

\vskip.2in
\pause
Once agreement is set, cooperation enforced by repeated-game punishments conditioned on history, history + DSB signal

\end{frame}

\section{Objective Fcn}
\subsection{Objective Function}
\begin{frame}{Restraining Political Pressure through TAs}
\pause
%It's easy to see that weak bindings keep lobbying alive relative to strong bindings
\begin{itemize}[<+->]
	\item Will TA be used to discourage lobbying? Depends on how gov't welfare varies in $\ga$
	\item With standard Baldwin-style objective function, welfare always increases with $\ga$:
\[
  W = \mathit{CS}_X(\tau) + \ga \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
\]
	\begin{itemize}
		\item Note `Protection for Sale' objective function is isomorphic
	\end{itemize}

	\item If we instead make weights sum to 1, welfare is no longer monotonic in $\ga$
\end{itemize}
\end{frame}

\section{Tariff Caps}
\subsection{Tariff Caps}
\begin{comment}
\begin{frame}{Tariff Caps: Exogenous vs. Endogenous $\ga$}
\pause
Strong binding: an exact tariff commitment
\begin{itemize}
	\pause
	\item Must apply the precise tariff level specified in TA
\end{itemize}

\pause
\vskip.2in
Weak binding: a tariff cap
\begin{itemize}
\pause
	\item Must set tariff at or below specified level 
\end{itemize}

\pause
\vskip.4in
Perfect external enforcement vs. self-enforcement (repeated-game)

\end{frame}

\begin{frame}{Strong Bindings}
Must set tariff at specified level
\pause
\begin{itemize}[<+->]
	\item $\ga$ exogenous (Bagwell $\&$ Staiger 2005): optimal (rigid) strong binding is the tariff that is politically optimal for the expected realization of $\ga$
  \item $\ga$ endogenous: if governments have no inherent bias toward protection, the lobbies exert no effort and are afforded no protection 
\end{itemize}
\end{frame}
\end{comment}

{\begin{frame}{Tariff Caps: Exogenous vs. Endogenous $\ga$}
\pause
Must set tariff at or below specified level (aka tariff cap)
\pause
\begin{itemize}[<+->]
	\item $\ga$ exogenous (Bagwell $\&$ Staiger 2005): Negotiated weak bindings (a) are higher than those gov'ts would choose if they instead negotiated strong bindings and (b) imply that governments with low realizations of $\ga$ set their applied tariffs strictly below the bound level.

	\item $\ga$ endogenous: Governments will not set applied tariffs strictly below the bound level. They may use the weak tariff binding either to encourage and/or restrain endogenous political pressure.

\end{itemize}
\end{frame}

\begin{frame}{Tariff Caps with Self Enforcement}
\pause
\begin{itemize}[<+->]
	\item $\ga$ exogenous (Bagwell $\&$ Staiger 2005): if governments patient enough ($\de$ high enough), optimal externally-enforced weak binding can be self-enforced
  \item $\ga$ endogenous: not necessarily true
		\begin{itemize}
			\item Problem: lobby is an additional repeated-game player
			\item Lobby's incentive constraint is harder to satisfy as $\de$ increases
		\end{itemize}

\end{itemize}

\end{frame}

\begin{comment}
\begin{frame}{Highlight: One-Shot Intuition}
\pause
\textbf{Legislature}
\pause
\begin{itemize}
	\item Breaks agreement if median legislator prefers $\btn$ to $\bta$
\end{itemize}

\pause
\vskip.1in
\textbf{Lobby}
\pause
\begin{itemize}[<+->]
	\item Given the $\bta$ it faces, lobby knows what $e_b$ is required to break the agreement
 	\item Lobby pays if $\bm{\pi}(\btn)$ - lobbying costs $> \pi(\bta)$
\end{itemize}

\pause
\vskip.13in
\textbf{Executives}
\pause
\begin{itemize}[<+->]
	\item Set $\bta$ to make paying $e_b$ unprofitable
		\pause
		\begin{itemize}
			\item[$\Rightarrow$] $e_b=0$, agreement remains in force
		\end{itemize}
	\item High tariffs, no lobbying, no trade disruptions
\end{itemize}
\end{frame}
\end{comment}

\begin{frame}{Repeated Game Intuition}
\pause
Legislature: break agreement if punishment not strong enough
\pause
\begin{itemize}
	\item i.e. if one period of gain from cheater's payoff is greater than T-periods of loss from trade-war
\end{itemize}

\vskip.1in
\pause
Lobby: solve for lowest effort ($\ov{e}_b$) that breaks this constraint
\pause
\begin{itemize}
	\item pay $\ov{e}_b$ if it's less than gain from $T$ periods of trade-war profits
\end{itemize}

\pause
\vskip.1in
Executives: set lowest $\bta$ that makes paying $\ov{e}_b$ unprofitable \textit{and} satisfies legislature's condition
\pause
\begin{itemize}
	\item[$\Rightarrow$] $e_b=0$, agreement remains in force
	\pause
	\item High tariffs, no lobbying, no trade disruptions
\end{itemize}
\end{frame}

\section{Escape Clause}
\subsection{Escape Clause}
\begin{frame}{Escape Clause with Exogenous Politics}

\pause
When $\ga$ is \textit{only} exogenous (Bagwell $\&$ Staiger 2005):

\pause
\begin{itemize}[<+->]
	\item Simple escape clause: add a second (higher) negotiated weak binding
		\begin{itemize}
			\item Escape clause is designed to allow higher applied tariff when realization of $\ga$ is high
		\end{itemize}
	\item Improves political efficiency
	\item Can improve self-enforcement
	\item Incentive compatibility becomes an issue
\end{itemize}
\end{frame}

\begin{frame}{Incentive compatibility}
\pause
Escape clause is meant to allow higher applied tariff when realized $\ga$ is high
\pause
\begin{itemize}[<+->]
	\item $\ga$ is private information
	\item We want truthful revelation, but truth-telling must be in the best interest of each gov't
	\item Gov't can exploit TOT externality by reporting high $\ga$ even when $\ga$ is low
		\begin{itemize}
			\item Only way to prevent this is with some cost of using escape clause
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Escape Clause with Endogenous Politics}
When $\ga$ is \textit{only} endogenous:
\pause
\begin{itemize}[<+->]
	\item Benefit of escape clause from exogenous case is gone
	\item Assuming lower binding is set to maximize political welfare, escape clause encourages inefficiently high lobbying effort / protection
	\item Incentive compatibility still an issue, but often not the central one
		\begin{itemize}[<+->]
			\item If lobby's preferred tariff $\geq$ escape clause binding, gov't experiences high $\ga$, no need to lie
		\end{itemize}
  \end{itemize}

\pause
\vskip.2in

If $\ga$ is only endogenous, escape clause causes problems, provides no benefits
\end{frame}

\begin{frame}{When the world is more complicated...}
Now suppose political pressure is a result of both endogenous and exogenous forces (i.e. $\ga(s,e)$):
\pause
\begin{itemize}[<+->]
	\item Want escape clause to deal with exogenous shock
	\item But endogenous part $\Rightarrow$ lobbying incentives make it hard to implement escape clause
\end{itemize}

\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Ineffectiveness of Political Criterion for Escape Clause}
  Assume $\ga(s,e) = \ga(s) + \ga(e)$. If an escape clause conditions on $\ga(s,e)$ and $\ga(s^L) < \ga(s^H) < \ga(e^L)$, the lower ``normal'' tariff binding will never be applied.
\end{beamerboxesrounded}
\end{frame}

\begin{frame}{When the world is more complicated... (2)}
\begin{itemize}[<+->]
	\item To make escape clause work, can't use $\ga$
	\begin{itemize}[<+->]
		\item Need signal of shock that is not influenced by endogenous pressure
	\end{itemize}
	\item Can condition directly on $s$
		\begin{itemize}
			\item This seems to be what the WTO actually \textit{does}
		\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{An Escape Clause for Endogenous Politics}
\pause
Assume a WTO-like set up: gov't can choose between $\tau^a$, `escape' tariff $\tau(s)$, or politically-optimal $\tau$ matched to $\ga(s,e)$
\pause
\begin{itemize}[<+->]
	\item Assume $s$ verifiable, so no punishment for $\tau(s)$
	\item Punishment for $\tau(\ga(s,e)) > \tau(s)$
\end{itemize}

\vskip.2in
\pause
Optimal $\tau^a$ may lead to government applying $\tau(\ga(s,e))$
\pause
\begin{itemize}[<+->]
	\item When this happens, it leads to dispute, not valid escape
	\item Otherwise, no extra rent-seeking is encouraged
\end{itemize}

\vskip.2in
\pause
May explain why escape clause has fallen out of use

\end{frame}

%\begin{frame}{Optimal Punishments}
%\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Optimal DSI}
%  In the case of political certainty, if non-trivial cooperation is possible in the presence of a lobby, the optimal punishment scheme is finite when the influence of the lobby on legislative preferences is sufficiently strong $\left(\frac{\partial \gamma}{\partial e} \text{ is sufficiently high} \right)$.
%\end{beamerboxesrounded}
%\end{frame}

\section{Conclusion}

\begin{comment}
\begin{frame}{Ex-Ante Lobbying}
Without ex-ante: gov't anticipates ex-post lobbying, chooses $\tau^{\text{TA}}$ that maximizes objective function given $e^{\text{EP}}$
  \[
	  \max_\tau W(\ga(e^{\text{EP}}),\tau) + W^*(\tau)
	\]
\pause
When ex-ante lobbying ($e^{\text{EA}}$) is possible, we could have
\pause
  \[
	  \max_\tau W(\ga(e^{\text{EA}}),\tau) + W^*(\tau)
	\]
	but the lobby would now have to pay \textit{twice}.
\end{frame}
\end{comment}

\begin{frame}{Future Work}
\pause
\begin{itemize}[<+->]
	\item Application of framework to other design questions
	\item Interactions between $\ga(s)$ and $\ga(e)$
	\item Choice between protective measures over time
\end{itemize}

\end{frame}

\begin{frame}{Conclusion}
Taking into account endogenous political forces alongside exogenous ones...
\pause
\begin{itemize}[<+->]
		\item provides additional general explanation for tariff caps
		\item demonstrates that TAs can be used to discourage lobbing activity in general
		\item helps explain the structure and enforcement of the WTO Safeguards measure
\end{itemize}

\end{frame}

\end{document}

### 2016-04-11 presentation.tex
remove stuff I REALLY don't need from presentation

@@
 
-\title[Endogenous Politics and the Design of Trade Institutions\hspace{2.05in}\insertframenumber/\inserttotalframenumber]{Endogenous Politics and \\ the Design of Trade Institutions}
+\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
 %\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
 \author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
-\date{April 6, 2016}
+\date{April 16, 2016}
 \begin{document}
@@
 			\item Internalize TOT externality $\Rightarrow$ free trade
-    \end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Role of Trade Agreements: TOT Externality}
-\pause
-Grossman and Helpman (1995)
-\pause
-\begin{itemize}[<+->]
-	\item Add endogenous politics
-	\item Now in ``Trade War'': two reasons for positive tariff
-		\begin{itemize}
-			\item TOT externality + pressure from import competing lobby
-		\end{itemize}
-
-	\item Trade agreement: only internalizes TOT externality
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Role of Trade Agreements: New Trade Theory}
-\pause
-``New Trade Theory'' externalities
-\pause
-\begin{itemize}[<+->]
-	\item Source: imperfect competition (firm level)
-		\begin{itemize}
-			\item Delocation: Ossa 2011, Bagwell and Staiger 2012
-			\item Profit Shifting: Mrazova 2011, Ossa 2012  
-		\end{itemize}
-	\item Trade agreements
-    \begin{itemize}
-			\item Now take into account impact on foreign welfare
-			\item Internalize these new externalities
-    \end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Role of Trade Agreements: Domestic Commitment}
-\pause
-\begin{itemize}[<+->]
-	\item Maggi and Rodriguez-Clare (1998, 2007)
-		\begin{itemize}
-			\item Allow for (imperfect) capital mobility
-			\item Domestic investment decisions depend on level of protection
-			\item Inability to commit $\Rightarrow$ investment too high b/c importers know protection will respond
-			\item Trade agreements provide commitment device
-    \end{itemize}
-	\item Mitra (2002)
-		\begin{itemize}
-			\item Here distortion is wasted resources in lobby formation
     \end{itemize}
@@
 \subsection{Tariff Caps}
-\begin{comment}
-\begin{frame}{Tariff Caps: Exogenous vs. Endogenous $\ga$}
-\pause
-Strong binding: an exact tariff commitment
-\begin{itemize}
-	\pause
-	\item Must apply the precise tariff level specified in TA
-\end{itemize}
-
-\pause
-\vskip.2in
-Weak binding: a tariff cap
-\begin{itemize}
-\pause
-	\item Must set tariff at or below specified level 
-\end{itemize}
-
-\pause
-\vskip.4in
-Perfect external enforcement vs. self-enforcement (repeated-game)
-
-\end{frame}
-
-\begin{frame}{Strong Bindings}
-Must set tariff at specified level
-\pause
-\begin{itemize}[<+->]
-	\item $\ga$ exogenous (Bagwell $\&$ Staiger 2005): optimal (rigid) strong binding is the tariff that is politically optimal for the expected realization of $\ga$
-  \item $\ga$ endogenous: if governments have no inherent bias toward protection, the lobbies exert no effort and are afforded no protection 
-\end{itemize}
-\end{frame}
-\end{comment}
 
@@
 
-\end{frame}
-
-\begin{comment}
-\begin{frame}{Highlight: One-Shot Intuition}
-\pause
-\textbf{Legislature}
-\pause
-\begin{itemize}
-	\item Breaks agreement if median legislator prefers $\btn$ to $\bta$
-\end{itemize}
-
-\pause
-\vskip.1in
-\textbf{Lobby}
-\pause
-\begin{itemize}[<+->]
-	\item Given the $\bta$ it faces, lobby knows what $e_b$ is required to break the agreement
- 	\item Lobby pays if $\bm{\pi}(\btn)$ - lobbying costs $> \pi(\bta)$
-\end{itemize}
-
-\pause
-\vskip.13in
-\textbf{Executives}
-\pause
-\begin{itemize}[<+->]
-	\item Set $\bta$ to make paying $e_b$ unprofitable
-		\pause
-		\begin{itemize}
-			\item[$\Rightarrow$] $e_b=0$, agreement remains in force
-		\end{itemize}
-	\item High tariffs, no lobbying, no trade disruptions
-\end{itemize}
-\end{frame}
-\end{comment}
-
-\begin{frame}{Repeated Game Intuition}
-\pause
-Legislature: break agreement if punishment not strong enough
-\pause
-\begin{itemize}
-	\item i.e. if one period of gain from cheater's payoff is greater than T-periods of loss from trade-war
-\end{itemize}
-
-\vskip.1in
-\pause
-Lobby: solve for lowest effort ($\ov{e}_b$) that breaks this constraint
-\pause
-\begin{itemize}
-	\item pay $\ov{e}_b$ if it's less than gain from $T$ periods of trade-war profits
-\end{itemize}
-
-\pause
-\vskip.1in
-Executives: set lowest $\bta$ that makes paying $\ov{e}_b$ unprofitable \textit{and} satisfies legislature's condition
-\pause
-\begin{itemize}
-	\item[$\Rightarrow$] $e_b=0$, agreement remains in force
-	\pause
-	\item High tariffs, no lobbying, no trade disruptions
-\end{itemize}
 \end{frame}
@@
 
-\begin{frame}{When the world is more complicated... (2)}
-\begin{itemize}[<+->]
-	\item To make escape clause work, can't use $\ga$
-	\begin{itemize}[<+->]
-		\item Need signal of shock that is not influenced by endogenous pressure
-	\end{itemize}
-	\item Can condition directly on $s$
-		\begin{itemize}
-			\item This seems to be what the WTO actually \textit{does}
-		\end{itemize}
-\end{itemize}
-
-\end{frame}
-
 \begin{frame}{An Escape Clause for Endogenous Politics}
@@
 
-\begin{comment}
-\begin{frame}{Ex-Ante Lobbying}
-Without ex-ante: gov't anticipates ex-post lobbying, chooses $\tau^{\text{TA}}$ that maximizes objective function given $e^{\text{EP}}$
-  \[
-	  \max_\tau W(\ga(e^{\text{EP}}),\tau) + W^*(\tau)
-	\]
-\pause
-When ex-ante lobbying ($e^{\text{EA}}$) is possible, we could have
-\pause
-  \[
-	  \max_\tau W(\ga(e^{\text{EA}}),\tau) + W^*(\tau)
-	\]
-	but the lobby would now have to pay \textit{twice}.
-\end{frame}
-\end{comment}
-
 \begin{frame}{Future Work}

### 2016-04-13 presentation.tex
remove pe-shocks content from presentation

@@
 \begin{enumerate}[<+->]
-\item When is endogenizing political pressure important for answering optimal design questions?
+\item When 
 	\begin{itemize}
-		\item Exogenous vs. endogenous politics
+		\item E
 	\end{itemize}
 	\vskip.1in
-\item Can trade agreements be used to manipulate domestic lobbying incentives?
+\item Can
 	\begin{itemize}
-		\item Government objective function
+		\item G
+	\end{itemize}
+\end{enumerate}
+
+\end{frame}
+
+\begin{frame}{Some Data}
+
+\pause
+\begin{enumerate}[<+->]
+\item When 
+	\begin{itemize}
+		\item E
+	\end{itemize}
+	\vskip.1in
+\item Can
+	\begin{itemize}
+		\item G
 	\end{itemize}
@@
 \begin{frame}{Preview}
-\frametitle{Political Economy of Trade Institutions}
+\frametitle{P}
 \pause
-With a few exceptions, TA literature has taken political economy forces to be exogenous. I:
+With . I:
 \pause
 \begin{itemize}[<+->]
-	\item endogenize politics into a standard model for studying TA design questions
-	\item carefully distinguish between dynamics induced by exogenous and endogenous politics for
+	\item e
+	\item c
 		\begin{itemize}[<+->]
-			\item base case with tariff caps
-			\item tariff caps with escape clause
+			\item b
+			\item t
 		\end{itemize}
-	\item examine escape clause design when both exogenous and endogenous forces are present
+	\item e
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Show that TAs may be used to manipulate domestic political actors (no long-run distortions)
-	\item For both tariff caps and escape clauses, outcomes are very different with endogenous politics
-	\item Demonstrate that (standard, theoretical) escape clause can't work in the presence of endogenous political pressure
+	\item S
+	\item F
+	\item D
 		\begin{itemize}
-			\item Points to real-world design of WTO Agreement on Safeguards
-			\item May explain why escape clause has fallen out of use
+			\item P
+			\item M
 		\end{itemize}
@@
 
-\begin{comment}
-\begin{frame}{Outline of Talk}
-\pause
-\begin{enumerate}[<+->]
-	\item Model
-	\item Government Objective Function
-	\item Base Model with Tariff Caps
-	\item Escape Clause
-	\item Conclusion
-\end{enumerate}
-\end{frame}
-\end{comment}
-
-\subsection{Role and Design of TAs}
-\begin{frame}{Role of Trade Agreements: TOT Externality}
-\pause
-Bagwell and Staiger (2002)
+\begin{frame}{Literature}
 \pause
 \begin{itemize}[<+->]
-	\item Joint social welfare maximized at free trade
-	\item Trade war (i.e. no agreement)
-		\begin{itemize}
-			\item Maximize with respect to home country welfare only
-			\item Terms of trade (TOT) externality $\Rightarrow$ positive tariffs  
-		\end{itemize}
-	\item Trade agreements
-    \begin{itemize}
-			\item Now take into account impact on foreign welfare
-			\item Internalize TOT externality $\Rightarrow$ free trade
-    \end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Design of Trade Agreements}
-\pause
-\begin{itemize}[<+->]
-	\item \textbf{Tariff caps}: Bagwell and Staiger 2005, Horn et al 2010, Amador and Bagwell 2012; Beshkar and Bond 2012
-	\item \textbf{Escape clause}: Bagwell and Staiger 2005, Horn et al 2010, 
-	\item \textbf{Shallow vs. deep integration}: Bagwell and Staiger 2001, DeRemer 2014
-	\item \textbf{Dispute settlement}: Maggi 1999, Ludema 2001, Maggi and Staiger 2011/2013, Klimenko et al 2008
-	%\item \textbf{Property vs. liability rules}: Pauwelyn 2008, Beshkar 2010, Maggi and Staiger 2014
-	\item \textbf{Retaliation}: Bown 2002/2004, Beshkar 2010
+	\item \textbf{Vote Buying in Legislatures}: 
+	\item \textbf{Stochastic Voting}: 
+	\item \textbf{Uncertainty}: 
 \end{itemize}
@@
 \section{Model}
-\subsection{Economic and Political Structure}
-\begin{frame}{Economy}
-Two countries: home and foreign (${}^*$)
+\subsection{Political Structure}
+\begin{frame}{Policy and Politics}
+
 \pause
-\begin{itemize}[<+->]
-	\item Separable in two goods: $X$ and $Y$
+T
+\pause
 \begin{itemize}
-				\item $P_i$: home price of good $i$
-				\item $P_i^*$: foreign price of good $i$
-			\end{itemize}
-	\item Demand identical for both goods in both countries
-		\begin{itemize}
-			\item $D(P_i) = 1 - P_i$
-		\end{itemize}
-	\item Supply: $Q_X^*(P_X) > Q_X(P_X)$ $\forall P_X$; symmetric for $Y$ 
-		\begin{itemize}
-			\item $Q_X(P_X) = \frac{P_X}{2}$; $Q_Y(P_Y) = P_Y$
-			\item Home net importer of $X$, net exporter of $Y$
-		\end{itemize}
+	\item A
+	\pause
+	\item B
 \end{itemize}
@@
 
-\begin{frame}{Policy and Politics}
-
-\pause
-Home levies $\tau$ on $X$, Foreign levies $\tau^*$ on $Y$
-\pause
-\begin{itemize}
-	\item $P_X=P_X^W + \tau$ increasing in $\tau$
-	\pause
-	\item $\pi_X(P_X)$ increasing in $P_X$, therefore also $\tau$
-\end{itemize}
-
-\pause
-\vskip.2in
-Non-tradable specific factors motivate political activity
-\end{frame}
-
 \begin{frame}{Timeline}
 \pause
-%\vskip.1in
-Each period:
-\pause
 \begin{enumerate}[<+->]
-	\item {\bfseries Trade Agreement Formed}
+	\item {\bfseries Who}
 		\begin{enumerate}[i.]
 			%\pause
-			\item Governments set trade policy in international agreement
+			\item Governments 
 		\end{enumerate}
 	%\pause
-	\item \textbf{Domestic Politics Played Out}
+	\item \textbf{Then}
 		\begin{enumerate}[i.]
 			%\pause
-			\item Exogenous shocks are realized AND/OR
+			\item A
 			%\pause
-			\item Import-competing industry lobbies government for protection 
+			\item B
 		\end{enumerate}
 	%\pause
-	\item \textbf{Tariffs are Applied}
+	\item \textbf{What}
 	%\pause
 		\begin{enumerate}[i.]
-			\item Given political pressure, governments choose applied tariff levels
+			\item If
 		\end{enumerate}
@@
 
-\begin{frame}{Applied Tariff Decision}
+\begin{frame}{D}
 \pause
-  Baldwin-style government objective function:
+  Objective function:
 \pause
@@
 \begin{itemize}[<+->]
-	\item Standard \textit{except} weight on import-competing industry profits $\ga(s,e)$: 
+	\item S
 		\begin{itemize}
-			\item $s$: exogenous shock
-			\item $e$: lobbying effort
+			\item $s$: 
+			\item $e$: 
 		\end{itemize}
-	\item Optimal applied tariff is a function of $\ga(s,e)$
+	\item Optimal 
 		\begin{itemize}
-			\item Ignores foreign welfare
-			\item Takes into account trade agreement enforcement
+			\item Ignores 
+			\item Takes 
 		\end{itemize}
-	\item Assume $\ga$, $\ga^*$ is private info of each government
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Domestic Political Pressure}
+\frametitle{Political Pressure}
 Two potential sources
@@
 \begin{enumerate}[<+->]
-	\item Exogenous shocks
-		\begin{itemize}[<+->]
-			\item Shock directly to $\ga$ as in Bagwell $\&$ Staiger (2005): $\ga$, $\ga^*$ with CDF $H(\ga)$ on support $\left[\un{\ga},\ov{\ga}\right]$; or
-			\item Can take $\ga$ as a function of $s$: $\ga(s)$
-		\end{itemize}
-
 	\item Endogenous effort choice of lobby, $e$
@@
 
-\begin{frame}{Trade Agreement Negotiation}
+\section{Results}
+\subsection{One Vote Buyer}
+\begin{frame}{}
+
 \pause
-Model as Nash bargain between the two countries' governments
+When :
 
@@
 \begin{itemize}[<+->]
-	\item Maximize joint political welfare
-	\item Disagreement point: non-cooperative outcome
-\end{itemize}
-
-\vskip.2in
-\pause
-Once agreement is set, cooperation enforced by repeated-game punishments conditioned on history, history + DSB signal
-
-\end{frame}
-
-\section{Objective Fcn}
-\subsection{Objective Function}
-\begin{frame}{Restraining Political Pressure through TAs}
-\pause
-%It's easy to see that weak bindings keep lobbying alive relative to strong bindings
-\begin{itemize}[<+->]
-	\item Will TA be used to discourage lobbying? Depends on how gov't welfare varies in $\ga$
-	\item With standard Baldwin-style objective function, welfare always increases with $\ga$:
-\[
-  W = \mathit{CS}_X(\tau) + \ga \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
-\]
-	\begin{itemize}
-		\item Note `Protection for Sale' objective function is isomorphic
-	\end{itemize}
-
-	\item If we instead make weights sum to 1, welfare is no longer monotonic in $\ga$
+	\item T
+	\item I
+	\item C
 \end{itemize}
@@
 
-\section{Tariff Caps}
-\subsection{Tariff Caps}
-
-{\begin{frame}{Tariff Caps: Exogenous vs. Endogenous $\ga$}
-\pause
-Must set tariff at or below specified level (aka tariff cap)
+\begin{frame}{When ...}
+Now 
 \pause
 \begin{itemize}[<+->]
-	\item $\ga$ exogenous (Bagwell $\&$ Staiger 2005): Negotiated weak bindings (a) are higher than those gov'ts would choose if they instead negotiated strong bindings and (b) imply that governments with low realizations of $\ga$ set their applied tariffs strictly below the bound level.
-
-	\item $\ga$ endogenous: Governments will not set applied tariffs strictly below the bound level.
-They may use the weak tariff binding either to encourage and/or restrain endogenous political pressure.
-
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Tariff Caps with Self Enforcement}
-\pause
-\begin{itemize}[<+->]
-	\item $\ga$ exogenous (Bagwell $\&$ Staiger 2005): if governments patient enough ($\de$ high enough), optimal externally-enforced weak binding can be self-enforced
-  \item $\ga$ endogenous: not necessarily true
-		\begin{itemize}
-			\item Problem: lobby is an additional repeated-game player
-			\item Lobby's incentive constraint is harder to satisfy as $\de$ increases
-		\end{itemize}
-
-\end{itemize}
-
-\end{frame}
-
-\section{Escape Clause}
-\subsection{Escape Clause}
-\begin{frame}{Escape Clause with Exogenous Politics}
-
-\pause
-When $\ga$ is \textit{only} exogenous (Bagwell $\&$ Staiger 2005):
-
-\pause
-\begin{itemize}[<+->]
-	\item Simple escape clause: add a second (higher) negotiated weak binding
-		\begin{itemize}
-			\item Escape clause is designed to allow higher applied tariff when realization of $\ga$ is high
-		\end{itemize}
-	\item Improves political efficiency
-	\item Can improve self-enforcement
-	\item Incentive compatibility becomes an issue
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Incentive compatibility}
-\pause
-Escape clause is meant to allow higher applied tariff when realized $\ga$ is high
-\pause
-\begin{itemize}[<+->]
-	\item $\ga$ is private information
-	\item We want truthful revelation, but truth-telling must be in the best interest of each gov't
-	\item Gov't can exploit TOT externality by reporting high $\ga$ even when $\ga$ is low
-		\begin{itemize}
-			\item Only way to prevent this is with some cost of using escape clause
-		\end{itemize}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Escape Clause with Endogenous Politics}
-When $\ga$ is \textit{only} endogenous:
-\pause
-\begin{itemize}[<+->]
-	\item Benefit of escape clause from exogenous case is gone
-	\item Assuming lower binding is set to maximize political welfare, escape clause encourages inefficiently high lobbying effort / protection
-	\item Incentive compatibility still an issue, but often not the central one
-		\begin{itemize}[<+->]
-			\item If lobby's preferred tariff $\geq$ escape clause binding, gov't experiences high $\ga$, no need to lie
-		\end{itemize}
+	\item Want 
+	\item But 
 \end{itemize}
@@
 \vskip.2in
-
-If $\ga$ is only endogenous, escape clause causes problems, provides no benefits
-\end{frame}
-
-\begin{frame}{When the world is more complicated...}
-Now suppose political pressure is a result of both endogenous and exogenous forces (i.e. $\ga(s,e)$):
-\pause
-\begin{itemize}[<+->]
-	\item Want escape clause to deal with exogenous shock
-	\item But endogenous part $\Rightarrow$ lobbying incentives make it hard to implement escape clause
-\end{itemize}
-
-\pause
-\vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Ineffectiveness of Political Criterion for Escape Clause}
-  Assume $\ga(s,e) = \ga(s) + \ga(e)$. If an escape clause conditions on $\ga(s,e)$ and $\ga(s^L) < \ga(s^H) < \ga(e^L)$, the lower ``normal'' tariff binding will never be applied.
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+  Assume ...
 \end{beamerboxesrounded}
 \end{frame}
-
-\begin{frame}{An Escape Clause for Endogenous Politics}
-\pause
-Assume a WTO-like set up: gov't can choose between $\tau^a$, `escape' tariff $\tau(s)$, or politically-optimal $\tau$ matched to $\ga(s,e)$
-\pause
-\begin{itemize}[<+->]
-	\item Assume $s$ verifiable, so no punishment for $\tau(s)$
-	\item Punishment for $\tau(\ga(s,e)) > \tau(s)$
-\end{itemize}
-
-\vskip.2in
-\pause
-Optimal $\tau^a$ may lead to government applying $\tau(\ga(s,e))$
-\pause
-\begin{itemize}[<+->]
-	\item When this happens, it leads to dispute, not valid escape
-	\item Otherwise, no extra rent-seeking is encouraged
-\end{itemize}
-
-\vskip.2in
-\pause
-May explain why escape clause has fallen out of use
-
-\end{frame}
-
-%\begin{frame}{Optimal Punishments}
-%\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Optimal DSI}
-%  In the case of political certainty, if non-trivial cooperation is possible in the presence of a lobby, the optimal punishment scheme is finite when the influence of the lobby on legislative preferences is sufficiently strong $\left(\frac{\partial \gamma}{\partial e} \text{ is sufficiently high} \right)$.
-%\end{beamerboxesrounded}
-%\end{frame}
 
@@
 \begin{itemize}[<+->]
-	\item Application of framework to other design questions
-	\item Interactions between $\ga(s)$ and $\ga(e)$
-	\item Choice between protective measures over time
+	\item A
+	\item I
+	\item C
 \end{itemize}
@@
 \begin{frame}{Conclusion}
-Taking into account endogenous political forces alongside exogenous ones...
+Taking into account
 \pause
 \begin{itemize}[<+->]
-		\item provides additional general explanation for tariff caps
-		\item demonstrates that TAs can be used to discourage lobbing activity in general
-		\item helps explain the structure and enforcement of the WTO Safeguards measure
+		\item provides 
+		\item demonstrates 
+		\item helps 
 \end{itemize}

### 2016-04-13 presentation.tex
paste results into presentation

@@
 \end{itemize}
+
+\pause
+\vskip.2in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+    When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points gross of bribes are equalized.
+Which two legislators are bribed depends on the bias parameter $\al$.
+\end{beamerboxesrounded}
+
 \end{frame}
@@
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
-  Assume ...
+    When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
 \end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+      When Vote Buyer $B$ pays bribes to exactly one legislator, it may be any one of the three legislators depending on the bias parameter $\al$.
+\end{beamerboxesrounded}
+
+\pause
+\vskip.2in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+  When Vote Buyer $B$ has a low willingness to pay, he does not bribe any legislator.
+\end{beamerboxesrounded}
+
+\end{frame}
+
+\begin{frame}{Varying Uncertainty Across Legislators}
+Now 
+\pause
+\begin{itemize}[<+->]
+	\item Want 
+	\item But 
+\end{itemize}
+
+\pause
+\vskip.2in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Conjecture}
+ When there is no bias in the positions of the legislators ($\al =0$), the bribes of legislators whose ideal points are at the median in terms of uncertainty receive the highest relative bribes.\end{beamerboxesrounded}
+\end{frame}
+
+\subsection{Two Vote Buyers}
+\begin{frame}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
+\end{beamerboxesrounded}
+
+\pause
+\vskip.2in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+  It is possible for both vote buyers to bribe legislators on the same vote.
+\end{beamerboxesrounded}
+
 \end{frame}

### 2016-04-15 presentation.tex
add figures
finish intro and first half of model section

@@
 \section{Overview}
-\subsection{Preview}
+\subsection{Overview}
 \begin{frame}{The Questions}
@@
 \begin{enumerate}[<+->]
-\item When 
+\item How does uncertainty about legislators' preferences impact 
 	\begin{itemize}
-		\item E
+		\item lobbying strategies (e.g. who to lobby, how much to `pay')
+		\item probability a bill passes
 	\end{itemize}
 	\vskip.1in
-\item Can
+\item Can we distentangle fundamental uncertainty about preferences from equilibrium and modeling uncertainty?
 	\begin{itemize}
-		\item G
+		\item[$\Rightarrow$] Build a structural model to take to U.S. House data
 	\end{itemize}
+	\vskip.1in
+\item Ultimately, want to identify cross-industry measures of legislative uncertainty
 \end{enumerate}
@@
 
-\begin{frame}{Some Data}
+\begin{frame}{Some Stylized Facts}
 
@@
 \begin{enumerate}[<+->]
-\item When 
-	\begin{itemize}
-		\item E
-	\end{itemize}
-	\vskip.1in
-\item Can
-	\begin{itemize}
-		\item G
-	\end{itemize}
+	\item In the U.S., about $\$ 4$ billion / yr spent on lobbying and campaign contributions
+	\item There is usually lobbying on both sides of a given issue
+	\item Moderate legislators receive more contributions than those that are ideologically extreme
+	\item Legislators about whom there is a moderate level of uncertainty are lobbied the most
 \end{enumerate}
 
-\end{frame}
-
-\begin{frame}{Preview}
-\frametitle{P}
 \pause
-With . I:
-\pause
-\begin{itemize}[<+->]
-	\item e
-	\item c
-		\begin{itemize}[<+->]
-			\item b
-			\item t
-		\end{itemize}
-	\item e
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Preview}
-\frametitle{Results}
-
-\pause
-\begin{itemize}[<+->]
-	\item S
-	\item F
-	\item D
-		\begin{itemize}
-			\item P
-			\item M
-		\end{itemize}
-\end{itemize}
+\vskip.2in
+Adding uncertainty to standard model captures (2) --- (4)
 \end{frame}
@@
 \begin{itemize}[<+->]
-	\item \textbf{Vote Buying in Legislatures}: 
-	\item \textbf{Stochastic Voting}: 
-	\item \textbf{Uncertainty}: 
+	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
+	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets (2007)
+	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
+	%\item \textbf{Uncertainty}: 
 \end{itemize}
+\end{frame}
+
+%\begin{frame}
+%\includegraphics[height=2.75in, width=4.25in]{graph2.jpg}
+%\end{frame}
+
+\begin{frame}
+\includegraphics[height=2.75in, width=4.25in]{graph1.jpg}
+\end{frame}
+
+\begin{frame}{Preview}
+\frametitle{Context}
+\pause
+U.S. House of Representative 
+\pause
+\begin{itemize}[<+->]
+	\item All roll call votes, 2005 through present
+	\item Interest group lobbying on each vote
+	\item PAC contributions, LDA lobbying data
+\end{itemize}
+
+\vskip.2in
+\pause
+Use multi-dimensional ideal-point estimation to identify measures of uncertainty
+\end{frame}
+
+\begin{frame}
+\includegraphics[height=2.75in, width=4.25in]{NSF_combined_graph.pdf}
 \end{frame}
@@
 \pause
-T
+Three legislators
 \pause
 \begin{itemize}
-	\item A
+	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
+	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
+	\item Decision made by majority vote
+\end{itemize}
+
 \pause
-	\item B
+\vskip.2in
+Two vote buyers, $A$ and $B$
+\pause
+\begin{itemize}
+	\item A prefers $x$, $B$ prefers $s$
 \end{itemize}
@@
 \begin{enumerate}[<+->]
-	\item {\bfseries Who}
+	\item {\bfseries Vote Buyer A}
 		\begin{enumerate}[i.]
 			%\pause
-			\item Governments 
+			\item Chooses bribes $\un{a} = \left(a_{-.5},a_0,a_{.5}\right)$
 		\end{enumerate}
 	%\pause
-	\item \textbf{Then}
+	\item \textbf{Vote Buyer B}
 		\begin{enumerate}[i.]
 			%\pause
-			\item A
+			\item Observes $\un{a}$
 			%\pause
-			\item B
+			\item Chooses bribes $\un{b} = \left(b_{-.5},b_0,b_{.5}\right)$
 		\end{enumerate}
 	%\pause
-	\item \textbf{What}
+	\item \textbf{Legislature}
 	%\pause
 		\begin{enumerate}[i.]
-			\item If
+			\item All legislators observe $\un{a},\un{b}$
+			\item Uncertainty about preferences realized: $\un{\ta} = \left(\ta_{-.5},\ta_0,\ta_{.5}\right)$
+			\item Each legislator votes for her preferred policy 
 		\end{enumerate}
@@
 \subsection{The Players}
+
+\begin{frame}{D}
+\pause
+  Objective function:
+\pause
+\[
+  W = \mathit{CS}_X(\tau) + \ga(s,e) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
+\]
+\vskip-.1in
+\pause
+\begin{itemize}[<+->]
+	\item S
+		\begin{itemize}
+			\item $s$: 
+			\item $e$: 
+		\end{itemize}
+	\item Optimal 
+		\begin{itemize}
+			\item Ignores 
+			\item Takes 
+		\end{itemize}
+\end{itemize}
+\end{frame}
 

### 2016-04-15 presentation.tex
finish model section and conclusions

@@
 
-\begin{frame}{D}
+\begin{frame}{Legislators}
 \pause
-  Objective function:
-\pause
-\[
-  W = \mathit{CS}_X(\tau) + \ga(s,e) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
-\]
-\vskip-.1in
+Take ideal point to be linear: $\alpha - \beta i$
 \pause
 \begin{itemize}[<+->]
-	\item S
+	\item Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
 		\begin{itemize}
-			\item $s$: 
-			\item $e$: 
+			\item Probability $i$ votes for $s$ is $\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right] = \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right] $
+			\item Assuming $\ta \sim \text{Logistic} \ (0,1)$, it's $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
 		\end{itemize}
-	\item Optimal 
-		\begin{itemize}
-			\item Ignores 
-			\item Takes 
 \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Vote Buyer B}
+\pause
+Assume vote buyers maximize expected value of winning net of bribes paid  
+\begin{itemize}[<+->]
+	\item Assume bribes must be non-negative
+	\item Vote buyer won't spend more than his willingness to pay, $W_B$
+	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s$
 \end{itemize}
@@
 
-\begin{frame}{D}
+\begin{frame}{Vote Buyer B's Objective Function}
 \pause
-  Objective function:
-\pause
-\[
-  W = \mathit{CS}_X(\tau) + \ga(s,e) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
-\]
-\vskip-.1in
-\pause
-\begin{itemize}[<+->]
-	\item S
-		\begin{itemize}
-			\item $s$: 
-			\item $e$: 
-		\end{itemize}
-	\item Optimal 
-		\begin{itemize}
-			\item Ignores 
-			\item Takes 
-		\end{itemize}
-\end{itemize}
+Let $X(i) = 1$ denote legislator $i$ votes for the status quo
+\begin{multline*}
+			    \max_{b_{-.5}, b_0, b_{.5}} 
+					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
+					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
+					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
+					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
+				\end{multline*}
 \end{frame}
 
-\begin{frame}
-\frametitle{Political Pressure}
-Two potential sources
+\begin{frame}{Vote Buyer A}
 \pause
-\begin{enumerate}[<+->]
-	\item Endogenous effort choice of lobby, $e$
+Vote Buyer A is just like Vote Buyer B \textit{except}
 \begin{itemize}[<+->]
-			\item Lobby chooses effort to maximize profits, $\pi(\cdot)$, net of lobbying effort, $e$
-			\item Call lobby's optimal effort choice $e^L$
-						\[
-						  e^L = \max_e \pi(\tau(\ga(e))) - e
-						\]
+	\item She gets to move first
+	\item She wants $x$ to win instead of $s$
 \end{itemize}
-\end{enumerate}
-
 \end{frame}
@@
 
-\begin{frame}{Future Work}
+\begin{frame}{Next Steps}
 \pause
 \begin{itemize}[<+->]
-	\item A
-	\item I
-	\item C
+	\item Modify model so that both legislators can lobby the \textit{same} legislator in equilibrium
+	\item Derive tight identification of empirical estimates from structural model
+	\item Provide micro-founded explanations for the variation in uncertainty that lobbies face
 \end{itemize}
@@
 \begin{frame}{Conclusion}
-Taking into account
+Taking into account uncertainty about the preferences of legislators brings vote buying models closer to capturing important stylized facts
 \pause
 \begin{itemize}[<+->]
-		\item provides 
-		\item demonstrates 
-		\item helps 
+		\item helps in understanding lobbying strategies
+		\item may shed light on why some lobbies are more successful than others
+		\item will help in the identification of measures of uncertainty that can be used in many applications
 \end{itemize}

### 2016-04-15 presentation.tex
finish first draft of presentation (results section)

@@
 \subsection{One Vote Buyer}
-\begin{frame}{}
+\begin{frame}{Two Non-Negative Bribes}
 
 \pause
-When :
+Let $X$ and $Y$ and $Z$ be the gross positions of each of the three legislators. Then the FOCs are
+\pause
+	\begin{equation}
+		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+	\end{equation}
+	\begin{equation}
+		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
+	\end{equation}
 
 \pause
-\begin{itemize}[<+->]
-	\item T
-	\item I
-	\item C
-\end{itemize}
-
-\pause
-\vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+\vskip.1in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Two non-negative bribes}
     When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points gross of bribes are equalized.
@@
 
-\begin{frame}{When ...}
-Now 
+\begin{frame}{Three Non-Negative Bribes}
+Similar intuition for the case where all three legislators are bribed
 \pause
-\begin{itemize}[<+->]
-	\item Want 
-	\item But 
-\end{itemize}
-
-\pause
-\vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+\vskip.4in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Three Non-Negative Bribes}
     When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
@@
 
-\begin{frame}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+\begin{frame}{The Rest of the Story...}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{One Non-Negative Bribe}
       When Vote Buyer $B$ pays bribes to exactly one legislator, it may be any one of the three legislators depending on the bias parameter $\al$.
@@
 \vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{No Non-Negative Bribes}
   When Vote Buyer $B$ has a low willingness to pay, he does not bribe any legislator.
@@
 \begin{frame}{Varying Uncertainty Across Legislators}
-Now 
+Now let the scale of uncertainty differ across legislators 
 \pause
 \begin{itemize}[<+->]
-	\item Want 
-	\item But 
+	\item To be precise: the scale parameters in the three logit distributions are not equal
 \end{itemize}
@@
 \subsection{Two Vote Buyers}
-\begin{frame}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+\begin{frame}{Two Vote Buyers}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{No Bribes}
   It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
@@
 \vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result...}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Both Vote Buyers Bribe}
   It is possible for both vote buyers to bribe legislators on the same vote.

### 2016-05-09 draft.tex
add probabilistic voting reference to Roemer (1997)

@@
 Stigler (1975), Peltzman (1976), Becker (1983), Laffont and Tirole (1994)).
+By putting legislators in the place of voters and lobbyists in the place of candidates, the idea can been seen as similar to that of the probabilistic voting models that incorporate policy motivation such as Roemer (1997).
 
@@
 
+\item Roemer, J. (1997), ``Political-economic Equilibrium when Parties Represent Constituents: The Unidimensional Case.'' {\em Social Choice and Welfare} 14, 479-502.
+
 \item Saiegh, S. (2009), ``Political  Prowess or Lady Luck? Evaluating Chief Executives' Legislative Success Rates,'' {\em The Journal of Politics}, 71, 1342-1356.

### 2016-05-09 presentation.tex
proof read for presentation at Midwest
more adjustments for Midwest talk
minor improvements to overview and model sec of presentation

@@
 \author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
-\date{April 16, 2016}
+\date{May 10, 2016}
 \begin{document}
@@
 	\begin{itemize}
-		\item[$\Rightarrow$] Build a structural model to take to U.S. House data
+		\item[$\Rightarrow$] build a structural model to take to U.S. House data
 	\end{itemize}
@@
 \item Ultimately, want to identify cross-industry measures of legislative uncertainty
+	\begin{itemize}
+		\item but for today, unidimensional model
+	\end{itemize}
 \end{enumerate}
 
+\end{frame}
+
+\begin{frame}{Literature}
+\pause
+\begin{itemize}[<+->]
+	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
+	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets 2007
+	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
+	\item \textbf{Influence w/out Vote Buying}: Fox $\&$ Rothenberg 2011
+\end{itemize}
 \end{frame}
@@
 Adding uncertainty to standard model captures (2) --- (4)
-\end{frame}
-
-\begin{frame}{Literature}
-\pause
-\begin{itemize}[<+->]
-	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
-	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets (2007)
-	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
-	%\item \textbf{Uncertainty}: 
-\end{itemize}
 \end{frame}
@@
 \pause
-Use multi-dimensional ideal-point estimation to identify measures of uncertainty
+Goal: use multi-dimensional ideal-point estimation to identify measures of uncertainty
 \end{frame}
@@
 \pause
-Three legislators
+Two vote buyers, $A$ and $B$
 \pause
 \begin{itemize}
-	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
-	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
-	\item Decision made by majority vote
+	\item A prefers $x$, $B$ prefers $s$
 \end{itemize}
@@
 \vskip.2in
-Two vote buyers, $A$ and $B$
+Three legislators
 \pause
+\begin{itemize}[<+->]
+	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
+	\item Decision made by majority vote
+	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,0.5\right\}$
 		\begin{itemize}
-	\item A prefers $x$, $B$ prefers $s$
+			\item Take ideal point to be linear: $\alpha - \beta i$
+		\end{itemize}
 \end{itemize}
@@
 \begin{frame}{Legislators}
+
 \pause
-Take ideal point to be linear: $\alpha - \beta i$
-\pause
+Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
 	\begin{itemize}[<+->]
-	\item Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
-		\begin{itemize}
-			\item Probability $i$ votes for $s$ is $\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right] = \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right] $
-			\item Assuming $\ta \sim \text{Logistic} \ (0,1)$, it's $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
-		\end{itemize}
+		\item Probability $i$ votes for $s$ is
+			\[ 
+				\Pr\left[\alpha -\beta i + \ta_i + a_i - b_i \leq 0 \right]
+			\]
+			\[
+				= \Pr\left[\ta_i \leq \beta i - \alpha - a_i + b_i \right]
+			\]
+		\item Assuming $\ta_i \text{ i.i.d.} \sim \text{Logistic} \ (0,1): \ = \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
 	\end{itemize}
@@
 Assume vote buyers maximize expected value of winning net of bribes paid  
+\pause
 \begin{itemize}[<+->]
@@
 	\item Vote buyer won't spend more than his willingness to pay, $W_B$
-	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s$
+	\item In three-seat legislature, maximize $[$ probability $\geq 2$ legislators vote for $s ]$ $\times W_B -$ bribes
 \end{itemize}
@@
 Let $X(i) = 1$ denote legislator $i$ votes for the status quo
+\pause
 \begin{multline*}
@@
 Vote Buyer A is just like Vote Buyer B \textit{except}
+\pause
 \begin{itemize}[<+->]
@@
 	\item She wants $x$ to win instead of $s$
+	\item Willingness-to-pay parameter $W_A$
 \end{itemize}

### 2016-05-09 presentation.tex
change indicator var in presentation from X(1) to S(1)

--- 2016-04-15 presentation.tex
@@
-%\documentclass{beamer} 
-\documentclass[handout]{beamer} 
+\documentclass{beamer} 
+%\documentclass[handout]{beamer} 
 \usetheme{Ilmenau}
@@
 \title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
-%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
-\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
+%\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  
+%\newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
+\author[Buzard, DiTraglia and Saiegh \hspace{2.7in} \url{kbuzard@syr.edu}]{Kristy Buzard \inst{1} \and Frank DiTraglia \inst{2} \and Sebastian Saiegh \inst{3}}
+\institute{\inst{1} Syracuse University and The Wallis Institute \and \inst{2} University of Pennsylvania \and \inst{3} UC San Diego}
 \date{April 16, 2016}
@@
 
+\begin{frame}{Literature}
+\pause
+\begin{itemize}[<+->]
+	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
+	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets (2007)
+	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
+	%\item \textbf{Uncertainty}: 
+\end{itemize}
+\end{frame}
+
 \begin{frame}{Some Stylized Facts}
@@
 \pause
-\begin{itemize}
+\begin{itemize}[<+->]
 	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
@@
 	\item Vote buyer won't spend more than his willingness to pay, $W_B$
-	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s$
+	\item In three-seat legislature, max probability that $\geq 2$ legislators vote for $s \times W_B -$ bribes
 \end{itemize}
@@
 \pause
-Let $X(i) = 1$ denote legislator $i$ votes for the status quo
+Let $S(i) = 1$ denote legislator $i$ votes for the status quo
+\pause
 \begin{multline*}
 			    \max_{b_{-.5}, b_0, b_{.5}} 
-					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
-					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
-					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
-					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
+					W_B \biggl[ \Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\left(S\left(.5\right)=0\right)  + \\
+					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=0\right)\Pr\left(S\left(.5\right)=1\right) + \\
+					\Pr\left(S\left(-.5\right)=0\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) + \\
+					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
 				\end{multline*}

### 2016-05-09 presentation.tex

--- 2016-05-09 presentation.tex
@@
 \title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
-%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
-\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
+\author[Buzard and Saiegh \hspace{2.7in} \url{kbuzard@syr.edu}]{Kristy Buzard \inst{1} \and Sebastian Saiegh \inst{2}}
+\institute{\inst{1} Syracuse University and The Wallis Institute \and \inst{2} UC San Diego}
 \date{May 10, 2016}
@@
 \pause
-Let $X(i) = 1$ denote legislator $i$ votes for the status quo
+Let $S(i) = 1$ denote legislator $i$ votes for the status quo
 \pause
@@
 			    \max_{b_{-.5}, b_0, b_{.5}} 
-					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
-					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
-					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
-					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
+					W_B \biggl[ \Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\left(S\left(.5\right)=0\right)  + \\
+					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=0\right)\Pr\left(S\left(.5\right)=1\right) + \\
+					\Pr\left(S\left(-.5\right)=0\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) + \\
+					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
 				\end{multline*}

### 2016-05-09 presentation.tex
make adjustments to add simultaneous model to presentation

@@
 \title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
-\author[Buzard and Saiegh \hspace{2.7in} \url{kbuzard@syr.edu}]{Kristy Buzard \inst{1} \and Sebastian Saiegh \inst{2}}
-\institute{\inst{1} Syracuse University and The Wallis Institute \and \inst{2} UC San Diego}
+\author[Buzard and Saiegh \hspace{3in} \url{kbuzard@syr.edu}]{Kristy Buzard\inst{1} \and Sebastian Saiegh\inst{2}}
+\institute{\inst{1}Syracuse University and The Wallis Institute \and 
+\inst{2}UC San Diego}
 \date{May 10, 2016}
@@
 			%\pause
-			\item Observes $\un{a}$
+			\item Observes $\un{a}$ (in sequential model)
 			%\pause
@@
 \begin{itemize}[<+->]
-	\item She gets to move first
+	\item She gets to move first (in sequential model)
 	\item She wants $x$ to win instead of $s$
@@
 
-\section{Results}
-\subsection{One Vote Buyer}
+\section{One Vote Buyer}
+\subsection{}
 \begin{frame}{Two Non-Negative Bribes}
@@
 
-\subsection{Two Vote Buyers}
-\begin{frame}{Two Vote Buyers}
+\section{Two Vote Buyers}
+\subsection{Sequential Model}
+\begin{frame}{Some Possibilities...}
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{No Bribes}
@@
 \end{beamerboxesrounded}
+
+\end{frame}
+
+\subsection{Simultaneous Model}
+\begin{frame}{Some Possibilities...}
+What I know...
+\begin{itemize}
+	\item FOCs look the same as for one vote buyer, e.g.
+		\begin{equation*}
+			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+		\end{equation*}
+			\begin{itemize}
+				\item Two roots, only larger one satisfies SOC
+			\end{itemize}
+\end{itemize}
 

### 2016-05-09 draft.tex
fix old typos in draft
fix A's probabilities and obj fcn

@@
 There are five players in the model.
-Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$.
+Each of three legislators faces a choice between the status quo, $s$ and a new policy proposal $x$.
 The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units.
@@
 	\[
-					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a_i - b_i \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a_i + b_i \right] 
+					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a_i - b_i \leq 0 \right] = \Pr\left[\ve \leq \beta i - \alpha - a_i + b_i \right] 
 	\]
@@
 For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$.
-Then $Y_B = \frac{\beta}{2} - \alpha - a_{-\frac{1}{2}} + b_{-\frac{1}{2}}$, $X_B = -\alpha - a_0+ b_0$ and $Z_B = -\frac{\beta}{2} - \alpha - a_{\frac{1}{2}} + b_{\frac{1}{2}}\label{page:sh}$ represent the net ideal points in terms of $B$'s probability of winning the issue.
+Let $Y_B = \frac{\beta}{2} - \alpha - a_{-\frac{1}{2}} + b_{-\frac{1}{2}}$, $X_B = -\alpha - a_0+ b_0$ and $Z_B = -\frac{\beta}{2} - \alpha - a_{\frac{1}{2}} + b_{\frac{1}{2}}\label{page:sh}$ represent the net ideal points in terms of $B$'s probability of winning the issue.
 We can then write the probability that each of the legislators, respectively, votes against the new proposal as $\frac{1}{1+e^{-Y_B}}$, $\frac{1}{1+e^{-X_B}}$ and $\frac{1}{1+e^{-Z_B}}$.
 
-Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes.
-So the net ideal points from her point of view---that is, in terms of her winning the issue---are $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$, $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$, and $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$ with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$.
-We can then write the probability that each of the legislators votes for the new proposal as $\frac{1}{1+e^{-Y_A}}$, $\frac{1}{1+e^{-X_A}}$ and $\frac{1}{1+e^{-Z_A}}$.
+We would also like to write the probabilities that the legislators vote in line with Vote Buyer A.
+The probability that a legislator votes for the new proposal is the complement of the probability that she votes for the status quo.
+Since Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes, we write these probabilities as $\frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}}$, $\frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}}$ and $\frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}}$ with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$.
 
@@
 \subsection{Vote Buyer A}
-Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
+Vote buyer A's objective function is similar in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
 			  \begin{multline}
 			    \max_{a_{-\frac{1}{2}}, a_0, a_{\frac{1}{2}}} 
-					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
-					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
-					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a_j .
+					W_A \biggl[ \frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}} \frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}} +
+					\frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}} \frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}} + \\
+					\frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}} \frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}} - 2	\frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}} \frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}} \frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a_j .
 					\label{eq:obja}

### 2016-05-09 A-optim.R
fix win % in A-optim.R; equiv to old formulation

@@ -5,15 +5,15 @@ rm(list = ls())
 al = 0
 WB=8
 
-v = seq(5,9,.4)
+v = seq(6,8,.4)
 o <- matrix(0,length(v),20)
 colnames(o) <- c("al","sy","sz","WA","WB","x", "y", "z","foe", "middle", "friend","Z", "X", "Y","value","wProbB","X_a", "Y_a", "Z_a","ValA")
 
 for (j in 1:length(v)) {
 
   WA = v[j]
-  sy=.9
-  sz=1.2
+  sy=1.1
+  sz=1
   
 h <- function(x0,y0,z0) {
   
@@ -26,9 +26,9 @@ h <- function(x0,y0,z0) {
   
   o <- optim(c(1,1,1,x0,y0,z0),function(B) f(B,x0,y0,z0),gr=NULL,method = "L-BFGS-B", lower = c(0,0,0), control = list(maxit=100000))
   
-  X = round(-x0 - al + o$par[2], digits = 3)       #B0   these are shorthand variables for the exponents
-  Y = round(-y0 - al + o$par[3], digits = 3)    #Bnp5  in the logistic CDFs; I don't use them in the function
-  Z = round(-z0 - al + o$par[1], digits=3)   #Bp5 but I've pasted in values here to check
+  X = round(-x0 - al + o$par[2], digits = 3)   #B0   these are shorthand variables for the exponents
+  Y = round(-y0 - al + o$par[3], digits = 3)   #Bnp5  in the logistic CDFs; I don't use them in the function
+  Z = round(-z0 - al + o$par[1], digits = 3)   #Bp5 but I've pasted in values here to check
   
   A0 = x0 
   Ap5 = z0 - .5
@@ -37,8 +37,8 @@ h <- function(x0,y0,z0) {
   pos <- c(Z,X,Y)
   bribes <- c(o$par,-o$value)
   bribesA <- c(A0,Anp5,Ap5)
[…]

### 2016-05-10 presentation.tex
fix footline; add B's full program

@@
 \usepackage{cite}
-\usepackage{times, verbatim,xcolor,bm}
+\usepackage{times,xcolor,bm}
 %\usepackage[usenames,dvipsnames]{color}
@@
 \title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
-\author[Buzard and Saiegh \hspace{3in} \url{kbuzard@syr.edu}]{Kristy Buzard\inst{1} \and Sebastian Saiegh\inst{2}}
-\institute{\inst{1}Syracuse University and The Wallis Institute \and 
+\author[Buzard and Saiegh]{Kristy Buzard\inst{1} \and Sebastian Saiegh\inst{2}}
+\institute{\inst{1}Syracuse University and The Wallis Institute \\ \url{kbuzard@syr.edu} \and 
 \inst{2}UC San Diego}
@@
 
+\begin{frame}{Vote Buyer B's Full Program}
+\pause
+\begin{equation}
+    \left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1 - \lambda_X}{W_B}
+		\label{eq:focB}
+\end{equation}
+\begin{equation}
+    \left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1 - \lambda_Y}{W_B}
+\end{equation}
+\begin{equation}
+    \left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2} = \frac{1 - \lambda_Z}{W_B}
+\end{equation}
+\[
+  b\left(0\right) \geq0 \hskip.2in b\left(-.5\right) \geq0 \hskip.2in b\left(.5\right) \geq0 
+\]
+\[
+  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
+\]
+\[
+  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(-.5\right) = 0 \hskip.2in \lambda_Z \cdot b\left(.5\right) = 0 
+\]
+
+\end{frame}
+
 \begin{frame}{Vote Buyer A}

### 2016-05-10 presentation.tex
add slide on simultaneous model; small fixes throughout presentation

@@
 Leg $i$ votes for $s$ if $v(i) = \alpha -\beta i + \ta_i + a_i - b_i \leq 0$
+\pause
 	\begin{itemize}[<+->]
 		\item Probability $i$ votes for $s$ is
+		\pause
 			\[ 
@@
 			\]
+		\pause
 			\[
@@
 			\]
+		\pause
 		\item Assuming $\ta_i \text{ i.i.d.} \sim \text{Logistic} \ (0,1): \ = \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$ 
 	\end{itemize}
-
 \end{frame}
@@
 \begin{frame}{Vote Buyer B's Full Program}
+\pause
+Let $X$, $Y$, $Z$ be the gross positions of the legislators
 \pause
@@
 	\item She gets to move first (in sequential model)
+	\item Willingness-to-pay parameter $W_A$
 	\item She wants $x$ to win instead of $s$
-	\item Willingness-to-pay parameter $W_A$
+		\begin{itemize}
+			\item Leg $i$ votes for $x$ w/probability
+				\[
+					1 - \frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}} = \frac{e^{-\left(\beta i - \alpha - a_i + b_i \right)}}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}
+				\]
+		\end{itemize}
+
 \end{itemize}
@@
 \pause
-Let $X$ and $Y$ and $Z$ be the gross positions of each of the three legislators. Then the FOCs are
+The FOCs are
 \pause
@@
 \begin{frame}{Three Non-Negative Bribes}
-Similar intuition for the case where all three legislators are bribed
+Similar intuition for the case where all three legislators are bribed:
 \pause
@@
 \subsection{Simultaneous Model}
-\begin{frame}{Some Possibilities...}
-What I know...
+\begin{frame}{What I know...}
+\pause
+FOCs look the same for Vote Buyer B, e.g.
+\pause
+	\[
+		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
+	\]
+	\vskip-.15in
+	\pause
 		\begin{itemize}
-	\item FOCs look the same as for one vote buyer, e.g.
-		\begin{equation*}
-			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
-		\end{equation*}
+			\item Either one root at zero, or
+			\pause
+			\item Two roots and only larger one (at $X_B>0$?) satisfies SOC
+		\end{itemize}
+
+\vskip.1in
+\pause
+For Vote Buyer A,
+\pause
+	\[
+		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{1}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
+	\]
+	\vskip-.15in
+	\pause
 		\begin{itemize}
-				\item Two roots, only larger one satisfies SOC
-			\end{itemize}
+			\item One root: zero or $X_B<0$
 		\end{itemize}

### 2016-05-10 presentation.tex
remove B subscript on a few X's since I don't use it elsewhere in presentation

@@
 	\item There is usually lobbying on both sides of a given issue
-	\item Moderate legislators receive more contributions than those that are ideologically extreme
+	\item Moderate legislators receive more contributions than those who are ideologically extreme
 	\item Legislators about whom there is a moderate level of uncertainty are lobbied the most
@@
 			\pause
-			\item Two roots and only larger one (at $X_B>0$?) satisfies SOC
+			\item Two roots and only larger one (at $X>0$?) satisfies SOC
 		\end{itemize}
@@
 		\begin{itemize}
-			\item One root: zero or $X_B<0$
+			\item One root: zero or $X<0$
 		\end{itemize}

### 2016-05-10 presentation.tex
make corrections from Wallis talk

@@
-\documentclass{beamer} 
-%\documentclass[handout]{beamer} 
+%\documentclass{beamer} 
+\documentclass[handout]{beamer} 
 \usetheme{Ilmenau}
@@
 \pause
-FOCs look the same for Vote Buyer B, e.g.
+FOC look the same for Vote Buyer B, e.g. for $b(0)$:
 \pause
@@
 \pause
-For Vote Buyer A,
+For Vote Buyer A, FOC for $a(0)$:
 \pause
 	\[
-		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{1}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
+		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
 	\]
@@
 		\begin{itemize}
-			\item One root: zero or $X<0$
+			\item Similar to $B$, except only smaller root satisfies SOC
 		\end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Modify model so that both legislators can lobby the \textit{same} legislator in equilibrium
+	\item Modify model so that both vote buyers can lobby the \textit{same} legislator in equilibrium
 	\item Derive tight identification of empirical estimates from structural model

### 2017-06-29 analysis/code/11_groups_5000_code.R
First commit: separate files into different folders based on type and function

@@ -1,0 +1,84 @@
+library(rstan)
+library(coda)
+library(ggmcmc)
+
+/////////////////LAPTOP
+votes<- read.csv("C:/Users/yusuf/Desktop/kristy/data_7_19.csv", header=TRUE)
+attach(votes)
+groups<- read.csv("C:/Users/yusuf/Desktop/kristy/11_groups_dummy.csv", header=TRUE)
+attach(groups)
+
+////////////// MODEL WITH GROUP IND
+votes_code<- '
+data {
+  int<lower=1> J;              // number of legislators
+  int<lower=1> K;              // number of votes
+  int<lower=1> N;              // number of observations
+  int<lower=1> G;              // number of groups
+  int<lower=1,upper=J> jj[N];  // legislator for observation n
+  int<lower=1,upper=K> kk[N];  // vote for observation n
+  matrix[N,G] x;			 // group indicators
+  int<lower=0,upper=1> y[N];   // position for observation n
+//  vector[N] y;                 // position for observation n
+}
+
+parameters {    
+  matrix[J,G] alpha;               //  
+  matrix[K,G] beta;                // 
+  real mu_beta;
+  real<lower=0> sigma_beta;
+  matrix<lower=0>[K,G] gamma;
+  real mu_gamma;
+  real<lower=0> sigma_gamma;}
+
+
+transformed parameters 
+{ 
+//  real total[N]; 
+  vector[N] total; 
+
+  { 
+    matrix[N,G] summands; 
+    for (g in 1:G) 
+      for (n in 1:N) 
+        summands[n,g]<- (x[n,g]*gamma[kk[n],g])*(alpha[jj[n],g] - beta[kk[n],g]); 
+
+    for (n in 1:N) 
+ //     for (g in 1:G) 
+        total[n] <- sum(summands[n]); 
+
+  } 
+} 
+
+
+model 
+{
+
+for (g in 1:G)
+alpha[g]~ normal(0,1);         
+
+for (g in 1:G)
+beta[g] ~ normal(mu_beta, sigma_beta);
+mu_beta~ normal(0, 3);
+sigma_beta ~ cauchy(0,3);
+
+for (g in 1:G)
+gamma[g] ~ lognormal(mu_gamma, sigma_gamma);
+mu_gamma ~ normal(0, 3);
+sigma_gamma ~ cauchy(0,3);
+
+for (n in 1:N)
[…]

### 2017-06-29 writing/output/model-notes.tex
move all files in the original repo into writing folder

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}

\setcounter{secnumdepth}{-1}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

\begin{document}

\title{\vskip-0.6in \Large Lobbying and Legislative Uncertainty}
\author{Kristy Buzard}
\date{\vskip-.1in \today}
\maketitle

\un{April 29, 2014} \\

Note the working title I came up with when I threw the draft together earlier this month is ``Lobbying and Legislative Uncertainty.'' I'm sure we can come up with something better...

\vskip.3in
Initial modeling thoughts, starting at the level of individual legislators.
\begin{itemize}
	\item I wanted to ground this in the Optimal Classification methodology, so I went back to Clinton, Jackman $\&$ Rivers (2004)---hereafter CJR.
	\item Their setup:
		\begin{itemize}
			\item Roll call votes are numbered $j=1,\ldots,m$
			\item Legislators are numbered $i=1,\dots,n$
			\item ``Yea'' position on bill $j$ is denoted $\zeta_j$
			\item ``Nay'' position on bill $j$ is denoted $\varphi_j$
				\begin{itemize}
					\item $\zeta_j$ and $\varphi_j$ are assumed to have $d$ dimensions; I will take $d=1$ for simplicity for now
				\end{itemize}
			\item $y_{ij}=1$ if legislator $i$ votes ``Yea'' on bill $j$; $y_{ij}=0$ if she votes ``Nay'' on bill $j$
			\item Utility functions are quadratic:
				\begin{itemize}
					\item $U_i(\zeta_j) = - \left( x_i - \zeta_j \right)^2 + \eta_{ij}$
					\item $U_i(\varphi_j) = - \left( x_i - \varphi_j \right)^2 + \nu_{ij}$ \\
					where $x_i$ is the ideal point of legislator $i$ and $\eta_{ij}$ and $\nu_{ij}$ are the errors or stochastic elements of utility
				\end{itemize}
			\item Utility maximization implies $y_{ij} = 1$ if 
				\begin{equation}
					U_i(\zeta_j) > U_i(\varphi_j),
				\label{eq:yesvote}
				\end{equation}
				0 otherwise
			\item CJR assume are jointly normal with equal means and var($\nu_{ij} - \varphi_{ij}$) $= \sigma_j^2$
		\end{itemize}
\end{itemize}

\newpage
One simple way to take account of lobbying effort
\begin{itemize}
	\item Let $e_i$ be lobbying effort exerted on legislator $i$. If we want it to be specific to bill $j$, then change notation to $e_{ij}$
	\item Without lobbying effort, legislator $i$ votes in favor of bill $j$ if (according to Expression~\ref{eq:yesvote})
		\[
		  - \left( x_i - \zeta_j \right)^2 + \eta_{ij} > - \left( x_i - \varphi_j \right)^2 + \nu_{ij}
		\]
	\item Now add the lobby. If the lobby is in favor of bill $j$ (this notation doesn't work if lobby is against bill $j$---$e_i$ would need to be negative, or we would need to switch ideal points around):
		\begin{itemize}
			\item just let lobbying effort shift the ideal point:
		\end{itemize}
		\[
		  - \left( x_i + e_i - \zeta_j \right)^2 + \eta_{ij} > - \left( x_i + e_i - \varphi_j \right)^2 + \nu_{ij}
		\]
    Then the probability that legislator $i$ votes yes on bill $j$ is given by
		\begin{equation}
		  P\left(y_{ij}=1\right) = P\left(U_i(\zeta_j) > U_i(\varphi_j)\right) = P\left(\nu_{ij} - \eta_{ij} <  \left( x_i + e_i - \varphi_j \right)^2 - \left( x_i + e_i - \zeta_j \right)^2\right)
		\label{eq:yeswe}
		\end{equation}
\end{itemize}

\vskip.3in
Expression~\ref{eq:yeswe} is what the lobby targets to change behavior. 
\begin{itemize}
	\item We don't know exactly what their rule is. But they must want to increase enough individual $P(y_{ij}=1)$'s so that $\sum_i y_{ij} > 218$ (in the U.S. House).
	\item We also don't know exactly what the benefit of bill passage is. May have to set a dummy value.
		\begin{itemize}
			\item If errors are normally distributed as we assume, this can't be achieved with certainty
			\item Maybe they target something like two standard deviations?
			\item Is it equivalent to model them as just targeting the total expected number of votes (as if votes were divisible)?
			\item Will there be some kind of marginal condition---extra increase in probability of voting ``yea'' should be the same for all legislators? Or no because these votes are actually indivisible? Maybe something more like expected probability of voting ``yea'' should be the same for all legislators the lobby engages with
		\end{itemize}
	\item Of course, they want to do this at minimal cost
	\item They may also want a sufficient margin --- lobbies might have different risk preferences
	\item Let's abstract from opposing lobbies for now
\end{itemize}

\newpage
Going back to Expression~\ref{eq:yeswe},
\begin{itemize}
	\item We estimate the $x_i$'s
	\item If we assume the errors are normally distributed and mean zero, we also estimate the variance of $\nu_{ij} - \eta_{ij}$ for each $i$---or something like it; it's actually a cross-interest-group measure;
		\begin{itemize}
			\item Need to figure out exactly how this standard deviation measure we create is connected to the theoretical underpinnings
			\item I think what we need to assume is that the $\nu_{ij}$ and $\eta_{ij}$ are iid within interest group votes (as well as that the ideal point doesn't vary for bills within interest groupings)
		\end{itemize}
	\item We will have to make assumptions about the locations of $\zeta_j$ and $\varphi_j$
\end{itemize}

\vskip.5in
For commercial banks, I tried looking at some of the voting records to see if I could get some intuition for the pattern of ideal points and standard deviations. It's not too hard to pull the votes out and match the legislator code in the results file to the voting record. The problem I ran into was that in my list of banking votes, I only came up with 46 from the 112th Congress, whereas your output says there were 65 votes.
\begin{itemize}
	\item I want to figure out what's going on here, especially because one of the things I'm looking at is two legislators with the same ideal point but drastically different standard deviations (Crenshaw and Adams both have ideal points for Commercial Banks of 1.32, but Crenshaw's std.dev. is double that of Adams). Their voting records are identical across the 46 bills I'm looking at except they took opposite positions on one amendment. I'm not sure if I need to make sense of that, or if I need to find 19 missing bills.
\end{itemize}

\newpage
Conversation on May 9, 2014
\begin{itemize}
	\item Clinton has another paper that may be helpful for me to look at
	\item I need to read about hyper-prior more carefully (Bafumi et al paper)
	\item Sebastian's brainstorm: take the utility function I have above
	  \[
		  - \left( x_i + e_i - \zeta_j \right)^2 + \eta_{ij} 
		\]
		and morph it into the discrimination parameter form:
		\[
		  \ga_k \left( x_i + e_i - \zeta_k \right) + \eta_{ik} 
		\]
		Does this make sense?
	\item He found that running a lot more simulations doesn't bring down the standard errors
		\begin{itemize}
			\item Okay empirically; my question is: what about theoretically?
		\end{itemize}
	\item In Bafumi's terminology, outliers are those who are misclasified
	\item We can look at the 20 guys around the cut-point (instead of median as we did before). This is going to depend on $\ga_k$, so subject to all our discussions about $\ga_k$ changing depending on sample of bills
	\item What does it mean to use whether you were lobbied or not as a prior?
	\item Correlate lobbying \textit{by bill} with $\ga_k$ (this is the discrimination parameter, not my $\ga$) --- not across bills, across industry, within bill	
\end{itemize}

\newpage
Conversation on June 4, 2014
\begin{itemize}
	\item What we really have is an n-dimensional policy space, but it's not clear what we should set the ``dimension'' variable in the Jackman code to (or if we can use the Jackman code)
		\begin{itemize}
			\item I need to dig into the Gelman and Hill book
		\end{itemize}
	\item I still need to look at James Lakes' data
	\item We will need to decide list of interest groups
		\begin{itemize}
			\item Either I need to compile number of bills per catcode, or instruct Yusuf to do it
		\end{itemize}
	\item Rjags is the package Sebastian uses. He sent me master code in an email today at 5:29pm (response to my ``Gelman and Hill Book'' email)
		\begin{itemize}
			\item In an earlier email, he sent three files: a BUGS program, an R program, and a PDF file that is Jackman's documentation for the R code
		\end{itemize}
\end{itemize}

\vskip.2in
Work on 6/9/14
\begin{itemize}
	\item Crespin $\&$ Rohde: divide votes into each appropriation category and run separate W-NOMINATE procedures on each (just like we were going to do)
	\item Clinton et al: Ex. 4 on page 9-12, party inducements.
		\[
		  y_{ij}^* = x_i \beta_j  - \alpha_j + \delta_j D_i  + \varepsilon_{ij}
		\]
		legislators are $i$, bills are $j$
\end{itemize}

\vskip1in
Possible modeling elements
\begin{itemize}
	\item Roll call votes are numbered $k=1,\ldots,K$
		\begin{itemize}
			\item Which groups $g$ take a position on it
		\end{itemize}
	\item Legislators are numbered $j=1,\dots,J$. Each is identified by
	\begin{itemize}
		\item State
		\item District
		\item Party
		\item Whether he/she is lobbied by a group $g$
		\item Committee assignments
	\end{itemize}
	\item Interest groups are numbered $g=1,\dots,G$
\end{itemize}

\vskip.2in
Want to model
\begin{itemize}
	\item How $j$ votes
	\item How vote total on $k$ is determined
	\item How lobby group $g$'s political uncertainty is determined
		\begin{itemize}
			\item Overall success rate?
			\item As function of lobbying effort?
			\item Economic distribution across districts?
			\item Committee chairs?
		\end{itemize}
\end{itemize}
\end{document}

### 2017-06-29 writing/output/two-groups.tex
move all files in the original repo into writing folder

--- 2016-02-22 two-groups.tex
@@
 			\end{itemize}
-		\item Can write out SOC (just after equation 33) and FOC, sub together to get
+		\item Can write out SOC and FOC, sub together to get
 			\[
-			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
+			  \frac{1}{1 + e^{-X}} \left(e^{-X} - 1\right) < 0
 			\]
@@
 	\item This is NOT the case when $X$ and $Y$ are the two non-negative bribes. They can get very large before the left-most legislator is bribed.
+\end{itemize}
+
+\newpage
+\section{Simultaneous Model}
+For most of the parameter space, there is no PSNE. What must a MSNE look like?
+\begin{itemize}
+	\item In a fully mixed strategy equilibrium, a probability distribution $F_b$ over strategies $$\bm{b_1} = \left(b_{-.5,1},b_{0,1},b_{.5,1}\right),\bm{b_2},\ldots$$ must make Vote Buyer $A$ indifferent between at least two vectors of strategies $$\bm{a_1} = \left(a_{-.5,1},a_{0,1},a_{.5,1}\right),\bm{a_2}$$
 \end{itemize}

### 2017-07-19 writing/output/draft.tex

--- 2016-05-09 draft.tex
@@
 The vertical axis represents the predicted net contributions to members of the U.S.
-House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislator's voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress.
+House of Representatives in 2012, and the horizontal axis shows the unpredictability of legislators' voting behavior measured using the 95$\%$ posterior confidence intervals of their ideal points estimated using Bayesian Markov chain simulation to scale all roll call votes taken in the 112th Congress.
 The solid vertical red line indicates the average uncertainty in the sample, and the vertical dashed red lines indicate increases/decreases of one-standard deviation from the average.

### 2017-07-19 writing/output/structural_model.tex

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}

\setcounter{secnumdepth}{-1}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

\begin{document}

\title{\vskip-0.6in \Large Lobbying and Legislative Uncertainty}
\author{Kristy Buzard}
\date{\vskip-.1in October 20, 2014}
\maketitle

Model notes
\begin{itemize}
	\item Bills come from some distribution of bills (dist'n can vary by issue area?)
	\item Assume errors are Type I extreme value in order to derive logit (Train p.45 of PDF)
	\item 3 legislators
		\begin{itemize}
			\item quadratic utility? (random utility model)
			\item the three have different ideal points; they all get variance from the same distribution
		\end{itemize}
	\item will eventually do two special interest groups (SIGs); start with one
		\begin{itemize}
			\item Assume they get a benefit $B$?
			\item with or without budget constraint?
		\end{itemize}
\end{itemize}

\vskip.2in
\begin{itemize}
	\item Write down equilibrium (variation across issue areas) to identify model
	\item Get relationship between variance parameters, mean parameters, bill locations, ideal points
\end{itemize}

\vskip.5in
\begin{itemize}
	\item Roll call votes are numbered $k=1,\ldots,K$
	\item Legislators are numbered $j=1,\dots,J$
	\item Interest groups are numbered $g=1,\dots,G$
		\begin{itemize}
			\item Interest groups take positions on multiple roll call votes; multiple interest groups can take positions (on both sides) on each vote
		\end{itemize}
	\item $y_{i}=1$ if legislator $j(i)$ votes ``Yea'' on bill $k(i)$; $y_{i}=0$ if she votes ``Nay'' on bill $k(i)$
\end{itemize}

\vskip.2in
Following CJR(2004):
\begin{itemize}
	\item Value to legislator $j$ from voting ``Yea'' on bill $k$: $U_j(\zeta_k) = - \left\| \bm{x}_j - \bm{\zeta}_k \right\|^2 + \eta_{jk}$
	\item Value to legislator $j$ from voting ``Nay'' on bill $k$: $U_j(\varphi_k) = - \left\| \bm{x}_j - \bm{\varphi}_k \right\|^2 + \nu_{jk}$
	\item Then $\Pr\left(y_{jk} = 1\right) = \Pr\left(U_j(\zeta_k) > U_j(\varphi_k) \right)$, that is
		\[
		  \Pr\left(y_{jk} = 1\right) = \Pr\left(- \left\| \bm{x}_j - \bm{\zeta}_k \right\|^2 + \eta_{jk} > - \left\| \bm{x}_j - \bm{\varphi}_k \right\|^2 + \nu_{jk} \right)
		\]
		\[
		  \Pr\left(y_{jk} = 1\right) = \Pr\left( \nu_{jk} - \eta_{jk} < - \left\| \bm{x}_j - \bm{\zeta}_k \right\|^2 + \left\| \bm{x}_j - \bm{\varphi}_k \right\|^2  \right)
		\]
		\[
		  \Pr\left(y_{jk} = 1\right) = \Pr\left( \nu_{jk} - \eta_{jk} < 2 \left(\bm{\zeta}_k - \bm{\varphi}_k  \right)'\bm{x}_j + \bm{\varphi}_k' \bm{\varphi}_k  - \bm{\zeta}_k' \bm{\zeta}_k \right)
		\]
\end{itemize}
CJR assume that the errors $\nu_{jk}$ and $\eta_{jk}$ have a joint extreme value distribution with $\expect\left[\nu_{jk}\right] = \expect\left[\eta_{jk}\right], \ \text{var}(\eta_{jk} - \nu_{jk}) = \sigma^2$ and the errors are independent across both legislators and roll calls. \\

Thus this model corresponds to a logit model with an unobserved regressor $\bm{x_j}$ where $\bm{\beta_j} = \frac{2 \left(\bm{\zeta}_k - \bm{\varphi}_k  \right)}{\sigma_j}$ and $\alpha_j = \frac{\bm{\zeta}_k' \bm{\zeta}_k - \bm{\varphi}_k' \bm{\varphi}_k}{\sigma_j}$.
    \[
		  \Pr\left(y_{jk} = 1\right) = \text{logit}^{-1}\left( \bm{\beta_j}'\bm{x}_j -\alpha_j \right)
		\]

\vskip.2in
\un{Lobbying} \\
Adding lobbying effort to CJR(2004), let $e_{j}$ be a vector of lobbying contributions (note that they go into the utility function as negative or positive depending on how the lobby wants to shift the legislator's preferences, but the lobby pays the absolute value)
\begin{itemize}
	\item Value to legislator $j$ from voting ``Yea'' on bill $k$ with inducement $\bm{e_j}$ from lobbies: $U_j(\zeta_k) = - \left\| \bm{x}_j + \bm{e_j} - \bm{\zeta}_k \right\|^2 + \eta_{jk}$
	\item Value to legislator $j$ from voting ``Nay'' on bill $k$: $U_j(\varphi_k) = - \left\| \bm{x}_j - \bm{\varphi}_k \right\|^2 + \nu_{jk}$
	\item Then $\Pr\left(y_{jk} = 1\right) = \Pr\left(U_j(\zeta_k) > U_j(\varphi_k) \right)$, that is
		\[
		  \Pr\left(y_{jk} = 1\right) = \Pr\left(- \left\| \bm{x}_j + \bm{e_j} - \bm{\zeta}_k \right\|^2 + \eta_{jk} > - \left\| \bm{x}_j - \bm{\varphi}_k \right\|^2 + \nu_{jk} \right)
		\]
		\[
		  \Pr\left(y_{jk} = 1\right) = \Pr\left( \nu_{jk} - \eta_{jk} < - \left\| \bm{x}_j + \bm{e_j}- \bm{\zeta}_k \right\|^2 + \left\| \bm{x}_j - \bm{\varphi}_k \right\|^2  \right)
		\]
		\[
		  \Pr\left(y_{jk} = 1\right) = \Pr\left( \nu_{jk} - \eta_{jk} < 2 \left(\bm{\zeta}_k - \bm{\varphi}_k  \right)'\bm{x}_j + \bm{\varphi}_k' \bm{\varphi}_k  - \bm{\zeta}_k' \bm{\zeta}_k + \underline{2 \bm{\zeta}_k'\bm{e_j} - \bm{e_j}'\bm{e_j} - 2 \bm{e_j} \bm{x_j}}\right)
		\]
\end{itemize}

%\vskip.2in
\newpage
The most basic ideal point model (following notation of Bafumi, Gelman, Park and Kaplan, \url{doi:10.1093/pan/mpi010}) adapted from the logistic item-response model (a.k.a. Rasch model) used in education/testing research) is:
\[
  \Pr(y_i = 1) = \text{logit}^{-1}\left( \alpha_{j(i)} - \beta_{k(i)}\right)
\]
where $\alpha_{j(i)}$ is the ideal point of legislator $j$ on item $i$ and $\beta_{k(i)}$ is the ideal point of a legislator who is indifferent on vote $k$. A standard set of priors is $\alpha_j \sim N(0,\sigma_\alpha^2), \ \beta_k \sim N(\mu_\beta,\sigma_\beta^2)$.\\

One common enhancement is the discrimination parameter, $\ga$. It's interpreted as a measure of the informativeness of vote $k$, and will become very useful below
\begin{equation}
  \Pr(y_i = 1) = \text{logit}^{-1}\left( \ga_{k(i)}\left( \alpha_{j(i)} - \beta_{k(i)}\right) \right)
	\label{eq:disc}
\end{equation}
Now we need to do something like $\alpha_j \sim N(0,1)$ to resolve the indeterminancy introduced by $\ga$, which we give the standard normal prior. \\

An essential piece of which we need to take account is lobbying by group $g$ (either on bill $k$ or in general) toward legislator $j$, but I'm going to leave this aside for now. \\

The most complete way of integrating the interest groups into the analysis may be to consider the $G$ groups as lobbying on $G$ distinct \un{dimensions}. This differs from a standard multidimensional OC model because we \textit{know} what the dimensions are and which bills are relevant to each dimension. \\

In place of one base ideal point for each legislator with a shifter for each group as I had been thinking, we want one ideal point with $G$ dimensions. Likewise, the indifference point $\beta_k$ for each bill should be $G$-dimensional (and, we will see, we can get a discrimination parameter for each dimension). \\

Consider the following very simple example, where there are three bills and two interest groups, and g1 and g2 are indicator variables for whether each interest group lobbies on a particular bill.
\begin{center}
\begin{tabular}{|  c| c | c |}
 \hline  & g1 & g2 \\ \hline
	k=1& 1 & 1 \\ \hline
	k=2& 1 & 0\\ \hline
	k=3& 0 & 1\\ \hline
 %\multicolumn{3}{c} {\textit{Figure 1: Example: interest group lobbying by 2 groups on 3 bills}}
\end{tabular}
\end{center}

In this case, assuming a multidimensional model that is additive (see Gelman $\&$ Hill, page 319), for a representative legislator $j$, it would seem reasonable to model the probability that legislator $j$ votes in favor of bills 1, 2 and 3 as
\begin{gather}
  \Pr(y_{j1} = 1) = \text{logit}^{-1}\left( \ga_{1}^{(1)}\left( \alpha_{j}^{(1)} - \beta_{1}^{(1)}\right) + \ga_{1}^{(2)}\left( \alpha_{j}^{(2)} - \beta_{1}^{(2)}\right) \right) \\
  \Pr(y_{j2} = 1) = \text{logit}^{-1}\left( \ga_{2}^{(1)}\left( \alpha_{j}^{(1)} - \beta_{2}^{(1)}\right) \right) \\
	\Pr(y_{j3} = 1) = \text{logit}^{-1}\left( \ga_{3}^{(2)}\left( \alpha_{j}^{(2)} - \beta_{3}^{(2)}\right) \right) 
\end{gather}
where superscripts in parentheses represent dimensions / groups. \\

I think the way to implement this is by interacting each of the parameters in Equation~\ref{eq:disc} with the group indicator variables. This just zeroes out the additive term for all the dimensions on each bill on which an interest group did not exert pressure, leaving expressions like Equations 2-4. \\

One way to write this is
\begin{equation}
  \Pr(y_i = 1) = \text{logit}^{-1}\left( \sum_{g=1}^G \ga_{k(i)}^{(g)}\left( \alpha_{j(i)}^{(g)} - \beta_{k(i)}^{(g)}\right) \right)
\end{equation}

The result will be a $G$-dimensional ideal point for each legislator, a $G$-dimensional indifference point for each bill, and $G$ discrimination parameters that give the importance of each dimension in determining the outcome of the vote. \\

I haven't quite figured out how to write down the priors on these three sets of parameters to take account of the clustering by group, but I'll keep working on that.

\end{document}

### 2020-06-30 Literature_review.tex
upload files

\documentclass[a4paper,12pt]{article}
\begin{document}
\title{Literature Review}
\maketitle

\begin{enumerate}
\item “The ideological mapping of American legislatures”. B Shor, N McCarty - American Political Science Review, 2011 - cambridge.org (cited by 652)
\begin{itemize}
\item Empirical applications of spatial theory to state politics have been limited by two important factors. The first is that roll call voting data over time have not been collected for all 50 states. The second impediment is that because ideal points are latent quantities, direct comparisons across states or even between chambers within the same state are generally difficult to make. 
\item The conjunction of these two problems reduces the scope of spatial theory in state politics to a choice between examining within-state variation for a handful of states or making dubious comparisons on a cross section of states. 
\item In this article, we tackle both these potential problems with state-level applications of the spatial model. First, we introduce a new data set of state legislative roll call votes that covers all state legislative bodies over approximately a decade. Second, we employ a new strategy to establish comparability of estimates across chambers, across states, and across time. Here we use a survey of legislative candidates at the state and federal levels over a number of years. Importantly, the survey questions are asked in an identical form across states, and many questions are repeated over time. The survey allows us to make cross-state, cross-chamber, and over-time comparisons. 
\item In particular, our spatial mapping not only adds a much needed cross-sectional element to empirical work on legislative institutions, but also will allow scholars to exploit institutional variation in ways not previously possible. 
\item Identification of the models relies on the existence of bridge actors who cast votes (or make votelike decisions) in multiple settings. 
\item Given the limitations of using bridge legislators to link states, we use the Project Vote Smart National Political Awareness Test (NPAT), a survey of state and federal legislative candidates. 
\item In this article, we use Bayesian item-response theory models to estimate the spatial models (Clinton, Jackman, and Rivers 2004; Jackman 2000, 2004; Martin and Quinn 2002).4 We performed the same analysis with Poole–Rosenthal NOMINATE scores (Poole and Rosenthal 1991). The estimates of ideal points correlate extremely strongly across methods, which is to be expected given what we know about the performance of these two procedures in data-rich environments (Carroll et al. 2009; Clinton and Jackman 2009). 
\item Figure 7 shows the distributions of scores by party, pooled across time within states. One of our most striking findings is the tremendous variation in polarization across states. 
\item Figure 15 shows that polarization at the state legislative level is real, at least for the previous 15 years. Moreover, it reveals how much polarization varies across states. In comparison to Congress, the majority of state legislatures are less polarized, whereas 15 are actually more polarized. 
\item Beyond the methodological breakthrough, our article makes a substantive contribution by documenting many key regularities of party positioning and ideological conflict in the American states. First, despite strong nationalizing trends in American politics, political parties below the national level are quite heterogeneous. Although no Republicans in Congress are more liberal than the most conservative Democrats, we find that many states have Republican state legislative contingents that are more liberal than the Democratic caucuses of many states. Moderate partisans thrive at the state level, just as they languish at the national level. Second, although the low stakes, salience, and information in many state legislative elections would point to a lack of ideological responsiveness, we find that this appears not to be the case. In the aggregate, state legislative medians correlate highly with voter ideology measures. At a more disaggregated level, the ideal points of state legislators correlate highly with presidential vote in their districts. How legislative responsiveness can subsist in such inhospitable environments is a key question for future research.  
\item Finally, we are the first to systematically measure legislative polarization at the state level. 
\end{itemize}

\newpage

\item “Using roll call estimates to test models of politics”. JD Clinton - Annual Review of Political Science, 2012. 
\begin{itemize}
\item I focus my review on some issues that scholars working with roll calls should consider when analyzing and interpreting the resulting estimates. I focus on the analysis of roll calls, but many of the same considerations likely apply to using any observed behavior to measure participants’ preferences. 
\item Evaluating the predictions of a formal model using roll calls faces at least two difficulties. First, the strategic interactions being modeled may be responsible for only a small amount of the variation in the data. Second, the modeling decisions made when analyzing roll calls may make it difficult to correctly characterize the variation of theoretical interest. Unlike the preferences of formal models that are exogenous primitives (McCarty \& Meirowitz 2007), \textbf{the ideal point estimates produced from roll call analyses reflect the preferences members reveal in their behavior as interpreted through the application of a statistical model to an underlying model of individual choice}. Even if the variation predicted by the model is empirically discernible, the predictions of a formal model might still not be supported by roll call estimates if (a) the formal model is wrong, (b) the formal model is correct but a statistical model used to generate or evaluate the estimates is wrong, or (c) both the formal and statistical models are wrong. 
\item Producing ideal points requires applying a statistical model to a model of individual choice. The meaning of the recovered estimates therefore depends critically on the modeling decisions that are made. Moreover, interpreting what the roll call estimates imply about the nature of politics often, but certainly not always, involves using the estimates to assess predictions from yet another model—a model of the political process (the “ideal point consumption” problem). 
\item I focus on three aspects of the individual choice model that are common to prevalently used roll call estimators [i.e., the various flavors of NOMINATE (Poole \& Rosenthal 2007) and the Bayesian item response models of Clinton et al. 2004a, Martin \& Quinn 2002, and Bafumi et al. 2005]: the meaning of the estimated ideal point, the nature of legislators’ voting behavior, and the assumed voting error.  
\item What is Ideal Point Model? … Given a most-preferred outcome or position in the policy space, the model of individual choice in roll call analyses assumes that legislators vote for the closest expected alternative in every pairwise comparison. The model of individual choice assumes that only the relative distance between a legislator’s most-preferred policy and the two alternatives being considered is relevant for determining her vote.  
\item The author discusses several problems that may occur with this technique and some assumptions.  
\item The presence of voting error is absolutely critical for roll call analyses because only ordinal rankings are identified with perfect (i.e., errorless) spatial voting (Poole 2000, 2005). If the assumption of probabilistic voting error is violated in some legislatures other methods may be required (e.g., Rosenthal \& Voeten 2004).
\item Even if legislators vote probabilistically, however, \textbf{how the voting errors occur in the model of individual choice may matter}. Standard roll call estimators assume that legislators sometimes vote incorrectly despite perfectly knowing their ideal point and the location of the proposals being voted on. \textbf{The assumed voting error is therefore not attributable to uncertainty about the proposals being voted on or the ideal point that the legislator is attempting to implement.}  Instead, each legislator experiences an independent and identically distributed exogenous shock to her calculation of which alternative is closer to her ideal point on every vote.
\item Alternative specifications of voting error are certainly possible, but the literature has only briefly explored them. Ladha (1991), for example, presents a probabilistic voting model where legislators idiosyncratically and imperfectly perceive the proposal being voted on, and Lauderdale (2010) allows for heteroskedastic voting error.
\item The author uses the Agenda Setting Selection Model as an example to demonstrate how selection models can affect whether estimated ideal point estimates reflect true preferences, consider the agenda setter game of Romer \& Rosenthal (1978). Many prominent law-making models in political science can be interpreted as a variant of this game (see, e.g., Krehbiel 1996, Chiou \& Rothenberg 2003, Cox \& McCubbins 2005). 
\item As an illustration, I explore how the selection model and the amount of voting error affect the recovery of true preferences using roll calls. I use a simulation study to demonstrate the importance of the roll call selection model and I characterize how the effect depends on the amount of voting error that is assumed to be present in the data-generating process. To be clear, the investigation is intended only to illustrate how simulations might be used to better understand the properties of roll call estimators when applied to particular contexts. 
\item Londregan (2000a,b), for example, extends the spatial voting model to include valence considerations in the individual voting model to analyze legislators’ votes in Chile, and McCarty et al. (2001) modify the model of individual choice to allow for the possibility of party influence in the US House. 
\end{itemize}

\newpage

\item “Unpredictable Voters in Ideal Point Estimation” BE Lauderdale - Political Analysis, 2010 -  
\begin{itemize}
\item In Section 2 of this paper, I discuss several substantive sources of variation in legislators' responsiveness to the primary political axes, including particularistic constituency interests and idiosyncratic legislator preferences. 
\item I describe a Bayesian heteroskedastic ideal point estimator that can be either understood as a generalization of Jackman's (Jackman 2001) homoskedastic Bayesian estimator or a Bayesian implementation of Poole's QN estimator (Poole 2001). I use Monte Carlo simulation to assess how the number of legislators, the number of roll call votes, and the degree of true heteroskedasticity influence the degree to which the data-generating at can be recovered. 
\item I find the heteroskedastic estimator outperforms the equivalent homo skedastic estimator for recovering ideal points, not only when there is substantial hetero skedasticity in the data generating process but even when the data-generating process is homoskedastic.
\item I use a series of examples to show how the legislator-specific variance 07 itself can help refine the summaries of legislative voting patterns provided by ideal point estimation. The heteroskedastic ideal point estimator explicitly measures which legislators are idiosyncratic in their voting. 
\item Bayesian Heteroskedastic Ideal Point Estimator: Some estimators are based on logistic disturbances (Poole and Rosenthal 1985; Bafumi et al. 2005), some on uniform disturbances (Heckman and Snyder 1997), and some on normal disturbances (Jackman 2001; Poole 2001). The quadratic loss, normal disturbance model has become especially popular in recent years, so I take that parametric form as my point of departure. 
\item If the heteroskedastic estimator is to prove useful, it should have two properties. First, it should perform better than the homoskedastic model at recovering ideal points from roll call data generated by a heteroskedastic process. Ideally, it should perform no worse when the data-generating process is actually homoskedastic. Second, it should recover the relative values of “phi (i)” (heteroskedastic parameter) with sufficient precision in realistic data sets to make meaningful inferences. In the only previous work that estimates a legislator-specific variance parameter, Poole (2001) reports Monte Carlo simulation results for the recovery of the ideal points from generated data, but does not compare homoskedastic and heteroskedastic estimators or evaluate success at recovering legislator-specific variances.
\item I found that the heteroskedastic estimator slightly outperforms the homoskedastic estimator at recovering the relative positions of ideal points, even when the true data-generating process is homoskedastic. 
\item As Fig. 1 shows, using the heteroskedastic instead of the homoskedastic model does not change estimated ideal points for most legislators. However, the legislators with large estimated “phi(i)” are estimated to have more extreme ideal points under the heteroskedastic estimator. This reflects a substantive advantage of the heteroskedastic model: it recognizes that not all deviations from the pole of extreme partisan voting reflect moderation, some reflect extreme positions. 
\item The homoskedastic model assumes that all individuals make the same magnitude voting errors, so when, for example, a democrat senator votes differently from ideologically similar senators, they are shifted towards the center, even if the reasons they deviated had nothing to do with the primary axis. The heteroskedastic model yields a more nuanced interpretation of the roll call data. 
\item The heteroskedastic estimator identifies that the individuals deviations are unrelated to the individual's primary axis position, because they do not match the deviations that most moderate indiciduals (from the same ideological party) make.
\item Just as heteroskedasticity can capture motivations that cannot be captured by a small number of spatial dimensions, it can also capture dimensions that were simply omitted. Examining legislators with large “phi(i)” (heteroskedastic parameter) is analogous to examining units with large residuals in a regression model. If many legislators who are difficult to predict have some shared substantive attribute, it is likely that adding another dimension to the model is justified. This diagnostic function of the heteroskedastic model os quite useful when one is interested in a high dimentional legislature like the EU parlament. Hix, Noury and Roland (2006, 2007) have demostrated that the EU Parlament can be effectively modeled using spatial modeling techniques. 
\end{itemize}

\newpage

\item “The Structure of Utility in Spatial Models of Voting”. Royce Carroll, Jeffrey B. Lewis, James Lo, Keith T. Poole, Howard Rosenthal. American Journal of Political Science, 2013   
\begin{itemize}
\item In this article, we first consider a model in which legislators' utility functions are allowed to be a mixture of the two most commonly assumed utility functions: the quadratic function and the Gaussian function assumed by NOMINATE.
\item Typically, the central objective in fitting empirical models of spatial voting is to estimate the ideal point X of each actor. In this article, we focus on the estimation of features of the utility function F. The central object of this research is to prove the limit of what it is possible to learn about F even conditional on the usual (strong) assumptions about the distribution of the idiosyncratic shocks. 
\item This is a one-dimensional model, because in a multidimensional model identification problems could appear.  
\item The paper begins by comparing a Gaussian utility representation with a quadratic one.  
\item (I didn’t go further into the details of the paper because it is about unidimensionality) 
\end{itemize}

\newpage

\item “Fast Estimation of Ideal Points with Massive Data”. K Imai, J Lo, J Olmsted - American Political Science Review, 2016    
\begin{itemize}
\item To overcome the resulting computational challenges, we propose fast estimation methods for ideal points with massive data. We derive the expectation-maximization (EM) algorithms to estimate the standard ideal point model with binary, ordinal, and continuous outcome variables. 
\item In cases where a standard Markov chain Monte Carlo algorithm would require several days to compute ideal points, the proposed algorithm can produce essentially identical estimates within minutes. 
\item Markov chain Monte Carlo (MCMC) algorithms can be prohibitively slow when applied to large data sets. As a result, researchers are often unable to estimate 
\item Their models using the entire data and are forced to adopt various shortcuts and compromises. For example, Shor and McCarty (2011) fit their model in multiple steps using subsets of the data whereas Bailey (2007) resorts to a simpler parametric dynamic model in order to reduce computational costs (p. 441) (see also Bailey 2013). Since a massive data set implies a large number of parameters under these models, the convergence of MCMC algorithms also becomes difficult to assess. Bafumi and Herron (2010), for example, express a concern about the convergence of ideal points for voters (footnote 24). 
\item In this article, we propose a fast estimation method for ideal points with massive data. Specifically, we develop the Expectation-Maximization (EM) algorithms (Dempster, Laird, and Rubin 1977) that either exactly or approximately maximize the posterior distribution under various ideal point models. The main advantage of EM algorithms is that they can dramatically reduce computational time. 
\item We begin by deriving the EM algorithm for the standard Bayesian ideal point model of Clinton, Jackman, and Rivers (2004). We show that the proposed algorithm produces ideal point estimates which are essentially identical to those from other existing methods. 
\item We implement the proposed algorithms via an opensource R package, \textbf{emIRT (Imai, Lo, and Olmsted 2015)}, so that others can apply them to their own research. 
\item Finally, an important and well-known drawback of these EM algorithms is that they do not produce uncertainty estimates such as standard errors. In contrast, the MCMC algorithms are designed to fully characterize the posterior, enabling the computation of uncertainty measures for virtually any quantities of interest. 
\item To address this problem, we apply the parametric bootstrap approach of Lewis and Poole (2004) (see also Carroll et al. 2009). Although this obviously increases the computational cost of the proposed approach, the proposed EM algorithms still scale much better than the existing alternatives. 
\item The authors test the EM model versus different known model of MCMC and present their results along with an empirical application. 
\end{itemize}

\newpage

\item “Lobbying, Campaign Contributions and Political Competition” J Rivas - 2017

\item (Question: Is there anything about uncertainty in this paper?)
\item Answer: There is, the second and third bullet point has an overview of the way the paper treats uncertainty.

\begin{itemize}
\item The purpose of this paper is to study how lobbying affects elections where candidates that are running for office can benefit from the funds offered by the lobbies in an exchange for adopting a political position favorable to these lobbies but different from that of the median voter.
\item we show that uncertainty about the voter’s behavior will increase polarization only for the party that gets offered the contract from the higher valuation lobby while it will decrease the polarization of the other party. This is because as uncertainty about the voter goes up adopting a more polarized position becomes less risky. The high valuation lobby takes advantage of this by asking its party for a more polarized position while the low valuation lobby instead allows its party to become less polarized to be in a better position against the now more polarized opposing party.
\item we obtain that uncertainty about the voter also increases the relative spending of the party associated with the high valuation lobby. This is because, as discussed in the previous paragraph, increasing uncertainty increases the polarization of the party associated with the high valuation lobby, which implies that now this lobby has to compensate its party by offering more funds proportional to the funds the other lobby offers.
\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
\item The model described above (previous paragraph in the paper) leads to a two stage four player Bayesian game where in the first stage each lobby simultaneously offers a contract to a different party, then in the second stage parties simultaneously and without knowing the contract offered to the other party decide whether to accept or to reject the contract. In a final stage which party wins the election is declared and its policy position implemented. We solve this game by finding its unique equilibrium and then we proceed to study how the different parameters in the model affect parties’ polarization, campaign spending, and voter’s welfare. 
\item In our results about polarization we find, among others, that the lobby that has a higher stake in the election (the high valuation lobby henceforth) forces its party to adopt a more polarized position than the other party. Although a more polarized position decreases voter support, this can be partly compensated by a higher campaign spending, which the high valuation lobby is willing to fund. 
\item In terms of campaign spending, we find that the higher valuation lobby will contribute more to campaign spending. Furthermore, we also find that the salience of the election decreases total campaign spending but increases the relative campaign spending of the party associated with the high valuation lobby (relative to the other party’s campaign spending). 
\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
\item This is a Bayesian game model, do not use data, only the Bayesian Equilibrium solution concept to characterize the model.

\end{itemize}

\newpage

\item “Incumbent Competition, Decision-making, and Policy Choice” AM Go - 2019

\begin{itemize}
\item We approach the lobbying process as one where cash-for-favour exchanges occur as a means to obtain access to legislators. The model takes into account the \textbf{degree of uncertainty} on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies. Instead, we adopt a simultaneous lobbying structure to capture how lobbying proceeds behind closed doors.
\item In this paper, we find that the degree of uncertainty of legislator preferences, given by the length of the bias intervals, directly affects the bidding strategy of lobbyists. At low levels of uncertainty, lobbyists bid aggressively. The bias of the legislator is not high enough to risk losing the legislator’s support. 
\item We explore \textbf{uncertainty} by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al. (2006).  However, uncertainty is rarely explored on its own. We redirect the focus of the paper to lobbyist interactions over one non-strategic legislator. We remove the dimension of budget allocation and instead assume that the lobbyists are willing to pay at most the value of the legislator support. The results show that uncertainty on its own can provide some good insights on how lobbying unfolds. 
\item We also include a measure of the legislator’s level of integrity. As with Che and Gale (1998), the politician does not hold an open sale for his support given restrictions on vote buying. We can think about this from the perspective of a reputation conscious politician. A reputation conscious politician may not want to be associated with more than one lobbying group for an issue, and would like to be viewed as consistent and honest by her constituents. The more controversial an issue is, the more likely it is for the politician’s threshold to be higher.

\end{itemize}

\newpage

\item “Multiple Ideal Points: Revealed Preferences in Different Domains” S Moser, A Rodriguez, CL Lofland - 2020
\begin{itemize}
\item We extend classical ideal point estimation to allow voters to have different preferences when voting in different domains – for example when voting on agricultural policy than when voting on defense policy. Our scaling procedure results in estimated ideal points on a common scale. As a result, we are able to directly compare a member’s revealed preferences across different domains of voting (different sets of motions) to assess if, for example, a member votes more conservatively on agriculture motions than on defense.  
\item The key novelty is to estimate rather than assume the identity of “stayers” – voters whose revealed preference is constant across votes. There are several methodological advantages to our approach. First, our model allows for testing sharp-hypotheses. Second, the methodology developed can be understood as a kind of partial-pooling model for IRT scaling, resulting in less uncertainty of estimates. Related, our estimation method provides a principled and unified approach to the issue of “granulatity” (i.e. the level of aggregation) in the analysis of roll-call data (Crespin \& Rohde, 2010; Roberts, Smith, \& Haptonstahl, 2016). 
\item The main issue in this line of work is how to ensure that the preferences of these different groups of political actors are indeed measured on a common scale. While each group of actors can be scaled independently using, e.g., NOMINATE (Poole \& Rosenthal, 1991; Poole \& Rosenthal, 2011) or IDEAL (Clinton, Jackman, \& Rivers, 2004), ensuring that the resulting scales are comparable is a delicate matter. 
\item We develop a novel technique to estimate legislators’ revealed preferences in different domains of voting on a common scale. In our approach, votes are broken into predetermined groups and legislators are, in principle, allowed to have different preferences for each group. A hierarchical Bayesian model that uses clustering priors is then used to shrink the number of distinct positions that a legislators might have. When all votes belong to the same group, or all legislators have identical positions in all issues, our model reduces to a standard Bayesian item response theory (IRT) model (Albert \& Chib, 1993; Clinton et al., 2004). Otherwise, our approach is a strict generalization of it that relaxes the usual assumption that all votes are “equal” (for purposes of estimating latent traits from roll-call votes). 
\item In addition to avoiding ex ante assumptions about allowable changes in revealed preferences, our approach has several other methodological advantages. First, our estimation approach results in a common scale, which allows us to properly compare the preferences of individuals across voting domains. In particular, our approach allows for the direct comparison and formal hypothesis tests across domains. For example, we may now formally test claims of the form “preferences in domain A are different than those in domain B” at the individual and group level.  
\item Second, unlike most other approaches in the literature, ours allows us to make statements about the consistency of preferences at the individual-level, the group-level and at the chamber level. This is a direct consequence of the fact that our model estimates the identify of members with consistent preferences in all domains.  
\item Third, because it relies on a joint model across all voting domains, the methodology developed here is a kind of “partial pooling” model for roll-call votes / IRT scaling, resulting in more precise estimates of preferences in each voting domain (a feature analogous to the “information borrowing” found in multi-level models).  
\item Finally, since our model uses a hierarchical Bayesian prior, it automatically adjusts for the large number of comparisons involved in the analysis (Scott \& Berger, 2006, 2010). 
\item The dimensionality of the voting is simply the number of latent traits required to accurately model legislators’ voting behavior. Hence, from a technical point of view, choosing the dimensionality of the policy space is essentially a model selection problem in which we aim to balance model fit with model complexity, and the dimensions in the latent space of a spatial voting model do not need not correspond to any politically relevant substantive issues. 
\item Our model corresponds to a traditional spatial voting model (as would be expected). However, if there is a subset of legislators whose voting pattern on certain groups of votes cannot be well explained through a common set of linear combinations of the latent traits, our model will introduce an additional set of legislator-specific ideal points. In this way, our model allows us to investigate the interrelation between substantive issues and the intrinsic dimensionality of the policy space. 
\item Our approach may the thought of as an intermediate compromise to the determination of “substantively relevant dimensions” in the language of Benoit and Laver (2012), having both inductive and deductive components. Namely, we start with (strong) priors on the structure of the conceptual space (by placing each vote in exactly one category we are effective putting a prior of 100\% that a vote v is of type g). And then inductively estimate the “. . . bundles of particular salient policy issues on which agents’ preferences are inter-correlated” (Benoit \& Laver, 2012, p. 205). This interpretation requires the vote-categories to be (at least prima face) related to dimensions spanning the conceptual space (Benoit \& Laver, 2012). 
\item To facilitate computation, the authors introduce auxiliary random variables.
\item Estimation of the model parameters is performed using a Markov chain Monte Carlo (MCMC) algorithm (Robert \& Casella, 2005). 
\item We illustrate the model through an analysis of preferences in different policy domains using recorded votes from the 97th to 114th U.S. House of Representatives (1981 - 2016). Motions brought to a vote in the U.S. Congress differ thematically by substantive issue (e.g., the economy, environment, criminal justice, etc.). We use the Policy Agendas Project main topic coding to categorize roll call votes by issue area (Adler \& Wilkerson, 2017; Policy Agendas Project, 2017). This taxonomy, which consists of 20 mutually exclusive major topics (e.g., Macroeconomics, Health, Environment, etc.), has been used to study legislative agendas (Baumgartner \& Jones, 1993) and attention (Jones \& Baumgartner, 2005), among other matters. 
\item We focus on the PAP categorization for two reasons. First, the application to issue areas illustrates the novel technical contributions of the model, namely (1) comparable revealed preferences across issues and (2) estimates of legislator-specific dimensionality. Second, as argued in Section 3, applying the model to votes grouped by issue area is relevant to the literature on dimensionality (Aldrich et al., 2014; Roberts et al., 2016; Talbert \& Potoski, 2002) by providing issue-specific revealed preference and an estimate of individual consistency – the posterior probably that a member has the same revealed preference in each issue area.
\item One of the key contributions of our approach is its ability to provide micro-level information about the behavior of specific legislators. 
\item Our model not only provides information about the identity of movers, but also about the nature of the issues in which they are movers, and the direction of preference changes. Similar to the procedure we used to define issue-specific ASFs, start by defining a member’s basic ideal point as their ideal point in their base cluster, and say a member has deviant preferences – preferences different than their basic ideal point – on issues not in their base cluster.
\item Figure 7 compares member’s basic ideal point against the ideal points associated with four PAP issues for legislators in the 111th House (Banking and Finance, Civil Rights, Government Operations and Macroeconomics). More specifically, these ternary
plots show the probability that a member’s ideal point in a specific issue is either left of, right of, or the same as their basic ideal point.
\item We compare our illustration to Gerrish and Blei (2012b). While a direct comparison is not possible (as there voters have a main preference and issue-specific deviations), some of the insights provided by both models are similar. Gerrish and Blei (2012b) find votes on appropriations, finance, energy and public lands to have the most movement (issues for which issue-specific preferences deviate the most from members’ base preferences, roughly akin to our deviant issues). Likewise they find issues with the lease amount of movement to be defence and military, education and foreign policy. Looking at the 111th House in particular, they find members preferences on Civil Rights to exhibit very little deviance from their base preference, which is somewhat different from our findings. We both, however, do find a considerable amount of movement/ deviance in the domain of Government Operations.
\item The author claimed that their model is less noicy than previous mocels in the literature, Figure 8. This is because their joint model borrows information across voting domains to estimate the ideal points, leading to lower \textbf{uncertainty}.
\item A key issue to appreciate here (in Figure 8) is that the uncertainty associated with the estimates of ranks varies drastically. Generally speaking, the uncertainty associated with the rank of legislators that are close to the median voter of their own party tends to be much larger than the uncertainty associated with the ranks of centrist or radical legislators (Figure 4). Similarly, the uncertainty in the estimates of the ranks can vary substantially between parties (in the case of the 111th, the uncertainty associated with the
ranks of Democrats is much larger than that of Republicans). As a consequence, changes in ranks for centrist, partisans and Republicans are easier to identify.
\item (Conclusion of the paper) We developed a novel Bayesian model extending classical ideal point estimation methods to enable the joint estimation of voters’ preferences across different domains of voting. The model places the resulting estimates of a member’s ideal point on each of K groups of votes on a common scale so that, for example, the revealed preferences of a member when voting on agriculture can be compared to their preferences on defense. The key innovation is to estimate, rather than assume, the identity of full stayers – voters with the same ideal point in all domains. 
\item The paper end with some applications and future research topics in which their model can be implemented.

\end{itemize}

\newpage

\item “Nonparametric ideal-point estimation and inference” A Tahk - Political Analysis, 2018 
\begin{itemize}
\item Existing approaches to estimating ideal points offer no method for consistent estimation or inference without relying on strong parametric assumptions. In this paper, I introduce a nonparametric approach to ideal point estimation and inference that goes beyond these limitations. I show that some inferences about the relative positions of two pairs of legislators can be made with minimal assumptions.  
\item The bulk of these studies have used parametric ideal-point models that specify particular functional forms for the utility functions and error distributions. It is well known that the choice of parametric assumptions can affect the estimates and inferences derived from data. This has been demonstrated in the ideal-point context (e.g., Ho and Quinn 2010; Krehbiel and Peskowitz 2015) and has led studies to different conclusions on questions such as the dimensionality of congressional voting (see Poole and Rosenthal 1991; Heckman and Snyder 1997). 
\item The only alternative approach has been to use Optimal Classification (OC), a model-free estimation method introduced by Poole (2000). Because OC “is not a statistical model” (Poole 2000, p. 211), statistical inference is not possible. OC is also not a consistent estimator of the rank order of the ideal points under quadratic utility. Thus, for many purposes, OC cannot be used in place of a parametric model. 
\item The main contribution of this paper is to introduce a method for ideal-point inference and estimation under much weaker assumptions than previous approaches. It requires no parametric assumptions, making it the first approach to nonparametric ideal-point inference. Its estimates of the rank order of ideal points are also consistent under the same weak, nonparametric assumptions. 
\item The model consists of two key assumptions: unidimensionality and concave utility

\item (given the key assumptions, I didn’t go further into the paper)

\end{itemize}

\newpage

\item “Measurement Uncertainty in Spatial Models: A Bayesian Dynamic Measurement Model” S Juhl - Political Analysis, 2019 
\begin{itemize}
\item The implicit assumption of perfectly measured covariates made by spatial econometric models creates a disjuncture between theory and empirics and threatens the validity of the findings. 
\item This paper contributes to the literature by investigating how measurement uncertainty affects the substantial inferences about parties’ interrelatedness.  
\item To this end, I develop a Bayesian dynamic item response (IRT) model with an evolution function that explicitly fits theoretical propositions. I model the ideological evolution of each party as a spatio-temporal autoregressive process and allow parties to strategically respond to movements made by their political competitors (e.g., Franzese and Hays 2007, 2008; Hays, Kachi, and Franzese 2010). 
\item This article demonstrates that imperfect measures can severely affect the results. Hence, accounting for measurement uncertainty is not merely a methodological concern but can lead to very different inferences. 
\item A key feature of the empirical analyses mentioned above is that the covariates—the parties’ positions—are latent quantities and therefore not directly observable.  
\item As a consequence, two major obstacles arise: first, comparing party positions over time is difficult because they need to be located in a common space. Empirical research widely acknowledges this problem and presents various solutions to it (e.g., Poole and Rosenthal 1991; Martin and Quinn 2002; Herron 2004; Bailey 2007; Park 2011; Shor and McCarty 2011; König, Marbach, and Osnabrügge 2013). Second, latent variables are, by definition, unobservable and, as a result, afflicted with a quantifiable amount of uncertainty. Even the most sophisticated measures are subject to random measurement error which can distort the substantive inferences as numerous simulation studies already demonstrate (e.g., Fuller 1987; McAvoy 1998; Blackwell, Honaker, and King 2017; Loken and Gelman 2017) 
\item I combine a predictive spatial econometric model with a dynamic measurement model for the latent quantities—parties’ ideological positions. I illustrate how the simultaneous estimation of party positions and their spatial dependencies avoids the assumption of perfectly measured regressors and presents an opportunity to directly incorporate theoretical predictions about parties’ reciprocal dependencies in empirical models.

\end{itemize}

\newpage

\item “Estimating ideal points from roll-call data: explore principal components analysis, especially for more than one dimension?” RF Potthoff - Social Sciences, 2018 
\begin{itemize}
\item The two main existing avenues for estimation of ideal points from roll-call data are the Poole-Rosenthal (P-R) approach and a Bayesian approach (CJR). We examine both of them critically, particularly for more than one dimension, before turning to detailed study of principal components analysis, a technique that has rarely seen use for ideal-point estimation but offers much promise. 
\item The paper works as a comparison between the (P-R), CJR and the PCA (principal components analysis) model, been the latest the one the author is advocating for.  
\item In two or more dimensions (there is no problem in one dimension), the gravest flaw of both P-R and CJR is their nonidentifiability of ideal points—nonidentifiability that goes beyond the simple indefiniteness of location, scale, and orientation. Unlimited numbers of transformations (ones that do not just change location or scale) produce shifts to new sets of ideal points that are substantively different but leave the maximized log likelihood unchanged. Troubles escalate as the number of dimensions increases. 
\item Recognizing the nonidentifiability of CJR in two dimensions, Jackman (2001) sought to circumvent it by assigning certain priors to two roll calls chosen to serve as second- dimension anchors. However, this patch seems arbitrary and subjective. 
\item For two or more dimensions, P-R has far more parameters than CJR (thus entailing worse identifiability troubles) yet even CJR itself lacks identifiability. 
\item As will be seen shortly, PCA does not have any of the characteristics that have just been described. It does not suffer from nonidentifiability, it enjoys the orthogonality property, and its ideal-point estimates for a given dimension do not change when the number of dimensions changes. Several further modeling issues, in the form of arbitrary parameter constraints or identification assumptions, cause trouble for P-R. None of them apply to either CJR or PCA. 
\item The author then explains how to use the PCA model to obtain ideal points with roll call data.  
\item PCA provides no means to assess uncertainty. CJR uses Bayesian methodology to estimate uncertainty for estimates of ideal points and other parameters. Lewis and Poole (2004) proposed parametric-bootstrap standard errors to handle uncertainty assessment for P-R. Both the P-R and CJR techniques, however, rely on an ungrounded assumption of (mutual) conditional independence of a legislator’s votes given the ideal points and roll-call parameters. Although for PCA one may try to find complex standard-error formulas that steer clear of that assumption, it appears that, whether for P-R, CJR, or PCA, any \textbf{effort to assess uncertainty is fraught with impediments}. 
\item Unlike P-R and CJR, PCA does not use a utility function in deriving its model. However, in its theory it is still based on a spatial voting model, just as P-R and CJR are. 
\item (conclusion) for two or more dimensions, whose study may be fruitful for varied situations (e.g., for certain locales and time periods or certain subsets of votes or legislators), the relative benefits of PCA are especially striking and should suffice to make PCA a preeminent contender.

\end{itemize}

\newpage

\item "The geometry of multidimensional quadratic utility in models of parliamentary roll call voting" KT Poole - Political Analysis, 2001
\begin{itemize}
\item The purpose of this paper is to show how the geometry of the quadratic utility function in the standard spatial model of choice can be exploited to estimate a model of parliamentary roll call voting.
\item In a standard spatial model of parliamentary roll call voting, the legislator votes for the policy outcome corresponding to Yea if her utility for Yea is greater than her utility for Nay. The voting decision of the legislator is modeled as a function of the difference between these two utilities. The difference between two quadratic utilities has a simple geometric interpretation that can be exploited to estimate legislator ideal points and roll call parameters in a standard framework where the stochastic portion of the utility function is normally distributed.
\item To reiterate, if voting is perfect, that is, sincere and without error, then in one dimension the legislator ideal points and the roll call midpoints are identified only up to a joint rank ordering. In more than one dimension, legislators are identified up to regions in the space (polytopes) and roll calls are identified up to cone-shaped regions containing the normal vectors and line segments on the normal vectors for the midpoints. These limits on identifica tion arise because the data are simply Yea and Nay. If legislators could report "thermometer scores" for the alternatives, then the perfect case would have an exact solution.
\item With quadratic utility, only the location of the cutting hyperplane and the signed distance between the Yea and the Nay alternatives can be estimated. In this framework, there is an infinite number of pairs of Yea and Nay points that produce the same hyperplane and signed distance. 
\item In contrast, an advantage to the normal distribution deterministic utility function used in NOMINATE is that it introduces enough nonlinearities in the utility differences to identify actual positions of the Yea and Nay alternatives. These points have to be used with some caution (Poole and Rosenthal 1997, Appendix A) but it is important to note that the use of the quadratic utility function precludes the estimation of specific Yea and Nay points.
\item Turning to the stochastic portion of the utility function stated in Eq. (3), three probability distributions have been used to model the error: the normal (Ladha 1991; Londregan 2000), uniform (Heckman and Snyder 1997), and logit (Poole and Rosenthal 1997). The normal is clearly the best from both a theoretical and a behavioral standpoint. 
\item From a statistical standpoint, given the difference between the two random errors, the standard assumptions are that they are a random sample (independent and identically distributed random variables) from a known distribution. Hence, it is therefore easy to write down the probability distribution of the difference.
\item  From a behavioral standpoint, it seems sensible to assume that the distributions of the diffrence of the errors are symmetric and unimodal and that they are uncorrelated. The normal distribution is the only one of the three distributions to satisfy all these criteria.
\item A further difficulty with the approaches taken both by Heckman and Snyder and by Poole and Rosenthal is that they assume that the error variance is homoskedastic. A more realistic assumption is that the error variance varies across the roll call votes and across the legislators. For the roll calls, it is impossible to distinguish between the underlying unknown error variance and the distance between the Yea and the Nay alternatives (Ladha 1991; Londregan 2000). The intuition behind this is straightforward. As the distance between the Yea and the Nay alternatives increases, the easier it is for legislators to distinguish between the two policy outcomes and the less likely it is that they make an error. Conversely, if the Yea and Nay alternatives are very close together, then the utility difference is small and it is more likely that voting errors occur. Increasing/decreasing the distance is equivalent to decreasing/increasing the variance of the underlying error
\item The approach developed in Section 5 allows the error to be heteroskedastic. The optimal classification algorithm developed by Poole (2000) can be used to obtain excellent estimates for the legislator points, the jc, 's, the roll call normal vectors, the nj's, and the cutpoints, the m/s.
\item The multidimensional quadratic utility model (QN) can be efficiently estimated in four steps. Within each step the approach taken is to estimate one parameter at a time with all the remaining parameters being held fixed. That is, the maximum of the likelihood function is found for the parameter being estimated conditioned on all the remaining parameters being held fixed. The algorithm always moves uphill in a city block-like fashion. At convergence, every parameter is at a maximum conditioned on all the remaining parameters being held fixed. Convergence to the true global maximum cannot be guaranteed but the conditional global maximum that the algorithm reaches is almost certainly close to the overall global maximum. Although this is not an EM algorithm, it is similar in spirit because the log likelihood always increases from one step to the next.
\item Section 6 compares the Monte Carlo test with other scaling procedures. 
\item Given the computational difficulties in more than one dimension, an attractive alternative to obtain standard errors is a bootstrap analysis. 
\item Because obtaining good-quality standard errors for the parame ters of spatial models of parliamentary voting is very difficult, embedding the geometry in the innovative MCMC work of Jackman (2000) would produce an alternative method of assessing uncertainty in the multidimensional spatial model.
\item The purpose of this paper was to show a method of estimating a multidimensional spatial voting model with quadratic utility and normally distributed errors. The geometry of the multidimensional quadratic utility function can be exploited to estimate legislator ideal points and roll call cutting planes in a standard framework where the stochastic portion of the utility function is normally distributed. The QN scaling procedure is quite stable and does a good job in recovering the true legislator configuration in Monte Carlo tests. 
\item The QN scaling procedure produces legislator configurations that are very similar to those produced by other scaling algorithms. A unique feature of QN is that it allows the variance of the error to vary across legislators. Although the legislator error variances are related to the level of correct classification, more than just correct classification is at work.

\end{itemize}

\end{enumerate}

\end{document}

### 2020-07-02 Literature_review.tex
Original Literature Review without comments

@@
 In comparison to Congress, the majority of state legislatures are less polarized, whereas 15 are actually more polarized.
-\item Beyond the methodological breakthrough, our article makes a substantive contribution by documenting many key regularities of party positioning and ideological conflict in the American states.
+\item (Conclusion) Beyond the methodological breakthrough, our article makes a substantive contribution by documenting many key regularities of party positioning and ideological conflict in the American states.
 First, despite strong nationalizing trends in American politics, political parties below the national level are quite heterogeneous.
@@
 \item “Using roll call estimates to test models of politics”. JD Clinton - Annual Review of Political Science, 2012. 
+(This paper is very good initial step to understand this topic, very clear explanations of the models, uses and problems)  
 \begin{itemize}
@@
 Second, the modeling decisions made when analyzing roll calls may make it difficult to correctly characterize the variation of theoretical interest.
-Unlike the preferences of formal models that are exogenous primitives (McCarty \& Meirowitz 2007), \textbf{the ideal point estimates produced from roll call analyses reflect the preferences members reveal in their behavior as interpreted through the application of a statistical model to an underlying model of individual choice}.
+Unlike the preferences of formal models that are exogenous primitives (McCarty \& Meirowitz 2007), the ideal point estimates produced from roll call analyses reflect the preferences members reveal in their behavior as interpreted through the application of a statistical model to an underlying model of individual choice.
 Even if the variation predicted by the model is empirically discernible, the predictions of a formal model might still not be supported by roll call estimates if (a) the formal model is wrong, (b) the formal model is correct but a statistical model used to generate or evaluate the estimates is wrong, or (c) both the formal and statistical models are wrong.
@@
 \item The author discusses several problems that may occur with this technique and some assumptions.  
-\item The presence of voting error is absolutely critical for roll call analyses because only ordinal rankings are identified with perfect (i.e., errorless) spatial voting (Poole 2000, 2005).
-If the assumption of probabilistic voting error is violated in some legislatures other methods may be required (e.g., Rosenthal \& Voeten 2004).
-\item Even if legislators vote probabilistically, however, \textbf{how the voting errors occur in the model of individual choice may matter}.
+\item Even if legislators vote probabilistically, however, how the voting errors occur in the model of individual choice may matter.
 Standard roll call estimators assume that legislators sometimes vote incorrectly despite perfectly knowing their ideal point and the location of the proposals being voted on.
-\textbf{The assumed voting error is therefore not attributable to uncertainty about the proposals being voted on or the ideal point that the legislator is attempting to implement.}  Instead, each legislator experiences an independent and identically distributed exogenous shock to her calculation of which alternative is closer to her ideal point on every vote.
-\item Alternative specifications of voting error are certainly possible, but the literature has only briefly explored them.
-Ladha (1991), for example, presents a probabilistic voting model where legislators idiosyncratically and imperfectly perceive the proposal being voted on, and Lauderdale (2010) allows for heteroskedastic voting error.
+The assumed voting error is therefore not attributable to uncertainty about the proposals being voted on or the ideal point that the legislator is attempting to implement.
+Instead, each legislator experiences an independent and identically distributed exogenous shock to her calculation of which alternative is closer to her ideal point on every vote.
 \item The author uses the Agenda Setting Selection Model as an example to demonstrate how selection models can affect whether estimated ideal point estimates reflect true preferences, consider the agenda setter game of Romer \& Rosenthal (1978).
 Many prominent law-making models in political science can be interpreted as a variant of this game (see, e.g., Krehbiel 1996, Chiou \& Rothenberg 2003, Cox \& McCubbins 2005).
-\item As an illustration, I explore how the selection model and the amount of voting error affect the recovery of true preferences using roll calls.
-I use a simulation study to demonstrate the importance of the roll call selection model and I characterize how the effect depends on the amount of voting error that is assumed to be present in the data-generating process.
-To be clear, the investigation is intended only to illustrate how simulations might be used to better understand the properties of roll call estimators when applied to particular contexts.
 \item Londregan (2000a,b), for example, extends the spatial voting model to include valence considerations in the individual voting model to analyze legislators’ votes in Chile, and McCarty et al.
@@
 In the only previous work that estimates a legislator-specific variance parameter, Poole (2001) reports Monte Carlo simulation results for the recovery of the ideal points from generated data, but does not compare homoskedastic and heteroskedastic estimators or evaluate success at recovering legislator-specific variances.
-\item I found that the heteroskedastic estimator slightly outperforms the homoskedastic estimator at recovering the relative positions of ideal points, even when the true data-generating process is homoskedastic.
+\item For the following Monte Carlo simulations, I begin by generating profiles of data generating parameters.
+I draw legislator ideal points xh ocj, and Pj from their prior distributions and 1/”phi” from a uniform distribution U(l - d, 1 + S).
+I simulate data with 3 = 0, 0.25, 0.5.
+The highest value of S approximates estimates from recent sessions of the U.S.
+House.
+I also vary the number of legislators n and the number of roll call votes m across values of 10, 32,100, and 320.
+For each of the 48 intersections of these parameters, I simulate 50 roll call matrices.
+I then compute mean posterior estimates for x and o* using both the homoskedastic estimator and the heteroskedastic estimator (both implemented in MCMCpack, Martin and Quinn 2009) on each simulated roll call matrix.
+\item The heteroskedastic estimator slightly outperforms the homoskedastic estimator at recovering the relative positions of ideal points, even when the true data-generating process is homoskedastic. 
 \item As Fig.
@@
 This reflects a substantive advantage of the heteroskedastic model: it recognizes that not all deviations from the pole of extreme partisan voting reflect moderation, some reflect extreme positions.
-\item The homoskedastic model assumes that all individuals make the same magnitude voting errors, so when, for example, a democrat senator votes differently from ideologically similar senators, they are shifted towards the center, even if the reasons they deviated had nothing to do with the primary axis.
-The heteroskedastic model yields a more nuanced interpretation of the roll call data.
-\item The heteroskedastic estimator identifies that the individuals deviations are unrelated to the individual's primary axis position, because they do not match the deviations that most moderate indiciduals (from the same ideological party) make.
 \item Just as heteroskedasticity can capture motivations that cannot be captured by a small number of spatial dimensions, it can also capture dimensions that were simply omitted.
@@
 If many legislators who are difficult to predict have some shared substantive attribute, it is likely that adding another dimension to the model is justified.
-This diagnostic function of the heteroskedastic model os quite useful when one is interested in a high dimentional legislature like the EU parlament.
-Hix, Noury and Roland (2006, 2007) have demostrated that the EU Parlament can be effectively modeled using spatial modeling techniques.
 \end{itemize}
@@
 \item “Lobbying, Campaign Contributions and Political Competition” J Rivas - 2017   
-
-\item (Question: Is there anything about uncertainty in this paper?)
-\item Answer: There is, the second and third bullet point has an overview of the way the paper treats uncertainty.
-
 \begin{itemize}
 \item The purpose of this paper is to study how lobbying affects elections where candidates that are running for office can benefit from the funds offered by the lobbies in an exchange for adopting a political position favorable to these lobbies but different from that of the median voter.
-\item we show that uncertainty about the voter’s behavior will increase polarization only for the party that gets offered the contract from the higher valuation lobby while it will decrease the polarization of the other party.
-This is because as uncertainty about the voter goes up adopting a more polarized position becomes less risky.
-The high valuation lobby takes advantage of this by asking its party for a more polarized position while the low valuation lobby instead allows its party to become less polarized to be in a better position against the now more polarized opposing party.
-\item we obtain that uncertainty about the voter also increases the relative spending of the party associated with the high valuation lobby.
-This is because, as discussed in the previous paragraph, increasing uncertainty increases the polarization of the party associated with the high valuation lobby, which implies that now this lobby has to compensate its party by offering more funds proportional to the funds the other lobby offers.
-\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
 \item The model described above (previous paragraph in the paper) leads to a two stage four player Bayesian game where in the first stage each lobby simultaneously offers a contract to a different party, then in the second stage parties simultaneously and without knowing the contract offered to the other party decide whether to accept or to reject the contract.
@@
 \item We approach the lobbying process as one where cash-for-favour exchanges occur as a means to obtain access to legislators.
-The model takes into account the \textbf{degree of uncertainty} on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies.
+The model takes into account the degree of uncertainty on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies.
 Instead, we adopt a simultaneous lobbying structure to capture how lobbying proceeds behind closed doors.
@@
 The bias of the legislator is not high enough to risk losing the legislator’s support.
-\item We explore \textbf{uncertainty} by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al.
+\item We explore uncertainty by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al.
 (2006).
@@
 This interpretation requires the vote-categories to be (at least prima face) related to dimensions spanning the conceptual space (Benoit \& Laver, 2012).
-\item To facilitate computation, the authors introduce auxiliary random variables.
 \item Estimation of the model parameters is performed using a Markov chain Monte Carlo (MCMC) algorithm (Robert \& Casella, 2005). 
-\item We illustrate the model through an analysis of preferences in different policy domains using recorded votes from the 97th to 114th U.S.
-House of Representatives (1981 - 2016).
-Motions brought to a vote in the U.S.
-Congress differ thematically by substantive issue (e.g., the economy, environment, criminal justice, etc.).
-We use the Policy Agendas Project main topic coding to categorize roll call votes by issue area (Adler \& Wilkerson, 2017; Policy Agendas Project, 2017).
-This taxonomy, which consists of 20 mutually exclusive major topics (e.g., Macroeconomics, Health, Environment, etc.), has been used to study legislative agendas (Baumgartner \& Jones, 1993) and attention (Jones \& Baumgartner, 2005), among other matters.
-\item We focus on the PAP categorization for two reasons.
-First, the application to issue areas illustrates the novel technical contributions of the model, namely (1) comparable revealed preferences across issues and (2) estimates of legislator-specific dimensionality.
-Second, as argued in Section 3, applying the model to votes grouped by issue area is relevant to the literature on dimensionality (Aldrich et al., 2014; Roberts et al., 2016; Talbert \& Potoski, 2002) by providing issue-specific revealed preference and an estimate of individual consistency – the posterior probably that a member has the same revealed preference in each issue area.
 \item One of the key contributions of our approach is its ability to provide micro-level information about the behavior of specific legislators. 
-\item Our model not only provides information about the identity of movers, but also about the nature of the issues in which they are movers, and the direction of preference changes.
-Similar to the procedure we used to define issue-specific ASFs, start by defining a member’s basic ideal point as their ideal point in their base cluster, and say a member has deviant preferences – preferences different than their basic ideal point – on issues not in their base cluster.
-\item Figure 7 compares member’s basic ideal point against the ideal points associated with four PAP issues for legislators in the 111th House (Banking and Finance, Civil Rights, Government Operations and Macroeconomics).
-More specifically, these ternary
-plots show the probability that a member’s ideal point in a specific issue is either left of, right of, or the same as their basic ideal point.
-\item We compare our illustration to Gerrish and Blei (2012b).
-While a direct comparison is not possible (as there voters have a main preference and issue-specific deviations), some of the insights provided by both models are similar.
-Gerrish and Blei (2012b) find votes on appropriations, finance, energy and public lands to have the most movement (issues for which issue-specific preferences deviate the most from members’ base preferences, roughly akin to our deviant issues).
-Likewise they find issues with the lease amount of movement to be defence and military, education and foreign policy.
-Looking at the 111th House in particular, they find members preferences on Civil Rights to exhibit very little deviance from their base preference, which is somewhat different from our findings.
-We both, however, do find a considerable amount of movement/ deviance in the domain of Government Operations.
-\item The author claimed that their model is less noicy than previous mocels in the literature, Figure 8.
-This is because their joint model borrows information across voting domains to estimate the ideal points, leading to lower \textbf{uncertainty}.
-\item A key issue to appreciate here (in Figure 8) is that the uncertainty associated with the estimates of ranks varies drastically.
-Generally speaking, the uncertainty associated with the rank of legislators that are close to the median voter of their own party tends to be much larger than the uncertainty associated with the ranks of centrist or radical legislators (Figure 4).
-Similarly, the uncertainty in the estimates of the ranks can vary substantially between parties (in the case of the 111th, the uncertainty associated with the
-ranks of Democrats is much larger than that of Republicans). As a consequence, changes in ranks for centrist, partisans and Republicans are easier to identify.
 \item (Conclusion of the paper) We developed a novel Bayesian model extending classical ideal point estimation methods to enable the joint estimation of voters’ preferences across different domains of voting.
@@
 Both the P-R and CJR techniques, however, rely on an ungrounded assumption of (mutual) conditional independence of a legislator’s votes given the ideal points and roll-call parameters.
-Although for PCA one may try to find complex standard-error formulas that steer clear of that assumption, it appears that, whether for P-R, CJR, or PCA, any \textbf{effort to assess uncertainty is fraught with impediments}.
+Although for PCA one may try to find complex standard-error formulas that steer clear of that assumption, it appears that, whether for P-R, CJR, or PCA, any effort to assess uncertainty is fraught with impediments.
 \item Unlike P-R and CJR, PCA does not use a utility function in deriving its model. However, in its theory it is still based on a spatial voting model, just as P-R and CJR are. 
 \item (conclusion) for two or more dimensions, whose study may be fruitful for varied situations (e.g., for certain locales and time periods or certain subsets of votes or legislators), the relative benefits of PCA are especially striking and should suffice to make PCA a preeminent contender.
-
-\end{itemize}
-
-\newpage
-
-\item "The geometry of multidimensional quadratic utility in models of parliamentary roll call voting" KT Poole - Political Analysis, 2001
-\begin{itemize}
-\item The purpose of this paper is to show how the geometry of the quadratic utility function in the standard spatial model of choice can be exploited to estimate a model of parliamentary roll call voting.
-\item In a standard spatial model of parliamentary roll call voting, the legislator votes for the policy outcome corresponding to Yea if her utility for Yea is greater than her utility for Nay.
-The voting decision of the legislator is modeled as a function of the difference between these two utilities.
-The difference between two quadratic utilities has a simple geometric interpretation that can be exploited to estimate legislator ideal points and roll call parameters in a standard framework where the stochastic portion of the utility function is normally distributed.
-\item To reiterate, if voting is perfect, that is, sincere and without error, then in one dimension the legislator ideal points and the roll call midpoints are identified only up to a joint rank ordering.
-In more than one dimension, legislators are identified up to regions in the space (polytopes) and roll calls are identified up to cone-shaped regions containing the normal vectors and line segments on the normal vectors for the midpoints.
-These limits on identifica tion arise because the data are simply Yea and Nay.
-If legislators could report "thermometer scores" for the alternatives, then the perfect case would have an exact solution.
-\item With quadratic utility, only the location of the cutting hyperplane and the signed distance between the Yea and the Nay alternatives can be estimated.
-In this framework, there is an infinite number of pairs of Yea and Nay points that produce the same hyperplane and signed distance.
-\item In contrast, an advantage to the normal distribution deterministic utility function used in NOMINATE is that it introduces enough nonlinearities in the utility differences to identify actual positions of the Yea and Nay alternatives.
-These points have to be used with some caution (Poole and Rosenthal 1997, Appendix A) but it is important to note that the use of the quadratic utility function precludes the estimation of specific Yea and Nay points.
-\item Turning to the stochastic portion of the utility function stated in Eq.
-(3), three probability distributions have been used to model the error: the normal (Ladha 1991; Londregan 2000), uniform (Heckman and Snyder 1997), and logit (Poole and Rosenthal 1997).
-The normal is clearly the best from both a theoretical and a behavioral standpoint.
-\item From a statistical standpoint, given the difference between the two random errors, the standard assumptions are that they are a random sample (independent and identically distributed random variables) from a known distribution.
-Hence, it is therefore easy to write down the probability distribution of the difference.
-\item  From a behavioral standpoint, it seems sensible to assume that the distributions of the diffrence of the errors are symmetric and unimodal and that they are uncorrelated.
-The normal distribution is the only one of the three distributions to satisfy all these criteria.
-\item A further difficulty with the approaches taken both by Heckman and Snyder and by Poole and Rosenthal is that they assume that the error variance is homoskedastic.
-A more realistic assumption is that the error variance varies across the roll call votes and across the legislators.
-For the roll calls, it is impossible to distinguish between the underlying unknown error variance and the distance between the Yea and the Nay alternatives (Ladha 1991; Londregan 2000).
-The intuition behind this is straightforward.
-As the distance between the Yea and the Nay alternatives increases, the easier it is for legislators to distinguish between the two policy outcomes and the less likely it is that they make an error.
-Conversely, if the Yea and Nay alternatives are very close together, then the utility difference is small and it is more likely that voting errors occur.
-Increasing/decreasing the distance is equivalent to decreasing/increasing the variance of the underlying error
-\item The approach developed in Section 5 allows the error to be heteroskedastic.
-The optimal classification algorithm developed by Poole (2000) can be used to obtain excellent estimates for the legislator points, the jc, 's, the roll call normal vectors, the nj's, and the cutpoints, the m/s.
-\item The multidimensional quadratic utility model (QN) can be efficiently estimated in four steps.
-Within each step the approach taken is to estimate one parameter at a time with all the remaining parameters being held fixed.
-That is, the maximum of the likelihood function is found for the parameter being estimated conditioned on all the remaining parameters being held fixed.
-The algorithm always moves uphill in a city block-like fashion.
-At convergence, every parameter is at a maximum conditioned on all the remaining parameters being held fixed.
-Convergence to the true global maximum cannot be guaranteed but the conditional global maximum that the algorithm reaches is almost certainly close to the overall global maximum.
-Although this is not an EM algorithm, it is similar in spirit because the log likelihood always increases from one step to the next.
-\item Section 6 compares the Monte Carlo test with other scaling procedures. 
-\item Given the computational difficulties in more than one dimension, an attractive alternative to obtain standard errors is a bootstrap analysis. 
-\item Because obtaining good-quality standard errors for the parame ters of spatial models of parliamentary voting is very difficult, embedding the geometry in the innovative MCMC work of Jackman (2000) would produce an alternative method of assessing uncertainty in the multidimensional spatial model.
-\item The purpose of this paper was to show a method of estimating a multidimensional spatial voting model with quadratic utility and normally distributed errors.
-The geometry of the multidimensional quadratic utility function can be exploited to estimate legislator ideal points and roll call cutting planes in a standard framework where the stochastic portion of the utility function is normally distributed.
-The QN scaling procedure is quite stable and does a good job in recovering the true legislator configuration in Monte Carlo tests.
-\item The QN scaling procedure produces legislator configurations that are very similar to those produced by other scaling algorithms.
-A unique feature of QN is that it allows the variance of the error to vary across legislators.
-Although the legislator error variances are related to the level of correct classification, more than just correct classification is at work.
-
 \end{itemize}

### 2020-07-02 Literature_review.tex

--- 2020-06-30 Literature_review.tex
@@
 \maketitle
+
+\section{Papers related to Ideal Point Models}
 
@@
 The survey allows us to make cross-state, cross-chamber, and over-time comparisons.
+\item For each state, we estimate one- and two-dimensional spatial models using the Bayesian item response model.We beginwith an examination of the predictive power of the spatial model for explaining patterns of roll call voting within each state
 \item In particular, our spatial mapping not only adds a much needed cross-sectional element to empirical work on legislative institutions, but also will allow scholars to exploit institutional variation in ways not previously possible.
@@
 \item The authors test the EM model versus different known model of MCMC and present their results along with an empirical application. 
-\end{itemize}
-
-\newpage
-
-\item “Lobbying, Campaign Contributions and Political Competition” J Rivas - 2017
-
-\item (Question: Is there anything about uncertainty in this paper?)
-\item Answer: There is, the second and third bullet point has an overview of the way the paper treats uncertainty.
-
-\begin{itemize}
-\item The purpose of this paper is to study how lobbying affects elections where candidates that are running for office can benefit from the funds offered by the lobbies in an exchange for adopting a political position favorable to these lobbies but different from that of the median voter.
-\item we show that uncertainty about the voter’s behavior will increase polarization only for the party that gets offered the contract from the higher valuation lobby while it will decrease the polarization of the other party.
-This is because as uncertainty about the voter goes up adopting a more polarized position becomes less risky.
-The high valuation lobby takes advantage of this by asking its party for a more polarized position while the low valuation lobby instead allows its party to become less polarized to be in a better position against the now more polarized opposing party.
-\item we obtain that uncertainty about the voter also increases the relative spending of the party associated with the high valuation lobby.
-This is because, as discussed in the previous paragraph, increasing uncertainty increases the polarization of the party associated with the high valuation lobby, which implies that now this lobby has to compensate its party by offering more funds proportional to the funds the other lobby offers.
-\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
-\item The model described above (previous paragraph in the paper) leads to a two stage four player Bayesian game where in the first stage each lobby simultaneously offers a contract to a different party, then in the second stage parties simultaneously and without knowing the contract offered to the other party decide whether to accept or to reject the contract.
-In a final stage which party wins the election is declared and its policy position implemented.
-We solve this game by finding its unique equilibrium and then we proceed to study how the different parameters in the model affect parties’ polarization, campaign spending, and voter’s welfare.
-\item In our results about polarization we find, among others, that the lobby that has a higher stake in the election (the high valuation lobby henceforth) forces its party to adopt a more polarized position than the other party.
-Although a more polarized position decreases voter support, this can be partly compensated by a higher campaign spending, which the high valuation lobby is willing to fund.
-\item In terms of campaign spending, we find that the higher valuation lobby will contribute more to campaign spending.
-Furthermore, we also find that the salience of the election decreases total campaign spending but increases the relative campaign spending of the party associated with the high valuation lobby (relative to the other party’s campaign spending).
-\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
-\item This is a Bayesian game model, do not use data, only the Bayesian Equilibrium solution concept to characterize the model.
-
-\end{itemize}
-
-\newpage
-
-\item “Incumbent Competition, Decision-making, and Policy Choice” AM Go - 2019
-
-\begin{itemize}
-\item We approach the lobbying process as one where cash-for-favour exchanges occur as a means to obtain access to legislators.
-The model takes into account the \textbf{degree of uncertainty} on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies.
-Instead, we adopt a simultaneous lobbying structure to capture how lobbying proceeds behind closed doors.
-\item In this paper, we find that the degree of uncertainty of legislator preferences, given by the length of the bias intervals, directly affects the bidding strategy of lobbyists.
-At low levels of uncertainty, lobbyists bid aggressively.
-The bias of the legislator is not high enough to risk losing the legislator’s support.
-\item We explore \textbf{uncertainty} by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al.
-(2006).
-However, uncertainty is rarely explored on its own.
-We redirect the focus of the paper to lobbyist interactions over one non-strategic legislator.
-We remove the dimension of budget allocation and instead assume that the lobbyists are willing to pay at most the value of the legislator support.
-The results show that uncertainty on its own can provide some good insights on how lobbying unfolds.
-\item We also include a measure of the legislator’s level of integrity.
-As with Che and Gale (1998), the politician does not hold an open sale for his support given restrictions on vote buying.
-We can think about this from the perspective of a reputation conscious politician.
-A reputation conscious politician may not want to be associated with more than one lobbying group for an issue, and would like to be viewed as consistent and honest by her constituents.
-The more controversial an issue is, the more likely it is for the politician’s threshold to be higher.
-
 \end{itemize}
@@
 
+\newpage
+
+\section{Papers not related to Ideal Point Models}
+
+\item “Lobbying, Campaign Contributions and Political Competition” J Rivas - 2017
+
+\begin{itemize}
+\item The purpose of this paper is to study how lobbying affects elections where candidates that are running for office can benefit from the funds offered by the lobbies in an exchange for adopting a political position favorable to these lobbies but different from that of the median voter.
+\item we show that uncertainty about the voter’s behavior will increase polarization only for the party that gets offered the contract from the higher valuation lobby while it will decrease the polarization of the other party.
+This is because as uncertainty about the voter goes up adopting a more polarized position becomes less risky.
+The high valuation lobby takes advantage of this by asking its party for a more polarized position while the low valuation lobby instead allows its party to become less polarized to be in a better position against the now more polarized opposing party.
+\item we obtain that uncertainty about the voter also increases the relative spending of the party associated with the high valuation lobby.
+This is because, as discussed in the previous paragraph, increasing uncertainty increases the polarization of the party associated with the high valuation lobby, which implies that now this lobby has to compensate its party by offering more funds proportional to the funds the other lobby offers.
+\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
+\item The model described above (previous paragraph in the paper) leads to a two stage four player Bayesian game where in the first stage each lobby simultaneously offers a contract to a different party, then in the second stage parties simultaneously and without knowing the contract offered to the other party decide whether to accept or to reject the contract.
+In a final stage which party wins the election is declared and its policy position implemented.
+We solve this game by finding its unique equilibrium and then we proceed to study how the different parameters in the model affect parties’ polarization, campaign spending, and voter’s welfare.
+\item In our results about polarization we find, among others, that the lobby that has a higher stake in the election (the high valuation lobby henceforth) forces its party to adopt a more polarized position than the other party.
+Although a more polarized position decreases voter support, this can be partly compensated by a higher campaign spending, which the high valuation lobby is willing to fund.
+\item In terms of campaign spending, we find that the higher valuation lobby will contribute more to campaign spending.
+Furthermore, we also find that the salience of the election decreases total campaign spending but increases the relative campaign spending of the party associated with the high valuation lobby (relative to the other party’s campaign spending).
+\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
+\item This is a Bayesian game model, do not use data, only the Bayesian Equilibrium solution concept to characterize the model.
+
+\end{itemize}
+
+\newpage
+
+\item “Incumbent Competition, Decision-making, and Policy Choice” AM Go - 2019
+
+\begin{itemize}
+\item We approach the lobbying process as one where cash-for-favour exchanges occur as a means to obtain access to legislators.
+The model takes into account the \textbf{degree of uncertainty} on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies.
+Instead, we adopt a simultaneous lobbying structure to capture how lobbying proceeds behind closed doors.
+\item In this paper, we find that the degree of uncertainty of legislator preferences, given by the length of the bias intervals, directly affects the bidding strategy of lobbyists.
+At low levels of uncertainty, lobbyists bid aggressively.
+The bias of the legislator is not high enough to risk losing the legislator’s support.
+\item We explore \textbf{uncertainty} by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al.
+(2006).
+However, uncertainty is rarely explored on its own.
+We redirect the focus of the paper to lobbyist interactions over one non-strategic legislator.
+We remove the dimension of budget allocation and instead assume that the lobbyists are willing to pay at most the value of the legislator support.
+The results show that uncertainty on its own can provide some good insights on how lobbying unfolds.
+\item We also include a measure of the legislator’s level of integrity.
+As with Che and Gale (1998), the politician does not hold an open sale for his support given restrictions on vote buying.
+We can think about this from the perspective of a reputation conscious politician.
+A reputation conscious politician may not want to be associated with more than one lobbying group for an issue, and would like to be viewed as consistent and honest by her constituents.
+The more controversial an issue is, the more likely it is for the politician’s threshold to be higher.
+
+\end{itemize}
+
 \end{enumerate}

### 2020-08-23 Summary_Summer_2020_JV.tex
Summary of the Summer 2020 from Jorge Valdebenito

\documentclass[a4paper,12pt]{article}

\begin{document}
\title{\vspace{-1.5 cm}Summary of the work during Summer 2020}
\author{Jorge Valdebenito}
\maketitle

This document presents the summary for the summer of 2020 work on the political uncertainty project. 
\begin{enumerate}
\item Literature review:
I updated the literature of the 2016 paper “Lobbying and Legislative Uncertainty” by Buzard and Saiegh (2016). This review contained the latest literature on ideal point models estimators and recent work on political uncertainty models using roll call data. An important filter for ideal point models was to focus on research that employs a multidimensional approach. Most of the papers that take a unidimensional approach were discarded, unless they specifically focus on uncertainty or efficiency of the unidimensional model.
The Literature review was based on:

\begin{itemize}
\item Bafumi, Gelman, Park, Kaplan (2005) 
\item Clinton, Jackman, Rivers (2004)
\item Crespin and Rohde (2010)
\end{itemize}
The document it’s called “Literature review” and it’s on the Github repository.

\item The code:
There are 2 codes mixed in the G drive and in the Github repository. The first code is from the early stages of the project and the developer is Yusuf, his work is very well detailed and documented in the “order of the files” word document. This word document explains the steps, data sets and order of how the program should be run. We discovered a problem with the code when we were running these models. This code uses the command “destring” to merge the data sets, the problem was that it is ignoring the suffix on each law, therefore if 2 laws have the same number, but different suffix, the code will consider them as the same. 
For example, let’s take the laws H 2 and HR 2. These are different laws/actions, but the “destring” command removes the suffix and both laws are now called 2. This is the problem. 
Another problem with this code is that, some of the programs are calling datasets and other pieces of code that were on Yusuf’s computer, not on the G drive. It is important to consider also, that this work generates several output files that are called by different programs, therefore there are difficult to track and are located in different folders.

The second code is an update of Yusuf’s work and the developer is Yimin. This code is documented in the “Replication” file located in the Github repository. This code consists in running only 3 different pieces of code. We encountered a problem with the third of these files called \texttt{“RStan\_model.R”}. This program presents some errors when we are running the rstan command in R.  This code avoids using the “destring” command and it should perform faster than Yusuf’s code.

At the time of writing this document, I am still working of running the rstan model, troubleshooting the errors.

The other 2 codes \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} runs perfectly and their output is located in the Combined files folder in the G drive.

One detail that brings confusion is that the codes of both programs (Yusuf’s and Yimin’s) are all located in the same folders. Therefore, future work will be to put them in different folders, which will entail changing the output locations in all the individual R and Stata programs.

\item Data
In Yusuf’s code, he is using the 3 different data sets, 2 from Maplight and one from Poole’s (Voteview.com). Bill Position Maplight, can be downloaded from their website using a key (need to request one for free) and Votes Maplight was emailed to professor Buzard. Poole’s data set can be downloaded from Voteview.com.
Yimin’s code only uses the two Maplight data sets, previously mentioned.

I requested a key from Maplight to update the dataset, but, as of the writing of this summary, haven’t received a link to download the dataset.

\end{enumerate}

\end{document}

### 2020-08-24 Summary_Summer_2020_JV.tex
Changed the word code to program where it was neccesary

@@
 \item The code:
-There are 2 codes mixed in the G drive and in the Github repository.
-The first code is from the early stages of the project and the developer is Yusuf, his work is very well detailed and documented in the “order of the files” word document.
+There are 2 programs mixed in the G drive and in the Github repository.
+The first program is from the early stages of the project and the developer is Yusuf, his work is very well detailed and documented in the “order of the files” word document.
 This word document explains the steps, data sets and order of how the program should be run.
 We discovered a problem with the code when we were running these models.
-This code uses the command “destring” to merge the data sets, the problem was that it is ignoring the suffix on each law, therefore if 2 laws have the same number, but different suffix, the code will consider them as the same.
-For example, let’s take the laws H 2 and HR 2. These are different laws/actions, but the “destring” command removes the suffix and both laws are now called 2. This is the problem. 
-Another problem with this code is that, some of the programs are calling datasets and other pieces of code that were on Yusuf’s computer, not on the G drive.
-It is important to consider also, that this work generates several output files that are called by different programs, therefore there are difficult to track and are located in different folders.
+This program uses the command “destring” to merge the data sets, the problem was that it is ignoring the suffix on each law, therefore if 2 laws have the same number, but different suffix, the code will consider them as the same.
+For example, let’s take the laws H 2 and HR 2. These are different laws/actions, but the “destring” command removes the suffix and both laws are now called 2. Which is not correct. 
+Another issue with this program is that it calls datasets and other pieces of code that were on Yusuf’s computer, not on the G drive.
+It is important to consider also, that this work generates several output files that are called by different pieces of code later on, making them difficult to track and are located in different folders.
 
-The second code is an update of Yusuf’s work and the developer is Yimin.
-This code is documented in the “Replication” file located in the Github repository.
-This code consists in running only 3 different pieces of code.
+The second program is an update of Yusuf’s work and the developer is Yimin.
+This program is documented in the “Replication” file located in the Github repository.
+This program consists of running 3 different pieces of code.
 We encountered a problem with the third of these files called \texttt{“RStan\_model.R”}.
-This program presents some errors when we are running the rstan command in R.
+This piece of code presents some errors when running the rstan command in R.
 This code avoids using the “destring” command and it should perform faster than Yusuf’s code.
+Its also makes the mergin more efficient and less by doing a better job at cleaning the data set.
 
@@
 
-The other 2 codes \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} runs perfectly and their output is located in the Combined files folder in the G drive.
+The other 2 codes \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} run perfectly and their output is located in the Combined files folder in the G drive.
 
-One detail that brings confusion is that the codes of both programs (Yusuf’s and Yimin’s) are all located in the same folders.
-Therefore, future work will be to put them in different folders, which will entail changing the output locations in all the individual R and Stata programs.
+One detail that brings confusion is that Yusuf's and Yimin's work are located in the same folders.
+Therefore, future work will be to separating them and organize this 2 programs, which will entail changing the output locations in all the individual R and Stata programs.
 
 \item Data
-In Yusuf’s code, he is using the 3 different data sets, 2 from Maplight and one from Poole’s (Voteview.com).
+In Yusuf’s program, he is using 3 different data sets, 2 from Maplight and one from Poole (Voteview.com).
 Bill Position Maplight, can be downloaded from their website using a key (need to request one for free) and Votes Maplight was emailed to professor Buzard.
 Poole’s data set can be downloaded from Voteview.com.
-Yimin’s code only uses the two Maplight data sets, previously mentioned.
+Yimin’s program only uses the two Maplight data sets, previously mentioned.
 

### 2020-08-27 Summary_Summer_2020_JV.tex

@@
 \item The code:
-There are 2 programs mixed in the G drive and in the Github repository.
-The first program is from the early stages of the project and the developer is Yusuf, his work is very well detailed and documented in the “order of the files” word document.
+There are 2 approaches mixed in the G drive and in the Github repository.
+The first one is from the early stages of the project and the developer is Yusuf, his work is very well detailed and documented in the “order of the files” word document.
 This word document explains the steps, data sets and order of how the program should be run.
 We discovered a problem with the code when we were running these models.
-This program uses the command “destring” to merge the data sets, the problem was that it is ignoring the suffix on each law, therefore if 2 laws have the same number, but different suffix, the code will consider them as the same.
+This approach uses the command “destring” to merge the data sets, the problem was that it is ignoring the suffix on each law, therefore if 2 laws have the same number, but different suffix, the code will consider them as the same.
 For example, let’s take the laws H 2 and HR 2. These are different laws/actions, but the “destring” command removes the suffix and both laws are now called 2. Which is not correct. 
-Another issue with this program is that it calls datasets and other pieces of code that were on Yusuf’s computer, not on the G drive.
+Another issue with this approach is that it calls datasets and other pieces of code that were on Yusuf’s computer, not on the G drive.
 It is important to consider also, that this work generates several output files that are called by different pieces of code later on, making them difficult to track and are located in different folders.
 
-The second program is an update of Yusuf’s work and the developer is Yimin.
-This program is documented in the “Replication” file located in the Github repository.
-This program consists of running 3 different pieces of code.
+The second approach is an update of Yusuf’s work and the developer is Yimin.
+His program is documented in the “Replication” file located in the Github repository.
+This approach consists of running 3 different pieces of code.
 We encountered a problem with the third of these files called \texttt{“RStan\_model.R”}.
@@
 One detail that brings confusion is that Yusuf's and Yimin's work are located in the same folders. 
-Therefore, future work will be to separating them and organize this 2 programs, which will entail changing the output locations in all the individual R and Stata programs.
+Yusuf's work is located inside folders build and analysis.
+It uses the subfolders input, output and code to call and export different files and datasets (following "order of the files" document must be used to work in these approach)
+Yimin's work is located in build/code ( \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} ) and analysis/code (“RStan\_model.R").
+His work is describe in "Replication", located in the political-uncertainty Github repository.
+Therefore, future work will be to separating them and organizing the files from these two different approaches, which will entail changing the output locations in all the individual R and Stata programs.
 
 \item Data
-In Yusuf’s program, he is using 3 different data sets, 2 from Maplight and one from Poole (Voteview.com).
+Yusuf's approach uses 3 different data sets, 2 from Maplight and one from Poole (Voteview.com).
 Bill Position Maplight, can be downloaded from their website using a key (need to request one for free) and Votes Maplight was emailed to professor Buzard.
@@
 I requested a key from Maplight to update the dataset, but, as of the writing of this summary, haven’t received a link to download the dataset.
+The API key is on the "Road Map" file on the github repository.
 

### 2020-10-10 Summary_Summer_2020_JV.tex
make small corrections / add questions to Jorge's summary of Summer 2020 work

@@
 \documentclass[a4paper,12pt]{article}
+\usepackage[htt]{hyphenat}
+\usepackage{url}
 
@@
 
-This document presents the summary for the summer of 2020 work on the political uncertainty project. 
+\noindent This document presents the summary for the summer of 2020 work on the political uncertainty project. 
 \begin{enumerate}
@@
 \end{itemize}
-The document it’s called “Literature review” and it’s on the Github repository.
+The document is called “Literature review” and it’s on the Github repository.
 
@@
 This approach consists of running 3 different pieces of code.
-We encountered a problem with the third of these files called \texttt{“RStan\_model.R”}.
+We encountered a problem with the third of these files called \texttt{RStan\_model.R}.
 This piece of code presents some errors when running the rstan command in R.
 This code avoids using the “destring” command and it should perform faster than Yusuf’s code.
-Its also makes the mergin more efficient and less by doing a better job at cleaning the data set.
+Its also makes the merging more efficient by doing a better job at cleaning the data set.
 
-At the time of writing this document, I am still working of running the rstan model, troubleshooting the errors.
+At the time of writing this document, I am still working on troubleshooting the errors in the rstan model. 
+\begin{itemize}
+	\item [KB 10/10/2020]: can you add some details about this now that your work is complete?
+You'll need to pull my updates to this document down to your repository to do this and then make a new pull request on the .tex and .pdf files for this summary
+\end{itemize}
 
-The other 2 codes \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} run perfectly and their output is located in the Combined files folder in the G drive.
+The other 2 programs \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} run perfectly and their output is located in the Combined files folder in the G drive.
 
 One detail that brings confusion is that Yusuf's and Yimin's work are located in the same folders. 
-Yusuf's work is located inside folders build and analysis.
-It uses the subfolders input, output and code to call and export different files and datasets (following "order of the files" document must be used to work in these approach)
-Yimin's work is located in build/code ( \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} ) and analysis/code (“RStan\_model.R").
-His work is describe in "Replication", located in the political-uncertainty Github repository.
-Therefore, future work will be to separating them and organizing the files from these two different approaches, which will entail changing the output locations in all the individual R and Stata programs.
+Yusuf's work is located inside folders \texttt{build} and \texttt{analysis}.
+It uses the subfolders \texttt{input}, \texttt{output} and \texttt{code} to call and export different files and datasets (following ``order of the files'' document must be used to work in these approach).
+\begin{itemize}
+	\item [KB 10/10/2020]: I don't know what ``following ``order of the files'' document must be used to work in these approach'' means
+\end{itemize}
+Yimin's work is located in build/code ( \texttt{Generate\_vote\_data\_for\_R.do} and \texttt{Generate\_group\_dummy\_by\_action.do} ) and analysis/code \texttt{RStan\_model.R}.
+His work is describe in ``Replication'', located in the political-uncertainty Github repository.
+
+Therefore, future work will be to separate them and organize the files from these two different approaches, which will entail changing the output locations in all the individual R and Stata programs.
 
 \item Data
+
 Yusuf's approach uses 3 different data sets, 2 from Maplight and one from Poole (Voteview.com).
 Bill Position Maplight, can be downloaded from their website using a key (need to request one for free) and Votes Maplight was emailed to professor Buzard.
+\begin{itemize}
+	\item [KB 10/10/2020] Is ``Bill Position Maplight'' \url{build\input\maplight_bill_positions.dta}, or a raw version of this file that is not in the Github folder?
+	\item [KB 10/10/2020] Similarly, is ``Votes Maplight'' \url{build\input\maplight_votes.dta}, or a raw version of this file that is not in the Github folder?
+\end{itemize}
 Poole’s data set can be downloaded from Voteview.com.
-Yimin’s program only uses the two Maplight data sets, previously mentioned.
+Yimin’s programs only use the two previously-mentioned Maplight data sets.
 
 I requested a key from Maplight to update the dataset, but, as of the writing of this summary, haven’t received a link to download the dataset.
-The API key is on the "Road Map" file on the github repository.
+The API key is in \texttt{Road Map.txt} in the main folder of the Github repository.
+The \texttt{Road Map.txt} document contains more detailed notes about my work over the summer.
+\begin{itemize}
+	\item [KB 10/10/2020] Is this the right way to characterize \texttt{Road Map.txt}?
+\end{itemize}
 
